### 2017-04-12 paper/ms.tex
Add paper sketch

\documentclass[letterpaper]{aastex6}

% to-do list
% ----------
% - add items here
% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.

\include{gitstuff}
\include{aastexmods}

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb}
\usepackage{tikz}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\normal}{{\mathcal{N}}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\!\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\mat}[1]{\mathbf{#1}}
\renewcommand{\vec}[1]{\bs{#1}}
\newcommand{\kms}{\ensuremath{\rm km~s^{-1}}}
\newcommand{\msun}{{\rm M}_\odot}
\newcommand{\data}{\mathrm{data}}
\newcommand{\snr}{[S/N]_\varpi}
\newcommand{\eye}{\mathbb{I}}
\newcommand{\absdvtan}{\ensuremath{|\Delta\vec v_\mathrm{t}|}}
\newcommand{\estimates}{\ensuremath{\{\hat{\varpi_i},\hat{\mu_{\alpha,i}},\hat{\mu_{\delta,i}},\hat{v_{r,i}}\}}}

\newcommand{\todo}[1]{{\color{blue}TODO:#1}}

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me

\title{A co-moving pair of bright stars with very different metallicities and abundances}

\author{Semyeong Oh\altaffilmark{\pu,\lead} \etal}

% Affiliations
\newcommand{\pu}{1}
\newcommand{\lead}{2}
\newcommand{\ccpp}{3}
\newcommand{\mpia}{4}
\newcommand{\cca}{5}

\altaffiltext{\pu}{Department of Astrophysical Sciences,
                   Princeton University, Princeton, NJ 08544, USA}
\altaffiltext{\lead}{To whom correspondence should be addressed:
                     \texttt{semyeong@astro.princeton.edu}}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
                     Department of Physics,
                     New York University, 4 Washington Place,
                     New York, NY 10003, USA}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                     K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cca}{Center for Computational Astrophysics, 162 5th Ave, New York, NY 10003, USA}

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright stars, HD 240429 and HD 240430,
  with their detailed abundance measured.
  The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
  are completely consistent with them co-moving in space.
  Yet, the metallicities and the abundances of XX elements between the stars
  separated by $\sim 0.6$~pc in space are very different,
  challenging the simple picture that these co-moving pairs are once wide binaries
  formed in a coeval star-forming event but now tidally stripping.
  We consider such and such scenarios of the formation of such pairs.
\end{abstract}

\section{Introduction} % (fold)
\label{sec:introduction}

% section introduction (end)

\section{Data}
\label{sec:data}

- initially discovered from ... with marginalized likelihood ratio of XX(>6)
- fortunately, brewer et al. 2016 studied these two stars as part of ... with high resolution spectroscopy.
  briefly what they measured
- indeed RVs are consistent
- surprisingly, the metallicities and abundances are significantly very different.

Figure: metallicity/abundance comparison plot

Table: present all data relevant to discussion

\section{Discussion}
\label{sec:discussion}

\end{document}

### 2017-04-13 paper/ms.tex
add items in discussion

@@
-\documentclass[letterpaper]{aastex6}
+\documentclass[manuscript]{aastex6}
 
@@
 \newcommand{\etal}{\textit{et al}.}
+\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
 
@@
 
-\title{A co-moving pair of bright stars with very different metallicities and abundances}
+\title{NEED A BETTER TITLE: A co-moving pair of bright stars \\
+  with very different metallicities and abundances}
 
-\author{Semyeong Oh\altaffilmark{\pu,\lead} \etal}
+\author{
+  Semyeong Oh\altaffilmark{\pu,\lead},
+  APW, JMB, KH, DWH, DNS
+}
 
@@
 \begin{abstract}
-  We report and discuss the discovery of a co-moving pair of bright stars, HD 240429 and HD 240430,
-  with their detailed abundance measured.
+  We report and discuss the discovery of a co-moving pair of bright stars,
+  HD 240429 and HD 240430, with their detailed abundance measured.
   The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
@@
 
-- initially discovered from ... with marginalized likelihood ratio of XX(>6)
-- fortunately, brewer et al. 2016 studied these two stars as part of ... with high resolution spectroscopy.
-  briefly what they measured
-- indeed RVs are consistent
-- surprisingly, the metallicities and abundances are significantly very different.
+In this section, we describe the data relevant to our discussion of the origin of the system.
+The co-moving pair was initially discovered in our recent search
+for co-moving pairs using the proper motions from Gaia DR1.
+We refer the readers to \citealt{2016arXiv161202440O} and briefly describe the method here.
+For a given pair, we performed a hypothesis test between the two hypotheses that
+the two stars share the same 3D velocity vector and that they have
+two independent 3D velocity vectors.
+In the catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
+the pair that we present here was assigned a group id of 1199,
+and the marginalized likelihood ratio (Bayes factor)
+between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
+well above a relatively conservative cut of 6 that we adopt.
+Additionally, we have checked that we do not find any possible additional co-moving companions
+to this pair even when we lower the selection threshold to less conservative but still reasonable values.
+The pair is in fact classified as a double star system independently
+in Washington Double Star Catalog (\cite{2001AJ....122.3466M}).
 
-Figure: metallicity/abundance comparison plot
+In a separate effort to study detailed chemical abundances of
+potential planet-hosting stars, \citet{2016ApJS..225...32B} studied these two stars
+with high resolution spectroscopy, and provided measurements of
+15 different elements (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y)
+as well as high precision radial velocities.
+We provide all measurements relevant to the present discussion in Table~\ref{tab:t2}.
 
-Table: present all data relevant to discussion
+% ----------------
+% Horizontal table
+% ----------------
+% \begin{table*}[htpb]
+%   \centering
+%   \caption{Astrometric and spectroscopic measurements}
+%   \label{tab:t1}
+%   \begin{tabular}{cccccccccc}
+% \hline\hline
+% Name & Sp Type & $T_\mathrm{eff}$ & $\log{g}$ & $v\sin{i}$ & $[\elem{Fe}/\elem{H}]$ & $v_r$ &
+% $\varpi$ & $\mu_\alpha^*$ & $\mu_\delta$ \\
+% % units
+% \hline
+% HD 240429 & G2 & 5878 & 4.43 & 1.1 & 0.01 & $-21.2$  & $9.35 \pm 0.24$ & $89.25 \pm 0.66$ & $-29.68 \pm 0.54$\\
+% HD 240430 & G0 & 5803 & 4.33 & 2.5 & 0.20 & $-21.2$  & $9.41 \pm 0.25$ & $89.41 \pm 0.69$ & $-30.12 \pm 0.52$\\
+% \hline\hline
+% \end{tabular}
+% \end{table*}
+
+\begin{table*}[htpb]
+  \centering
+  \caption{Astrometric and spectroscopic measurements}
+  \label{tab:t2}
+  \begin{tabular}{ccc}
+\hline\hline
+Name & HD 240429 & HD 240430 \\
+\hline
+Sp Type & G2 & G0 \\
+$T_\mathrm{eff}$ & 5878 & 5803 \\
+$\log{g}$ & 4.43 & 4.33 \\
+$v\sin{i}$ & 1.1 & 2.5 \\
+$[\elem{Fe}/\elem{H}]$ & 0.01 & 0.20 \\
+$v_r$ & $-21.2$ & $-21.2$ \\
+$\varpi$ & $9.35 \pm 0.24$ & $9.41 \pm 0.25$ \\
+$\mu_\alpha^*$ & $89.25 \pm 0.66$ & $89.41 \pm 0.69$ \\ 
+$\mu_\delta$  & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$\\
+\hline\hline
+\end{tabular}
+\end{table*}
+
+We first confirm that the two stars are indeed co-moving with very similar
+velocities using the radial velocities.
+\todo{APW: discuss kinematics, posterior of separation/dV}
+
+\todo{Figure: posterior distributions of separation and delta V}
+
+Given their proximity in space and kinematics,
+it is generally accepted to assume that the two stars were born coeval
+perhaps in a wide binary from the same birth cloud.
+Thus, we expect the two stars to have identical metallicities and abundance patterns,
+\todo{except for thoese elements like Li...}
+Surprisingly, one of the stars, HD 240430 is significantly more metal
+rich than the other by 0.2~dex ($\approx 60\%$; Figure~\ref{fig:abundances}).
+What is more puzzling is that the abundances of this star
+shows selective depletion in C, N, O, Na, and Mn.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.9\linewidth]{abundances.pdf}
+  \caption{Abundances of the co-moving pair, HD 240429 and HD 240430.}
+  \label{fig:abundances}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.9\linewidth]{relabun_tc.pdf}
+  \caption{Abundance of HD 240430 ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
+    relative to HD 240429 ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
+    as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
+  }
+  \label{fig:relabun_tc}
+\end{figure}
 
@@
 
+We discuss the possible origins of this pair.
+
+% chance pair
+Given that their metallicities and abundance patterns are significantly
+different, one may simply conclude that the two stars are not related (coeval)
+but they merely happen to be co-moving at such small separation ($\approx 0.6$~pc)
+by chance.
+The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
+at the stars' location, one may compute the probability that a star moving at
+the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
+...
+
+% binary-single and binary-binary exchange
+Another scenario that two unrelated stars may end up in a wide binary system
+is multi-body gravitational scattering.
+We consider the exchange probabilities in binary-single and binary-binary interactions.
+Given their low binding energy compared to incoming velocity of field stars,
+this is low.
+
+% planet-or-the-like engulfment
+Yet another possibility is that the more metal-rich of the two stars
+was recently? bombarded by something that selectively removed the depleted elements but not the others.
+
+Present the relative abundance figure here
+
+\bibliography{ref}
+
 \end{document}

### 2017-04-13 paper/ms.tex
add some missing items

@@
   We report and discuss the discovery of a co-moving pair of bright stars,
-  HD 240429 and HD 240430, with their detailed abundance measured.
+  HD 240429 and HD 240430, with their detailed abundances measured.
   The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
@@
 between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
-well above a relatively conservative cut of 6 that we adopt.
+well above a relatively conservative cut of 6 that we adopted.
 Additionally, we have checked that we do not find any possible additional co-moving companions
@@
 In a separate effort to study detailed chemical abundances of
-potential planet-hosting stars, \citet{2016ApJS..225...32B} studied these two stars
-with high resolution spectroscopy, and provided measurements of
-15 different elements (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y)
-as well as high precision radial velocities.
+potential planet-hosting stars, \citet{2016ApJS..225...32B}
+measured abundances of 15 different elements
+(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y)
+of these two stars as well as high precision radial velocities
+with high resolution spectroscopy.
 We provide all measurements relevant to the present discussion in Table~\ref{tab:t2}.
@@
 
+The abundance of HD 30 is peculiar on its own compared to other disk stars with
+similar $[\elem{Fe}/\elem{H}]$. \todo{discuss}
+
 \begin{figure}[htpb]
@@
 We discuss the possible origins of this pair.
+Let us first consider scenarios in which the two stars are not actually born together.
 
@@
 
-% planet-or-the-like engulfment
+The unlikeliness of the above possibilities naturally leads us to 
+consider the alternative.
+What can selectively enrich XX elements in one of the two stars that are born together?
+
+% inhomogeneity in star formation
+It may be that the two stars are born at the same time from the same cloud, but
+there is inhomogeneity. Highly doubtful based on
+- Brewer et al. binaries that seem identical.
+- other?
+
+% rocky planets (or the like) engulfment
 Yet another possibility is that the more metal-rich of the two stars

### 2017-04-13 paper/ms.tex
words on peculiarity of HD30

@@
 \usepackage{microtype}  % ALWAYS!
-\usepackage{amsmath,amssymb}
+\usepackage{amsmath,amssymb,natbib}
 \usepackage{tikz}
@@
 The abundance of HD 30 is peculiar on its own compared to other disk stars with
-similar $[\elem{Fe}/\elem{H}]$. \todo{discuss}
+similar $[\elem{Fe}/\elem{H}]$.
+For a star with $[\elem{Fe}/\elem{H}] \approx 0.2$, we generally expect
+$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
+(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of HD 30 ever more unlikely.
+We stress that none of the binary pairs examined in \citealt{2016ApJS..225...32B}
+show discrepancies in abundances between the stars at this level.
+In fact, no strong trend is found in pair for most elements
+except N and Y.
+For Y, the trend for this pair is opposite of the others in Teff.
+Specifically, no difference within pair is found for Mn.
 
@@
 
+None of the above scenarios is quite satisfactory as it offers no
+insight on the peculiarity in abundances of HD 30 (see \ref{sec:data}).
+
 The unlikeliness of the above possibilities naturally leads us to 

### 2017-04-13 paper/ms.tex
todo

@@
 (\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of HD 30 ever more unlikely.
-We stress that none of the binary pairs examined in \citealt{2016ApJS..225...32B}
+We stress that none of the \tood{how many} binary pairs examined in \citealt{2016ApJS..225...32B}
 show discrepancies in abundances between the stars at this level.
@@
 Specifically, no difference within pair is found for Mn.
+(see figure X in that paper; purple is this pair)
 

### 2017-04-13 paper/ms.tex
NL for insights on scattering

@@
   Semyeong Oh\altaffilmark{\pu,\lead},
-  APW, JMB, KH, DWH, DNS
+  APW, JMB, KH, NL, DWH, DNS
 }
@@
 (\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of HD 30 ever more unlikely.
-We stress that none of the \tood{how many} binary pairs examined in \citealt{2016ApJS..225...32B}
+We stress that none of the \todo{how many} binary pairs examined in \citealt{2016ApJS..225...32B}
 show discrepancies in abundances between the stars at this level.
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{relabun_tc.pdf}
+  \includegraphics[width=0.9\linewidth]{relabun_tc_XH.pdf}
   \caption{Abundance of HD 240430 ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
@@
 
+estimate: 10 earth mass
+
 Present the relative abundance figure here
+
+Change in stellar abundance due to ingestion of planets has been considered
+for similar bright star pairs HD XX/XX (Mack) and HD XX/XX(Mack).
+
+% Concluding remakrs
 

### 2017-04-15 paper/ms.tex
new item placeholder
note on scattering

@@
 to this pair even when we lower the selection threshold to less conservative but still reasonable values.
-The pair is in fact classified as a double star system independently
+The pair is in fact classified as a visual double star system independently
 in Washington Double Star Catalog (\cite{2001AJ....122.3466M}).
@@
 
+paragraph on lithium and ages
+
 \begin{figure}[htpb]
@@
 this is low.
+Two factors that make this even more unlikely are that both stars are very young given their large Li,
+and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
+not HD30 with anomalous abundance patterns.
 

### 2017-04-15 paper/ms.tex
took a stab at the abstract

@@
 % - add items here
+
 % style notes
@@
 \newcommand{\msun}{{\rm M}_\odot}
+\newcommand{\pc}{{\rm pc}}
 \newcommand{\data}{\mathrm{data}}
@@
 
-\title{NEED A BETTER TITLE: A co-moving pair of bright stars \\
-  with very different metallicities and abundances}
+\title{A pair of co-moving, Sun-like stars with different chemical abundances:\\
+       a possible signature of copious rocky accretion (needs work)}
 
@@
 \begin{abstract}
-  We report and discuss the discovery of a co-moving pair of bright stars,
-  HD 240429 and HD 240430, with their detailed abundances measured.
-  The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
-  are completely consistent with them co-moving in space.
-  Yet, the metallicities and the abundances of XX elements between the stars
-  separated by $\sim 0.6$~pc in space are very different,
-  challenging the simple picture that these co-moving pairs are once wide binaries
-  formed in a coeval star-forming event but now tidally stripping.
-  We consider such and such scenarios of the formation of such pairs.
+  We report and discuss the discovery of a co-moving pair of bright solar-type
+  stars, HD 240429 and HD 240430, with significant differences in their chemical
+  abundance patterns.
+  The two stars are co-spatial $|\Delta \bs{x}| < XX~\pc$ at a distance of
+  $r\approx 100~\pc$ with nearly identical three-dimensional velocity vectors
+  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
+  \tgas\ proper motions and high signal-to-noise radial-velocity measurements.
+  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
+  their lithium abundances, favoring the idea that these were born together and
+  are or were recently a bound, wide binary system.
+  However, the metallicities and chemical abundances of high
+  condensation-temperature elements of the two stars are very different,
+  challenging this simple picture.
+  We consider formation scenarios in which the pair either (1) formed together
+  with identical abundances but later accreted very different quantities of
+  protoplantary, rocky material, (2) were born together but with very different
+  metal abundances, or (3) interacted with a field star or binary and exchanged
+  a member.
+  We favor scenario (1), in which the star HD 240430 consumed $\approx$10's of
+  Earth masses of rocky material in small units (many rocky bodies rather than
+  a few giant planets).
+  Direct-imaging and precision radial-velocity follow-up to study the existence
+  or properties of planetary systems around these stars would help distinguish
+  these scenarios.
 \end{abstract}

### 2017-04-15 paper/ms.tex
added a todo
parens

@@
 % ----------
-% - add items here
+% - Add references and uncertainties to Table 1
 
@@
   abundance patterns.
-  The two stars are co-spatial $|\Delta \bs{x}| < XX~\pc$ at a distance of
+  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
   $r\approx 100~\pc$ with nearly identical three-dimensional velocity vectors

### 2017-04-16 paper/ms.tex
tweak

--- 2017-04-15 paper/ms.tex
@@
 % ----------
-% - add items here
+% - Add references and uncertainties to Table 1
+
 % style notes
@@
 \begin{abstract}
-  We report and discuss the discovery of a co-moving pair of bright stars,
-  HD 240429 and HD 240430, with their detailed abundances measured.
-  The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
-  are completely consistent with them co-moving in space.
-  Yet, the metallicities and the abundances of XX elements between the stars
-  separated by $\sim 0.6$~pc in space are very different,
-  challenging the simple picture that these co-moving pairs are once wide binaries
-  formed in a coeval star-forming event but now tidally stripping.
-  We consider such and such scenarios of the formation of such pairs.
+  We report and discuss the discovery of a co-moving pair of bright solar-type
+  stars, HD 240429 and HD 240430, with significant differences in their chemical
+  abundance patterns.
+  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
+  $r\approx 100~\pc$ with nearly identical three-dimensional velocities
+  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
+  \tgas\ proper motions and high resolution radial velocity measurements.
+  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
+  their lithium abundances, favoring the idea that they were born together and
+  are or were recently a bound, wide binary system.
+  However, the metallicities and chemical abundances of refractory
+  elements of the two stars are very different, challenging this simple picture.
+  In order to reconcile the seemingly contradictory observations,
+  we consider scenarios in which the pair is unrelated despite
+  its current spatial and kinematic configuration, and
+  those in which the pair formed together but may now have different chemistry.
+  In the latter, we consider the possibility that the more metal-rich of the two,
+  HD 240430, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
+  selectively enhancing the refractory elements.
+  Direct-imaging and precision radial velocity follow-up to study the existence
+  or properties of planetary systems around these stars would help distinguish
+  these scenarios.
 \end{abstract}

### 2017-04-16 paper/ms.tex
add text to data section and new figures

@@
   However, the metallicities and chemical abundances of refractory
-  elements of the two stars are very different, challenging this simple picture.
+  elements in the two stars are very different, challenging this simple picture.
   In order to reconcile the seemingly contradictory observations,
@@
 
-In this section, we describe the data relevant to our discussion of the origin of the system.
-The co-moving pair was initially discovered in our recent search
-for co-moving pairs using the proper motions from Gaia DR1.
-We refer the readers to \citealt{2016arXiv161202440O} and briefly describe the method here.
-For a given pair, we performed a hypothesis test between the two hypotheses that
-the two stars share the same 3D velocity vector and that they have
-two independent 3D velocity vectors.
-In the catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
-the pair that we present here was assigned a group id of 1199,
+Though previously recognized as a visual double star system
+(\citealt{2001AJ....122.3466M}), HD 240429 and HD 240430 were identified as a
+candidate co-moving star pair in our recent search for co-moving stars using the
+proper motions and parallaxes from the \tgas catalog, a component of \gaia\ \dr\
+(the astrometric measurements are listed in \tablename~\ref{tab:t2}).
+We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
+full explanation of the methodology behind this search and only briefly describe
+the method here.
+For a given pair, we compute a marginalized likelihood ratio between the
+hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
+(2) that they have independent 3D velocity vectors, both given only observations
+of two components of the velocities (proper motions).
+We then select a sample of high-confidence co-moving star pairs by making a
+conservative cut on this likelihood ratio.
+In the resulting catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
+the pair presented in this paper was assigned a group id of 1199,
 and the marginalized likelihood ratio (Bayes factor)
 between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
-well above a relatively conservative cut of 6 that we adopted.
-Additionally, we have checked that we do not find any possible additional co-moving companions
-to this pair even when we lower the selection threshold to less conservative but still reasonable values.
-The pair is in fact classified as a visual double star system independently
-in Washington Double Star Catalog (\cite{2001AJ....122.3466M}).
+well above the adopted cut value of 6.
+We have checked that we do not find any possible additional co-moving companions
+by lowering the likelihood ratio cut for the stars around this pair.
 
@@
 potential planet-hosting stars, \citet{2016ApJS..225...32B}
-measured abundances of 15 different elements
-(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y)
-of these two stars as well as high precision radial velocities
-with high resolution spectroscopy.
-We provide all measurements relevant to the present discussion in Table~\ref{tab:t2}.
+obtained high resolution spectroscopy for both HD 240429 and HD 240430.
+\todo{from where? mention briefly Keck HIRES}
+The resulting measurements from this effort include abundances measured for 15
+checmical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
+well as high precision radial velocities.
+Other stellar parameters derived from these spectra are included in
+\tablename~\ref{tab:t2}.
+
+Combining these precise radial velocities with the \gaia\ astrometry, we can
+compare differences between the inferred 6D phase-space properties for the
+two stars.
+We start by generating posterior samples over the Heliocentric distance, $r$,
+tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
+given the observed parallax, $\pi$, and proper motion components,
+$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
+By defining the vectors
+\begin{eqnarray}
+  \vec{y} &=&
+      \transp{\left(
+        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
+          \pi &
+          \mu_{\alpha^*} &
+          \mu_\delta &
+          v_r
+        \end{array}
+      \right)}\\
+  \hat{\vec{y}} &=&
+      \transp{\left(
+        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
+          r^{-1} &
+          r^{-1}\,v_\alpha &
+          r^{-1}\,v_\delta &
+          \hat{v}_r
+        \end{array}
+      \right)}
+\end{eqnarray}
+and by considering the covariance matrix $\mat{C}$ between the observed
+quantities (provided by \tgas\ and extended to include the uncorrelated radial
+velocity uncertainty), the likelihood can be written
+\begin{eqnarray}
+p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
+  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
+    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
+    \mat{C}^{-1} \,
+    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
+\end{eqnarray}
+We adopt a uniform space density prior for the distance and an isotropic
+Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
+\begin{eqnarray}
+p(r) &=&
+  \begin{cases}
+    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
+    0              & \text{otherwise}
+  \end{cases}\\
+p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
+  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
+\end{eqnarray}
+For each of the two stars, we use \project{emcee}
+(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
+v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
+first 512 steps as the burn-in period.
+For each sample, we convert the heliocentric phase-space coordinates into
+Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
+= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
+etc.}).
+\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
+Galactocentric phase-space coordinates for the two stars.
+In all components, the pair is consistent with being co-moving and close in
+separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
+but the median 3-space separation is $\approx$$0.6~\pc$.
+
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
+  \end{center}
+  \caption{%
+    Differences in posterior samples over Galactocentric phase-space coordinates
+    for the two stars HD 240429 and HD 240430.
+    \label{fig:dxdv}}
+\end{figure}
+
+\figurename~\ref{fig:orbit} shows an orbit computed from the median posterior
+sample over 6D phase-space coordinates for HD 240429 (black line), integrated
+in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
+explain}
+The Sun's orbit in this same Milky Way model is under-plotted for comparison
+(grey line); the orbits of the stars in this pair have large scale-heights
+relative to the Sun's orbit despite being young.
+
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{orbits.pdf}
+  \end{center}
+  \caption{%
+    Galactic orbits computed for HD 240429 (black) and the Sun (grey).
+    For HD 240429, the initial conditions are set to the median posterior
+    sample over the inferred 6D phase-space coordinates.
+    The orbits are computed by integrating backwards from the present-day
+    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
+    Leapfrog integration scheme implemented in \project{Gala}
+    (\citealt{Gala:2017}). \todo{APW: citation...}
+\label{fig:orbit}}
+\end{figure}
 
@@
 \end{table*}
-
-We first confirm that the two stars are indeed co-moving with very similar
-velocities using the radial velocities.
-\todo{APW: discuss kinematics, posterior of separation/dV}
 

### 2017-04-16 paper/ms.tex
change tablename
add new figure to tex

--- 2017-04-16 paper/ms.tex
@@
 
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.9\linewidth]{deltaXH_Tc_violins.png}
+  \caption{Difference in abundances of this pair and other binary pairs in
+    \citealt{2016ApJS..225...32B}.
+    Additionally, we show the distribution of abundance difference
+    between stars with similar metallicity difference
+    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
+    as violins with medians indicated by black line segments
+    by randomly pairing up single stars at two metallicity bins similar to
+    the pair of interest.
+    The difference is always relative to the lower-$[\elem{Fe}/\elem{H}]$ star.
+  }
+  \label{fig:deltaXH}
+\end{figure}
+
 \section{Discussion}

### 2017-04-16 paper/ms.tex

--- 2017-04-16 paper/ms.tex
@@
 \newcommand{\todo}[1]{{\color{blue}TODO:#1}}
+
+\renewcommand\tablename{Table}
 

### 2017-04-17 paper/ms.tex
typo and comment

@@
 The resulting measurements from this effort include abundances measured for 15
-checmical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
+chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
 well as high precision radial velocities.
@@
 By defining the vectors
+% SMOH: I understand you meant hat v_r as the latent true radial velocity but
+% personally think a) it can confuse some people that there are hat quantities
+% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
+% quantities for observed variables and no-hat for latent true ones.
+% SMOH: v_r is missing in the LHS of eq(3)
 \begin{eqnarray}

### 2017-04-17 paper/ms.tex
macro for star identifiers

@@
 \newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
+\newcommand{\sunanalog}{\ensuretext{HD HD 240429}}
+\newcommand{\bizarrone}{\ensuretext{HD 240430}}
 
@@
   We report and discuss the discovery of a co-moving pair of bright solar-type
-  stars, HD 240429 and HD 240430, with significant differences in their chemical
+  stars, \sunanalog\ and \bizarreone\, with significant differences in their chemical
   abundance patterns.
@@
   In the latter, we consider the possibility that the more metal-rich of the two,
-  HD 240430, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
+  \bizarreone, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
   selectively enhancing the refractory elements.
@@
 Though previously recognized as a visual double star system
-(\citealt{2001AJ....122.3466M}), HD 240429 and HD 240430 were identified as a
+(\citealt{2001AJ....122.3466M}), \sunanalog\ and \bizarreone\ were identified as a
 candidate co-moving star pair in our recent search for co-moving stars using the
@@
 potential planet-hosting stars, \citet{2016ApJS..225...32B}
-obtained high resolution spectroscopy for both HD 240429 and HD 240430.
+obtained high resolution spectroscopy for both \sunanalog\ and \bizarreone\.
 \todo{from where? mention briefly Keck HIRES}
@@
     Differences in posterior samples over Galactocentric phase-space coordinates
-    for the two stars HD 240429 and HD 240430.
+    for the two stars \sunanalog\ and \bizarreone\.
     \label{fig:dxdv}}
@@
 \figurename~\ref{fig:orbit} shows an orbit computed from the median posterior
-sample over 6D phase-space coordinates for HD 240429 (black line), integrated
+sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
 in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
@@
   \caption{%
-    Galactic orbits computed for HD 240429 (black) and the Sun (grey).
-    For HD 240429, the initial conditions are set to the median posterior
+    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
+    For \sunanalog\, the initial conditions are set to the median posterior
     sample over the inferred 6D phase-space coordinates.
@@
 \todo{except for thoese elements like Li...}
-Surprisingly, one of the stars, HD 240430 is significantly more metal
+Surprisingly, one of the stars, \bizarreone\ is significantly more metal
 rich than the other by 0.2~dex ($\approx 60\%$; Figure~\ref{fig:abundances}).
@@
 
-The abundance of HD 30 is peculiar on its own compared to other disk stars with
+The abundance of \bizarreone\ is peculiar on its own compared to other disk stars with
 similar $[\elem{Fe}/\elem{H}]$.
@@
 $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
-(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of HD 30 ever more unlikely.
+(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\ ever more unlikely.
 We stress that none of the \todo{how many} binary pairs examined in \citealt{2016ApJS..225...32B}
@@
   \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the co-moving pair, HD 240429 and HD 240430.}
+  \caption{Abundances of the co-moving pair, \sunanalog\ and \bizarreone\.}
   \label{fig:abundances}
@@
   \includegraphics[width=0.9\linewidth]{relabun_tc_XH.pdf}
-  \caption{Abundance of HD 240430 ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
-    relative to HD 240429 ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
+  \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
+    relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
     as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
@@
 None of the above scenarios is quite satisfactory as it offers no
-insight on the peculiarity in abundances of HD 30 (see \ref{sec:data}).
+insight on the peculiarity in abundances of HD 30 (see \sectionname~{\ref{sec:data}).
 

### 2017-04-19 paper/ms.tex
Fix latex mistakes and add binary-single discussion

@@
 \usepackage{amsmath,amssymb,natbib}
-\usepackage{tikz}
 \hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
@@
 \newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
-\newcommand{\sunanalog}{\ensuretext{HD HD 240429}}
-\newcommand{\bizarrone}{\ensuretext{HD 240430}}
+\newcommand{\sunanalog}{\text{HD 240429}}
+\newcommand{\bizarreone}{\text{HD 240430}}
 
@@
 potential planet-hosting stars, \citet{2016ApJS..225...32B}
-obtained high resolution spectroscopy for both \sunanalog\ and \bizarreone\.
+obtained high resolution spectroscopy for both \sunanalog\ and \bizarreone.
 \todo{from where? mention briefly Keck HIRES}
@@
     Differences in posterior samples over Galactocentric phase-space coordinates
-    for the two stars \sunanalog\ and \bizarreone\.
+    for the two stars \sunanalog\ and \bizarreone.
     \label{fig:dxdv}}
@@
 % binary-single and binary-binary exchange
-Another scenario that two unrelated stars may end up in a wide binary system
-is multi-body gravitational scattering.
-We consider the exchange probabilities in binary-single and binary-binary interactions.
-Given their low binding energy compared to incoming velocity of field stars,
-this is low.
-Two factors that make this even more unlikely are that both stars are very young given their large Li,
-and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
-not HD30 with anomalous abundance patterns.
+Two stars unrelated at birth may end up in a binary system via binary-single scattering event
+that results in an exchange of binary member.
+In order to estimate the rate at which any binary-single
+event will produce a wide binary system such as \sunanalog\ and \bizarreone,
+we may consider the rate at which this wide binary will scatter with a field star to
+result in an exchange reaction.
+The exchange rate for a binary with semi-major axis $a$ is
+\begin{eqnarray}
+  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
+\end{eqnarray}
+where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
+\begin{eqnarray}
+  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
+\end{eqnarray}
+when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
+which is appropriate for wide binaries scattering with field (disk) stars.
+If we assume that field stars are made of solar mass stars with constant $n=1$~pc$^{-3}$,
+and the incoming velocity is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
+stars in any direction, the rate of exchange scattering is
+\begin{eqnarray}
+  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
+  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
+\end{eqnarray}
+low enough to be negligible.
+
+In regions where binarity fraction is high, binary-binary scattering may be more important
+than binary-single scattering (\todo{CITE})
+
+%Two factors that make this even more unlikely are that both stars are very young given their large Li,
+%and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
+%not HD30 with anomalous abundance patterns.
 

### 2017-04-19 paper/ms.tex
all abundances to table; cannot center it right
note on what star means
making sense

@@
 \usepackage{amsmath,amssymb,natbib}
+\usepackage[flushleft]{threeparttable}
 \hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
@@
 \newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
+\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
 \newcommand{\sunanalog}{\text{HD 240429}}
@@
 \begin{table*}[htpb]
+  \caption{Astrometric and spectroscopic measurements.}
+  \label{tab:t2}
+  \begin{threeparttable}
   \centering
-  \caption{Astrometric and spectroscopic measurements}
-  \label{tab:t2}
   \begin{tabular}{ccc}
@@
 $v_r$                                     & $-21.2$           & $-21.2$           \\
-$\varpi$ & $9.35 \pm 0.24$ & $9.41 \pm 0.25$ \\
-$\mu_\alpha^*$ & $89.25 \pm 0.66$ & $89.41 \pm 0.69$ \\
-$\mu_\delta$  & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$\\
+$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
+$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
+$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
+\hline
+\multicolumn{3}{c}{$T_c < 1200$~K} \\
+\hline
+$\elemH{Li}_*$ \footnotemark[2]           & $2.25$            & $2.75$            \\
+$\elemH{C}$                               & $0.00$            & $0.09$            \\
+$\elemH{N}$                               & $-0.06$           & $-0.01$           \\
+$\elemH{O}$                               & $0.01$            & $0.09$            \\
+$\elemH{Na}$                              & $-0.06$           & $-0.04$           \\
+$\elemH{Mn}$                              & $-0.03$           & $0.00$            \\
+\hline
+\multicolumn{3}{c}{$T_c > 1200$~K} \\
+\hline
+$\elemH{Mg}$                              & $0.01$            & $0.19$            \\
+$\elemH{Al}$                              & $0.01$            & $0.21$            \\
+$\elemH{Si}$                              & $0.00$            & $0.16$            \\
+$\elemH{Ca}$                              & $0.02$            & $0.23$            \\
+$\elemH{Ti}$                              & $0.02$            & $0.20$            \\
+$\elemH{V}$                               & $0.02$            & $0.20$            \\
+$\elemH{Cr}$                              & $0.01$            & $0.17$            \\
+$\elemH{Fe}$                              & $0.01$            & $0.20$            \\
+$\elemH{Ni}$                              & $-0.01$           & $0.21$            \\
+$\elemH{Y}$                               & $0.04$            & $0.26$            \\
 \hline\hline
 \end{tabular}
+%
+\begin{tablenotes}
+  \item All spectroscopic measurements except $\elem{Li}$ are from \citealt{2016ApJS..225...32B}.
+  \footnotetext[1]{From \tgas. }
+  \footnotetext[2]{Absolute abundance from \todo{CITE}.}
+\end{tablenotes}
+  \end{threeparttable}
 \end{table*}
@@
 result in an exchange reaction.
-The exchange rate for a binary with semi-major axis $a$ is
+The cross-section of exchange scattering for a binary with semi-major axis $a$ is
 \begin{eqnarray}
@@
 which is appropriate for wide binaries scattering with field (disk) stars.
-If we assume that field stars are made of solar mass stars with constant $n=1$~pc$^{-3}$,
-and the incoming velocity is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
+If we assume that field stars are made of solar mass stars
+with constant number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars
+is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
 stars in any direction, the rate of exchange scattering is

### 2017-04-21 paper/ms.tex
data discussion on lithium

@@
 (\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\ ever more unlikely.
-We stress that none of the \todo{how many} binary pairs examined in \citealt{2016ApJS..225...32B}
+We stress that none of the other seven binary pairs examined in \citealt{2016ApJS..225...32B}
 show discrepancies in abundances between the stars at this level.
@@
 
-paragraph on lithium and ages
+Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
+due to mixing induced by convection or rotation which brings lithium
+into the interior ($T>2.5 \times 10^{6}$~K)
+where it will be destroyed by proton capture burning.
+Thus, surface lithium abundance is an indicator of stellar ages.
+The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
+according to the theoretical models tuned to explain the solar lithium abundance
+and rotational profile (\citealt{2005Sci...309.2189C}).
+The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
+showing the largest difference among all measured elements.
+Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
+it is unclear, however, whether this higher $\elem{Li}$ abundance
+means a younger age or something else.
+For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
+to the engulfment of substellar companions such as gas giant planets are brown dwarfs
+which may replenishe unburnt $\elem{Li}$ (\citealt{Casey:2016aa}).
+We come back to the $\elem{Li}$ difference later in our discussion.
 

### 2017-04-21 paper/ms.tex
typo city

@@
 For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
-to the engulfment of substellar companions such as gas giant planets are brown dwarfs
-which may replenishe unburnt $\elem{Li}$ (\citealt{Casey:2016aa}).
+to the engulfment of substellar companions such as gas giant planets or brown dwarfs
+which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
 We come back to the $\elem{Li}$ difference later in our discussion.

### 2017-04-26 paper/ms.tex
paragraph on inhomogeneity

@@
 \newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
+\newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
 \newcommand{\sunanalog}{\text{HD 240429}}
@@
 showing the largest difference among all measured elements.
+This translates to $\sim 500$~Myr difference in age.
 Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
@@
 low enough to be negligible.
+Because the exchange scattering cross section steeply depends on the incoming velocity
+relative to the critical velocity (of the order of orbital velocity of the binary),
+the rate of exchange scattering with a star within the same star forming region
+may be much larger.
+However, even in such scenario, the age difference of $\sim 500$~Myr is too large
+for two stars of the same star forming region.
 
@@
 
-None of the above scenarios is quite satisfactory as it offers no
+None of the above scenarios is satisfactory as it offers no
 insight on the peculiarity in abundances of HD 30 (see \sectionname~{\ref{sec:data}).
@@
 It may be that the two stars are born at the same time from the same cloud, but
-there is inhomogeneity. Highly doubtful based on
-- Brewer et al. binaries that seem identical.
-- other?
+there is inhomogeneity within the cloud.
+However, there is already ample amount of evidence against such scenario.
+First, none of the other seven similar wide binaries examined in \citealt{2016ApJS..225...32B}
+show the same level differences in abundances although there is generally
+a larger spread in $\elem{C}$, $\elem{N}$ and $\elem{O}$, and some pairs show
+a large as $\approx 0.15$~dex difference in particular elements.
+The median and maximum \feh\ difference between component stars in the other seven pairs
+is $0.02$~dex and $0.09$~dex, respectively.
+This is consistent with the findings of \citealt{Desidera:2004aa} who examined 23 wide bianries
+of late F to K dwarfs, and found most pairs show difference in \feh\ less than $0.02$~dex
+and none larger than $0.07$~dex.
+
+% summarize other pair studies in detailed chemical abundance here
 

### 2017-05-01 paper/ms.tex
more on ages

@@
 which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
-We come back to the $\elem{Li}$ difference later in our discussion.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{isochrones.png}
+  \caption{Isochrone ages of \sunanalog\ and \bizarreone.
+    On the left, we show the two stars on $T_\mathrm{eff}-\log(g)$ plane,
+    and on the right, the color-magnitude diagram using \gaia\ $G$ band
+    and \tmass\ $J$ band magnitudes.
+    In each panel, \project{MIST} isochrones (\citealt{Choi:2016aa}) at $28$~Myr and $2$~Gyr are
+    plotted. The thicker and thinner lines are for $\feh = 0.$ and $0.2$,
+    corresponding to values of \sunanalog\ and \bizarreone.
+  }
+  \label{fig:isochrones}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.8\linewidth]{sed.png}
+  \caption{Spectral energy distributions (SEDs) of \sunanalog\ and \bizarreone.
+    The yellow line is the SED of a blackbody at $T=5878$ scaled arbitrarily.
+  }
+  \label{fig:sed}
+\end{figure}
+
+Given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
+comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
+We compared the measured $\log(g)$ and $T_\mathrm{eff}$ to \project{MIST} isochrones at two
+different $\feh$ of $0$ and $0.2$, corresponding to the $\feh$ of \sunanalog\ and \bizarreone.
+The two most consistent isochrones at $28$~Myr and $2$~Gyr based on $\chi^2$ values
+are plotted in Figure~\ref{fig:isochrones}.
+For \sunanalog\ ($\feh = 0.01$), the most consistent isochrone is that for
+an age of $2$~Gyr and $\feh = 0.2$.
+The $\log(g)$ values of the two stars, especially of \bizarreone\, seem to suggest
+that they could be at the end of the pre-main sequence phase.
+However, an age of $28$~Myr for \sunanalog\ is in tension with the larger age ($800$~Myr)
+inferred from its $\elem{Li}$ abundance.
+Also, at such a young age, we may expect to see infrared excess from a circumstellar disk or
+X-ray emission from magnetic activity. 
+However, the spectral energy distributions of the two stars based on
+\project{Tycho-2}, \tmass, \project{WISE} photometry (\todo{CITE}) are consistent with blackbody,
+and no relatable X-ray point sources are found in the \project{ROSAT} All-Sky Survey
+around the two stars,
+On the other hand, the most consistent main sequence age ($2$~Gyr) also is in tension with
+its relatively high $\elem{Li}$ abundance, not to mention with the $\log(g)$ of \bizarreone\
+if the two stars should have the same age.
 

### 2017-05-04 paper/ms.tex
star names fixed

@@
 \newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
-\newcommand{\sunanalog}{\text{HD 240429}}
-\newcommand{\bizarreone}{\text{HD 240430}}
+\newcommand{\sunanalog}{\text{Krios}}
+\newcommand{\bizarreone}{\text{Kronos}}
 
@@
 
-\title{A pair of co-moving, Sun-like stars with different chemical abundances:\\
-       a possible signature of copious rocky accretion (needs work)}
+\title{Kronos \& Krios: TBD}
 
@@
 \label{sec:introduction}
+
+Wide binaries are valuable tools for studying star and planet formation as well as
+Galactic dynamics and chemical evolution.
+They tidally disrupt.
 
@@
 different $\feh$ of $0$ and $0.2$, corresponding to the $\feh$ of \sunanalog\ and \bizarreone.
-The two most consistent isochrones at $28$~Myr and $2$~Gyr based on $\chi^2$ values
+The ages most consistent with $\log(g)$ and $t_\mathrm{eff}$ for
+\sunanalog\ and \bizarreone\ using the isochrones of corresponding metallicities
+is $\approx 4$~Gyr and $\approx 5.6$~Gyr respectively, based on $\chi^2$ values.
+This is in tension with the relatively high $\elem{Li}$ abundance in both stars.
+Even for \sunanalog\, a $\elem{Li}$ abundance of 2.25 is unusually high for a sunlike star with
+similar ages.
+
 are plotted in Figure~\ref{fig:isochrones}.

### 2017-05-04 paper/ms.tex
intro sketch ... first attempt

@@
   Semyeong Oh\altaffilmark{\pu,\lead},
-  APW, JMB, KH, NL, DWH, DNS
+  APW, JMB, KH, NL, DWH, DNS, JW
 }
@@
 Galactic dynamics and chemical evolution.
-They tidally disrupt.
+In the context of studying the evolution of the Milky Way, they are useful for
+two main reasons.
+First, because wide binaries are weakly bound systems that may be tidally
+disrupted by e.g., field stars, molecular clouds, or the Galactic tidal field,
+their statistics can be informative of the Galactic mass distribution.
+\todo{Give specific examples.}
+On the other hand, they are also a prime target to test the
+chemical tagging hypotheses that we may trace back a group of co-eval stars
+by detailed chemical abundance patterns as ``tag''s.
+A multiple-star system of any size that we believe are co-eval,
+with massive open clusters at one extreme, can serve this purpose.
+Wide binaries are at the other extreme in that we may be less confident of
+their coevality but they are much more abundant than the larger systems like open clusters.
 
-% section introduction (end)
+Independently, in efforts to connect the host star's chemistry to
+its planetary system, wide binaries with similar or very different planetary systems around
+component stars are very useful as chemical signatures related to planet formation or accretion
+can be revealed in a differential sense without any regard to Galactic chemical evolution
+as long as we assume that the two stars should have been born together with identical chemistry.
+\todo{Give examples and summary: Teske, Mack, Melendez.}
+
+So far the strongest evidence for accretion of planetary material by host star comes
+from spectral analysis of polluted white dwarfs.
+\todo{Discuss Zuckerman, Klein}.
+
+Here, we report and discuss the discovery of a co-moving pair of solar twin stars,
+HD~240429 and HD~240430, with unusual chemical abundance and differential abundance patterns
+that strongly suggest a dramatic accretion of planetary material by the two stars.
+\todo{section summary}
 

### 2017-05-04 paper/ms.tex
introduce nicknames

@@
 Here, we report and discuss the discovery of a co-moving pair of solar twin stars,
-HD~240429 and HD~240430, with unusual chemical abundance and differential abundance patterns
+HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
 that strongly suggest a dramatic accretion of planetary material by the two stars.
+We nickname the two stars \bizarreone\ (HD~240430) and
+\sunanalog\ (HD~240429) throughout the \documentname.
 \todo{section summary}

### 2017-05-05 paper/ms.tex
Tc caution reminder
Fix symbol for absolute Li abundance
discuss eight age indicators

@@
 \todo{section summary}
+
+\todo{Explicit cautionary remark that Tc is just a proxy here?}
+%SMOH: I prefer in the relevant discussion.
 
@@
 \hline
-$\elemH{Li}_*$ \footnotemark[2]           & $2.25$            & $2.75$            \\
+$A(\elem{Li})$ \footnotemark[2]           & $2.25$            & $2.75$            \\
 $\elemH{C}$                               & $0.00$            & $0.09$            \\
@@
 
-Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
-due to mixing induced by convection or rotation which brings lithium
-into the interior ($T>2.5 \times 10^{6}$~K)
-where it will be destroyed by proton capture burning.
-Thus, surface lithium abundance is an indicator of stellar ages.
-The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
-according to the theoretical models tuned to explain the solar lithium abundance
-and rotational profile (\citealt{2005Sci...309.2189C}).
-The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
-showing the largest difference among all measured elements.
-This translates to $\sim 500$~Myr difference in age.
-Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
-it is unclear, however, whether this higher $\elem{Li}$ abundance
-means a younger age or something else.
-For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
-to the engulfment of substellar companions such as gas giant planets or brown dwarfs
-which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
-
 \begin{figure}[htpb]
@@
 
-Given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
+The fact that the two stars share a very similar space motion
+at a separation of $0.6$~pc strongly argues that the pair is coeval.
+We consider other age indicators apart from their phase space coordinates
+to assess the ages and coevality of the two stars.
+First, given the precise measurements of $\log(g)$, $T_\mathrm{eff}$,
 comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
-We compared the measured $\log(g)$ and $T_\mathrm{eff}$ to \project{MIST} isochrones at two
-different $\feh$ of $0$ and $0.2$, corresponding to the $\feh$ of \sunanalog\ and \bizarreone.
-The ages most consistent with $\log(g)$ and $t_\mathrm{eff}$ for
-\sunanalog\ and \bizarreone\ using the isochrones of corresponding metallicities
-is $\approx 4$~Gyr and $\approx 5.6$~Gyr respectively, based on $\chi^2$ values.
-This is in tension with the relatively high $\elem{Li}$ abundance in both stars.
-Even for \sunanalog\, a $\elem{Li}$ abundance of 2.25 is unusually high for a sunlike star with
-similar ages.
+We perform isochrone fitting using the Yale-Yonsei model isocrones (\todo{CITE}).
+The input data are $\log(g)$, $T_\mathrm{eff}$, \feh, parallaxes, $B$-band magnitudes, and their errors.
+The isochrone ages of \sunanalog\ and \bizarreone\ are
+$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
+consistent with them being coeval.
 
-are plotted in Figure~\ref{fig:isochrones}.
-For \sunanalog\ ($\feh = 0.01$), the most consistent isochrone is that for
-an age of $2$~Gyr and $\feh = 0.2$.
-The $\log(g)$ values of the two stars, especially of \bizarreone\, seem to suggest
-that they could be at the end of the pre-main sequence phase.
-However, an age of $28$~Myr for \sunanalog\ is in tension with the larger age ($800$~Myr)
-inferred from its $\elem{Li}$ abundance.
-Also, at such a young age, we may expect to see infrared excess from a circumstellar disk or
-X-ray emission from magnetic activity. 
-However, the spectral energy distributions of the two stars based on
-\project{Tycho-2}, \tmass, \project{WISE} photometry (\todo{CITE}) are consistent with blackbody,
-and no relatable X-ray point sources are found in the \project{ROSAT} All-Sky Survey
-around the two stars,
-On the other hand, the most consistent main sequence age ($2$~Gyr) also is in tension with
-its relatively high $\elem{Li}$ abundance, not to mention with the $\log(g)$ of \bizarreone\
-if the two stars should have the same age.
+Surface lithium abundance in a sun-like star decreases with its age
+due to mixing induced by convection or rotation which brings lithium
+into the interior ($T>2.5 \times 10^{6}$~K)
+where it will be destroyed by proton capture burning.
+Thus, surface lithium abundance is an indicator of stellar ages.
+The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
+according to the theoretical models tuned to explain the solar lithium abundance
+and rotational profile (\citealt{2005Sci...309.2189C}).
+The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
+showing the largest difference among all measured elements.
+This translates to $\sim 500$~Myr difference in age.
+Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
+it is unclear, however, whether this higher $\elem{Li}$ abundance
+means a younger age or something else.
+For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
+to the engulfment of substellar companions such as gas giant planets or brown dwarfs
+which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
+
+In fact, the surface lithium abundance is the only indication that points to younger ages.
+If the two stars are indeed only several hundred Myrs old at most,
+they are expected to be part of a larger co-moving group of stars.
+However, as we mention above, there is no evidence in our search of co-moving pairs
+using \tgas\ that the two stars belong to a larger group of young stars.
+Very young stars are often show signs of activity such as
+X-ray emission from magnetic activity, emission lines, or infrared excess due to
+circumstellar disks.
+We have looked for these signs for the pair to find none, and their spectral energy
+distribution is consistent with blackbody.
+The low $v\sin(i)$ values also argue against very young ages inferred from the
+surface lithium abundances.
+% TODO: ref for vertical action as age?
+Finally, their fiducial orbit in a Milky Way-like potential show that the vertical action
+for this pair is larger than the Sun, favoring an older age.
+We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main sequence
+stars, and that their unusually high \elem{Li} abundance requires an alternative explanation.
 
@@
   \label{fig:relabun_tc}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[angle=90,height=0.9\textheight]{TcRank_deltaXH.pdf}
+  \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
+    relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
+    as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
+  }
+  \label{fig:relabun_tcrank}
 \end{figure}

### 2017-05-07 notebooks/specplot.py
add module for spectrum plotting

@@ -1,0 +1,275 @@
+# -*- coding: utf-8 -*-
+"""
+    CronusCrius.specplot
+    ~~~~~~~~~~~~~~~~~~~~
+
+    Module for plotting JMB's spectra and models
+
+    :copyright: (c) 2017 by Semyeong Oh, John M. Brewer.
+    :license: MIT, see LICENSE for more details.
+"""
+
+from __future__ import division # to get float division with ints
+
+# Import readsav so we can read IDL Save Files
+import warnings
+from scipy.io import readsav
+warnings.filterwarnings('ignore', message="warning: empty strings")
+
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+
+import re
+
+mpl.rcParams['figure.figsize']=(16.,10.)
+mpl.rcParams['font.size']=16
+mpl.rcParams['axes.linewidth'] = 3.0
+
+# set x tick size and width
+mpl.rcParams['xtick.major.size'] = 5
+mpl.rcParams['xtick.major.width'] = 2
+mpl.rcParams['xtick.minor.size'] = 2
+mpl.rcParams['xtick.minor.width'] = 1
+
+# set tick width
+mpl.rcParams['ytick.major.size'] = 5
+mpl.rcParams['ytick.major.width'] = 2
+mpl.rcParams['ytick.minor.size'] = 2
+mpl.rcParams['ytick.minor.width'] = 1
+
+# Speed of light for calculating offsets in wavelengths due to RV shifts
+cLight = 299792.458 # km/s
+
+# These are the "Tableau 20" colors as RGB.  
+tableau20 = [(31, 119, 180), (174, 199, 232), (255, 127, 14), (255, 187, 120),  
+             (44, 160, 44), (152, 223, 138), (214, 39, 40), (255, 152, 150),  
+             (148, 103, 189), (197, 176, 213), (140, 86, 75), (196, 156, 148),  
+             (227, 119, 194), (247, 182, 210), (127, 127, 127), (199, 199, 199),  
+             (188, 189, 34), (219, 219, 141), (23, 190, 207), (158, 218, 229)]  
+  
+# Scale the RGB values to the [0, 1] range, which is the format matplotlib accepts.  
+for i in range(len(tableau20)):  
+    r, g, b = tableau20[i]  
+    tableau20[i] = (r / 255., g / 255., b / 255.)  
+
+def getColor(i):
[…]

### 2017-05-08 notebooks/specplot.py
unopinionate styles and add option to omit wavelengths in labels

@@ -23,21 +23,6 @@ from matplotlib.backends.backend_pdf import PdfPages
 
 import re
 
-mpl.rcParams['figure.figsize']=(16.,10.)
-mpl.rcParams['font.size']=16
-mpl.rcParams['axes.linewidth'] = 3.0
-
-# set x tick size and width
-mpl.rcParams['xtick.major.size'] = 5
-mpl.rcParams['xtick.major.width'] = 2
-mpl.rcParams['xtick.minor.size'] = 2
-mpl.rcParams['xtick.minor.width'] = 1
-
-# set tick width
-mpl.rcParams['ytick.major.size'] = 5
-mpl.rcParams['ytick.major.width'] = 2
-mpl.rcParams['ytick.minor.size'] = 2
-mpl.rcParams['ytick.minor.width'] = 1
 
 # Speed of light for calculating offsets in wavelengths due to RV shifts
 cLight = 299792.458 # km/s
@@ -148,7 +133,7 @@ class SpecPlot(object):
 
     def plotSeg(self, segIdx=0, wRange=[5170.,5175.], showLines=[], ax=None,
                 yMin=0.0, showModel=True, obsColor='#999999', obsWidth=2, modColor='b', modWidth=2,
-                lineWidth=1):
+                lineWidth=1, labelSpeciesOnly=False):
         spec = self.spec
         # Speed of light for calculating offsets in wavelengths due to RV shifts
         cLight = 299792.458 # km/s
@@ -178,8 +163,8 @@ class SpecPlot(object):
         
         if ax == None:
             ax = plt.gca()
-            ax.set_xlabel("Wavelength",fontweight='bold')
-            ax.set_ylabel("Residual Intensity",fontweight='bold')
+            ax.set_xlabel("Wavelength")
+            ax.set_ylabel("Residual Intensity")
             ax.get_xaxis().set_major_formatter(
                 mpl.ticker.FuncFormatter(lambda x, p: "{:6.1f}".format(x)))
         
@@ -267,9 +252,12 @@ class SpecPlot(object):
                 
                 lBot = np.min(mod[wavesOfInterest]) + lineOffset
                 p = ax.plot([lWave,lWave],[lBot,labelLineTop],linestyle='-',color=lColor,linewidth=lineWidth)
-                pt = ax.text(lWave,labelTextBot,"{} - {:8.3f}".format(species[idx],lWave),
+                if labelSpeciesOnly:
+                    labelText = "{}".format(species[idx])
+                else:
[…]

### 2017-05-09 paper/ms.tex
add caption for spec plots

@@
 
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec1.pdf}
+  \caption{Selective segments of spectra of \sunanalog\ and \bizarreone.
+    For each row, the continuum-normalized data and model are plotted in the upper panel,
+    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
+    are plotted in the lower panel.
+  }
+  \label{fig:spec1}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec2.pdf}
+  \caption{Same as \figname~\ref{fig:spec1} but for smaller portions of spectra that are
+    not dominated by \elem{Fe}. We mark elements that give rise to strong lines.
+    The feature in the third column of the second row is a strong \elem{Li} line that was
+    not modeled by \citealt{2016ApJS..225...32B}. This line was studied in a separate study
+    \todo{CITE}.
+  }
+  \label{fig:spec2}
+\end{figure}
+
 \bibliography{ref}

### 2017-05-20 paper/ms.tex
Improve Tc rank vs delta X/H figure
working on summary of previous studies

@@
 \newcommand{\bizarreone}{\text{Kronos}}
+\newcommand{\Tcondens}{\ensuremath{T_C}}
+\newcommand{\mearth}{\ensuremath{M_\oplus}}
+\newcommand{\mjupiter}{\ensuremath{M_\mathrm{Jup}}}
 
@@
 etc.}).
-\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
+\figname~\ref{fig:dxdv} shows differences in posterior samples converted to
 Galactocentric phase-space coordinates for the two stars.
@@
 
-\figurename~\ref{fig:orbit} shows an orbit computed from the median posterior
+\figname~\ref{fig:orbit} shows an orbit computed from the median posterior
 sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
@@
 Surprisingly, one of the stars, \bizarreone\ is significantly more metal
-rich than the other by 0.2~dex ($\approx 60\%$; Figure~\ref{fig:abundances}).
+rich than the other by 0.2~dex ($\approx 60\%$; \figname~\ref{fig:abundances}).
 What is more puzzling is that the abundances of this star
@@
 Surface lithium abundance in a sun-like star decreases with its age
-due to mixing induced by convection or rotation which brings lithium
+due to mixing induced by convection or rotation, which brings the lithium
 into the interior ($T>2.5 \times 10^{6}$~K)
@@
   \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the co-moving pair, \sunanalog\ and \bizarreone\.}
+  \caption{Abundances of the co-moving pair, \sunanalog\ and \bizarreone.}
   \label{fig:abundances}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{relabun_tc_XH.pdf}
-  \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
-    relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
-    as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
-  }
-  \label{fig:relabun_tc}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[angle=90,height=0.9\textheight]{TcRank_deltaXH.pdf}
+  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
   \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
@@
 
-None of the above scenarios is satisfactory as it offers no
-insight on the peculiarity in abundances of HD 30 (see \sectionname~{\ref{sec:data}).
-
+None of the above scenarios is satisfactory as they offer no
+insight on the peculiarity of the abundances of \bizarreone
+(see \sectionname~{\ref{sec:data}}).
+In case that the pair formed from a exchange scattering event,
+we would expect the pair to be composed of typical field stars.
 The unlikeliness of the above possibilities naturally leads us to
 consider the alternative.
-What can selectively enrich XX elements in one of the two stars that are born together?
+What can selectively enrich refractory (high $T_C$) elements
+in one of the two stars that are born together?
 
@@
 is $0.02$~dex and $0.09$~dex, respectively.
-This is consistent with the findings of \citealt{Desidera:2004aa} who examined 23 wide bianries
+This is consistent with the findings of \citealt{Desidera:2004aa}, who examined 23 wide binaries
 of late F to K dwarfs, and found most pairs show difference in \feh\ less than $0.02$~dex
@@
 % rocky planets (or the like) engulfment
-Yet another possibility is that the more metal-rich of the two stars
-was recently? bombarded by something that selectively removed the depleted elements but not the others.
+Yet another possibility that may change a star's surface abundance after formation
+is accretion of its planets or asteroids.
+Instabilities may develop in a multi-planet system due to chaotic
+nature of many body system, which may lead to planet engulfment by the host star.
+
+One informative proxy that may reveal the composition of the hypothetical material
+that was accreted to the stars is the condensation temperature.
 
@@
 
-Change in stellar abundance due to ingestion of planets has been considered
-for similar bright star pairs HD XX/XX (Mack) and HD XX/XX(Mack).
+\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
+with a projected separation of $\sim9000$~AU (correspoding to 4.2~arcmin sky separation).
+Both stars in this system host close-in giant planets.
+HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
+pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
+with moderately high eccentricity ($e\sim0.1-0.3$).
+They found that the abundances of 15 elements between the two stars are consistent with each other.
+However, they argued that there is a moderately significant ($\sim 2\sigma$)
+positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
+{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
+(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
+of their measurements).
+They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
+H-depleted rocky material that were pushed in during giant planet migration.
 
-% Concluding remakrs
+\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
+with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
+host a hot Jupiter.
+The planet hosted by WASP-94A is transiting with a misaligned, probably
+retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
+more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
+star.
+With a claimed precision of $0.006$~dex (median among all elements), they
+detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
+elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
+1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
+Excluding K, which is based on one strong line and largely affected by non-LTE
+effect, their analysis shows a statistically significant non-zero slope between
+$\Delta\elemH{X}$ and $\Tcondens$\footnote{Note that the condensation
+  temperature $\Tcondens$ used is for solar (system? atmosphere?) composition
+  gas, which can differ from that of higher metallicity gas.}.
+They considered multiple possibilities related to the formation and evolution
+of planetary systems around each star as well as causes unrelated to planets
+such as dust cleansing during the fully convective phase or different rotation
+and granulation between the stars, but did not favor any particular one.
+
+The pair of G5 stars HD 80606/HD 80607 has been independently studied by
+\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
+spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
+on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
+planets.
+Both stars are super solar with $\feh=0.35$.
+
+% Concluding remarks
 
@@
   \includegraphics[width=0.95\linewidth]{spec1.pdf}
-  \caption{Selective segments of spectra of \sunanalog\ and \bizarreone.
+  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
     For each row, the continuum-normalized data and model are plotted in the upper panel,

### 2017-05-22 paper/ms.tex
add text on other studies (wip)

@@
 \newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
+\newcommand*\teff{\ensuremath{T_\mathrm{eff}}}
+\newcommand*\logg{\ensuremath{\log{g}}}
 \newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
@@
 None of the above scenarios is satisfactory as they offer no
-insight on the peculiarity of the abundances of \bizarreone
+insight on the peculiarity of the abundances of \bizarreone\
 (see \sectionname~{\ref{sec:data}}).
@@
 
+\input{otherstudies.tex}
+
+We summarize the few wide separation common proper motion pairs that have been
+studied in detailed chemical abundance so far.
+These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
+WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
+Main properties of the systems relevant to the present discussion are
+summarized in \tablename~\ref{tab:otherstudies}.
+Their reported abundance differences $\Delta\elemH{X}$ where the difference is
+always taken as $\mathrm{higher}~\feh - \mathrm{lower}~\feh$ are plotted in
+\figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
+comparision with this pair.
+
+{\bf HD~20782/HD~20782:} 
 \citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
@@
 
+{\bf WASP-94A/WASP-94B:} 
 \citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
@@
 
+{\bf HD~80606/HD~80607:}
 The pair of G5 stars HD 80606/HD 80607 has been independently studied by
@@
 Both stars are super solar with $\feh=0.35$.
+
+{\bf HAT-P-1:}
+HAT-P-1 is a pair of G0 stars separated 11\farcs apart in sky
+with $\feh\approx0.15$.
+The secondary star in the system is known to host one transiting giant planet
+while no planet has been discovered around the primary star.
+\citealt{Liu:2014aa} found that the two stars are identical in their atmospheric composition:
+\feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for the primary and secondary respectively,
+and $\Delta\elem{X}/{Fe}$ is consistent with zero for 23 elements measured
+with the mean error being $0.013$~dex.
+Based on this analysis, they concluded that the presence of close-in giant planet
+does not necessarily lead to stellar atmospheric pollution of the host star.
+
+{\bf XO-2N/XO-2S:}
+The double star system XO-2 has received much attention due to
+possibly the most robust and significant difference between the component stars
+among those so far studied.
+XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
+each hosting planet(s).
+XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
+masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
+0.15$) orbits at $<0.5$~AU.
+
+The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
+essentially no significant difference in Fe, Ni, C, and O between the two
+stars.
+However, re-analysis of the system using the same data in
+\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
+\Tcondens\ varies significantly depending on the stellar parameters chosen in
+their analysis. Both analyses were based on spectra
+using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
+covering $4450-5660~\AA$ and $5860-7100~\AA$ with S/N of $170-230$
+(\citealt{Teske:2013aa}).
+
+Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
+$4080-8300~\AA$) of the component stars with S/N of $350$ (in $5000-7500~\AA$)
+to perform a differential abundance analysis.
+They find that all 23 elements including Fe is enhanced in XO-2N
+compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
+a significant correlation with \Tcondens.
+At low \Tcondens, volatile elements differ by $0.015$~dex
+while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
+There are inconsistencies in the determination of stellar parameters
+(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
+and photometric analysis,
+but the existence of correlation between $\Delta\elem{H}$ and
+\Tcondens\ seems robust.
+
+\citealt{Ramirez:2015aa} argued that the {\it depletion} of
+volatile elements in XO-2S relative to XO-2N is plausibly
+due to {\it more} gas giant planets around XO-2S,
+following a similar interpretation of \citealt{Melendez:2009aa}
+on the trend between solar twins and the Sun.
+In this scenario, forming planets in the protoplanetary disk
+are supposed to ``lock'' heavier elements to the core of gas giant
+planets as well as some volatile elements in their envelopes.
+Then, the host star will somehow accrete {\it gas} depleted in
+metals compared to their protostellar condition.
+By tuning the metal content ($Z/X$) of gas giant planets
+and when the accretion of gas occurs in terms of how much mass
+is in the convective envelop then, they can match
+the mass difference of gas giant planets around each star,
+which is at least $1~\mjupiter$.
+For the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
+\citealt{Ramirez:2015aa} estimated that $20~\mearth$
+of equal-part mixture of Earth and CM chondrite-like material
+can explain the trend either as
+refractory {\it depletion} in XO-2S due to {\it more} rocky planets
+around XO-2S, or refractory enhancement in XO-2N by late time accretion
+in which case the complete opposite would be true.
+
+Finally, \citealt{Biazzo:2015aa}
+
+% Useful follow up efforts
 

### 2017-05-23 paper/ms.tex
Add text on toy calculation and Li (wip)

@@
 \graphicspath{{figures/}}
+\bibliographystyle{aasjournal.bst}
 
@@
 Wide binaries are at the other extreme in that we may be less confident of
-their coevality but they are much more abundant than the larger systems like open clusters.
+the coevality of individual systems
+but they are much more abundant than the larger systems like open clusters,
+rendering their statistics a meaningful indication of whether the hypothesis works.
 
@@
 potential planet-hosting stars, \citet{2016ApJS..225...32B}
-obtained high resolution spectroscopy for both \sunanalog\ and \bizarreone.
-\todo{from where? mention briefly Keck HIRES}
-The resulting measurements from this effort include abundances measured for 15
+analyzed high resolution spectra of both stars obtained using HIRES spectrograph
+on Keck~I telescope.
+The spectral resolution is \todo{$R\approx XXX$} and the wavelength coverage is \todo{$XXX-XXX$~\AA}.
+The resulting measurements include abundances measured for 15
 chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
@@
 
-% summarize other pair studies in detailed chemical abundance here
-
 % rocky planets (or the like) engulfment
@@
 
-estimate: 10 earth mass
+Present the relative abundance figure here
 
-Present the relative abundance figure here
+One can carry out simple toy calculations of expected $\Delta\elemH{X}$
+in a Sun-like star's atmosphere when adding material of e.g., bulk Earth composition
+under these assumptions:
+\begin{itemize}
+  \item The material added is instantly and completely mixed.
+  \item The atmospheric composition that we measure is identical throughout
+    the star's radiative and convective zone.
+\end{itemize}
+We take the solar abundances $\elemH{X}$ of \citealt{Asplund:2009aa}
+which can be converted to mass fraction in each element $X$ as in
+\begin{equation}
+  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
+\end{equation}
+where $m_X$ is the mass of each element in e.g., atomic mass unit.
+One can check that the \citealt{Asplund:2009aa} abundances
+are consistent with mass fraction in \elem{H}, \elem{He} and metals
+$X,\,Y,\,Z=0.757,\,0.249,\,0.0134$ as stated in that work.
+Assuming a fraction of the star's convective zone in mass $f_\mathrm{CZ}$,
+and that the added material has a total mass $M_\mathrm{add}$ and mass fraction in each
+element $f_{X,\mathrm{add}}$,
+the abundance difference is
+\begin{equation}
+  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star} + f_{X,\mathrm{add}}\,M_\mathrm{add}}
+    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
+\end{equation}
+We take the composition of bulk Earth from a chondritic model of the Earth
+(\citealt{mcdonough2001composition}) and CI chondrite from \citealt{2009LanB...4B...44L}.
+
+Figure~\ref{fig:toycalc} shows the expected change of surface abundances in a
+Sun-like star after $20~\mearth$ of material with composition of bulk Earth or
+CI chondrite is added.
+The CI chondrites are believed to have the closest in composition to the solar nebular.
+Their composition closely matches that of the solar atmosphere except
+Li, highly volatile ($\Tcondens < 250$~K) elements, and the noble gases.
+Other groups of chondrites show differing level of variations from CI chondrites.
+It has been long known that compared to CI or other carbonaceous chondrites,
+the composition of the Earth shows a volatilaity trend that moderately volatile
+elements (including Mn and Na) and volatile elements are incearsingly more
+depleted with decreasing condensation temperature (\citealt{mcdonough2001composition}).
+This trend is presumed to be closely related to the formation of terrestrial planets.
+Given the simplistic assumptions laid out above, and the uncertainties
+in our current knowledge of the compositions of terrestrial planets including bulk Earth,
+the match between our toy calculation and the observed abundance difference
+between \bizarreone\ and \sunanalog\ is remarkable.
+
+% some discussion of individual elements
+
+The element \elem{Li} is worth a special attention in the context of accretion scenario.
+Because Li is present in either carbonaceous chondrites or the bulk Earth with
+a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition,}),
+but is depleted over time on the surface of a Sun-like star, accretion of
+either at later time will significantly replenish the lithium on the star's
+surface.
+For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
+material results in $\Delta\elemH{Li} \approx 1.6$~dex.
+Incidentally, the star under examination, \bizarreone, has an age (informed by
+stellar parameters) very close to the Sun ().
+Thus, as long as we believe the Sun's present-day surface Li abundance
+to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
+in its Li.
+This is in fact exactly what we find: the Li abundance of \bizarreone\ is
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t2}, \todo{CITE JM?})
+approximately $1.6$~dex higher than the solar value of $1.1$~dex.
+Furthermore, this implies that the accretion event should have happened
+very recently from a time ago that is shorter than the \elem{Li} depletion time.
+
+It is further worth pointing out that measuring the \elem{Li} abundance
+with some of the refractory elements such as $\elem{Fe}$
+provides a way to estimate the time of the event.
+%exlain
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.8\linewidth]{toycalc.pdf}
+  \caption{Solar surface abundance change expected from adding $20~\mearth$ of
+    material with bulk Earth or CI chondrite composition.
+    The assumed mass fraction in the convective zone is $0.03$.
+    For bulk earth composition, which is a closer match to the abundance difference
+    seen in \bizarreone\ and \sunanalog, we indicate measured elements with black boundary
+    lines around symbols.
+  }
+  \label{fig:toycalc}
+\end{figure}
 
@@
 \figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
-comparision with this pair.
+comparison with this pair.
 
@@
 \citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
-with a projected separation of $\sim9000$~AU (correspoding to 4.2~arcmin sky separation).
+with a projected separation of $\sim9000$~AU (corresponding to 4.2~arcmin sky separation).
 Both stars in this system host close-in giant planets.

### 2017-05-26 paper/ms.tex
Use deluxetable and seperate file

@@
   Semyeong Oh\altaffilmark{\pu,\lead},
-  APW, JMB, KH, NL, DWH, DNS, JW
+  APW, JMB, KH, NL, DWH, DNS \etal\
 }
@@
 \begin{abstract}
-  We report and discuss the discovery of a co-moving pair of bright solar-type
+  We report and discuss the discovery of a comoving pair of bright solar-type
   stars, \sunanalog\ and \bizarreone\, with significant differences in their chemical
@@
 
-Here, we report and discuss the discovery of a co-moving pair of solar twin stars,
+Here, we report and discuss the discovery of a comoving pair of solar twin stars,
 HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
@@
 
+\input{kk.tex}
+
 Though previously recognized as a visual double star system
 (\citealt{2001AJ....122.3466M}), \sunanalog\ and \bizarreone\ were identified as a
-candidate co-moving star pair in our recent search for co-moving stars using the
+candidate comoving star pair in our recent search for comoving stars using the
 proper motions and parallaxes from the \tgas catalog, a component of \gaia\ \dr\
-(the astrometric measurements are listed in \tablename~\ref{tab:t2}).
+(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
 We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
@@
 of two components of the velocities (proper motions).
-We then select a sample of high-confidence co-moving star pairs by making a
+We then select a sample of high-confidence comoving star pairs by making a
 conservative cut on this likelihood ratio.
-In the resulting catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
+In the resulting catalog of comoving pairs (\citealt{2016arXiv161202440O}),
 the pair presented in this paper was assigned a group id of 1199,
@@
 well above the adopted cut value of 6.
-We have checked that we do not find any possible additional co-moving companions
+We have checked that we do not find any possible additional comoving companions
 by lowering the likelihood ratio cut for the stars around this pair.
@@
 Other stellar parameters derived from these spectra are included in
-\tablename~\ref{tab:t2}.
+\tablename~\ref{tab:kk}.
 
@@
 Galactocentric phase-space coordinates for the two stars.
-In all components, the pair is consistent with being co-moving and close in
+In all components, the pair is consistent with being comoving and close in
 separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
@@
 \end{figure}
-
-% ----------------
-% Horizontal table
-% ----------------
-% \begin{table*}[htpb]
-%   \centering
-%   \caption{Astrometric and spectroscopic measurements}
-%   \label{tab:t1}
-%   \begin{tabular}{cccccccccc}
-% \hline\hline
-% Name & Sp Type & $T_\mathrm{eff}$ & $\log{g}$ & $v\sin{i}$ & $[\elem{Fe}/\elem{H}]$ & $v_r$ &
-% $\varpi$ & $\mu_\alpha^*$ & $\mu_\delta$ \\
-% % units
-% \hline
-% HD 240429 & G2 & 5878 & 4.43 & 1.1 & 0.01 & $-21.2$  & $9.35 \pm 0.24$ & $89.25 \pm 0.66$ & $-29.68 \pm 0.54$\\
-% HD 240430 & G0 & 5803 & 4.33 & 2.5 & 0.20 & $-21.2$  & $9.41 \pm 0.25$ & $89.41 \pm 0.69$ & $-30.12 \pm 0.52$\\
-% \hline\hline
-% \end{tabular}
-% \end{table*}
-
-\begin{table*}[htpb]
-  \caption{Astrometric and spectroscopic measurements.}
-  \label{tab:t2}
-  \begin{threeparttable}
-  \centering
-  \begin{tabular}{ccc}
-\hline\hline
-Name & HD 240429 & HD 240430 \\
-\hline
-Sp Type                                   & G2                & G0                \\
-$T_\mathrm{eff}$                          & 5878              & 5803              \\
-$\log{g}$                                 & 4.43              & 4.33              \\
-$v\sin{i}$                                & 1.1               & 2.5               \\
-$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
-$v_r$                                     & $-21.2$           & $-21.2$           \\
-$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
-$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
-$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
-\hline
-\multicolumn{3}{c}{$T_c < 1200$~K} \\
-\hline
-$A(\elem{Li})$ \footnotemark[2]           & $2.25$            & $2.75$            \\
-$\elemH{C}$                               & $0.00$            & $0.09$            \\
-$\elemH{N}$                               & $-0.06$           & $-0.01$           \\
-$\elemH{O}$                               & $0.01$            & $0.09$            \\
-$\elemH{Na}$                              & $-0.06$           & $-0.04$           \\
-$\elemH{Mn}$                              & $-0.03$           & $0.00$            \\
-\hline
-\multicolumn{3}{c}{$T_c > 1200$~K} \\
-\hline
-$\elemH{Mg}$                              & $0.01$            & $0.19$            \\
-$\elemH{Al}$                              & $0.01$            & $0.21$            \\
-$\elemH{Si}$                              & $0.00$            & $0.16$            \\
-$\elemH{Ca}$                              & $0.02$            & $0.23$            \\
-$\elemH{Ti}$                              & $0.02$            & $0.20$            \\
-$\elemH{V}$                               & $0.02$            & $0.20$            \\
-$\elemH{Cr}$                              & $0.01$            & $0.17$            \\
-$\elemH{Fe}$                              & $0.01$            & $0.20$            \\
-$\elemH{Ni}$                              & $-0.01$           & $0.21$            \\
-$\elemH{Y}$                               & $0.04$            & $0.26$            \\
-\hline\hline
-\end{tabular}
-%
-\begin{tablenotes}
-  \item All spectroscopic measurements except $\elem{Li}$ are from \citealt{2016ApJS..225...32B}.
-  \footnotetext[1]{From \tgas. }
-  \footnotetext[2]{Absolute abundance from \todo{CITE}.}
-\end{tablenotes}
-  \end{threeparttable}
-\end{table*}
 
@@
 If the two stars are indeed only several hundred Myrs old at most,
-they are expected to be part of a larger co-moving group of stars.
-However, as we mention above, there is no evidence in our search of co-moving pairs
+they are expected to be part of a larger comoving group of stars.
+However, as we mention above, there is no evidence in our search of comoving pairs
 using \tgas\ that the two stars belong to a larger group of young stars.
@@
   \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the co-moving pair, \sunanalog\ and \bizarreone.}
+  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone.}
   \label{fig:abundances}
@@
 different, one may simply conclude that the two stars are not related (coeval)
-but they merely happen to be co-moving at such small separation ($\approx 0.6$~pc)
+but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
 by chance.
@@
 This is in fact exactly what we find: the Li abundance of \bizarreone\ is
-$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t2}, \todo{CITE JM?})
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \todo{CITE JM?})
 approximately $1.6$~dex higher than the solar value of $1.1$~dex.
@@
 provides a way to estimate the time of the event.
-%exlain
+If the observed \elem{Li} abundance is less than what is inferred from
+abundance differences of other elements, and
+we have a model of \elem{Li} depletion, the time of \elem{Li} enhancement
+may be calculated.
+
+What about \sunanalog?
+\sunanalog\ is also enhanced in \elem{Li} considering its age of $4.00_{-1.56}^{+1.51}$~Gyr
+than the nominal \elem{Li} depletion predics by $\approx 1$~dex.
+This enhancement puts an upper limit on the accreted mass to be \todo{$\approx 4$~\mearth}
+assuming \elem{Li} concentration of $1.1$~ppm (\citealt{mcdonough2001composition}).
+Unlike \bizarreone, we cannot know the pre-accretion abundances of \sunanalog.
+However, we note that the span of abundance difference between highly volatile elements
+(C, N, O, Na) and refractory elements such as \elem{Fe} expected from accreting
+\todo{$\approx 4$~\mearth} to the Sun is $\approx 0.05$~dex.
+This is comparable to the abundance difference between N, Na and Fe in \sunanalog.
+It is also interesting that \sunanalog\ also shows a deficit in the same
+volatile and moderately volatile elements (C, N, O, Na, and Mn) relative to Fe
+just as in \bizarreone.
+Thus, we conclude that \sunanalog\ is also likely to have had a similar
+accretion event, but the amount of accretion was much smaller than \bizarreone.
+
+We stress that
+% - these calculations are carried out with very simple and unverified assumptions
+% - uncertainties exist on the bulk Earth
 
@@
 star.
-With a claimed precision of $0.006$~dex (median among all elements), they
+With a claimed median uncertainty of $0.006$~dex among all elements, they
 detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
@@
 % Useful follow up efforts
+We discuss the follow up efforts that would be useful to further
+illuminate the peculiar abundance difference between the pair.
+
+\section{Summary}
+\label{sec:summary}
+
+We have reported and discussed the discovery of a comoving pair of bright solar-type stars
+HD~240430 and HD~240429 (G0 and G2)
+with very different metallicity ($\Delta\feh \approx 0.2$~dex),
+and a condensation temperature-dependent abundance difference.
 

### 2017-05-28 paper/ms.tex
Add text on other pair studies

@@
   We report and discuss the discovery of a comoving pair of bright solar-type
-  stars, \sunanalog\ and \bizarreone\, with significant differences in their chemical
+  stars, HD~240430 and HD~240429, with a significant difference in their chemical
   abundance patterns.
@@
 
-Wide binaries are valuable tools for studying star and planet formation as well as
-Galactic dynamics and chemical evolution.
+Wide binaries are valuable tools for studying star and planet formation as well
+as Galactic dynamics and chemical evolution.
 In the context of studying the evolution of the Milky Way, they are useful for
@@
 their statistics can be informative of the Galactic mass distribution.
-\todo{Give specific examples.}
-On the other hand, they are also a prime target to test the
-chemical tagging hypotheses that we may trace back a group of co-eval stars
-by detailed chemical abundance patterns as ``tag''s.
-A multiple-star system of any size that we believe are co-eval,
-with massive open clusters at one extreme, can serve this purpose.
+For example, the separation distribution of halo binaries has been
+used to constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
+On the other hand, they are also prime targets to test the chemical tagging
+hypothesis that stars of the same birthplace may be traced back by detailed
+chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
+A multiple-star system of any size that we believe are born together can serve this purpose,
+with massive open clusters at one extreme.
 Wide binaries are at the other extreme in that we may be less confident of
@@
 Independently, in efforts to connect the host star's chemistry to
-its planetary system, wide binaries with similar or very different planetary systems around
-component stars are very useful as chemical signatures related to planet formation or accretion
-can be revealed in a differential sense without any regard to Galactic chemical evolution
-as long as we assume that the two stars should have been born together with identical chemistry.
-\todo{Give examples and summary: Teske, Mack, Melendez.}
+its planetary system, wide binaries with similar or very different planetary architectures around
+the component stars are particularly useful as chemical signatures related to planet formation or accretion
+can be revealed in a differential sense without any regard to the Galactic chemical evolution
+as long as we assume that the two stars should have been born together with identical composition.
+For close-in giant planets, it has been established that the planet-metallicity relation
+is primordial, and that the enhanced metallicity in giant planet-hosting stars likely
+promoted the formation of giant planets (\citealt{Fischer:2005aa}) by increasing
+the availability of small particle condensates that forms planetesimals.
+On the other hand, if host stars are to be polluted after their birth
+by rocky planetary material with high refractory-to-volatile ratio,
+the convective envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
+compared to their initial state.
+Thus, differing planet formation or accretion in the two otherwise identical stars
+may imprint a difference of chemical abundances that depends on the
+condensation temperature (\Tcondens).
+Several systems in which at least one star hosts at least one planet
+have been studied so far with high resolution spectroscopy in this context
+(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
+  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
+The results and interpretations of these studies are varied:
+while some systems (e.g., HAT-P-1 (\citealt{Liu:2014aa}),
+HD~20782/1 (\citealt{Mack:2014aa}), HD~80606/7 (\citealt{Saffe:2015aa,Mack:2014aa});
+see also \citealt{Desidera:2004aa,Gratton:2001aa})
+found no difference, other studies (e.g., XO-2 (\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa}))
+have found a \Tcondens-dependent difference in abundance.
+The increasing difference of abundance with condensation temperature
+has been attributed both to more yet-undiscovered rocky planets around
+the relatively refractory-poor star and to late time accretion of
+refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}.
+% want to point out the former interpretation roots back to melendez+09
+% and some doubt to that interpretation...
 
-So far the strongest evidence for accretion of planetary material by host star comes
+So far the strongest evidence for accretion of planetary material by a host star comes
 from spectral analysis of polluted white dwarfs.
@@
 \sunanalog\ (HD~240429) throughout the \documentname.
-\todo{section summary}
-
-\todo{Explicit cautionary remark that Tc is just a proxy here?}
-%SMOH: I prefer in the relevant discussion.
+In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
+about the two stars relevant to the present discussion.
+In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
+the abundance difference between the pair.
+We summarize or discussions in \sectionname~\ref{sec:summary}.
 

### 2017-05-29 paper/ms.tex
Add text on WDs in intro

@@
 refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}.
-% want to point out the former interpretation roots back to melendez+09
+% maybe want to point out the former interpretation roots back to melendez+09
 % and some doubt to that interpretation...
@@
 So far the strongest evidence for accretion of planetary material by a host star comes
-from spectral analysis of polluted white dwarfs.
-\todo{Discuss Zuckerman, Klein}.
+from spectral analysis of polluted white dwarfs (WDs).
+Because the gravitational settling times of elements heavier than \elem{He} in
+atmosphere is much shorter than the WD cooling time essentially providing a
+clean slate for any sign of accretion, detection of metals indicates a
+reservoir of dusty material around the WD.
+Indeed, many of the polluted WDs have been shown to own a dusty disk detected
+in the infrared.
+Some of the most dramatically polluted WDs were revealed to have
+surface abundances closely matched by rocky planetary material
+indicated by e.g., bulk Earth composition, strongly arguing
+that the disk formed from tidally disrupted minor planets
+(\citealt{Zuckerman:2007aa,Klein:2010aa}).
+Recently, transit signals from small bodies orbiting around a polluted WD
+has been detected by \project{Kepler} adding further support to the picture
+(\citealt{2015Natur.526..546V}).
 

### 2017-05-29 paper/ms.tex
Add reference for yonsei-yale isochrone
Remove individual system listings in intro

@@
   Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
-The results and interpretations of these studies are varied:
-while some systems (e.g., HAT-P-1 (\citealt{Liu:2014aa}),
-HD~20782/1 (\citealt{Mack:2014aa}), HD~80606/7 (\citealt{Saffe:2015aa,Mack:2014aa});
-see also \citealt{Desidera:2004aa,Gratton:2001aa})
-found no difference, other studies (e.g., XO-2 (\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa}))
-have found a \Tcondens-dependent difference in abundance.
+The results and interpretations of these studies are varied: while some systems
+found no difference (see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
+studies  have found a \Tcondens-dependent difference in abundance.
 The increasing difference of abundance with condensation temperature
@@
 comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
-We perform isochrone fitting using the Yale-Yonsei model isocrones (\todo{CITE}).
+We perform isochrone fitting using the Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
 The input data are $\log(g)$, $T_\mathrm{eff}$, \feh, parallaxes, $B$-band magnitudes, and their errors.

### 2017-05-29 paper/ms.tex
Take care of minor todos and update planets for HD20782/1

@@
 on Keck~I telescope.
-The spectral resolution is \todo{$R\approx XXX$} and the wavelength coverage is \todo{$XXX-XXX$~\AA}.
+The spectral resolution is $R\approx 70000$ and the wavelength coverage is
+$5164-7799$~\AA.
+Typical signal-to-noise ratio in continuum is $>200$~per pixel.
 The resulting measurements include abundances measured for 15
@@
 \tablename~\ref{tab:kk}.
+For the details of the spectral analysis, we refer the readers to
+\citealt{2016ApJS..225...32B}.
 
@@
 \end{figure}
-
-\todo{Figure: posterior distributions of separation and delta V}
 
@@
 This is in fact exactly what we find: the Li abundance of \bizarreone\ is
-$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \todo{CITE JM?})
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
 approximately $1.6$~dex higher than the solar value of $1.1$~dex.
@@
 pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
-with moderately high eccentricity ($e\sim0.1-0.3$).
+with moderately high eccentricity ($e\sim0.1-0.3$)
+\footnote{The two stars were monitored by \project{HARPS} campaign, and it has recently
+  been reported by \citealt{} that HD~20781 hosts four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\
+  with $e \le 0.11$ within $\approx 0.35$~AU.}.
 They found that the abundances of 15 elements between the two stars are consistent with each other.

### 2017-06-01 paper/ms.tex
Remove otherstudies table; doubting its costeffectiveness
add boring title
enhance figure captions and restructure data (WIP)

@@
 
-\title{Kronos \& Krios: TBD}
+\title{Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair}
 
@@
 
-Though previously recognized as a visual double star system
-(\citealt{2001AJ....122.3466M}), \sunanalog\ and \bizarreone\ were identified as a
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.9\linewidth]{abundances.pdf}
+  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone\
+    normalized to \elem{H} (top) and \elem{Fe} (bottom).
+    Lines are drawn for each star only to guide the eye.
+    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to \sunanalog\
+    along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca}, \elem{Ti}, \elem{V},
+    \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
+  }
+  \label{fig:abundances}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
+  \caption{Difference in abundances of this pair and other wide binaries in
+    \citealt{2016ApJS..225...32B}.
+    Additionally, we show the distribution of abundance difference
+    between stars with similar metallicity difference
+    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
+    as violins with medians indicated by black line segments
+    by randomly pairing up single stars in \citealt{2016ApJS..225...32B} at two metallicity bins,
+    $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
+    similar to \bizarreone\ and \sunanalog.
+    The difference is always taken to be $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
+    Thus, the narrower range of in $\Delta\feh$ is by construction.
+    First, we see that most of the other comoving wide binaries included in \citealt{2016ApJS..225...32B}
+    have small ($<0.1$~dex) differences in all elements making a difference of $\approx 0.2$~dex seen in
+    \bizarreone-\sunanalog\ pair rare.
+    Second, random pairings of disk stars with similar $\Delta\feh$ usually show
+    similar enhancement in all other elements.
+    %Notably, the relative depletion of \elem{Na} and \elem{Mn} with respect to \elem{Fe}
+    %suggests that even when we assume \bizarreone\ and \sunanalog\ are of different origin,
+    %Galactic evolution cannot explain the difference.
+  }
+  \label{fig:deltaXH}
+\end{figure}
+
+\sunanalog\ and \bizarreone\ were identified as a
 candidate comoving star pair in our recent search for comoving stars using the
@@
 well above the adopted cut value of 6.
+The pair has also been previously recognized as a visual double star system
+in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
 We have checked that we do not find any possible additional comoving companions
@@
 
-In a separate effort to study detailed chemical abundances of
-potential planet-hosting stars, \citet{2016ApJS..225...32B}
-analyzed high resolution spectra of both stars obtained using HIRES spectrograph
-on Keck~I telescope.
+In a separate effort to study detailed chemical abundances of potential
+planet-hosting stars, \citet{2016ApJS..225...32B} analyzed high resolution
+spectra of both stars obtained using HIRES spectrograph on Keck~I telescope.
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is
@@
 Typical signal-to-noise ratio in continuum is $>200$~per pixel.
-The resulting measurements include abundances measured for 15
-chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
-well as high precision radial velocities.
-Other stellar parameters derived from these spectra are included in
-\tablename~\ref{tab:kk}.
+The resulting measurements include abundances measured for 15 chemical species
+(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
+and high precision radial velocities.
 For the details of the spectral analysis, we refer the readers to
 \citealt{2016ApJS..225...32B}.
+The \elem{Li} doublet at $6707.6$~\AA\ for this sample was
+investigated in a separate work (\citealt{jmlithium}).
+We list all spectroscopic measurements including
+the absolute abundance\footnote{
+  Absolute abundance of element \elem{X} is $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
+  where $n_\elem{X}$ is the number density of element \elem{X}.
+} of \elem{Li} for the two stars in Table~\ref{tab:kk}.
 
-Combining these precise radial velocities with the \gaia\ astrometry, we can
-compare differences between the inferred 6D phase-space properties for the
-two stars.
-We start by generating posterior samples over the Heliocentric distance, $r$,
-tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
-given the observed parallax, $\pi$, and proper motion components,
-$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
-By defining the vectors
-% SMOH: I understand you meant hat v_r as the latent true radial velocity but
-% personally think a) it can confuse some people that there are hat quantities
-% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
-% quantities for observed variables and no-hat for latent true ones.
-% SMOH: v_r is missing in the LHS of eq(3)
-\begin{eqnarray}
-  \vec{y} &=&
-      \transp{\left(
-        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
-          \pi &
-          \mu_{\alpha^*} &
-          \mu_\delta &
-          v_r
-        \end{array}
-      \right)}\\
-  \hat{\vec{y}} &=&
-      \transp{\left(
-        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
-          r^{-1} &
-          r^{-1}\,v_\alpha &
-          r^{-1}\,v_\delta &
-          \hat{v}_r
-        \end{array}
-      \right)}
-\end{eqnarray}
-and by considering the covariance matrix $\mat{C}$ between the observed
-quantities (provided by \tgas\ and extended to include the uncorrelated radial
-velocity uncertainty), the likelihood can be written
-\begin{eqnarray}
-p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
-  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
-    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
-    \mat{C}^{-1} \,
-    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
-\end{eqnarray}
-We adopt a uniform space density prior for the distance and an isotropic
-Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
-\begin{eqnarray}
-p(r) &=&
-  \begin{cases}
-    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
-    0              & \text{otherwise}
-  \end{cases}\\
-p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
-  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
-\end{eqnarray}
-For each of the two stars, we use \project{emcee}
-(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
-v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
-first 512 steps as the burn-in period.
-For each sample, we convert the heliocentric phase-space coordinates into
-Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
-= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
-etc.}).
-\figname~\ref{fig:dxdv} shows differences in posterior samples converted to
-Galactocentric phase-space coordinates for the two stars.
-In all components, the pair is consistent with being comoving and close in
-separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
-but the median 3-space separation is $\approx$$0.6~\pc$.
+%In all components, the pair is consistent with being comoving and close in
+%separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
+%but the median 3-space separation is $\approx$$0.6~\pc$.
 
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
-  \end{center}
-  \caption{%
-    Differences in posterior samples over Galactocentric phase-space coordinates
-    for the two stars \sunanalog\ and \bizarreone.
-    \label{fig:dxdv}}
-\end{figure}
+%\begin{figure}[htbp]
+%  \begin{center}
+%    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
+%  \end{center}
+%  \caption{%
+%    Differences in posterior samples over Galactocentric phase-space coordinates
+%    for the two stars \sunanalog\ and \bizarreone.
+%    \label{fig:dxdv}}
+%\end{figure}
 
-\figname~\ref{fig:orbit} shows an orbit computed from the median posterior
-sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
-in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
-explain}
-The Sun's orbit in this same Milky Way model is under-plotted for comparison
-(grey line); the orbits of the stars in this pair have large scale-heights
-relative to the Sun's orbit despite being young.
+%\figname~\ref{fig:orbit} shows an orbit computed from the median posterior
+%sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
+%in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
+%explain}
+%The Sun's orbit in this same Milky Way model is under-plotted for comparison
+%(grey line); the orbits of the stars in this pair have large scale-heights
+%relative to the Sun's orbit despite being young.
 
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{orbits.pdf}
-  \end{center}
-  \caption{%
-    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
-    For \sunanalog\, the initial conditions are set to the median posterior
-    sample over the inferred 6D phase-space coordinates.
-    The orbits are computed by integrating backwards from the present-day
-    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
-    Leapfrog integration scheme implemented in \project{Gala}
-    (\citealt{Gala:2017}). \todo{APW: citation...}
-\label{fig:orbit}}
-\end{figure}
+%\begin{figure}[htbp]
+%  \begin{center}
+%    \includegraphics[width=\linewidth]{orbits.pdf}
+%  \end{center}
+%  \caption{%
+%    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
+%    For \sunanalog\, the initial conditions are set to the median posterior
+%    sample over the inferred 6D phase-space coordinates.
+%    The orbits are computed by integrating backwards from the present-day
+%    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
+%    Leapfrog integration scheme implemented in \project{Gala}
+%    (\citealt{Gala:2017}). \todo{APW: citation...}
+%\label{fig:orbit}}
+%\end{figure}
 
-Given their proximity in space and kinematics,
-it is generally accepted to assume that the two stars were born coeval
-perhaps in a wide binary from the same birth cloud.
-Thus, we expect the two stars to have identical metallicities and abundance patterns,
-\todo{except for thoese elements like Li...}
-Surprisingly, one of the stars, \bizarreone\ is significantly more metal
+Although selected based only on their proper motions, the two stars
+have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
+confirming that they are comoving in all directions.
+The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
+and the 3D separation is $\approx 0.6$~pc.
+Given their proximity in phase space, it is generally accepted to assume that
+the two stars were born together perhaps to form a wide binary system from the
+same birth cloud.
+Thus, we expect the two stars to have identical metallicities and abundance patterns.
+Surprisingly, however, one of the stars, \bizarreone\ is significantly more metal
 rich than the other by 0.2~dex ($\approx 60\%$; \figname~\ref{fig:abundances}).
-What is more puzzling is that the abundances of this star
-shows selective depletion in C, N, O, Na, and Mn.
+What is more puzzling is that not all elements are equally enhanced:
+the abundances of \bizarreone\ shows selective depletion in
+\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
+relative to \elem{Fe}.
 
-The abundance of \bizarreone\ is peculiar on its own compared to other disk stars with
-similar $[\elem{Fe}/\elem{H}]$.
-For a star with $[\elem{Fe}/\elem{H}] \approx 0.2$, we generally expect
-$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
-(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\ ever more unlikely.
-We stress that none of the other seven binary pairs examined in \citealt{2016ApJS..225...32B}
-show discrepancies in abundances between the stars at this level.
+The validity of the measured abundance differences is further demonstrated
+in \figname~\ref{fig:spec1} and \ref{fig:spec2} where we show
+segments of the spectra and model of the two stars.
+As expected from metallicity difference ($\Delta\feh \approx 0.2$),
+the ratio of data and model between the two stars show significant
+residuals of almost all metal features, largely dominated by \elem{Fe}.
+However, for lines of elements that are not as enhanced in \bizarreone\,
+the residuals are much smaller in amplitude.
+%Li?
+
+We stress that none of the other four twin-like ($\Delta T_mathrm{eff} \lesssim 100$~K)
+wide binary pairs examined in \citealt{2016ApJS..225...32B} show discrepancies in abundances between the
+stars at this level (\figname~\ref{fig:deltaXH}).
+As shown in \figname~\ref{fig:deltaXH}, 
 In fact, no strong trend is found in pair for most elements
@@
 (see figure X in that paper; purple is this pair)
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{isochrones.png}
-  \caption{Isochrone ages of \sunanalog\ and \bizarreone.
-    On the left, we show the two stars on $T_\mathrm{eff}-\log(g)$ plane,
-    and on the right, the color-magnitude diagram using \gaia\ $G$ band
-    and \tmass\ $J$ band magnitudes.
-    In each panel, \project{MIST} isochrones (\citealt{Choi:2016aa}) at $28$~Myr and $2$~Gyr are
-    plotted. The thicker and thinner lines are for $\feh = 0.$ and $0.2$,
-    corresponding to values of \sunanalog\ and \bizarreone.
-  }
-  \label{fig:isochrones}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.8\linewidth]{sed.png}
-  \caption{Spectral energy distributions (SEDs) of \sunanalog\ and \bizarreone.
-    The yellow line is the SED of a blackbody at $T=5878$ scaled arbitrarily.
-  }
-  \label{fig:sed}
-\end{figure}
+Moreoever, the abundance differences cannot be due to different chemical enrichment
+history in the disk even if the two stars were of different origin.
+\figname~\ref{fig:deltaXH} shows the distribution of $\Delta[\elem{X}/\elem{H}]$
+for random pairings of two stars from similar \feh\ as \bizarreone\ and \sunanalog
+as violins for each element.
+We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
+all other elements are enhanced at a similar level with some variations.
+% Clean up:
+% Specifically, it is very unlikely that the star 
+% The abundance of \bizarreone\ is peculiar on its own compared to other disk
+stars with similar \feh.
+%For a star with $\feh \approx 0.2$ like \bizarreone, we generally expect
+%$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
+%(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\
+%very unlikely to arise from Galactic chemical evolution.
 
 The fact that the two stars share a very similar space motion
-at a separation of $0.6$~pc strongly argues that the pair is coeval.
+at a separation of $\approx 0.6$~pc strongly argues that the pair is coeval.
 We consider other age indicators apart from their phase space coordinates
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone.}
-  \label{fig:abundances}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
   \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
@@
     relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
-    as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
+    ranked by the condensation temperature of elements in solar composition gas
+    from \citealt{2003ApJ...591.1220L}.
+    We show three wide binary systems selected from the literature:
+    HD~20782/1 (\citealt{Mack:2014aa}), XO-2N/S (\citealt{Biazzo:2015aa}),
+    and WASP-94AB (\citealt{Teske:2016aa}).
+    Note that multiple values are reported 
   }
   \label{fig:relabun_tcrank}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.9\linewidth]{deltaXH_Tc_violins.png}
-  \caption{Difference in abundances of this pair and other binary pairs in
-    \citealt{2016ApJS..225...32B}.
-    Additionally, we show the distribution of abundance difference
-    between stars with similar metallicity difference
-    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
-    as violins with medians indicated by black line segments
-    by randomly pairing up single stars at two metallicity bins similar to
-    the pair of interest.
-    The difference is always relative to the lower-$[\elem{Fe}/\elem{H}]$ star.
-  }
-  \label{fig:deltaXH}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{toycalc.pdf}
-  \caption{Solar surface abundance change expected from adding $20~\mearth$ of
-    material with bulk Earth or CI chondrite composition.
+  \includegraphics[width=0.95\linewidth]{toycalc.pdf}
+  \caption{Expected change in solar surface abundance after adding $20~\mearth$ of
+    material with bulk Earth composition (\citealt{mcdonough2001composition}).
     The assumed mass fraction in the convective zone is $0.03$.
-    For bulk earth composition, which is a closer match to the abundance difference
-    seen in \bizarreone\ and \sunanalog, we indicate measured elements with black boundary
-    lines around symbols.
+    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
+    suggests that the abundance difference may be due to accretion of
+    $20~\mearth$ of rocky planetary material.
+    We elements measured for \bizarreone-\sunanalog\ pair are filled with purple
+    while those without measurements are left empty.
   }
@@
 \end{figure}
-
-\input{otherstudies.tex}
 
@@
 WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
-Main properties of the systems relevant to the present discussion are
-summarized in \tablename~\ref{tab:otherstudies}.
 Their reported abundance differences $\Delta\elemH{X}$ where the difference is
@@
 
-% Useful follow up efforts
-We discuss the follow up efforts that would be useful to further
-illuminate the peculiar abundance difference between the pair.
-
 \section{Summary}
@@
 % Concluding remarks
+% include Useful follow up efforts
 

### 2017-06-02 paper/ms.tex
Clean up data section

@@
   \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone\
+  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
     normalized to \elem{H} (top) and \elem{Fe} (bottom).
     Lines are drawn for each star only to guide the eye.
-    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to \sunanalog\
-    along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca}, \elem{Ti}, \elem{V},
-    \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
+    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
+    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
+    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
+    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
   }
@@
   \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
-  \caption{Difference in abundances of this pair and other wide binaries in
+  \caption{Abundance difference in this pair and other twin-like
+    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
     \citealt{2016ApJS..225...32B}.
-    Additionally, we show the distribution of abundance difference
+    The differences in other pairs are small ($<0.05$~dex)
+    for all elements except \elem{N} and \elem{O} which are the most
+    uncertain, making the difference of $\approx 0.2$~dex seen in
+    \bizarreone-\sunanalog\ rare.
+    Additionally, we show the distribution of abundance differences
     between stars with similar metallicity difference
@@
     Thus, the narrower range of in $\Delta\feh$ is by construction.
-    First, we see that most of the other comoving wide binaries included in \citealt{2016ApJS..225...32B}
-    have small ($<0.1$~dex) differences in all elements making a difference of $\approx 0.2$~dex seen in
-    \bizarreone-\sunanalog\ pair rare.
-    Second, random pairings of disk stars with similar $\Delta\feh$ usually show
-    similar enhancement in all other elements.
-    %Notably, the relative depletion of \elem{Na} and \elem{Mn} with respect to \elem{Fe}
-    %suggests that even when we assume \bizarreone\ and \sunanalog\ are of different origin,
-    %Galactic evolution cannot explain the difference.
+    Random pairings of disk stars with similar $\Delta\feh$ usually show
+    similar enhancement in all other elements
+    unlike the pattern seen in \bizarreone-\sunanalog\ pair.
   }
@@
 
-%In all components, the pair is consistent with being comoving and close in
-%separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
-%but the median 3-space separation is $\approx$$0.6~\pc$.
-
-%\begin{figure}[htbp]
-%  \begin{center}
-%    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
-%  \end{center}
-%  \caption{%
-%    Differences in posterior samples over Galactocentric phase-space coordinates
-%    for the two stars \sunanalog\ and \bizarreone.
-%    \label{fig:dxdv}}
-%\end{figure}
-
-%\figname~\ref{fig:orbit} shows an orbit computed from the median posterior
-%sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
-%in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
-%explain}
-%The Sun's orbit in this same Milky Way model is under-plotted for comparison
-%(grey line); the orbits of the stars in this pair have large scale-heights
-%relative to the Sun's orbit despite being young.
-
-%\begin{figure}[htbp]
-%  \begin{center}
-%    \includegraphics[width=\linewidth]{orbits.pdf}
-%  \end{center}
-%  \caption{%
-%    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
-%    For \sunanalog\, the initial conditions are set to the median posterior
-%    sample over the inferred 6D phase-space coordinates.
-%    The orbits are computed by integrating backwards from the present-day
-%    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
-%    Leapfrog integration scheme implemented in \project{Gala}
-%    (\citealt{Gala:2017}). \todo{APW: citation...}
-%\label{fig:orbit}}
-%\end{figure}
-
 Although selected based only on their proper motions, the two stars
@@
 
-We stress that none of the other four twin-like ($\Delta T_mathrm{eff} \lesssim 100$~K)
-wide binary pairs examined in \citealt{2016ApJS..225...32B} show discrepancies in abundances between the
-stars at this level (\figname~\ref{fig:deltaXH}).
+We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
+\lesssim 100$~K) wide binary pairs examined in \citealt{2016ApJS..225...32B}
+show discrepancies in abundances between the stars at this level.
 As shown in \figname~\ref{fig:deltaXH},
-In fact, no strong trend is found in pair for most elements
-except N and Y.
-For Y, the trend for this pair is opposite of the others in Teff.
-Specifically, no difference within pair is found for Mn.
-(see figure X in that paper; purple is this pair)
+the differences in other pairs for all elements except \elem{N} and \elem{O},
+which are also the most uncertain (\tablename~\ref{tab:kk})
+are less than $0.05$~dex, makiing \bizarreone-\sunanalog\ pair an outlier.
 Moreoever, the abundance differences cannot be due to different chemical enrichment
 history in the disk even if the two stars were of different origin.
-\figname~\ref{fig:deltaXH} shows the distribution of $\Delta[\elem{X}/\elem{H}]$
-for random pairings of two stars from similar \feh\ as \bizarreone\ and \sunanalog
+\figname~\ref{fig:deltaXH} additioanlly shows the distribution of $\Delta[\elem{X}/\elem{H}]$
+for random pairings of two stars with similar \feh\ as \bizarreone\ and \sunanalog
 as violins for each element.
@@
 all other elements are enhanced at a similar level with some variations.
-% Clean up:
-% Specifically, it is very unlikely that the star 
-% The abundance of \bizarreone\ is peculiar on its own compared to other disk
-stars with similar \feh.
-%For a star with $\feh \approx 0.2$ like \bizarreone, we generally expect
-%$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
-%(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\
-%very unlikely to arise from Galactic chemical evolution.
+Specifically, for a typical star with $\elem{Fe} \approx 0.2$~dex,
+we generally expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
+(\citealt{Battistini:2015aa,Bensby:2003aa})
+making the low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$ seen in \bizarreone\
+very unlikely to arise from variations in Galactic chemical evolution.
+
+% HOGG to provide some theoretical account adding to the above empirical evidence.
 
@@
 
-Surface lithium abundance in a sun-like star decreases with its age
-due to mixing induced by convection or rotation, which brings the lithium
-into the interior ($T>2.5 \times 10^{6}$~K)
-where it will be destroyed by proton capture burning.
+Surface lithium abundance in a sun-like star decreases with its age due to
+mixing induced by convection or rotation, which brings the lithium into the
+interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
+burning.
 Thus, surface lithium abundance is an indicator of stellar ages.
-The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
-according to the theoretical models tuned to explain the solar lithium abundance
-and rotational profile (\citealt{2005Sci...309.2189C}).
-The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
-showing the largest difference among all measured elements.
+The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim
+1$~Gyr according to the theoretical models tuned to explain the solar lithium
+abundance and rotational profile (\citealt{2005Sci...309.2189C}).
+The lithium abundance of \bizarreone\ is still higher by $0.5$~dex showing the
+largest difference among all measured elements.
 This translates to $\sim 500$~Myr difference in age.
-Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
-it is unclear, however, whether this higher $\elem{Li}$ abundance
-means a younger age or something else.
-For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
-to the engulfment of substellar companions such as gas giant planets or brown dwarfs
-which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
+Given the overall higher metal abundances and the peculiar abundance patterns
+in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
+abundance means a younger age or something else.
+For example, the presence of $\elem{Li}$-rich red giant stars has been
+attributed to the engulfment of substellar companions such as gas giant planets
+or brown dwarfs which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
 
@@
 We have looked for these signs for the pair to find none, and their spectral energy
-distribution is consistent with blackbody.
+distributions are consistent with blackbody.
 The low $v\sin(i)$ values also argue against very young ages inferred from the
 surface lithium abundances.
-% TODO: ref for vertical action as age?
-Finally, their fiducial orbit in a Milky Way-like potential show that the vertical action
-for this pair is larger than the Sun, favoring an older age.
-We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main sequence
-stars, and that their unusually high \elem{Li} abundance requires an alternative explanation.
+% TODO: reference for vertical action as age?
+Finally, the pair's fiducial orbit in a axisymmeric Milky Way-like potential
+has a vertical action larger than the Sun, favoring an older age.
+We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main
+sequence stars, and that their unusually high \elem{Li} abundance requires an
+alternative explanation.
 
@@
 
-We discuss the possible origins of this pair.
-Let us first consider scenarios in which the two stars are not actually born together.
+We discuss the possible origins of the peculiar abundance differences of
+\bizarreone-\sunanalog.
+Although the data described above strongly suggests that the two stars are
+coeval, let us first consider scenarios in which the two stars are not actually
+born together.
 
@@
 
-In regions where binarity fraction is high, binary-binary scattering may be more important
-than binary-single scattering (\todo{CITE})
+%LEIGH
 

### 2017-06-05 paper/ms.tex
Clean up preamble; add affiliations

@@
 % ----------
-% - Add references and uncertainties to Table 1
+% - Add items here.
 
@@
 % - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
+% - Use "comoving" instead of "co-moving".
+% - Write elements as \elem{X}.
 
-\include{gitstuff}
 \include{aastexmods}
@@
 
-\title{Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair}
+\title{
+  Kronos \& Krios:
+  Evidence for accretion of massive, rocky planetary system in a sun-like pair
+}
 
@@
   Semyeong Oh\altaffilmark{\pu,\lead},
-  APW, JMB, KH, NL, DWH, DNS \etal\
+  Adrian M. Price-Whelan\altaffilmark{\pu},
+  John M. Brewer\altaffilmark{\yale},
+  Keith A. Hawkins\altaffilmark{\columbia},
+  Nathan W. C. Leigh\altaffilmark{\amnh},
+  David W. Hogg\altaffilmark{\ccpp,\mpia,\cca},
+  David N. Spergel\altaffilmark{\pu,\cca},
+  Justin Myles\altaffilmark{\yale} \etal\
 }
@@
 \newcommand{\lead}{2}
-\newcommand{\ccpp}{3}
-\newcommand{\mpia}{4}
-\newcommand{\cca}{5}
+\newcommand{\yale}{3}
+\newcommand{\columbia}{4}
+\newcommand{\amnh}{5}
+\newcommand{\ccpp}{6}
+\newcommand{\mpia}{7}
+\newcommand{\cca}{8}
 
 \altaffiltext{\pu}{Department of Astrophysical Sciences,
-                   Princeton University, Princeton, NJ 08544, USA}
+  Princeton University, 4 Ivy Ln, Princeton, NJ 08544, USA}
 \altaffiltext{\lead}{To whom correspondence should be addressed:
   \texttt{semyeong@astro.princeton.edu}}
+\altaffiltext{\columbia}{Department of Astronomy,
+  Columbia University, 550 W 120th St, New York, NY 10027, USA}
+\altaffiltext{\yale}{Department of Astronomy,
+  Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
+\altaffiltext{\amnh}{Department of Astrophysics,
+  American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
 \altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
@@
   K\"onigstuhl 17, D-69117 Heidelberg, Germany}
-\altaffiltext{\cca}{Center for Computational Astrophysics, 162 5th Ave, New York, NY 10003, USA}
+\altaffiltext{\cca}{Center for Computational Astrophysics,
+  Flatiron Institute, 162 5th Ave, New York, NY 10003, USA}
 

### 2017-06-05 paper/ms.tex
Restructure tex and paper
- Add text to discussion and summary.
- Move figures and paragraphs around.
- Figure captions enhanced.

@@
 the relatively refractory-poor star and to late time accretion of
-refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}.
+refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
 % maybe want to point out the former interpretation roots back to melendez+09
@@
     Additionally, we show the distribution of abundance differences
-    between stars with similar metallicity difference
+    between field stars with similar metallicity difference
     ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
-    as violins with medians indicated by black line segments
-    by randomly pairing up single stars in \citealt{2016ApJS..225...32B} at two metallicity bins,
+    as violins with medians indicated by black line segments.
+    These are random pairings of single stars in 
+    in \citealt{2016ApJS..225...32B} at two metallicity bins,
     $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
     similar to \bizarreone\ and \sunanalog.
-    The difference is always taken to be $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
+    The difference is always taken to be
+    $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
     Thus, the narrower range of in $\Delta\feh$ is by construction.
@@
   \label{fig:deltaXH}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec1.pdf}
+  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
+    Alternating sets of two rows show
+    the continuum-normalized data and model in the upper panel,
+    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
+    in the lower panel.
+  }
+  \label{fig:spec1}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec2.pdf}
+  \caption{Same as \figname~\ref{fig:spec1}
+    but for smaller portions of spectra at longer wavelengths that are
+    not dominated by \elem{Fe}.
+    We mark elements that give rise to strong lines.
+    The feature in the third column of the second row is a strong \elem{Li}
+    line that was not modeled by \citealt{2016ApJS..225...32B}. This line was
+    studied in a separate work (\citealt{jmlithium}).
+    Note that the lines of \elem{Na} and \elem{O} which are under-enhanced
+    in \bizarreone\ relative to \elem{Fe} or other refractory elements
+    show weaker residuals.
+  }
+  \label{fig:spec2}
 \end{figure}
@@
 \figname~\ref{fig:deltaXH} additioanlly shows the distribution of $\Delta[\elem{X}/\elem{H}]$
-for random pairings of two stars with similar \feh\ as \bizarreone\ and \sunanalog
+for random pairings of two stars with similar \feh\ as \bizarreone\ and \sunanalog\
 as violins for each element.
@@
 % TODO: reference for vertical action as age?
-Finally, the pair's fiducial orbit in a axisymmeric Milky Way-like potential
+Finally, the pair's fiducial orbit in a axisymmetric Milky Way-like potential
 has a vertical action larger than the Sun, favoring an older age.
@@
   \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
-  \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
-    relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
-    ranked by the condensation temperature of elements in solar composition gas
+  \caption{Abundance difference of \bizarreone-\sunanalog\ pair
+    ranked by the condensation temperature of elements for solar composition gas
     from \citealt{2003ApJ...591.1220L}.
+    The condensation temperature may be read from the gray line and right y-axis.
     We show three wide binary systems selected from the literature:
-    HD~20782/1 (\citealt{Mack:2014aa}), XO-2N/S (\citealt{Biazzo:2015aa}),
-    and WASP-94AB (\citealt{Teske:2016aa}).
-    Note that multiple values are reported 
+    HD~20782/1 (\citealt{Mack:2014aa}, $\feh\approx0$),
+    XO-2N/S (\citealt{Biazzo:2015aa}, $\feh\approx0.35$),
+    and WASP-94AB (\citealt{Teske:2016aa}, $\feh\approx0.3$).
+    Locations of elements with at least one measurement from any study
+    are indicated by a vertical line and its symbol.
+    Note that often multiple values are reported for one element corresponding
+    to different ionization states in equivalent width analyses.
+    No other pair studied so far were shown to have such large difference
+    in metallicity or sharp contrast between (moderately-)volatile and
+    refractory elements as \bizarreone-\sunanalog.
   }
@@
   n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
-  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
+  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
 \end{eqnarray}
@@
 may be much larger.
-However, even in such scenario, the age difference of $\sim 500$~Myr is too large
-for two stars of the same star forming region.
+However, this, or any other exchange scattering scenario,
+is still unsatisfactory as it offers no insight on the
+peculiarity of the abundances of \bizarreone\ (see
+\sectionname~{\ref{sec:data}}).
+In case that the pair formed from an exchange scattering event,
+we would expect the pair to be composed of typical field stars,
+not one with such low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$.
 
-%LEIGH
+%LEIGH to fill in binary-binary exchange scattering?
 
-%Two factors that make this even more unlikely are that both stars are very young given their large Li,
-%and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
-%not HD30 with anomalous abundance patterns.
-
-None of the above scenarios is satisfactory as they offer no
-insight on the peculiarity of the abundances of \bizarreone\
-(see \sectionname~{\ref{sec:data}}).
-In case that the pair formed from a exchange scattering event,
-we would expect the pair to be composed of typical field stars.
-The unlikeliness of the above possibilities naturally leads us to
-consider the alternative.
-What can selectively enrich refractory (high $T_C$) elements
-in one of the two stars that are born together?
+The unlikeliness of the above possibilities naturally leads us to consider the
+alternative that their peculiar disparity in chemical abundance space may be
+more naturally explained.
 
@@
 It may be that the two stars are born at the same time from the same cloud, but
-there is inhomogeneity within the cloud.
+there is chemical inhomogeneity within the cloud.
 However, there is already ample amount of evidence against such scenario.
-First, none of the other seven similar wide binaries examined in \citealt{2016ApJS..225...32B}
-show the same level differences in abundances although there is generally
-a larger spread in $\elem{C}$, $\elem{N}$ and $\elem{O}$, and some pairs show
-a large as $\approx 0.15$~dex difference in particular elements.
-The median and maximum \feh\ difference between component stars in the other seven pairs
-is $0.02$~dex and $0.09$~dex, respectively.
-This is consistent with the findings of \citealt{Desidera:2004aa}, who examined 23 wide binaries
-of late F to K dwarfs, and found most pairs show difference in \feh\ less than $0.02$~dex
-and none larger than $0.07$~dex.
+First, none of the other seven similar wide binaries examined in
+\citealt{2016ApJS..225...32B} show the same level differences in abundances
+although there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
+$\elem{O}$, and some pairs show a large as $\approx 0.15$~dex difference in
+particular elements.
+The median and maximum \feh\ difference between component stars in the other
+seven pairs is $0.02$~dex and $0.09$~dex, respectively.
+The differences are even smaller (maximum $\Delta\feh = 0.03$~dex)
+if we compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs.
+This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
+23 wide binaries of late F to K dwarfs, and found most pairs show difference in
+\feh\ less than $0.02$~dex and none larger than $0.07$~dex.
+Similarly \citealt{Gratton:2001aa} found that four out of six equal mass binaries
+have the same chemical composition with $\gtrsim 0.01$~dex uncertainties.
+Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair
+cannot be due to chemical inhomogeneity in the birth cloud.
 
 % rocky planets (or the like) engulfment
-Yet another possibility that may change a star's surface abundance after formation
-is accretion of its planets or asteroids.
-Instabilities may develop in a multi-planet system due to chaotic
-nature of many body system, which may lead to planet engulfment by the host star.
+Yet another more exotic possibility is that a star's surface abundance may
+be altered by accretion of planetary material after birth.
+Instabilities may develop in a multi-planet system due to its chaotic nature
+which may lead to planet engulfment or ejection by the host star.
+%TODO: needs references
+% kozai?
+Indeed, it is an important goal of many exoplanet studies
+to detect chemical signatures of planet formation or accretion,
+distinguish them from Galactic chemical evolution, and
+connect them to theories of evolution of planetary systems.
+One approach that is free from confusion with Galactic chemical evolution
+is to compare two almost identical stars in a wide binary system,
+which are assumed to be born together.
 
-One informative proxy that may reveal the composition of the hypothetical material
-that was accreted to the stars is the condensation temperature.
+%One proxy that is informative of the composition of the material
+%that was hypothetically accreted to a star is the condensation temperature (\Tcondens).
+% TODO: why?
 
-Present the relative abundance figure here
+Only a handful of wide binary systems have been studied with high-resolution
+spectroscopy in their detailed chemical abundances so far.
+These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
+WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
+We first review and summarize the studies of these systems focusing on key
+characteristics of stars and planets, and interpretation of any trend in
+$\Delta\elemH{X}$.
+These studies commonly look for
+%TODO: needs to include **16 Cyg** and HD~133131AB
 
+{\bf HD~20782/HD~20782:} 
+\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
+stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
+4.2~arcmin sky separation). Both stars in this system host close-in giant
+planets.
+HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
+orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
+Neptune-mass planets within 0.3~AU with moderately high eccentricity
+($e\sim0.1-0.3$) \footnote{
+  The two stars were monitored by \project{HARPS}
+  campaign, and it has recently been reported by \citealt{} that HD~20781 hosts
+  four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
+  0.11$ within $\approx 0.35$~AU.}.
+They found that the abundances of 15 elements between the two stars are
+consistent with each other.
+However, they argued that there is a moderately significant ($\sim 2\sigma$)
+positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
+{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
+(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
+of their measurements).
+They interpreted that this slope may be evidence for accretion of
+$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
+planet migration.
+
+{\bf HAT-P-1:}
+HAT-P-1 is a pair of G0 stars separated 11\arcsec\ apart in sky
+with $\feh\approx0.15$.
+The secondary star in the system is known to host one transiting giant planet
+while no planet has been discovered around the primary star.
+\citealt{Liu:2014aa} found that the two stars are identical in their
+atmospheric composition: \feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for
+the primary and secondary respectively, and $\Delta\elem{X}/\elem{Fe}$ is
+consistent with zero for 23 elements measured with the mean error being
+$0.013$~dex.
+Based on this analysis, they concluded that the presence of close-in giant planet
+does not necessarily lead to stellar atmospheric pollution of the host star.
+
+{\bf HD~80606/HD~80607:}
+A pair of G5 stars with super-solar metallicity ($\feh \approx 0.35$),
+HD 80606/HD 80607, has been independently studied by
+\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
+spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
+on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
+planets.
+Both studies have concluded that there is no significant
+chemical difference between the two stars similar to the case of HAT-P-1.
+
+{\bf XO-2N/XO-2S:}
+The double star system XO-2 has received much attention due to
+possibly the most robust and significant difference between the component stars
+among those so far studied.
+XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
+each hosting planet(s).
+XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
+masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
+0.15$) orbits at $<0.5$~AU.
+
+The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
+essentially no significant difference in Fe, Ni, C, and O between the two
+stars.
+However, re-analysis of the system by the same authors using the same data in
+\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
+\Tcondens\ varies significantly depending on the stellar parameters chosen in
+their analysis. Both analyses were based on spectra
+using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
+covering $4450-5660$~\AA\ and $5860-7100$~\AA\ with S/N of $170-230$
+(\citealt{Teske:2013aa}).
+
+Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
+$4080-8300$~\AA) of the component stars with S/N of $350$ (in $5000-7500$~\AA)
+to perform a differential abundance analysis.
+They find that all 23 elements including Fe are enhanced in XO-2N
+compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
+a significant correlation with \Tcondens.
+At low \Tcondens, volatile elements differ by $0.015$~dex
+while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
+There are inconsistencies in the determination of stellar parameters
+(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
+and photometric analysis,
+but the existence of correlation between $\Delta\elem{H}$ and
+\Tcondens\ seems robust.
+
+\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
+in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
+giant planets around XO-2S, following a similar interpretation of
+\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
+In this scenario, forming planets in the protoplanetary disk are supposed to
+``lock'' heavier elements to the core of gas giant planets as well as some
+volatile elements in their envelopes. Then, the host star will accrete {\it
+  gas} depleted in metals compared to their protostellar condition.
+By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
+of gas occurs in terms of how much mass is in the convective envelop then, they
+can match the mass difference of gas giant planets around each star, which is
+at least $1~\mjupiter$.
+On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
+\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
+Earth and CM chondrite-like material can explain the trend either as refractory
+{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
+refractory enhancement in XO-2N by late time accretion in which case the
+complete opposite would be true.
+
+Finally, \citealt{Biazzo:2015aa}
+
+{\bf WASP-94A/WASP-94B:} 
+\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
+with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
+host a hot Jupiter.
+The planet hosted by WASP-94A is transiting with a misaligned, probably
+retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
+more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
+star.
+With a claimed median uncertainty of $0.006$~dex among all elements, they
+detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
+elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
+1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
+Excluding K, which is based on one strong line and largely affected by non-LTE
+effect, their analysis shows a statistically significant non-zero slope between
+$\Delta\elemH{X}$ and $\Tcondens$\footnote{
+  %TODO: double check the following statement
+  Note that the condensation
+  temperature $\Tcondens$ used is for solar system composition
+  gas, which can differ from that of higher metallicity gas.}.
+They considered multiple possibilities related to the formation and evolution
+of planetary systems around each star as well as causes unrelated to planets
+such as dust cleansing during the fully convective phase or different rotation
+and granulation between the stars, but did not favor any particular one.
+
+We now turn to \bizarreone-\sunanalog\ pair.
+In Figure~\ref{fig:relabun_tcrank}, we show the abundace difference
+between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
+of each element.
+The equilibrium condensation temperatures for the composition of solar system
+are taken from \citealt{2003ApJ...591.1220L} (Table~8).
+The difference seen in \bizarreone-\sunanalog\ is
+compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
+The metallicity difference of $\approx 0.2$~dex observed in this pair
+is larger than the differences seen in any other pairs studied so far.
+%Indeed, some may consider such large difference in metallicity
+%enough to concluded that the two stars are completely unrelated.
+Strikingly, the five under-enhanced elements in \bizarreone\
+relative to \sunanalog\ are the five most volatile in all elements measured.
+The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
+\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
+This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
+combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
+strongly suggests that accretion of rocky material has occured in \bizarreone.
+
+How much mass of rocky material is needed to explain an increment of $\approx 0.2$~dex?
 One can carry out simple toy calculations of expected $\Delta\elemH{X}$
 in a Sun-like star's atmosphere when adding material of e.g., bulk Earth composition
-under these assumptions:
+under these simplifying assumptions:
 \begin{itemize}
@@
     the star's radiative and convective zone.
+  \item The surface abundance of the star has been altered once only by this
+    accretion event, and remained the same since.
 \end{itemize}
+
 We take the solar abundances $\elemH{X}$ of \citealt{Asplund:2009aa}
@@
 We take the composition of bulk Earth from a chondritic model of the Earth
-(\citealt{mcdonough2001composition}) and CI chondrite from \citealt{2009LanB...4B...44L}.
+(\citealt{mcdonough2001composition}).
 
-Figure~\ref{fig:toycalc} shows the expected change of surface abundances in a
-Sun-like star after $20~\mearth$ of material with composition of bulk Earth or
-CI chondrite is added.
-The CI chondrites are believed to have the closest in composition to the solar nebular.
-Their composition closely matches that of the solar atmosphere except
-Li, highly volatile ($\Tcondens < 250$~K) elements, and the noble gases.
-Other groups of chondrites show differing level of variations from CI chondrites.
+Figure~\ref{fig:toycalc} shows the expected change of surface abundances of
+metals in a Sun-like star after $20~\mearth$ of material with composition of
+bulk Earth is added.
 It has been long known that compared to CI or other carbonaceous chondrites,
@@
 elements (including Mn and Na) and volatile elements are incearsingly more
-depleted with decreasing condensation temperature (\citealt{mcdonough2001composition}).
-This trend is presumed to be closely related to the formation of terrestrial planets.
-Given the simplistic assumptions laid out above, and the uncertainties
-in our current knowledge of the compositions of terrestrial planets including bulk Earth,
-the match between our toy calculation and the observed abundance difference
-between \bizarreone\ and \sunanalog\ is remarkable.
+depleted with decreasing condensation temperature
+(\citealt{mcdonough2001composition}).
+This trend is presumed to be closely related to the formation of terrestrial
+planets in particular to the radial temperature gradient in a protoplanetary
+disk.
+Given the simplistic assumptions laid out above, and the uncertainties in our
+current knowledge of the compositions of terrestrial planets including bulk
+Earth, the match between our toy calculation and the observed abundance
+difference between \bizarreone\ and \sunanalog\ is remarkable.
 
@@
 
+What about \elem{Li}?
 The element \elem{Li} is worth a special attention in the context of accretion scenario.
 Because Li is present in either carbonaceous chondrites or the bulk Earth with
-a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition,}),
-but is depleted over time on the surface of a Sun-like star, accretion of
-either at later time will significantly replenish the lithium on the star's
-surface.
+a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition}),
+but is depleted quickly within the first couple of Gyrs on the surface of a
+Sun-like star, accretion of either material at later times will significantly
+replenish the lithium on the star's surface.
 For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
-material results in $\Delta\elemH{Li} \approx 1.6$~dex.
+material results in $\Delta\elemH{Li} \approx 1.6$~dex (which
+is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
 Incidentally, the star under examination, \bizarreone, has an age (informed by
-stellar parameters) very close to the Sun ().
-Thus, as long as we believe the Sun's present-day surface Li abundance
+stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$).
+Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
 to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
-in its Li.
-This is in fact exactly what we find: the Li abundance of \bizarreone\ is
+in its \elem{Li}.
+This is in fact exactly what we find: the \elem{Li} abundance of \bizarreone\ is
 $A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
-approximately $1.6$~dex higher than the solar value of $1.1$~dex.
-Furthermore, this implies that the accretion event should have happened
-very recently from a time ago that is shorter than the \elem{Li} depletion time.
+approximately $1.65$~dex higher than the solar value of $1.1$~dex.
+% TODO: solar Li needs reference
+Furthermore, this implies that the accretion event should have happened very
+recently from a time ago that is shorter than the \elem{Li} depletion time.
 
@@
 What about \sunanalog?
-\sunanalog\ is also enhanced in \elem{Li} considering its age of $4.00_{-1.56}^{+1.51}$~Gyr
-than the nominal \elem{Li} depletion predics by $\approx 1$~dex.
-This enhancement puts an upper limit on the accreted mass to be \todo{$\approx 4$~\mearth}
-assuming \elem{Li} concentration of $1.1$~ppm (\citealt{mcdonough2001composition}).
-Unlike \bizarreone, we cannot know the pre-accretion abundances of \sunanalog.
-However, we note that the span of abundance difference between highly volatile elements
-(C, N, O, Na) and refractory elements such as \elem{Fe} expected from accreting
-\todo{$\approx 4$~\mearth} to the Sun is $\approx 0.05$~dex.
-This is comparable to the abundance difference between N, Na and Fe in \sunanalog.
+\sunanalog\ is also enhanced in \elem{Li} considering its age of
+$4.00_{-1.56}^{+1.51}$~Gyr than the nominal \elem{Li} depletion predics by
+$\approx 1$~dex.
+This enhancement puts an upper limit on the accreted mass to be
+$\approx 4$~\mearth assuming \elem{Li} concentration of $1.1$~ppm
+(\citealt{mcdonough2001composition}).
+Unlike \bizarreone, we cannot know the pre-accretion abundances of \sunanalog
+\footnote{
+  Strictly speaking, we can never know the pre-accretion abundances
+  for \bizarreone\ either.
+  We only have an {\it approximate} idea that this is not far from a solar-twin
+  star \sunanalog, and because the deviation from this ``anchor'' star is
+  large, it is reasonable to consider an accretion by the Sun.
+  In reality, \sunanalog\ may as well have had its own accretion history,
+  which indeed seems to be the case according to its \elem{Li} abundance.
+}.
+However, we note that the span of abundance difference between highly volatile
+elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
+as \elem{Fe} expected from accreting $4$~\mearth to the Sun is $\approx
+0.05$~dex.
+This is comparable to the abundance difference between N, Na and Fe in
+\sunanalog.
 It is also interesting that \sunanalog\ also shows a deficit in the same
-volatile and moderately volatile elements (C, N, O, Na, and Mn) relative to Fe
+volatile and moderately volatile elements
+(\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}) relative to Fe
 just as in \bizarreone.
@@
 
-We stress that
-% - these calculations are carried out with very simple and unverified assumptions
-% - uncertainties exist on the bulk Earth
+We stress that while the calculation carried out is useful in
+order-of-magnitude sense, further investigation of each of the simplifying
+assumptions made is warranted.
+In addition,
+
+Given these limitations, the level of agreement for the refractory {\it and}
+\elem{Li} for \bizarreone\ is remarkable.
 
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{toycalc.pdf}
+  \includegraphics[width=0.95\linewidth]{toycalc.png}
   \caption{Expected change in solar surface abundance after adding $20~\mearth$ of
@@
 
-We summarize the few wide separation common proper motion pairs that have been
-studied in detailed chemical abundance so far.
-These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
-WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
-Their reported abundance differences $\Delta\elemH{X}$ where the difference is
-always taken as $\mathrm{higher}~\feh - \mathrm{lower}~\feh$ are plotted in
-\figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
-comparison with this pair.
-
-{\bf HD~20782/HD~20782:} 
-\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
-with a projected separation of $\sim9000$~AU (corresponding to 4.2~arcmin sky separation).
-Both stars in this system host close-in giant planets.
-HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
-pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
-with moderately high eccentricity ($e\sim0.1-0.3$)
-\footnote{The two stars were monitored by \project{HARPS} campaign, and it has recently
-  been reported by \citealt{} that HD~20781 hosts four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\
-  with $e \le 0.11$ within $\approx 0.35$~AU.}.
-They found that the abundances of 15 elements between the two stars are consistent with each other.
-However, they argued that there is a moderately significant ($\sim 2\sigma$)
-positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
-{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
-(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
-of their measurements).
-They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
-H-depleted rocky material that were pushed in during giant planet migration.
-
-{\bf WASP-94A/WASP-94B:} 
-\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
-with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
-host a hot Jupiter.
-The planet hosted by WASP-94A is transiting with a misaligned, probably
-retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
-more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
-star.
-With a claimed median uncertainty of $0.006$~dex among all elements, they
-detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
-elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
-1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
-Excluding K, which is based on one strong line and largely affected by non-LTE
-effect, their analysis shows a statistically significant non-zero slope between
-$\Delta\elemH{X}$ and $\Tcondens$\footnote{Note that the condensation
-  temperature $\Tcondens$ used is for solar (system? atmosphere?) composition
-  gas, which can differ from that of higher metallicity gas.}.
-They considered multiple possibilities related to the formation and evolution
-of planetary systems around each star as well as causes unrelated to planets
-such as dust cleansing during the fully convective phase or different rotation
-and granulation between the stars, but did not favor any particular one.
-
-{\bf HD~80606/HD~80607:}
-The pair of G5 stars HD 80606/HD 80607 has been independently studied by
-\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
-spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
-on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
-planets.
-Both stars are super solar with $\feh=0.35$.
-
-{\bf HAT-P-1:}
-HAT-P-1 is a pair of G0 stars separated 11\farcs apart in sky
-with $\feh\approx0.15$.
-The secondary star in the system is known to host one transiting giant planet
-while no planet has been discovered around the primary star.
-\citealt{Liu:2014aa} found that the two stars are identical in their atmospheric composition:
-\feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for the primary and secondary respectively,
-and $\Delta\elem{X}/{Fe}$ is consistent with zero for 23 elements measured
-with the mean error being $0.013$~dex.
-Based on this analysis, they concluded that the presence of close-in giant planet
-does not necessarily lead to stellar atmospheric pollution of the host star.
-
-{\bf XO-2N/XO-2S:}
-The double star system XO-2 has received much attention due to
-possibly the most robust and significant difference between the component stars
-among those so far studied.
-XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
-each hosting planet(s).
-XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
-masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
-0.15$) orbits at $<0.5$~AU.
-
-The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
-essentially no significant difference in Fe, Ni, C, and O between the two
-stars.
-However, re-analysis of the system using the same data in
-\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
-\Tcondens\ varies significantly depending on the stellar parameters chosen in
-their analysis. Both analyses were based on spectra
-using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
-covering $4450-5660~\AA$ and $5860-7100~\AA$ with S/N of $170-230$
-(\citealt{Teske:2013aa}).
-
-Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
-$4080-8300~\AA$) of the component stars with S/N of $350$ (in $5000-7500~\AA$)
-to perform a differential abundance analysis.
-They find that all 23 elements including Fe is enhanced in XO-2N
-compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
-a significant correlation with \Tcondens.
-At low \Tcondens, volatile elements differ by $0.015$~dex
-while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
-There are inconsistencies in the determination of stellar parameters
-(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
-and photometric analysis,
-but the existence of correlation between $\Delta\elem{H}$ and
-\Tcondens\ seems robust.
-
-\citealt{Ramirez:2015aa} argued that the {\it depletion} of
-volatile elements in XO-2S relative to XO-2N is plausibly
-due to {\it more} gas giant planets around XO-2S,
-following a similar interpretation of \citealt{Melendez:2009aa}
-on the trend between solar twins and the Sun.
-In this scenario, forming planets in the protoplanetary disk
-are supposed to ``lock'' heavier elements to the core of gas giant
-planets as well as some volatile elements in their envelopes.
-Then, the host star will somehow accrete {\it gas} depleted in
-metals compared to their protostellar condition.
-By tuning the metal content ($Z/X$) of gas giant planets
-and when the accretion of gas occurs in terms of how much mass
-is in the convective envelop then, they can match
-the mass difference of gas giant planets around each star,
-which is at least $1~\mjupiter$.
-For the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
-\citealt{Ramirez:2015aa} estimated that $20~\mearth$
-of equal-part mixture of Earth and CM chondrite-like material
-can explain the trend either as
-refractory {\it depletion} in XO-2S due to {\it more} rocky planets
-around XO-2S, or refractory enhancement in XO-2N by late time accretion
-in which case the complete opposite would be true.
-
-Finally, \citealt{Biazzo:2015aa}
-
 \section{Summary}
@@
 
-We have reported and discussed the discovery of a comoving pair of bright solar-type stars
-HD~240430 and HD~240429 (G0 and G2)
-with very different metallicity ($\Delta\feh \approx 0.2$~dex),
-and a condensation temperature-dependent abundance difference.
+We have reported and discussed the discovery of a comoving pair of bright
+solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
+metallicities ($\Delta\feh \approx 0.2$~dex), and a condensation temperature
+(\Tcondens)-dependent abundance differences.
+The more metal-rich of the two, HD~240430 (\bizarreone), show enhancement in
+all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
+enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
+\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
+The two stars also have anomalously high surface \elem{Li} abundance compared
+to their ages of $\sim 4$~Gyr.
+We considered that the comoving pair may have formed from two stars of different
+birth origins in a exchange scattering event, or that there may be chemical
+inhomogeneity in the birth cloud to find both unlikely.
 
-% Concluding remarks
-% include Useful follow up efforts
+In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
+abundance, we considered accretion of planetary material due to e.g., dynamical
+instability in some detail.
+We have argued that a recent accretion of $20$~\mearth\ of bulk Earth
+composition to \bizarreone\ can explain the enhancement in both refractory
+elements and the \elem{Li}.
+For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
+we put an upper limit of $\approx 4$~\mearth\ on the accreted mass
+based on the \elem{Li} concentration of carbonaceous chondrites and bulk Earth.
+While the case is not as clear as \bizarreone\ without a chemical reference star,
+the range of abundances from volatile to refractory elements is
+similar to that expected from $\approx 4$~\mearth\ accretion of bulk Earth.
+It is unclear what triggered the accretions to both stars.
+A possiblity is that a fly-by field star might have
+perturbed the planetary systems of both stars.
 
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec1.pdf}
-  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
-    For each row, the continuum-normalized data and model are plotted in the upper panel,
-    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
-    are plotted in the lower panel.
-  }
-  \label{fig:spec1}
-\end{figure}
+The two stars have not been included in any planet search programs
+by high-precision radial velocity or transit method.
+In case that there indeed were accretions to both stars as we
+have argued, it will be interesting to see the architectures
+of the planetary systems left behind, and whether
+they are very different betweeen the two stars.
 
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec2.pdf}
-  \caption{Same as \figname~\ref{fig:spec1} but for smaller portions of spectra that are
-    not dominated by \elem{Fe}. We mark elements that give rise to strong lines.
-    The feature in the third column of the second row is a strong \elem{Li} line that was
-    not modeled by \citealt{2016ApJS..225...32B}. This line was studied in a separate study
-    \todo{CITE}.
-  }
-  \label{fig:spec2}
-\end{figure}
+% somewhat of a rant that can be removed ...
+The investigation and conclusion on this puzzling comoving pair, like any other
+problem, depends strongly on one's prior belief.
+A difference of $\approx 0.2$~dex in \feh\ may enough for one to conclude that
+the two stars are unrelated and their proximity in phase space is by chance.
+On the other hand, if one has a stronger prior belief that two stars in such
+proximity in phase space ought to be of the same birth origin, and thus
+must have had near-identical chemical compisiton at birth, an engulment of
+refractory-rich planetary material provides an explanation for their
+$\Tcondens$-dependent abundance difference.
+
+%Implications
+%- chemical tagging, frequency is of concern
+%- exoplaneteers looking for accretion signature: look for the most odd ones in
+%the expected direction not just in binaries already known to host a planet.
+
+\acknowledgements
+
+% Gaia
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement.
+
+\software{
+  %The data and code used in this project is available from
+  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
+  %software license.
+  This research utilized:
+  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
+  \texttt{IPython} (\citealt{Perez:2007}),
+  \texttt{matplotlib} (\citealt{Hunter:2007}),
+  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
+  and \texttt{pandas} (\citealt{pandas}).}
 

### 2017-06-05 paper/ms.tex
Add keywords
Edit the abstract

@@
   We report and discuss the discovery of a comoving pair of bright solar-type
-  stars, HD~240430 and HD~240429, with a significant difference in their chemical
-  abundance patterns.
-  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
-  $r\approx 100~\pc$ with nearly identical three-dimensional velocities
-  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
-  \tgas\ proper motions and high resolution radial velocity measurements.
-  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
-  their lithium abundances, favoring the idea that they were born together and
-  are or were recently a bound, wide binary system.
-  However, the metallicities and chemical abundances of refractory
-  elements in the two stars are very different, challenging this simple picture.
-  In order to reconcile the seemingly contradictory observations,
-  we consider scenarios in which the pair is unrelated despite
-  its current spatial and kinematic configuration, and
-  those in which the pair formed together but may now have different chemistry.
-  In the latter, we consider the possibility that the more metal-rich of the two,
-  \bizarreone, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
-  selectively enhancing the refractory elements.
-  Direct-imaging and precision radial velocity follow-up to study the existence
-  or properties of planetary systems around these stars would help distinguish
-  these scenarios.
+  stars, HD~240430 and HD~240429, with a significant difference in their
+  chemical abundances.
+  The two stars are separated $0.6$~pc at a distance of
+  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
+  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
+  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
+  high-resolution radial velocity measurements.
+  Their stellar parameters determined from high-resolution KECK spectra
+  indicate that both stars are $\sim 4$~Gyr old,
+  yet both stars show high surface \elem{Li} abundance considering their ages.
+  Moreoever, the more metal-rich of the two, HD~240430, shows an enhancement of
+  refractory ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as
+  large enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
+  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}):
+  this is the largest and the most significant difference found in
+  wide binary pairs yet.
+  The proximity in phase space and ages between the two stars suggests that
+  they formed together with the same composition, at odds with the observed
+  differences in metallicity and abundance patterns.
+  In order to reconcile the seemingly contradictory observations, we suggest
+  that the star recently accreted $\approx 20$~\mearth\ of rocky material after
+  birth selectively enhancing the refractory elements in its surface and
+  convective envelope.
+  The other star, HD~240429, may also have had a similar accretion event given
+  its high surface \elem{Li} abundance but of much smaller amount
+  ($\approx 4$~\mearth).
+  Follow-ups to study the existence and properties of the planetary systems
+  around these stars will help illuminate more on planet-star interactions.
 \end{abstract}
+
+\keywords{
+  binaries: visual
+  ---
+  planet-star interactions
+  ---
+  stars: abundances
+  ---
+  stars: formation
+  ---
+  stars: individual (HD~240430, HD~240429)
+  ---
+  stars: solar-type
+}
 
@@
     No other pair studied so far were shown to have such large difference
-    in metallicity or sharp contrast between (moderately-)volatile and
+    in metallicity or sharp contrast between (moderately) volatile and
     refractory elements as \bizarreone-\sunanalog.

### 2017-06-05 paper/ms.tex
Clean up discussion; comment out some non critical parts

@@
 chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
-A multiple-star system of any size that we believe are born together can serve this purpose,
-with massive open clusters at one extreme.
+A multiple-star system of any size that we believe are born together can serve
+this purpose, with massive open clusters at one extreme.
 Wide binaries are at the other extreme in that we may be less confident of
@@
 % chance pair
-Given that their metallicities and abundance patterns are significantly
-different, one may simply conclude that the two stars are not related (coeval)
-but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
-by chance.
-The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
-at the stars' location, one may compute the probability that a star moving at
-the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
-...
+%Given that their metallicities and abundance patterns are significantly
+%different, one may simply conclude that the two stars are not related (coeval)
+%but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
+%by chance.
+%The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
+%at the stars' location, one may compute the probability that a star moving at
+%the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
+%...
 
@@
 %TODO: needs references
-% kozai?
+%TODO: kozai?
 Indeed, it is an important goal of many exoplanet studies
@@
 which are assumed to be born together.
-
-%One proxy that is informative of the composition of the material
-%that was hypothetically accreted to a star is the condensation temperature (\Tcondens).
-% TODO: why?
+Assuming that the component stars were born together with identical
+initial composition, we may see a difference in their surface abundances
+if the two stars then went through different amount of accretion
+of planetary material.
+This abundance difference may depend on the condensation temperatures of
+elements in the protoplanetary disks from which the accreted planets formed
+as their compositions depend on the radial temperature gradient in the disk.
+%TODO: cautions on condensation temperature
+% 1. it is just a proxy
+% 2. it is **equlibrium** condensation temperature
 
@@
 characteristics of stars and planets, and interpretation of any trend in
-$\Delta\elemH{X}$.
-These studies commonly look for
+$\Delta\elemH{X}$ with \Tcondens.
 %TODO: needs to include **16 Cyg** and HD~133131AB
@@
 Incidentally, the star under examination, \bizarreone, has an age (informed by
-stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$).
+stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
 Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
@@
 approximately $1.65$~dex higher than the solar value of $1.1$~dex.
-% TODO: solar Li needs reference
+%TODO: solar Li needs reference
 Furthermore, this implies that the accretion event should have happened very
@@
 
-It is further worth pointing out that measuring the \elem{Li} abundance
-with some of the refractory elements such as $\elem{Fe}$
-provides a way to estimate the time of the event.
-If the observed \elem{Li} abundance is less than what is inferred from
-abundance differences of other elements, and
-we have a model of \elem{Li} depletion, the time of \elem{Li} enhancement
-may be calculated.
+%TODO: not sure if this is too obvious of a point or useful in practice..
+%It is further worth pointing out that measuring the \elem{Li} abundance
+%with some of the refractory elements such as $\elem{Fe}$
+%provides a way to estimate the time of the event.
+%If the observed \elem{Li} abundance is less than what is inferred from
+%abundance differences of other elements, and
+%we have a model of \elem{Li} depletion, the time of \elem{Li} enhancement
+%may be calculated.
 
@@
 
+%TODO: augment this paragraph
+% - more geochemical study references
 We stress that while the calculation carried out is useful in
@@
 assumptions made is warranted.
-In addition,
-
+In addition, the composition of bulk Earth also has some uncertainties.
+For example, the reported bulk Earth concentration of the siderphile element
+\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
+While the latter value from \citealt{mcdonough2001composition} has been used in
+our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
+to an even closer agreement.
 Given these limitations, the level of agreement for the refractory {\it and}
@@
   \includegraphics[width=0.95\linewidth]{toycalc.png}
-  \caption{Expected change in solar surface abundance after adding $20~\mearth$ of
+  \caption{
+    Comparing the observed abundance difference vs. \Tcondens\ rank
+    to the expected change in solar surface abundance after adding $20$~\mearth\ of
     material with bulk Earth composition (\citealt{mcdonough2001composition}).
     The assumed mass fraction in the convective zone is $0.03$.
+    All metals are ranked by their \Tcondens\ for solar composition gas,
+    same as in \figname~\ref{fig:relabun_tcrank}.
+    Locations of the elements measured for \bizarreone-\sunanalog\ pair are
+    indicated by a vertical line and its symbol.
     The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
     suggests that the abundance difference may be due to accretion of
-    $20~\mearth$ of rocky planetary material.
-    We elements measured for \bizarreone-\sunanalog\ pair are filled with purple
-    while those without measurements are left empty.
+    $20$~\mearth\ of rocky planetary material.
+    The element \elem{Li} is off the plot and indicated with a red arrow
+    (see text for details).
   }
@@
 
-%Implications
+%TODO: Implications
 %- chemical tagging, frequency is of concern

### 2017-06-05 paper/ms.tex
Mention what gray line is in toycalc figure.

@@
     All metals are ranked by their \Tcondens\ for solar composition gas,
+    and the condensation temperature may be read from the gray line and right y-axis,
     same as in \figname~\ref{fig:relabun_tcrank}.

### 2017-06-06 paper/ms.tex
I don't have energy to finish this non-critical par. today
switch to aastex6.1

@@
-\documentclass[manuscript]{aastex6}
+\documentclass[modern, letterpaper]{aastex61}
+% \documentclass[twocolumn]{aastex61}
 
@@
 
-\include{aastexmods}
-
 % packages
@@
 \graphicspath{{figures/}}
-\bibliographystyle{aasjournal.bst}
+\bibliographystyle{aasjournal}
 
@@
 
-\author{
-  Semyeong Oh\altaffilmark{\pu,\lead},
-  Adrian M. Price-Whelan\altaffilmark{\pu},
-  John M. Brewer\altaffilmark{\yale},
-  Keith A. Hawkins\altaffilmark{\columbia},
-  Nathan W. C. Leigh\altaffilmark{\amnh},
-  David W. Hogg\altaffilmark{\ccpp,\mpia,\cca},
-  David N. Spergel\altaffilmark{\pu,\cca},
-  Justin Myles\altaffilmark{\yale} \etal\
-}
+\author{Semyeong Oh} % TODO: need ORCID
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
+\affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}
 
-% Affiliations
-\newcommand{\pu}{1}
-\newcommand{\lead}{2}
-\newcommand{\yale}{3}
-\newcommand{\columbia}{4}
-\newcommand{\amnh}{5}
-\newcommand{\ccpp}{6}
-\newcommand{\mpia}{7}
-\newcommand{\cca}{8}
+\author{John M. Brewer} % TODO: need ORCID
+\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
 
-\altaffiltext{\pu}{Department of Astrophysical Sciences,
-  Princeton University, 4 Ivy Ln, Princeton, NJ 08544, USA}
-\altaffiltext{\lead}{To whom correspondence should be addressed:
-  \texttt{semyeong@astro.princeton.edu}}
-\altaffiltext{\columbia}{Department of Astronomy,
-  Columbia University, 550 W 120th St, New York, NY 10027, USA}
-\altaffiltext{\yale}{Department of Astronomy,
-  Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
-\altaffiltext{\amnh}{Department of Astrophysics,
-  American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
-\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
-  Department of Physics,
-  New York University, 4 Washington Place,
-  New York, NY 10003, USA}
-\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
-  K\"onigstuhl 17, D-69117 Heidelberg, Germany}
-\altaffiltext{\cca}{Center for Computational Astrophysics,
-  Flatiron Institute, 162 5th Ave, New York, NY 10003, USA}
+\author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
+
+\author[0000-0003-2866-9403]{David W. Hogg}
+\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, room 1005, New York, NY 10003, USA}
+\affil{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
+\affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg}
+
+\author{David N. Spergel} % TODO: need ORCID
+\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+
+% \author{Keith A. Hawkins}
+% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}
+
+% \author{Nathan W. C. Leigh}
+% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
+
+\author{Justin Myles} % TODO: need ORCID
+\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
 
@@
   The two stars were monitored by \project{HARPS}
-  campaign, and it has recently been reported by \citealt{} that HD~20781 hosts
+  campaign, and it has recently been reported by \citealt{todo} that HD~20781 hosts
   four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
-  0.11$ within $\approx 0.35$~AU.}.
+  0.11$ within $\approx 0.35~{\rm AU}$.}.
 They found that the abundances of 15 elements between the two stars are
@@
 
-Finally, \citealt{Biazzo:2015aa}
+%TODO: summarize Biazzo+ on XO-2
+%Finally, \citealt{Biazzo:2015aa}
 

### 2017-06-06 paper/ms.tex
put AU back outside math

@@
   four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
-  0.11$ within $\approx 0.35~{\rm AU}$.}.
+  0.11$ within $\approx 0.35$~AU.}.
 They found that the abundances of 15 elements between the two stars are

### 2017-06-06 paper/ms.tex
oops order
Add smoh orcid id
Fix typo
Edit abstract grammar etc.

@@
 
-\author{Semyeong Oh} % TODO: need ORCID
+\author[0000-0001-7790-5308]{Semyeong Oh}
 \affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
@@
 
+\author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
+
 \author{John M. Brewer} % TODO: need ORCID
 \affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
-
-\author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
-\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
 
@@
   chemical abundances.
-  The two stars are separated $0.6$~pc at a distance of
+  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
   $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
@@
   high-resolution radial velocity measurements.
-  Their stellar parameters determined from high-resolution KECK spectra
+  Stellar parameters determined from high-resolution Keck HIRES spectra
   indicate that both stars are $\sim 4$~Gyr old,
-  yet both stars show high surface \elem{Li} abundance considering their ages.
-  Moreoever, the more metal-rich of the two, HD~240430, shows an enhancement of
+  yet both stars show high surface \elem{Li} abundance for this age.
+  The more metal-rich of the two, HD~240430, shows an enhancement of
   refractory ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as
@@
   differences in metallicity and abundance patterns.
-  In order to reconcile the seemingly contradictory observations, we suggest
-  that the star recently accreted $\approx 20$~\mearth\ of rocky material after
-  birth selectively enhancing the refractory elements in its surface and
-  convective envelope.
-  The other star, HD~240429, may also have had a similar accretion event given
+  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted $\approx 20$~\mearth\ of
+  rocky material after birth selectively enhancing the refractory elements in
+  its surface and convective envelope.
+  The other star HD~240429, ``Krios'', may also have had a similar accretion event given
   its high surface \elem{Li} abundance but of much smaller amount
@@
 the abundance difference between the pair.
-We summarize or discussions in \sectionname~\ref{sec:summary}.
+We summarize our discussions in \sectionname~\ref{sec:summary}.
 

### 2017-06-06 paper/ms.tex
Rework intro according to APW's comments.

@@
 
-Wide binaries are valuable tools for studying star and planet formation as well
+Wide binary stars are valuable tools for studying star and planet formation as well
 as Galactic dynamics and chemical evolution.
@@
 First, because wide binaries are weakly bound systems that may be tidally
-disrupted by e.g., field stars, molecular clouds, or the Galactic tidal field,
+disrupted by, e.g., field stars, molecular clouds, or the Galactic tidal field,
 their statistics can be informative of the Galactic mass distribution.
-For example, the separation distribution of halo binaries has been
-used to constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
+For example, the separation distribution of halo binaries has been used to
+constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
 On the other hand, they are also prime targets to test the chemical tagging
-hypothesis that stars of the same birthplace may be traced back by detailed
+hypothesis that stars from the same birthplace may be traced back using detailed
 chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
@@
 this purpose, with massive open clusters at one extreme.
-Wide binaries are at the other extreme in that we may be less confident of
-the coevality of individual systems
-but they are much more abundant than the larger systems like open clusters,
-rendering their statistics a meaningful indication of whether the hypothesis works.
+Wide binaries are at the other extreme in that we may be less confident of the
+coevality of individual systems but they are much more abundant than larger
+systems like open clusters, rendering their statistics a meaningful indication
+of whether the hypothesis works.
 
-Independently, in efforts to connect the host star's chemistry to
-its planetary system, wide binaries with similar or very different planetary architectures around
-the component stars are particularly useful as chemical signatures related to planet formation or accretion
-can be revealed in a differential sense without any regard to the Galactic chemical evolution
-as long as we assume that the two stars should have been born together with identical composition.
-For close-in giant planets, it has been established that the planet-metallicity relation
-is primordial, and that the enhanced metallicity in giant planet-hosting stars likely
-promoted the formation of giant planets (\citealt{Fischer:2005aa}) by increasing
-the availability of small particle condensates that forms planetesimals.
-On the other hand, if host stars are to be polluted after their birth
-by rocky planetary material with high refractory-to-volatile ratio,
-the convective envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
+Wide binaries with similar or very different planetary architectures around the
+component stars have been used to connect a host star's chemistry to its
+planetary system.
+A differential analysis may reveal chemical signatures related to planet
+formation or accretion without any regard to Galactic chemical evolution as
+long as the two stars are assumed to be born together with identical
+composition.
+For close-in giant planets, it has been established that the planet-metallicity
+relation is primordial, and that the enhanced metallicity in giant
+planet-hosting stars likely promotes the formation of giant planets by
+increasing the availability of small particle condensates that form
+planetesimals (\citealt{Fischer:2005aa}).
+On the other hand, if host stars are polluted after their birth by rocky
+planetary material with high refractory-to-volatile ratio, the convective
+envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
 compared to their initial state.
-Thus, differing planet formation or accretion in the two otherwise identical stars
-may imprint a difference of chemical abundances that depends on the
+Thus, differences in planet formation or accretion in two otherwise identical
+stars may imprint differences in chemical abundances that depend on the
 condensation temperature (\Tcondens).
@@
   Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
-The results and interpretations of these studies are varied: while some systems
-found no difference (see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
-studies  have found a \Tcondens-dependent difference in abundance.
-The increasing difference of abundance with condensation temperature
-has been attributed both to more yet-undiscovered rocky planets around
-the relatively refractory-poor star and to late time accretion of
-refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
+The results and interpretations of these studies are varied:
+while some systems appear to have undetectable differences
+(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
+studies have reported a \Tcondens-dependent difference in abundance
+with higher-\Tcondens\ elements showing larger differences.
+The increasing abundance difference with condensation temperature has been
+attributed both to more yet-undiscovered rocky planets around the relatively
+refractory-poor star and to late time accretion of refractory-rich planetary
+material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
+The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
+and often at $\approx 0.05$~dex level making them challenging to detect even
+with a careful analysis of high-resolution high signal-to-noise spectra.
 % maybe want to point out the former interpretation roots back to melendez+09
@@
 
-So far the strongest evidence for accretion of planetary material by a host star comes
-from spectral analysis of polluted white dwarfs (WDs).
+So far the strongest evidence for accretion of planetary material by a host
+star comes from spectral analysis of polluted white dwarfs (WDs).
 Because the gravitational settling times of elements heavier than \elem{He} in
-atmosphere is much shorter than the WD cooling time essentially providing a
-clean slate for any sign of accretion, detection of metals indicates a
-reservoir of dusty material around the WD.
-Indeed, many of the polluted WDs have been shown to own a dusty disk detected
+atmosphere is much shorter than the WD cooling time, detection of metals likely
+indicates the presence of a reservoir of dusty material around the WD.
+Indeed, many of the polluted WDs host a dusty debris disk detected
 in the infrared.
-Some of the most dramatically polluted WDs were revealed to have
+Some of the most dramatically polluted WDs show
 surface abundances closely matched by rocky planetary material
-indicated by e.g., bulk Earth composition, strongly arguing
+with, e.g., bulk Earth composition, strongly arguing
 that the disk formed from tidally disrupted minor planets
@@
 HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
-that strongly suggest a dramatic accretion of planetary material by the two stars.
+that strongly suggest dramatic accretion of planetary material by the two stars.
 We nickname the two stars \bizarreone\ (HD~240430) and

### 2017-06-06 paper/ms.tex
Work on comments on data section.

@@
     not dominated by \elem{Fe}.
-    We mark elements that give rise to strong lines.
+    We mark elements that give rise to strong absorption lines.
     The feature in the third column of the second row is a strong \elem{Li}
-    line that was not modeled by \citealt{2016ApJS..225...32B}. This line was
+    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
     studied in a separate work (\citealt{jmlithium}).
-    Note that the lines of \elem{Na} and \elem{O} which are under-enhanced
-    in \bizarreone\ relative to \elem{Fe} or other refractory elements
+    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
+    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
     show weaker residuals.
@@
 candidate comoving star pair in our recent search for comoving stars using the
-proper motions and parallaxes from the \tgas catalog, a component of \gaia\ \dr\
+proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr\
 (the astrometric measurements are listed in \tablename~\ref{tab:kk}).
@@
 (2) that they have independent 3D velocity vectors, both given only observations
-of two components of the velocities (proper motions).
+of two components of the velocities (parallaxes and proper motions).
 We then select a sample of high-confidence comoving star pairs by making a
@@
 In a separate effort to study detailed chemical abundances of potential
-planet-hosting stars, \citet{2016ApJS..225...32B} analyzed high resolution
-spectra of both stars obtained using HIRES spectrograph on Keck~I telescope.
+planet-hosting stars, \citet{2016ApJS..225...32B} obtained and analyzed high resolution
+spectra of both stars using the HIRES spectrograph on the Keck~I telescope.
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is
-$5164-7799$~\AA.
-Typical signal-to-noise ratio in continuum is $>200$~per pixel.
-The resulting measurements include abundances measured for 15 chemical species
+$5164--7799$~\AA.
+A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
+The resulting measurements include elemental abundances for 15 chemical species
 (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
@@
 \citealt{2016ApJS..225...32B}.
-The \elem{Li} doublet at $6707.6$~\AA\ for this sample was
-investigated in a separate work (\citealt{jmlithium}).
+The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
+\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
+work (\citealt{jmlithium}).
 We list all spectroscopic measurements including
 the absolute abundance\footnote{
-  Absolute abundance of element \elem{X} is $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
+  Absolute abundance of element \elem{X} is
+  $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
   where $n_\elem{X}$ is the number density of element \elem{X}.
-} of \elem{Li} for the two stars in Table~\ref{tab:kk}.
+}
+of \elem{Li} for the two stars in Table~\ref{tab:kk}.
 
-Although selected based only on their proper motions, the two stars
+Although selected based only on their astrometry, the two stars
 have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
-confirming that they are comoving in all directions.
+confirming that they are truly comoving.
 The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
 and the 3D separation is $\approx 0.6$~pc.
+% note on uncertainties
 Given their proximity in phase space, it is generally accepted to assume that
-the two stars were born together perhaps to form a wide binary system from the
-same birth cloud.
+the two stars were born together and, perhaps, are a bound wide binary system.
 Thus, we expect the two stars to have identical metallicities and abundance patterns.
-Surprisingly, however, one of the stars, \bizarreone\ is significantly more metal
-rich than the other by 0.2~dex ($\approx 60\%$; \figname~\ref{fig:abundances}).
-What is more puzzling is that not all elements are equally enhanced:
-the abundances of \bizarreone\ shows selective depletion in
+Surprisingly, one of the stars, \bizarreone\ is significantly more metal
+rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
+Even more puzzling is that not all elements are equally enhanced:
+the abundances of \bizarreone\ show selective depletion in
 \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
@@
 in \figname~\ref{fig:spec1} and \ref{fig:spec2} where we show
-segments of the spectra and model of the two stars.
-As expected from metallicity difference ($\Delta\feh \approx 0.2$),
+segments of the spectra and models of the two stars
+used to measure their abundances.
+As expected from their reported metallicity difference ($\Delta\feh \approx 0.2$),
 the ratio of data and model between the two stars show significant
-residuals of almost all metal features, largely dominated by \elem{Fe}.
+residuals of almost all metal line features, largely dominated by \elem{Fe}.
 However, for lines of elements that are not as enhanced in \bizarreone\,
@@
 the differences in other pairs for all elements except \elem{N} and \elem{O},
-which are also the most uncertain (\tablename~\ref{tab:kk})
-are less than $0.05$~dex, makiing \bizarreone-\sunanalog\ pair an outlier.
-Moreoever, the abundance differences cannot be due to different chemical enrichment
-history in the disk even if the two stars were of different origin.
-\figname~\ref{fig:deltaXH} additioanlly shows the distribution of $\Delta[\elem{X}/\elem{H}]$
-for random pairings of two stars with similar \feh\ as \bizarreone\ and \sunanalog\
-as violins for each element.
+which are also the most uncertain (\tablename~\ref{tab:kk}),
+are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
+
+The abundance differences cannot be due to different chemical enrichment
+histories in the disk even if the two stars were of different origin.
+\figname~\ref{fig:deltaXH} additionally shows the distribution of abundance
+differences, $\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars
+with similar \feh\ as \bizarreone\ and \sunanalog\.
 We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
-all other elements are enhanced at a similar level with some variations.
-Specifically, for a typical star with $\elem{Fe} \approx 0.2$~dex,
+all other elements are typically enhanced at a similar level, with some variations.
+Specifically, for a typical star with $\feh \approx 0.2$~dex,
 we generally expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
 (\citealt{Battistini:2015aa,Bensby:2003aa})
-making the low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$ seen in \bizarreone\
+making the low [\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\
 very unlikely to arise from variations in Galactic chemical evolution.
@@
 
-The fact that the two stars share a very similar space motion
-at a separation of $\approx 0.6$~pc strongly argues that the pair is coeval.
-We consider other age indicators apart from their phase space coordinates
+The fact that the two stars share a nearly identical space motion
+at a separation of $< 1$~pc strongly argues that the pair is coeval.
+We therefore  consider other age indicators apart from their phase space coordinates
 to assess the ages and coevality of the two stars.
-First, given the precise measurements of $\log(g)$, $T_\mathrm{eff}$,
-comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
-We perform isochrone fitting using the Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
-The input data are $\log(g)$, $T_\mathrm{eff}$, \feh, parallaxes, $B$-band magnitudes, and their errors.
-The isochrone ages of \sunanalog\ and \bizarreone\ are
+First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
+we can constrain the ages of the two stars by
+comparing these values to theoretical isochrones.
+We perform isochrone fitting to these values using the Yale-Yonsei model
+isochrones (\citealt{2013ApJ...776...87S}).
+The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
+parallaxes, $B$-band magnitudes, and their errors.
+The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
 $4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
@@
 
-Surface lithium abundance in a sun-like star decreases with its age due to
+The Surface lithium abundance in a sun-like star decreases with its age due to
 mixing induced by convection or rotation, which brings the lithium into the
@@
 Thus, surface lithium abundance is an indicator of stellar ages.
-The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim
-1$~Gyr according to the theoretical models tuned to explain the solar lithium
-abundance and rotational profile (\citealt{2005Sci...309.2189C}).
-The lithium abundance of \bizarreone\ is still higher by $0.5$~dex showing the
-largest difference among all measured elements.
-This translates to $\sim 500$~Myr difference in age.
+The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
+of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
+solar lithium abundance and rotational profile (\citealt{2005Sci...309.2189C}).
+The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
+among all measured elements.
+This translates to a $\sim 500$~Myr difference in age.
 Given the overall higher metal abundances and the peculiar abundance patterns
@@
 distributions are consistent with blackbody.
-The low $v\sin(i)$ values also argue against very young ages inferred from the
-surface lithium abundances.
+The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
+young ages inferred from the surface lithium abundances.
 % TODO: reference for vertical action as age?
@@
 has a vertical action larger than the Sun, favoring an older age.
-We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main
+We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr old main
 sequence stars, and that their unusually high \elem{Li} abundance requires an
@@
   \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
-  \caption{Abundance difference of \bizarreone-\sunanalog\ pair
+  \caption{Abundance differences of the \bizarreone-\sunanalog\ pair
     ranked by the condensation temperature of elements for solar composition gas

### 2017-06-06 paper/ms.tex
Use present tense throughout summary sec.; other grammar, wording edits.

@@
 
-We have reported and discussed the discovery of a comoving pair of bright
+We report the discovery of a comoving pair of bright
 solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
-metallicities ($\Delta\feh \approx 0.2$~dex), and a condensation temperature
+metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
 (\Tcondens)-dependent abundance differences.
-The more metal-rich of the two, HD~240430 (\bizarreone), show enhancement in
+The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
 all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
@@
 to their ages of $\sim 4$~Gyr.
-We considered that the comoving pair may have formed from two stars of different
+We consider that the comoving pair may have formed from two stars of different
 birth origins in a exchange scattering event, or that there may be chemical
-inhomogeneity in the birth cloud to find both unlikely.
+inhomogeneity in the birth cloud, and find both unlikely.
 
 In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
-abundance, we considered accretion of planetary material due to e.g., dynamical
-instability in some detail.
-We have argued that a recent accretion of $20$~\mearth\ of bulk Earth
+abundance, we consider accretion of planetary material as the cause.
+We argue that a recent accretion of $20$~\mearth\ of bulk Earth
 composition to \bizarreone\ can explain the enhancement in both refractory
@@
 It is unclear what triggered the accretions to both stars.
-A possiblity is that a fly-by field star might have
+One possibility is that a fly-by field star may have
 perturbed the planetary systems of both stars.
 
-The two stars have not been included in any planet search programs
-by high-precision radial velocity or transit method.
-In case that there indeed were accretions to both stars as we
-have argued, it will be interesting to see the architectures
-of the planetary systems left behind, and whether
-they are very different betweeen the two stars.
+The two stars have not been included in any publicly released data from planet
+search programs.
+If both stars have accreted planetary material, it would be very interesting to
+search for the existence and architectures of the planetary systems left
+behind, and whether they are very different between the two stars.
 
@@
 proximity in phase space ought to be of the same birth origin, and thus
-must have had near-identical chemical compisiton at birth, an engulment of
+must have had near-identical chemical composition at birth, an engulfment of
 refractory-rich planetary material provides an explanation for their

### 2017-06-06 paper/ms.tex
Use consistent notation for arcmin

@@
 stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
-4.2~arcmin sky separation). Both stars in this system host close-in giant
+4.2\arcmin\ sky separation). Both stars in this system host close-in giant
 planets.

### 2017-06-06 paper/ms.tex
Restrure attempt: lit review to intro, age to discussion, divide discussion

@@
 and often at $\approx 0.05$~dex level making them challenging to detect even
-with a careful analysis of high-resolution high signal-to-noise spectra.
+with a careful analysis of high-resolution high signal-to-noise ratio spectra.
 % maybe want to point out the former interpretation roots back to melendez+09
@@
 We summarize our discussions in \sectionname~\ref{sec:summary}.
+
+\subsection{Review of Detailed Chemical Abundance Studies of Wide Binary Stars}
+\label{sub:review}
+
+Anticipating the forth coming discussion, we review and summarize a handful of
+wide binary systems that have been studied in
+their detailed chemical abundances so far with high-resolution spectroscopy.
+These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
+WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
+We focus on key characteristics of stars and planets, and interpretation of any
+trend in $\Delta\elemH{X}$ with \Tcondens.
+%TODO: needs to include **16 Cyg** and HD~133131AB
+
+{\bf HD~20782/HD~20782:}
+\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
+stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
+4.2\arcmin\ sky separation). Both stars in this system host close-in giant
+planets.
+HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
+orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
+Neptune-mass planets within 0.3~AU with moderately high eccentricity
+($e\sim0.1-0.3$) \footnote{
+  The two stars were monitored by \project{HARPS}
+  campaign, and it has recently been reported by \citealt{todo} that HD~20781 hosts
+  four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
+  0.11$ within $\approx 0.35$~AU.}.
+They found that the abundances of 15 elements between the two stars are
+consistent with each other.
+However, they argued that there is a moderately significant ($\sim 2\sigma$)
+positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
+{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
+(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
+of their measurements).
+They interpreted that this slope may be evidence for accretion of
+$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
+planet migration.
+
+{\bf HAT-P-1:}
+HAT-P-1 is a pair of G0 stars separated 11\arcsec\ apart in sky
+with $\feh\approx0.15$.
+The secondary star in the system is known to host one transiting giant planet
+while no planet has been discovered around the primary star.
+\citealt{Liu:2014aa} found that the two stars are identical in their
+atmospheric composition: \feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for
+the primary and secondary respectively, and $\Delta\elem{X}/\elem{Fe}$ is
+consistent with zero for 23 elements measured with the mean error being
+$0.013$~dex.
+Based on this analysis, they concluded that the presence of close-in giant planet
+does not necessarily lead to stellar atmospheric pollution of the host star.
+
+{\bf HD~80606/HD~80607:}
+A pair of G5 stars with super-solar metallicity ($\feh \approx 0.35$),
+HD 80606/HD 80607, has been independently studied by
+\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
+spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
+on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
+planets.
+Both studies have concluded that there is no significant
+chemical difference between the two stars similar to the case of HAT-P-1.
+
+{\bf XO-2N/XO-2S:}
+The double star system XO-2 has received much attention due to
+possibly the most robust and significant difference between the component stars
+among those so far studied.
+XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
+each hosting planet(s).
+XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
+masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
+0.15$) orbits at $<0.5$~AU.
+
+The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
+essentially no significant difference in Fe, Ni, C, and O between the two
+stars.
+However, re-analysis of the system by the same authors using the same data in
+\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
+\Tcondens\ varies significantly depending on the stellar parameters chosen in
+their analysis. Both analyses were based on spectra
+using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
+covering $4450-5660$~\AA\ and $5860-7100$~\AA\ with S/N of $170-230$
+(\citealt{Teske:2013aa}).
+
+Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
+$4080-8300$~\AA) of the component stars with S/N of $350$ (in $5000-7500$~\AA)
+to perform a differential abundance analysis.
+They find that all 23 elements including Fe are enhanced in XO-2N
+compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
+a significant correlation with \Tcondens.
+At low \Tcondens, volatile elements differ by $0.015$~dex
+while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
+There are inconsistencies in the determination of stellar parameters
+(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
+and photometric analysis,
+but the existence of correlation between $\Delta\elem{H}$ and
+\Tcondens\ seems robust.
+
+\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
+in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
+giant planets around XO-2S, following a similar interpretation of
+\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
+In this scenario, forming planets in the protoplanetary disk are supposed to
+``lock'' heavier elements to the core of gas giant planets as well as some
+volatile elements in their envelopes. Then, the host star will accrete {\it
+  gas} depleted in metals compared to their protostellar condition.
+By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
+of gas occurs in terms of how much mass is in the convective envelop then, they
+can match the mass difference of gas giant planets around each star, which is
+at least $1~\mjupiter$.
+On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
+\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
+Earth and CM chondrite-like material can explain the trend either as refractory
+{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
+refractory enhancement in XO-2N by late time accretion in which case the
+complete opposite would be true.
+
+%TODO: summarize Biazzo+ on XO-2
+%Finally, \citealt{Biazzo:2015aa}
+
+{\bf WASP-94A/WASP-94B:}
+\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
+with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
+host a hot Jupiter.
+The planet hosted by WASP-94A is transiting with a misaligned, probably
+retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
+more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
+star.
+With a claimed median uncertainty of $0.006$~dex among all elements, they
+detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
+elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
+1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
+Excluding K, which is based on one strong line and largely affected by non-LTE
+effect, their analysis shows a statistically significant non-zero slope between
+$\Delta\elemH{X}$ and $\Tcondens$\footnote{
+  %TODO: double check the following statement
+  Note that the condensation
+  temperature $\Tcondens$ used is for solar system composition
+  gas, which can differ from that of higher metallicity gas.}.
+They considered multiple possibilities related to the formation and evolution
+of planetary systems around each star as well as causes unrelated to planets
+such as dust cleansing during the fully convective phase or different rotation
+and granulation between the stars, but did not favor any particular one.
 
@@
 
-The fact that the two stars share a nearly identical space motion
-at a separation of $< 1$~pc strongly argues that the pair is coeval.
-We therefore  consider other age indicators apart from their phase space coordinates
-to assess the ages and coevality of the two stars.
-First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
-we can constrain the ages of the two stars by
-comparing these values to theoretical isochrones.
-We perform isochrone fitting to these values using the Yale-Yonsei model
-isochrones (\citealt{2013ApJ...776...87S}).
-The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
-parallaxes, $B$-band magnitudes, and their errors.
-The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
-$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
-consistent with them being coeval.
-
-The Surface lithium abundance in a sun-like star decreases with its age due to
-mixing induced by convection or rotation, which brings the lithium into the
-interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
-burning.
-Thus, surface lithium abundance is an indicator of stellar ages.
-The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
-of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
-solar lithium abundance and rotational profile (\citealt{2005Sci...309.2189C}).
-The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
-among all measured elements.
-This translates to a $\sim 500$~Myr difference in age.
-Given the overall higher metal abundances and the peculiar abundance patterns
-in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
-abundance means a younger age or something else.
-For example, the presence of $\elem{Li}$-rich red giant stars has been
-attributed to the engulfment of substellar companions such as gas giant planets
-or brown dwarfs which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
-
-In fact, the surface lithium abundance is the only indication that points to younger ages.
-If the two stars are indeed only several hundred Myrs old at most,
-they are expected to be part of a larger comoving group of stars.
-However, as we mention above, there is no evidence in our search of comoving pairs
-using \tgas\ that the two stars belong to a larger group of young stars.
-Very young stars are often show signs of activity such as
-X-ray emission from magnetic activity, emission lines, or infrared excess due to
-circumstellar disks.
-We have looked for these signs for the pair to find none, and their spectral energy
-distributions are consistent with blackbody.
-The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
-young ages inferred from the surface lithium abundances.
-% TODO: reference for vertical action as age?
-Finally, the pair's fiducial orbit in a axisymmetric Milky Way-like potential
-has a vertical action larger than the Sun, favoring an older age.
-We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr old main
-sequence stars, and that their unusually high \elem{Li} abundance requires an
-alternative explanation.
-
 \begin{figure}[htpb]
@@
 %...
+
+\subsection{Stellar Ages \& Coevality}
+\label{sub:ages}
+
+The fact that the two stars share a nearly identical space motion
+at a separation of $< 1$~pc strongly argues that the pair is coeval.
+We therefore  consider other age indicators apart from their phase space coordinates
+to assess the ages and coevality of the two stars.
+First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
+we can constrain the ages of the two stars by
+comparing these values to theoretical isochrones.
+We perform isochrone fitting to these values using the Yale-Yonsei model
+isochrones (\citealt{2013ApJ...776...87S}).
+The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
+parallaxes, $B$-band magnitudes, and their errors.
+The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
+$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
+consistent with them being coeval.
+
+The surface lithium abundance in a sun-like star decreases with its age due to
+mixing induced by convection or rotation, which brings the lithium into the
+interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
+burning.
+Thus, surface lithium abundance is an indicator of stellar ages.
+The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
+of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
+solar lithium abundance and rotational profile (\citealt{2005Sci...309.2189C}).
+The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
+among all measured elements.
+This translates to a $\sim 500$~Myr difference in age.
+Given the overall higher metal abundances and the peculiar abundance patterns
+in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
+abundance means a younger age or something else.
+For example, the presence of $\elem{Li}$-rich red giant stars has been
+attributed to the engulfment of substellar companions such as gas giant planets
+or brown dwarfs which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
+
+In fact, the surface lithium abundance is the only indication that points to younger ages.
+If the two stars are indeed only several hundred Myrs old at most,
+they are expected to be part of a larger comoving group of stars.
+However, as we mention above, there is no evidence in our search of comoving pairs
+using \tgas\ that the two stars belong to a larger group of young stars.
+Very young stars are often show signs of activity such as
+X-ray emission from magnetic activity, emission lines, or infrared excess due to
+circumstellar disks.
+We have looked for these signs for the pair to find none, and their spectral energy
+distributions are consistent with blackbody.
+The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
+young ages inferred from the surface lithium abundances.
+% TODO: reference for vertical action as age?
+Finally, the pair's fiducial orbit in a axisymmetric Milky Way-like potential
+has a vertical action larger than the Sun, favoring an older age.
+We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr old main
+sequence stars, and that their unusually high \elem{Li} abundance requires an
+alternative explanation.
+
+\subsection{Exchange Scattering}
+\label{sub:exchange_scattering}
 
@@
 
+\subsection{Chemical Inhomogeneity in Star Formation}
+\label{sub:chemical_inhomogeneity_in_star_formation}
+
 % inhomogeneity in star formation
@@
 cannot be due to chemical inhomogeneity in the birth cloud.
+
+\subsection{Accretion of rocky planetary material}
+\label{sub:accretion}
 
@@
 % 2. it is **equlibrium** condensation temperature
-
-Only a handful of wide binary systems have been studied with high-resolution
-spectroscopy in their detailed chemical abundances so far.
-These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
-WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
-We first review and summarize the studies of these systems focusing on key
-characteristics of stars and planets, and interpretation of any trend in
-$\Delta\elemH{X}$ with \Tcondens.
-%TODO: needs to include **16 Cyg** and HD~133131AB
-
-{\bf HD~20782/HD~20782:}
-\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
-stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
-4.2\arcmin\ sky separation). Both stars in this system host close-in giant
-planets.
-HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
-orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
-Neptune-mass planets within 0.3~AU with moderately high eccentricity
-($e\sim0.1-0.3$) \footnote{
-  The two stars were monitored by \project{HARPS}
-  campaign, and it has recently been reported by \citealt{todo} that HD~20781 hosts
-  four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
-  0.11$ within $\approx 0.35$~AU.}.
-They found that the abundances of 15 elements between the two stars are
-consistent with each other.
-However, they argued that there is a moderately significant ($\sim 2\sigma$)
-positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
-{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
-(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
-of their measurements).
-They interpreted that this slope may be evidence for accretion of
-$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
-planet migration.
-
-{\bf HAT-P-1:}
-HAT-P-1 is a pair of G0 stars separated 11\arcsec\ apart in sky
-with $\feh\approx0.15$.
-The secondary star in the system is known to host one transiting giant planet
-while no planet has been discovered around the primary star.
-\citealt{Liu:2014aa} found that the two stars are identical in their
-atmospheric composition: \feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for
-the primary and secondary respectively, and $\Delta\elem{X}/\elem{Fe}$ is
-consistent with zero for 23 elements measured with the mean error being
-$0.013$~dex.
-Based on this analysis, they concluded that the presence of close-in giant planet
-does not necessarily lead to stellar atmospheric pollution of the host star.
-
-{\bf HD~80606/HD~80607:}
-A pair of G5 stars with super-solar metallicity ($\feh \approx 0.35$),
-HD 80606/HD 80607, has been independently studied by
-\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
-spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
-on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
-planets.
-Both studies have concluded that there is no significant
-chemical difference between the two stars similar to the case of HAT-P-1.
-
-{\bf XO-2N/XO-2S:}
-The double star system XO-2 has received much attention due to
-possibly the most robust and significant difference between the component stars
-among those so far studied.
-XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
-each hosting planet(s).
-XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
-masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
-0.15$) orbits at $<0.5$~AU.
-
-The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
-essentially no significant difference in Fe, Ni, C, and O between the two
-stars.
-However, re-analysis of the system by the same authors using the same data in
-\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
-\Tcondens\ varies significantly depending on the stellar parameters chosen in
-their analysis. Both analyses were based on spectra
-using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
-covering $4450-5660$~\AA\ and $5860-7100$~\AA\ with S/N of $170-230$
-(\citealt{Teske:2013aa}).
-
-Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
-$4080-8300$~\AA) of the component stars with S/N of $350$ (in $5000-7500$~\AA)
-to perform a differential abundance analysis.
-They find that all 23 elements including Fe are enhanced in XO-2N
-compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
-a significant correlation with \Tcondens.
-At low \Tcondens, volatile elements differ by $0.015$~dex
-while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
-There are inconsistencies in the determination of stellar parameters
-(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
-and photometric analysis,
-but the existence of correlation between $\Delta\elem{H}$ and
-\Tcondens\ seems robust.
-
-\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
-in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
-giant planets around XO-2S, following a similar interpretation of
-\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
-In this scenario, forming planets in the protoplanetary disk are supposed to
-``lock'' heavier elements to the core of gas giant planets as well as some
-volatile elements in their envelopes. Then, the host star will accrete {\it
-  gas} depleted in metals compared to their protostellar condition.
-By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
-of gas occurs in terms of how much mass is in the convective envelop then, they
-can match the mass difference of gas giant planets around each star, which is
-at least $1~\mjupiter$.
-On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
-\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
-Earth and CM chondrite-like material can explain the trend either as refractory
-{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
-refractory enhancement in XO-2N by late time accretion in which case the
-complete opposite would be true.
-
-%TODO: summarize Biazzo+ on XO-2
-%Finally, \citealt{Biazzo:2015aa}
-
-{\bf WASP-94A/WASP-94B:}
-\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
-with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
-host a hot Jupiter.
-The planet hosted by WASP-94A is transiting with a misaligned, probably
-retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
-more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
-star.
-With a claimed median uncertainty of $0.006$~dex among all elements, they
-detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
-elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
-1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
-Excluding K, which is based on one strong line and largely affected by non-LTE
-effect, their analysis shows a statistically significant non-zero slope between
-$\Delta\elemH{X}$ and $\Tcondens$\footnote{
-  %TODO: double check the following statement
-  Note that the condensation
-  temperature $\Tcondens$ used is for solar system composition
-  gas, which can differ from that of higher metallicity gas.}.
-They considered multiple possibilities related to the formation and evolution
-of planetary systems around each star as well as causes unrelated to planets
-such as dust cleansing during the fully convective phase or different rotation
-and granulation between the stars, but did not favor any particular one.
 

### 2017-06-06 paper/ms.tex
Add a missing reference.

@@
 ($e\sim0.1-0.3$) \footnote{
-  The two stars were monitored by \project{HARPS}
-  campaign, and it has recently been reported by \citealt{todo} that HD~20781 hosts
-  four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
-  0.11$ within $\approx 0.35$~AU.}.
+  The two stars were monitored by \project{HARPS} campaign, and it has recently
+  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
+  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
+  within $\approx 0.35$~AU.}.
 They found that the abundances of 15 elements between the two stars are

### 2017-06-06 paper/ms.tex
Update published bib record.

@@
 (the astrometric measurements are listed in \tablename~\ref{tab:kk}).
-We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
+We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
 full explanation of the methodology behind this search and only briefly describe
@@
 conservative cut on this likelihood ratio.
-In the resulting catalog of comoving pairs (\citealt{2016arXiv161202440O}),
+In the resulting catalog of comoving pairs (\citealt{2017AJ....153..257O}),
 the pair presented in this paper was assigned a group id of 1199,

### 2017-06-07 paper/ms.tex
Revert posterior dist of dx,dv and orbit figures.

@@
 
+Throughout the \documentname\, we use the following convention for
+chemical abundances of stars: [\elemH{X}] is the ratio of number density of
+element \elem{X} to \elem{H} relative to the solar values.
+The absolute abundance of \elem{X} is
+$A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
+where $n_\elem{X}$ is the number density of element \elem{X}.
+
 \subsection{Review of Detailed Chemical Abundance Studies of Wide Binary Stars}
@@
 the absolute abundance\footnote{
-  Absolute abundance of element \elem{X} is
+  The absolute abundance of element \elem{X} is
   $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
@@
 
+The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
+and the 3D separation is $\approx 0.6$~pc.
 Although selected based only on their astrometry, the two stars
@@
 confirming that they are truly comoving.
-The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
-and the 3D separation is $\approx 0.6$~pc.
-% note on uncertainties
+Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
+can compare differences between the inferred 6D phase space coordinates of the
+two stars.
+We start by generating posterior samples over the Heliocentric distance, $r$,
+tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
+given the observed parallax, $\pi$, and proper motion components,
+$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
+By defining the vectors
+% SMOH: I understand you meant hat v_r as the latent true radial velocity but
+% personally think a) it can confuse some people that there are hat quantities
+% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
+% quantities for observed variables and no-hat for latent true ones.
+% SMOH: v_r is missing in the LHS of eq(3)
+\begin{eqnarray}
+  \vec{y} &=&
+      \transp{\left(
+        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
+          \pi &
+          \mu_{\alpha^*} &
+          \mu_\delta &
+          v_r
+        \end{array}
+      \right)}\\
+  \hat{\vec{y}} &=&
+      \transp{\left(
+        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
+          r^{-1} &
+          r^{-1}\,v_\alpha &
+          r^{-1}\,v_\delta &
+          \hat{v}_r
+        \end{array}
+      \right)}
+\end{eqnarray}
+and by considering the covariance matrix $\mat{C}$ between the observed
+quantities (provided by \tgas\ and extended to include the uncorrelated radial
+velocity uncertainty), the likelihood can be written
+\begin{eqnarray}
+p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
+  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
+    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
+    \mat{C}^{-1} \,
+    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
+\end{eqnarray}
+We adopt a uniform space density prior for the distance and an isotropic
+Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
+\begin{eqnarray}
+p(r) &=&
+  \begin{cases}
+    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
+    0              & \text{otherwise}
+  \end{cases}\\
+p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
+  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
+\end{eqnarray}
+For each of the two stars, we use \project{emcee}
+(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
+v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
+first 512 steps as the burn-in period.
+For each sample, we convert the heliocentric phase-space coordinates into
+Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
+= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
+etc.}).
+\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
+Galactocentric phase-space coordinates for the two stars.
+In all components, the pair is consistent with being co-moving and close in
+separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
+but the median 3-space separation is $\approx$$0.6~\pc$.
+
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
+  \end{center}
+  \caption{%
+    Differences in posterior samples over Galactocentric phase-space coordinates
+    for the two stars \sunanalog\ and \bizarreone.
+    \label{fig:dxdv}}
+\end{figure}
+
 Given their proximity in phase space, it is generally accepted to assume that
@@
 alternative explanation.
+
+\figurename~\ref{fig:orbit} shows an orbit computed from the median posterior
+sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
+in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
+explain}
+The Sun's orbit in this same Milky Way model is under-plotted for comparison
+(grey line); the orbits of the stars in this pair have large scale-heights
+relative to the Sun's orbit despite being young.
+
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{orbits.pdf}
+  \end{center}
+  \caption{%
+    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
+    For \sunanalog\, the initial conditions are set to the median posterior
+    sample over the inferred 6D phase-space coordinates.
+    The orbits are computed by integrating backwards from the present-day
+    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
+    Leapfrog integration scheme implemented in \project{Gala}
+    (\citealt{Gala:2017}). \todo{APW: citation...}
+\label{fig:orbit}}
+\end{figure}
 

### 2017-06-07 paper/ms.tex
Fix various minor things.

@@
 Recently, transit signals from small bodies orbiting around a polluted WD
-has been detected by \project{Kepler} adding further support to the picture
+have been detected by \project{Kepler} adding further support to the picture
 (\citealt{2015Natur.526..546V}).
@@
 Throughout the \documentname\, we use the following convention for
-chemical abundances of stars: [\elemH{X}] is the ratio of number density of
-element \elem{X} to \elem{H} relative to the solar values.
+chemical abundances of stars: \elemH{X} is the ratio of number density of
+element \elem{X} to \elem{H} relative to the solar value.
 The absolute abundance of \elem{X} is
@@
 
-Anticipating the forth coming discussion, we review and summarize a handful of
+Anticipating the forthcoming discussion, we review and summarize a handful of
 wide binary systems that have been studied in
@@
 WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
-We focus on key characteristics of stars and planets, and interpretation of any
-trend in $\Delta\elemH{X}$ with \Tcondens.
+We focus on key characteristics of stars and planets, and interpretations of
+any trend in $\Delta\elemH{X}$ with \Tcondens.
 %TODO: needs to include **16 Cyg** and HD~133131AB
 
-{\bf HD~20782/HD~20782:}
+{\bf HD~20782/HD~20781:}
 \citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf

### 2017-06-08 paper/ms.tex
Trim down review section.

@@
 {\bf HD~20782/HD~20781:}
-\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
-stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
-4.2\arcmin\ sky separation). Both stars in this system host close-in giant
-planets.
+Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
+$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
+host close-in giant planets.
 HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
@@
 Neptune-mass planets within 0.3~AU with moderately high eccentricity
-($e\sim0.1-0.3$) \footnote{
+($e\sim0.1-0.3$).\footnote{
   The two stars were monitored by \project{HARPS} campaign, and it has recently
@@
   planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
-  within $\approx 0.35$~AU.}.
-They found that the abundances of 15 elements between the two stars are
-consistent with each other.
-However, they argued that there is a moderately significant ($\sim 2\sigma$)
-positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
-{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
-(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
-of their measurements).
-They interpreted that this slope may be evidence for accretion of
-$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
-planet migration.
+  within $\approx 0.35$~AU.}
+The measured abundances of 15 elements in the two stars are consistent
+(\citealt{Mack:2014aa}).
+However, \citealt{Mack:2014aa} argued that there is a moderately significant
+($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
+increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
+Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
+the abundances of each star {\it individually}.
+They suggest that this slope is evidence that the stars accreted
+$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
+migration.
 
 {\bf HAT-P-1:}
-HAT-P-1 is a pair of G0 stars separated 11\arcsec\ apart in sky
-with $\feh\approx0.15$.
-The secondary star in the system is known to host one transiting giant planet
+A pair of G0 stars separated by 11\arcsec\ each with $\feh\approx0.15$ has
+different planetary systems:
+the secondary star is known to host one transiting giant planet
 while no planet has been discovered around the primary star.
-\citealt{Liu:2014aa} found that the two stars are identical in their
-atmospheric composition: \feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for
-the primary and secondary respectively, and $\Delta\elem{X}/\elem{Fe}$ is
-consistent with zero for 23 elements measured with the mean error being
-$0.013$~dex.
-Based on this analysis, they concluded that the presence of close-in giant planet
-does not necessarily lead to stellar atmospheric pollution of the host star.
+The two stars are identical
+in metallicities and abundances for 23 elements measured with
+the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
+Thus it seems that the presence of close-in giant planet does not necessarily
+lead to atmospheric pollution of its host star.
 
 {\bf HD~80606/HD~80607:}
-A pair of G5 stars with super-solar metallicity ($\feh \approx 0.35$),
-HD 80606/HD 80607, has been independently studied by
-\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
-spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
-on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
-planets.
-Both studies have concluded that there is no significant
-chemical difference between the two stars similar to the case of HAT-P-1.
+Similar to HAT-P-1, no significant chemical difference between HD~80606 which
+hosts a very eccentric ($e\approx0.94$) giant planet and HD~80607 which has no
+detected planets are found in this pair of G5 stars with super-solar
+metallicity ($\feh \approx 0.35$;\citealt{Saffe:2015aa,Mack:2016aa}).
 
 {\bf XO-2N/XO-2S:}
-The double star system XO-2 has received much attention due to
+A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
+each hosting planet(s):
+XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
+masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
+0.15$) orbits at $<0.5$~AU.
+The system has received much attention due to
 possibly the most robust and significant difference between the component stars
 among those so far studied.
-XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
-each hosting planet(s).
-XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
-masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
-0.15$) orbits at $<0.5$~AU.
-
-The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
-essentially no significant difference in Fe, Ni, C, and O between the two
-stars.
-However, re-analysis of the system by the same authors using the same data in
-\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
-\Tcondens\ varies significantly depending on the stellar parameters chosen in
-their analysis. Both analyses were based on spectra
-using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
-covering $4450-5660$~\AA\ and $5860-7100$~\AA\ with S/N of $170-230$
-(\citealt{Teske:2013aa}).
-
-Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
-$4080-8300$~\AA) of the component stars with S/N of $350$ (in $5000-7500$~\AA)
-to perform a differential abundance analysis.
-They find that all 23 elements including Fe are enhanced in XO-2N
-compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
-a significant correlation with \Tcondens.
-At low \Tcondens, volatile elements differ by $0.015$~dex
-while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
-There are inconsistencies in the determination of stellar parameters
-(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
-and photometric analysis,
-but the existence of correlation between $\Delta\elem{H}$ and
-\Tcondens\ seems robust.
+%TODO: check following with Biazzo+
+All measured elements including \elem{Fe} are enhanced in XO-2N relative to
+XO-2S, and the difference shows a significant correlation with \Tcondens\
+(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
+\citealt{Teske:2013aa}).
+At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
+difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
 
@@
 refractory enhancement in XO-2N by late time accretion in which case the
-complete opposite would be true.
-
-%TODO: summarize Biazzo+ on XO-2
-%Finally, \citealt{Biazzo:2015aa}
+opposite would be true.
 
 {\bf WASP-94A/WASP-94B:}
-\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
-with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
-host a hot Jupiter.
-The planet hosted by WASP-94A is transiting with a misaligned, probably
-retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
-more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
-star.
-With a claimed median uncertainty of $0.006$~dex among all elements, they
-detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
-elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
-1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
-Excluding K, which is based on one strong line and largely affected by non-LTE
-effect, their analysis shows a statistically significant non-zero slope between
-$\Delta\elemH{X}$ and $\Tcondens$\footnote{
+Each star in a pair of F8 and F9 stars with super-solar metallicity
+($\feh\approx 0.3$) hosts a hot Jupiter.
+The planet around WASP-94A is transiting with a misaligned, probably retrograde
+circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
+massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
+WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
+elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
+elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
+uncertainty of $0.006$~dex among all elements
+resulting in a statistically significant non-zero slope between
+$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
   %TODO: double check the following statement
@@
   temperature $\Tcondens$ used is for solar system composition
-  gas, which can differ from that of higher metallicity gas.}.
-They considered multiple possibilities related to the formation and evolution
+  gas, which can differ from that of higher metallicity gas.}
+Multiple possibilities related to the formation and evolution
 of planetary systems around each star as well as causes unrelated to planets
 such as dust cleansing during the fully convective phase or different rotation
-and granulation between the stars, but did not favor any particular one.
+and granulation between the stars were considered, but none was favored.
 

### 2017-06-08 paper/ms.tex
Minor wording edit.

@@
 By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
-of gas occurs in terms of how much mass is in the convective envelop then, they
-can match the mass difference of gas giant planets around each star, which is
-at least $1~\mjupiter$.
+of gas occurs in terms of how much mass is in the convective envelope of the
+host star, they can match the mass difference of gas giant planets around each
+star, which is at least $1~\mjupiter$.
 On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,

### 2017-06-08 paper/ms.tex
Fix formatting issues

@@
 This enhancement puts an upper limit on the accreted mass to be
-$\approx 4$~\mearth assuming \elem{Li} concentration of $1.1$~ppm
+$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
 (\citealt{mcdonough2001composition}).
-Unlike \bizarreone, we cannot know the pre-accretion abundances of \sunanalog
-\footnote{
+Unlike \bizarreone, we cannot know the pre-accretion abundances of
+\sunanalog.\footnote{
   Strictly speaking, we can never know the pre-accretion abundances
@@
   which indeed seems to be the case according to its \elem{Li} abundance.
-}.
+}
 However, we note that the span of abundance difference between highly volatile

### 2017-06-08 paper/ms.tex
Move dxdv figure.
Clean up text on dxdv.

@@
 % - Use "comoving" instead of "co-moving".
+% - USe "phase space" not "phase-space".
 % - Write elements as \elem{X}.
@@
 
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
+  \end{center}
+  \caption{%
+    Differences in posterior samples over Galactocentric phase-space coordinates
+    for the two stars \sunanalog\ and \bizarreone.
+    \label{fig:dxdv}}
+\end{figure}
+
 \begin{figure}[htpb]
@@
 We start by generating posterior samples over the Heliocentric distance, $r$,
-tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
-given the observed parallax, $\pi$, and proper motion components,
-$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
-By defining the vectors
-% SMOH: I understand you meant hat v_r as the latent true radial velocity but
-% personally think a) it can confuse some people that there are hat quantities
-% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
-% quantities for observed variables and no-hat for latent true ones.
-% SMOH: v_r is missing in the LHS of eq(3)
+tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
+given the observed parallax, $\hat\pi$, and proper motions,
+$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
+We assume the noise is Gaussian, and the radial velocity measurement is
+uncorrelated with the astrometric measurements.
+If we define
 \begin{eqnarray}
-  \vec{y} &=&
+  \vec{\hat y} &=&
       \transp{\left(
         \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
-          \pi &
-          \mu_{\alpha^*} &
-          \mu_\delta &
-          v_r
+          \hat\pi &
+          \hat\mu_{\alpha^*} &
+          \hat\mu_\delta &
+          \hat v_r
         \end{array}
       \right)}\\
-  \hat{\vec{y}} &=&
+  \vec{y} &=&
       \transp{\left(
@@
           r^{-1}\,v_\delta &
-          \hat{v}_r
+          v_r
         \end{array}
@@
 \end{eqnarray}
-and by considering the covariance matrix $\mat{C}$ between the observed
-quantities (provided by \tgas\ and extended to include the uncorrelated radial
-velocity uncertainty), the likelihood can be written
-\begin{eqnarray}
-p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
-  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
-    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
-    \mat{C}^{-1} \,
-    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
-\end{eqnarray}
+then the likelihood is
+\begin{equation}
+  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
+\end{equation} where $\mat{C}$ is the covariance matrix.
+%TODO: what is assumed for uncertanties in RV?
 We adopt a uniform space density prior for the distance and an isotropic
@@
 \end{eqnarray}
+%
 For each of the two stars, we use \project{emcee}
-(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
-v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
-first 512 steps as the burn-in period.
-For each sample, we convert the heliocentric phase-space coordinates into
-Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
-= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
-etc.}).
+(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
+v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
+512 steps as the burn-in period.
+For each sample, we convert the heliocentric phase space coordinates into
+Galactocentric coordinates assuming that the Sun's position and velocity are
+$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot = (10,\,244,\,7.17)~\kms$.
+% TODO: APW (\citealt{bovy, etc.}).
 \figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
-Galactocentric phase-space coordinates for the two stars.
-In all components, the pair is consistent with being co-moving and close in
-separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
-but the median 3-space separation is $\approx$$0.6~\pc$.
-
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
-  \end{center}
-  \caption{%
-    Differences in posterior samples over Galactocentric phase-space coordinates
-    for the two stars \sunanalog\ and \bizarreone.
-    \label{fig:dxdv}}
-\end{figure}
+Galactocentric phase space coordinates for the two stars.
+The differences in positions and velocities are consistent with zero.
 

### 2017-06-08 paper/ms.tex
Edit discussion :scream:

@@
   \centering
+  \includegraphics[width=0.95\linewidth]{spec1.pdf}
+  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
+    Alternating sets of two rows show
+    the continuum-normalized data and model in the upper panel,
+    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
+    in the lower panel.
+  }
+  \label{fig:spec1}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec2.pdf}
+  \caption{Same as \figname~\ref{fig:spec1}
+    but for smaller portions of spectra at longer wavelengths that are
+    not dominated by \elem{Fe}.
+    We mark elements that give rise to strong absorption lines.
+    The feature in the third column of the second row is a strong \elem{Li}
+    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
+    studied in a separate work (\citealt{jmlithium}).
+    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
+    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
+    show weaker residuals.
+  }
+  \label{fig:spec2}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
   \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
@@
 
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec1.pdf}
-  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
-    Alternating sets of two rows show
-    the continuum-normalized data and model in the upper panel,
-    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
-    in the lower panel.
-  }
-  \label{fig:spec1}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec2.pdf}
-  \caption{Same as \figname~\ref{fig:spec1}
-    but for smaller portions of spectra at longer wavelengths that are
-    not dominated by \elem{Fe}.
-    We mark elements that give rise to strong absorption lines.
-    The feature in the third column of the second row is a strong \elem{Li}
-    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
-    studied in a separate work (\citealt{jmlithium}).
-    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
-    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
-    show weaker residuals.
-  }
-  \label{fig:spec2}
-\end{figure}
-
 \sunanalog\ and \bizarreone\ were identified as a
@@
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is
-$5164--7799$~\AA.
+$5164-7799$~\AA.
 A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
@@
 relative to \elem{Fe}.
+Both stars have high surface \elem{Li} abundances, and the difference in
+\elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
+measured.
 
@@
 
-The abundance differences cannot be due to different chemical enrichment
-histories in the disk even if the two stars were of different origin.
-\figname~\ref{fig:deltaXH} additionally shows the distribution of abundance
-differences, $\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars
-with similar \feh\ as \bizarreone\ and \sunanalog\.
-We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
-all other elements are typically enhanced at a similar level, with some variations.
-Specifically, for a typical star with $\feh \approx 0.2$~dex,
-we generally expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
-(\citealt{Battistini:2015aa,Bensby:2003aa})
-making the low [\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\
-very unlikely to arise from variations in Galactic chemical evolution.
-
-% HOGG to provide some theoretical account adding to the above empirical evidence.
+%TODO: what is the histogram of?
+%TODO: plot styles...
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{orbits.pdf}
+  \end{center}
+  \caption{Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
+    For \sunanalog, the initial conditions are set to the median of the
+    posterior sample over the phase space coordinates.
+    The orbits are computed by integrating backwards from the present-day
+    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
+    integration scheme implemented in \project{Gala} (\citealt{gala}).
+  }
+  \label{fig:orbit}
+\end{figure}
 
@@
 \bizarreone-\sunanalog.
-Although the data described above strongly suggests that the two stars are
-coeval, let us first consider scenarios in which the two stars are not actually
-born together.
+We first discuss the ages and coevality of the stars in this pair, and consider
+both possibilities in which the two stars are or are not coeval.
+Our favored scenario is discussed in the last subsection,
+\sectionname~\ref{sub:accretion}.
 
@@
 
-The fact that the two stars share a nearly identical space motion
-at a separation of $< 1$~pc strongly argues that the pair is coeval.
+The fact that the two stars share nearly identical space motion
+at a separation of $< 1$~pc strongly supports that the pair is coeval.
 We therefore consider other age indicators apart from their phase space coordinates
@@
 circumstellar disks.
-We have looked for these signs for the pair to find none, and their spectral energy
-distributions are consistent with blackbody.
+%TODO: refernces
+We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
+and found no evidence for indications of activity in their spectral energy
+distributions.
 The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
-young ages inferred from the surface lithium abundances.
+young ages that would be inferred from the surface lithium abundances.
 % TODO: reference for vertical action as age?
-Finally, the pair's fiducial orbit in a axisymmetric Milky Way-like potential
-has a vertical action larger than the Sun, favoring an older age.
-We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr old main
-sequence stars, and that their unusually high \elem{Li} abundance requires an
-alternative explanation.
-
-\figurename~\ref{fig:orbit} shows an orbit computed from the median posterior
-sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
-in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
-explain}
-The Sun's orbit in this same Milky Way model is under-plotted for comparison
-(grey line); the orbits of the stars in this pair have large scale-heights
-relative to the Sun's orbit despite being young.
-
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{orbits.pdf}
-  \end{center}
-  \caption{%
-    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
-    For \sunanalog\, the initial conditions are set to the median posterior
-    sample over the inferred 6D phase-space coordinates.
-    The orbits are computed by integrating backwards from the present-day
-    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
-    Leapfrog integration scheme implemented in \project{Gala}
-    (\citealt{Gala:2017}). \todo{APW: citation...}
-\label{fig:orbit}}
-\end{figure}
+Finally, we computed the Galactic orbit of the pair using the median of the
+posterior sample over the phase space coordinates of \sunanalog, in a Milky
+Way-like gravitational potential using \project{Gala} (\citealt{gala}).
+%TODO: APW to check (missing) citations
+The pair's fiducial orbit has a vertical action larger than the Sun, favoring
+an older age.
+We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
+old main sequence stars, and that their unusually high \elem{Li} abundance
+requires an alternative explanation.
 
@@
 
-% binary-single and binary-binary exchange
-Two stars unrelated at birth may end up in a binary system via binary-single scattering event
-that results in an exchange of binary member.
+Although the data described above strongly suggests that the two stars are
+coeval, we may still consider scenarios in which the two stars are not actually
+born together.
+Two stars unrelated at birth may end up in a binary system via a binary-single
+scattering event that results in an exchange of binary members.
 In order to estimate the rate at which any binary-single
@@
   \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
+  \label{eq:crosssection}
 \end{eqnarray}
-where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
+where $v$ is the incoming velocity, $v_i$, in units of critical velocity, $v_c$, defined as
 \begin{eqnarray}
-  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
+  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
 \end{eqnarray}
-when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
-which is appropriate for wide binaries scattering with field (disk) stars.
-If we assume that field stars are made of solar mass stars
-with constant number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars
-is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
-stars in any direction, the rate of exchange scattering is
+\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$ (\citealt{Hut:1983aa,Hut:1983ab}),
+which is the case for wide binaries scattering with field (disk) stars.
+If we assume that field stars are made of solar mass stars with a constant
+number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
+$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
+any direction, the rate of exchange scattering is
 \begin{eqnarray}
   n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
-  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
+  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
+  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
 \end{eqnarray}
-low enough to be negligible.
-Because the exchange scattering cross section steeply depends on the incoming velocity
-relative to the critical velocity (of the order of orbital velocity of the binary),
-the rate of exchange scattering with a star within the same star forming region
-may be much larger.
-However, this, or any other exchange scattering scenario,
-is still unsatisfactory as it offers no insight on the
-peculiarity of the abundances of \bizarreone\ (see
-\sectionname~{\ref{sec:data}}).
-In case that the pair formed from an exchange scattering event,
-we would expect the pair to be composed of typical field stars,
-not one with such low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$.
-
-%LEIGH to fill in binary-binary exchange scattering?
-
-The unlikeliness of the above possibilities naturally leads us to consider the
-alternative that their peculiar disparity in chemical abundance space may be
-more naturally explained.
+which is low enough to be negligible.
+
+In fact, any exchange scattering scenario is unsatisfactory as typical
+field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
+unlikely to show the abundance difference pattern observed.
+In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
+\bizarreone-\sunanalog\ with the distribution of abundance differences,
+$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
+\feh\ as \bizarreone\ and \sunanalog.
+We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
+all other elements are typically enhanced at a similar level, with some variations.
+Specifically, for a typical star with $\feh \approx 0.2$~dex, we generally
+expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
+(\citealt{Battistini:2015aa,Bensby:2003aa}) making the low
+[\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
+unlikely to arise from variations in Galactic chemical evolution.
+
+% HOGG to provide some theoretical account adding to the above empirical evidence.
 
@@
 
-% inhomogeneity in star formation
-It may be that the two stars are born at the same time from the same cloud, but
-there is chemical inhomogeneity within the cloud.
-However, there is already ample amount of evidence against such scenario.
+In case we assume that the two stars were born together, one possibility to
+explain the chemical difference is that there was chemical inhomogeneity within
+the birth cloud.
+However, there is already ample evidence against such a scenario.
 First, none of the other seven similar wide binaries examined in
-\citealt{2016ApJS..225...32B} show the same level differences in abundances
-although there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
-$\elem{O}$, and some pairs show a large as $\approx 0.15$~dex difference in
-particular elements.
+\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
+Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
+$\elem{O}$, and some pairs show a difference in particular elements as large as
+$\approx 0.15$~dex.
 The median and maximum \feh\ difference between component stars in the other
 seven pairs is $0.02$~dex and $0.09$~dex, respectively.
-The differences are even smaller (maximum $\Delta\feh = 0.03$~dex)
-if we compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs.
+The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
+compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
+(\figname~\ref{fig:deltaXH}).
 This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
-23 wide binaries of late F to K dwarfs, and found most pairs show difference in
+23 wide binaries of late F to K dwarfs, and found most pairs show a difference in
 \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
-Similarly \citealt{Gratton:2001aa} found that four out of six equal mass binaries
+Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass binaries
 have the same chemical composition with $\gtrsim 0.01$~dex uncertainties.
-Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair
-cannot be due to chemical inhomogeneity in the birth cloud.
-
-\subsection{Accretion of rocky planetary material}
-\label{sub:accretion}
-
-% rocky planets (or the like) engulfment
-Yet another more exotic possibility is that a star's surface abundance may
-be altered by accretion of planetary material after birth.
-Instabilities may develop in a multi-planet system due to its chaotic nature
-which may lead to planet engulfment or ejection by the host star.
-%TODO: needs references
-%TODO: kozai?
-Indeed, it is an important goal of many exoplanet studies
-to detect chemical signatures of planet formation or accretion,
-distinguish them from Galactic chemical evolution, and
-connect them to theories of evolution of planetary systems.
-One approach that is free from confusion with Galactic chemical evolution
-is to compare two almost identical stars in a wide binary system,
-which are assumed to be born together.
-Assuming that the component stars were born together with identical
-initial composition, we may see a difference in their surface abundances
-if the two stars then went through different amount of accretion
-of planetary material.
-This abundance difference may depend on the condensation temperatures of
-elements in the protoplanetary disks from which the accreted planets formed
-as their compositions depend on the radial temperature gradient in the disk.
-%TODO: cautions on condensation temperature
-% 1. it is just a proxy
-% 2. it is **equlibrium** condensation temperature
-
-We now turn to \bizarreone-\sunanalog\ pair.
-In Figure~\ref{fig:relabun_tcrank}, we show the abundace difference
-between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
-of each element.
-The equilibrium condensation temperatures for the composition of solar system
-are taken from \citealt{2003ApJ...591.1220L} (Table~8).
-The difference seen in \bizarreone-\sunanalog\ is
-compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
-The metallicity difference of $\approx 0.2$~dex observed in this pair
-is larger than the differences seen in any other pairs studied so far.
-%Indeed, some may consider such large difference in metallicity
-%enough to concluded that the two stars are completely unrelated.
-Strikingly, the five under-enhanced elements in \bizarreone\
-relative to \sunanalog\ are the five most volatile in all elements measured.
-The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
-\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
-This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
-combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
-strongly suggests that accretion of rocky material has occured in \bizarreone.
-
-How much mass of rocky material is needed to explain an increment of $\approx 0.2$~dex?
-One can carry out simple toy calculations of expected $\Delta\elemH{X}$
-in a Sun-like star's atmosphere when adding material of e.g., bulk Earth composition
-under these simplifying assumptions:
-\begin{itemize}
-  \item The material added is instantly and completely mixed.
-  \item The atmospheric composition that we measure is identical throughout
-    the star's radiative and convective zone.
-  \item The surface abundance of the star has been altered once only by this
-    accretion event, and remained the same since.
-\end{itemize}
-
-We take the solar abundances $\elemH{X}$ of \citealt{Asplund:2009aa}
-which can be converted to mass fraction in each element $X$ as in
-\begin{equation}
-  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
-\end{equation}
-where $m_X$ is the mass of each element in e.g., atomic mass unit.
-One can check that the \citealt{Asplund:2009aa} abundances
-are consistent with mass fraction in \elem{H}, \elem{He} and metals
-$X,\,Y,\,Z=0.757,\,0.249,\,0.0134$ as stated in that work.
-Assuming a fraction of the star's convective zone in mass $f_\mathrm{CZ}$,
-and that the added material has a total mass $M_\mathrm{add}$ and mass fraction in each
-element $f_{X,\mathrm{add}}$,
-the abundance difference is
-\begin{equation}
-  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star} + f_{X,\mathrm{add}}\,M_\mathrm{add}}
-    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
-\end{equation}
-We take the composition of bulk Earth from a chondritic model of the Earth
-(\citealt{mcdonough2001composition}).
-
-Figure~\ref{fig:toycalc} shows the expected change of surface abundances of
-metals in a Sun-like star after $20~\mearth$ of material with composition of
-bulk Earth is added.
-It has been long known that compared to CI or other carbonaceous chondrites,
-the composition of the Earth shows a volatilaity trend that moderately volatile
-elements (including Mn and Na) and volatile elements are incearsingly more
-depleted with decreasing condensation temperature
-(\citealt{mcdonough2001composition}).
-This trend is presumed to be closely related to the formation of terrestrial
-planets in particular to the radial temperature gradient in a protoplanetary
-disk.
-Given the simplistic assumptions laid out above, and the uncertainties in our
-current knowledge of the compositions of terrestrial planets including bulk
-Earth, the match between our toy calculation and the observed abundance
-difference between \bizarreone\ and \sunanalog\ is remarkable.
-
-% some discussion of individual elements
-
-What about \elem{Li}?
-The element \elem{Li} is worth a special attention in the context of accretion scenario.
-Because Li is present in either carbonaceous chondrites or the bulk Earth with
-a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition}),
-but is depleted quickly within the first couple of Gyrs on the surface of a
-Sun-like star, accretion of either material at later times will significantly
-replenish the lithium on the star's surface.
-For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
-material results in $\Delta\elemH{Li} \approx 1.6$~dex (which
-is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
-Incidentally, the star under examination, \bizarreone, has an age (informed by
-stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
-Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
-to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
-in its \elem{Li}.
-This is in fact exactly what we find: the \elem{Li} abundance of \bizarreone\ is
-$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
-approximately $1.65$~dex higher than the solar value of $1.1$~dex.
-%TODO: solar Li needs reference
-Furthermore, this implies that the accretion event should have happened very
-recently from a time ago that is shorter than the \elem{Li} depletion time.
-
-%TODO: not sure if this is too obvious of a point or useful in practice..
-%It is further worth pointing out that measuring the \elem{Li} abundance
-%with some of the refractory elements such as $\elem{Fe}$
-%provides a way to estimate the time of the event.
-%If the observed \elem{Li} abundance is less than what is inferred from
-%abundance differences of other elements, and
-%we have a model of \elem{Li} depletion, the time of \elem{Li} enhancement
-%may be calculated.
-
-What about \sunanalog?
-\sunanalog\ is also enhanced in \elem{Li} considering its age of
-$4.00_{-1.56}^{+1.51}$~Gyr than the nominal \elem{Li} depletion predics by
-$\approx 1$~dex.
-This enhancement puts an upper limit on the accreted mass to be
-$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
-(\citealt{mcdonough2001composition}).
-Unlike \bizarreone, we cannot know the pre-accretion abundances of
-\sunanalog.\footnote{
-  Strictly speaking, we can never know the pre-accretion abundances
-  for \bizarreone\ either.
-  We only have an {\it approximate} idea that this is not far from a solar-twin
-  star \sunanalog, and because the deviation from this ``anchor'' star is
-  large, it is reasonable to consider an accretion by the Sun.
-  In reality, \sunanalog\ may as well have had its own accretion history,
-  which indeed seems to be the case according to its \elem{Li} abundance.
-}
-However, we note that the span of abundance difference between highly volatile
-elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
-as \elem{Fe} expected from accreting $4$~\mearth to the Sun is $\approx
-0.05$~dex.
-This is comparable to the abundance difference between N, Na and Fe in
-\sunanalog.
-It is also interesting that \sunanalog\ also shows a deficit in the same
-volatile and moderately volatile elements
-(\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}) relative to Fe
-just as in \bizarreone.
-Thus, we conclude that \sunanalog\ is also likely to have had a similar
-accretion event, but the amount of accretion was much smaller than \bizarreone.
-
-%TODO: augment this paragraph
-% - more geochemical study references
-We stress that while the calculation carried out is useful in
-order-of-magnitude sense, further investigation of each of the simplifying
-assumptions made is warranted.
-In addition, the composition of bulk Earth also has some uncertainties.
-For example, the reported bulk Earth concentration of the siderphile element
-\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
-While the latter value from \citealt{mcdonough2001composition} has been used in
-our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
-to an even closer agreement.
-Given these limitations, the level of agreement for the refractory {\it and}
-\elem{Li} for \bizarreone\ is remarkable.
+Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
+not likely due to chemical inhomogeneity in the birth cloud.
 
@@
 
+\subsection{Accretion of rocky planetary material}
+\label{sub:accretion}
+
+Another possibility that two coeval stars may end up with different surface
+abundances is accretion of planetary material after birth.
+Instabilities may develop in a multi-planet system due to its chaotic nature
+which may lead to planet engulfment or ejection by the host star.
+%TODO: needs references
+%TODO: kozai?
+Indeed, it is an important goal of many exoplanet studies
+to detect chemical signatures of planet formation or accretion,
+distinguish them from Galactic chemical evolution, and
+connect them to theories of evolution of planetary systems.
+One approach that is free from confusion with Galactic chemical evolution
+is to compare two almost identical stars in a wide binary system.
+Assuming that the component stars were born together with identical
+initial composition, we may see a difference in their surface abundances
+if the two stars then accreted different amounts of accretion
+of planetary material.
+The resulting abundance difference may depend on the condensation
+temperatures of elements in the protoplanetary disks from which the accreted
+planets formed, as their compositions depend on the radial temperature gradient
+in the disk.
+%TODO: cautions on condensation temperature
+% 1. it is just a proxy
+% 2. it is **equlibrium** condensation temperature
+
+In Figure~\ref{fig:relabun_tcrank}, we show the abundace difference
+between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
+of each element.
+The equilibrium condensation temperatures for the composition of solar system
+are taken from \citealt{2003ApJ...591.1220L} (Table~8).
+The difference seen in \bizarreone-\sunanalog\ is
+compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
+The metallicity difference of $\approx 0.2$~dex observed in this pair
+is larger than the differences seen in any other pairs studied so far.
+Strikingly, the five under-enhanced elements in \bizarreone\
+relative to \sunanalog\ are the five most volatile in all elements measured.
+The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
+\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
+This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
+combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
+strongly suggests that accretion of rocky material has occured in \bizarreone.
+
+How much mass of rocky material is needed to explain an increment of $\approx 0.2$~dex?
+We carry out simple toy calculations of expected $\Delta\elemH{X}$
+in a Sun-like star's atmosphere by adding certian mass of bulk Earth composition
+under these simplifying assumptions:
+\begin{itemize}
+  \item The material added is instantly and completely mixed.
+  \item The atmospheric composition that we measure is identical throughout
+    the star's radiative and convective zone.
+  \item The surface abundance of the star has been altered only by the
+    accretion event(s).
+\end{itemize}
+
+We take the solar abundances, $\elemH{X}$, of element \elem{X}
+(\citealt{Asplund:2009aa}) which can be converted to mass fraction as
+\begin{equation}
+  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
+\end{equation}
+where $m_X$ is the mass of each element in e.g., atomic mass unit.
+Assuming that the added material has a total mass $M_\mathrm{add}$, and the
+mass fraction in each element $f_{X,\mathrm{add}}$,
+the abundance difference is
+\begin{equation}
+  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
+    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
+    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
+\end{equation}
+where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
+We take the composition of bulk Earth from a chondritic model of the Earth
+(\citealt{mcdonough2001composition}).
+
+Figure~\ref{fig:toycalc} shows the expected change of surface abundances of
+metals in a Sun-like star after $20~\mearth$ of material with composition of
+bulk Earth is added.
+A volatility trend that more volatile (low \Tcondens) elements are more
+depleted in the Earth relative to CI or other carbonaceous chondrites
+has long been known (\citealt{mcdonough2001composition}).
+This trend is presumed to be closely related to the formation of terrestrial
+planets and, in particular to the radial temperature gradient in a
+protoplanetary disk.
+The trend resulting from adding $20~\mearth$ of bulk Earth
+provides an overall good match to the observed $\Delta\elemH{X}$,
+suggeting that the refractory-enhanced star, \bizarreone\,
+accreted $20~\mearth$ more of rocky planetary material than \sunanalog.
+
+What about \elem{Li}?
+The element \elem{Li} is worth special attention in the context of the
+accretion scenario.
+Because Li is present in either carbonaceous chondrites or bulk Earth with
+a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition}),
+but is depleted quickly within the first couple of Gyrs on the surface of a
+Sun-like star, accretion of either material at later times will significantly
+replenish the lithium on the star's surface.
+For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
+material results in $\Delta\elemH{Li} \approx 1.6$~dex (which
+is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
+Incidentally, the star under examination, \bizarreone, has an age (informed by
+stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
+Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
+to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex
+enhancement in its \elem{Li}.
+This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
+approximately $1.65$~dex higher than the solar value of $1.1$~dex.
+%TODO: solar Li needs reference
+Furthermore, this implies that the accretion event should have happened very
+recently, or at least within the \elem{Li} depletion time.
+
+What about \sunanalog?
+Considering its age of $4.00_{-1.56}^{+1.51}$~Gyr, \sunanalog\ is also enhanced
+in \elem{Li} compared to other stars of similar ages by $\approx 1$~dex.
+This enhancement puts an upper limit on the accreted mass to be
+$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
+(\citealt{mcdonough2001composition}).
+Unlike \bizarreone, we cannot know the pre-accretion abundances of
+\sunanalog.\footnote{
+  Strictly speaking, we can never know the pre-accretion abundances
+  for \bizarreone\ either.
+  We only have an {\it approximate} idea that this is not far from a solar-twin
+  star \sunanalog, and because the deviation from this ``anchor'' star is
+  large, it is reasonable to consider accretion by the Sun.
+  In reality, \sunanalog\ may as well have had its own accretion history,
+  which indeed seems to be the case according to its \elem{Li} abundance.
+}
+However, we note that the span of abundance difference between highly volatile
+elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
+as \elem{Fe} expected from accreting $4$~\mearth to the Sun is $\approx
+0.05$~dex.
+This is comparable to the abundance difference between N, Na and Fe in
+\sunanalog.
+It is also interesting that \sunanalog\ shows a deficit in the same volatile
+and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
+\elem{Mn}) relative to Fe as in \bizarreone.
+Thus, we conclude that \sunanalog\ is also likely to have had a similar
+accretion event, but the amount of accretion was much smaller than \bizarreone.
+
+%TODO: augment this paragraph
+% - more geochemical study references
+We stress that while the calculation carried out is useful in
+order-of-magnitude sense, further investigation of each of the simplifying
+assumptions made is warranted.
+In addition, the composition of bulk Earth also has some uncertainties.
+For example, the reported bulk Earth concentration of the siderphile element
+\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
+While the latter value from \citealt{mcdonough2001composition} has been used in
+our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
+to an even closer agreement.
+Given these limitations, the level of agreement for the refractory {\it and}
+\elem{Li} for \bizarreone\ is remarkable.
+
 \section{Summary}

### 2017-06-08 paper/ms.tex
Delete rant.

@@
 
-% somewhat of a rant that can be removed ...
-The investigation and conclusion on this puzzling comoving pair, like any other
-problem, depends strongly on one's prior belief.
-A difference of $\approx 0.2$~dex in \feh\ may enough for one to conclude that
-the two stars are unrelated and their proximity in phase space is by chance.
-On the other hand, if one has a stronger prior belief that two stars in such
-proximity in phase space ought to be of the same birth origin, and thus
-must have had near-identical chemical composition at birth, an engulfment of
-refractory-rich planetary material provides an explanation for their
-$\Tcondens$-dependent abundance difference.
-
 %TODO: Implications

### 2017-06-08 paper/ms.tex
Question to APW.
En-dashes are important.
phase space phase-space

@@
 % - Use "comoving" instead of "co-moving".
-% - USe "phase space" not "phase-space".
+% - Use "phase space" not "phase-space", "phase-space coordinates" not "phase space coordinates".
 % - Write elements as \elem{X}.
@@
   wide binary pairs yet.
-  The proximity in phase space and ages between the two stars suggests that
+  The proximity in phase-space and ages between the two stars suggests that
   they formed together with the same composition, at odds with the observed
@@
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is
-$5164-7799$~\AA.
+$5164$--$7799$~\AA.
 A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
@@
 Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
-can compare differences between the inferred 6D phase space coordinates of the
+can compare differences between the inferred 6D phase-space coordinates of the
 two stars.
@@
 512 steps as the burn-in period.
-For each sample, we convert the heliocentric phase space coordinates into
+For each sample, we convert the heliocentric phase-space coordinates into
 Galactocentric coordinates assuming that the Sun's position and velocity are
@@
 \figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
-Galactocentric phase space coordinates for the two stars.
+Galactocentric phase-space coordinates for the two stars.
 The differences in positions and velocities are consistent with zero.
@@
 
-%TODO: what is the histogram of?
+%TODO: APW what is the histogram of?
 %TODO: plot styles...
@@
     For \sunanalog, the initial conditions are set to the median of the
-    posterior sample over the phase space coordinates.
+    posterior sample over the phase-space coordinates.
     The orbits are computed by integrating backwards from the present-day
@@
 at a separation of $< 1$~pc strongly supports that the pair is coeval.
-We therefore consider other age indicators apart from their phase space coordinates
-to assess the ages and coevality of the two stars.
+We therefore consider other age indicators apart from their phase-space
+coordinates to assess the ages and coevality of the two stars.
 First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,

### 2017-06-08 paper/ms.tex
linewraps

@@
 \author[0000-0001-7790-5308]{Semyeong Oh}
-\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
+  Princeton, NJ 08544, USA}
 \affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}
@@
 \author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
-\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
+  Princeton, NJ 08544, USA}
 
 \author{John M. Brewer} % TODO: need ORCID
-\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
+\affil{Department of Astronomy, Yale University, 260 Whitney Ave,
+  New Haven, CT 06511, USA}
 
 \author[0000-0003-2866-9403]{David W. Hogg}
-\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
-\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, room 1005, New York, NY 10003, USA}
-\affil{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
+\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
+  New York, NY 10010, USA}
+\affil{Center for Cosmology and Particle Physics,
+  Department of Physics, New York University, 726 Broadway,
+  New York, NY 10003, USA}
+\affil{Center for Data Science, New York University, 60 Fifth Ave,
+  New York, NY 10011, USA}
 \affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg}
@@
 \author{David N. Spergel} % TODO: need ORCID
-\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
+  Princeton, NJ 08544, USA}
+\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
+  New York, NY 10010, USA}
 
@@
   yet both stars show high surface \elem{Li} abundance for this age.
-  The more metal-rich of the two, HD~240430, shows an enhancement of
-  refractory ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as
-  large enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
+  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
+  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
+  enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
   \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}):
@@
   differences in metallicity and abundance patterns.
-  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted $\approx 20$~\mearth\ of
-  rocky material after birth selectively enhancing the refractory elements in
-  its surface and convective envelope.
-  The other star HD~240429, ``Krios'', may also have had a similar accretion event given
-  its high surface \elem{Li} abundance but of much smaller amount
+  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
+  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
+  refractory elements in its surface and convective envelope.
+  The other star HD~240429, ``Krios'', may also have had a similar accretion
+  event given its high surface \elem{Li} abundance but of much smaller amount
   ($\approx 4$~\mearth).
@@
 
-In fact, the surface lithium abundance is the only indication that points to younger ages.
+In fact, the surface lithium abundance is the only indication that points to
+younger ages.
 If the two stars are indeed only several hundred Myrs old at most,
@@
 \end{eqnarray}
-where $v$ is the incoming velocity, $v_i$, in units of critical velocity, $v_c$, defined as
+where $v$ is the incoming velocity, $v_i$, in units of critical velocity,
+$v_c$, defined as
 \begin{eqnarray}
@@
 \end{eqnarray}
-\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$ (\citealt{Hut:1983aa,Hut:1983ab}),
-which is the case for wide binaries scattering with field (disk) stars.
+\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
+(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
+scattering with field (disk) stars.
 If we assume that field stars are made of solar mass stars with a constant
@@
 This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
-23 wide binaries of late F to K dwarfs, and found most pairs show a difference in
-\feh\ less than $0.02$~dex and none larger than $0.07$~dex.
-Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass binaries
-have the same chemical composition with $\gtrsim 0.01$~dex uncertainties.
+23 wide binaries of late F to K dwarfs, and found most pairs show a difference
+in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
+Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
+binaries have the same chemical composition with $\gtrsim 0.01$~dex
+uncertainties.
 Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
@@
 
-How much mass of rocky material is needed to explain an increment of $\approx 0.2$~dex?
+How much mass of rocky material is needed to explain an increment of
+$\approx 0.2$~dex?
 We carry out simple toy calculations of expected $\Delta\elemH{X}$

### 2017-06-09 paper/ms.tex
Add software ack.
Remove todo.
No also.
fix title grammar

@@
   Kronos \& Krios:
-  Evidence for accretion of massive, rocky planetary system in a sun-like pair
+  Evidence for accretion of a massive, rocky planetary system in a sun-like pair
 }
@@
 \end{equation} where $\mat{C}$ is the covariance matrix.
-%TODO: what is assumed for uncertanties in RV?
 We adopt a uniform space density prior for the distance and an isotropic
@@
 assumptions made is warranted.
-In addition, the composition of bulk Earth also has some uncertainties.
+In addition, the composition of bulk Earth has some uncertainties.
 For example, the reported bulk Earth concentration of the siderphile element
@@
   \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
+  \texttt{emcee} (\citealt{2013PASP..125..306F}),
   \texttt{IPython} (\citealt{Perez:2007}),

### 2017-06-09 paper/ms.tex
fill in TODOs, create a new one

@@
 Galactocentric coordinates assuming that the Sun's position and velocity are
-$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot = (10,\,244,\,7.17)~\kms$.
-% TODO: APW (\citealt{bovy, etc.}).
+$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
+(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.
+
 \figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
@@
 The differences in positions and velocities are consistent with zero.
+\todo{should we instead show $|\Delta\boldsymbol{x}|$ and
+$|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
 
@@
 posterior sample over the phase space coordinates of \sunanalog, in a Milky
-Way-like gravitational potential using \project{Gala} (\citealt{gala}).
-%TODO: APW to check (missing) citations
+Way-like gravitational potential (similar to \texttt{MWPotential2014} from
+\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring

### 2017-06-09 paper/ms.tex
space in todo
oops, explain histogram too

@@
 
-\newcommand{\todo}[1]{{\color{blue}TODO:#1}}
+\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
 
@@
 
-%TODO: APW what is the histogram of?
 %TODO: plot styles...
@@
   \end{center}
-  \caption{Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
+  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
+    Sun (grey).
     For \sunanalog, the initial conditions are set to the median of the
-    posterior sample over the phase-space coordinates.
+    posterior samples over the phase-space coordinates.
     The orbits are computed by integrating backwards from the present-day
@@
     integration scheme implemented in \project{Gala} (\citealt{gala}).
+    Right panel: distribution of maximum $z$-heights for orbits computed from
+    all posterior samples.
   }

### 2017-06-09 paper/ms.tex
Make some todos visible.

@@
 X-ray emission from magnetic activity, emission lines, or infrared excess due to
-circumstellar disks.
-%TODO: refernces
+circumstellar disks (\todo{needs refernces}).
 We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
@@
 young ages that would be inferred from the surface lithium abundances.
-% TODO: reference for vertical action as age?
 Finally, we computed the Galactic orbit of the pair using the median of the
@@
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age.
+an older age (\todo{needs references for vertical action as age indicator}).
 We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
@@
 Instabilities may develop in a multi-planet system due to its chaotic nature
-which may lead to planet engulfment or ejection by the host star.
-%TODO: needs references
+which may lead to planet engulfment or ejection by the host star
+(\todo{needs references}).
 %TODO: kozai?
@@
 $A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
-approximately $1.65$~dex higher than the solar value of $1.1$~dex.
-%TODO: solar Li needs reference
+approximately $1.65$~dex higher than the solar value of $1.1$~dex
+(\todo{needs reference}).
 Furthermore, this implies that the accretion event should have happened very

### 2017-06-09 paper/ms.tex
Break paragraph.
Tweak last par in intro.

@@
 condensation temperature (\Tcondens).
+
 Several systems in which at least one star hosts at least one planet
@@
 Here, we report and discuss the discovery of a comoving pair of solar twin stars,
-HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
-that strongly suggest dramatic accretion of planetary material by the two stars.
-We nickname the two stars \bizarreone\ (HD~240430) and
-\sunanalog\ (HD~240429) throughout the \documentname.
+HD~240430 and HD~240429, with unusual chemical abundance differences
+that strongly suggest accretion of planetary material by the two stars.
+Throughout the \documentname, we nickname the two stars \bizarreone\
+(HD~240430) and \sunanalog\ (HD~240429).
+We use the following convention for chemical abundances of stars: \elemH{X} is
+the ratio of number density of element \elem{X} to \elem{H} relative to the
+solar value.
+The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
+(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
+\elem{X}.
 In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
@@
 We summarize our discussions in \sectionname~\ref{sec:summary}.
-
-Throughout the \documentname\, we use the following convention for
-chemical abundances of stars: \elemH{X} is the ratio of number density of
-element \elem{X} to \elem{H} relative to the solar value.
-The absolute abundance of \elem{X} is
-$A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
-where $n_\elem{X}$ is the number density of element \elem{X}.
 

### 2017-06-09 paper/ms.tex
Tweaks

@@
 any trend in $\Delta\elemH{X}$ with \Tcondens.
-%TODO: needs to include **16 Cyg** and HD~133131AB
+(\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added})
 
@@
 {\bf HAT-P-1:}
-A pair of G0 stars separated by 11\arcsec\ each with $\feh\approx0.15$ has
+A pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
 different planetary systems:
@@
 {\bf HD~80606/HD~80607:}
-Similar to HAT-P-1, no significant chemical difference between HD~80606 which
-hosts a very eccentric ($e\approx0.94$) giant planet and HD~80607 which has no
-detected planets are found in this pair of G5 stars with super-solar
-metallicity ($\feh \approx 0.35$;\citealt{Saffe:2015aa,Mack:2016aa}).
+Similar to HAT-P-1, no significant chemical difference is found between two
+common proper motion G5 stars with super-solar metallicity ($\feh \approx
+0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
+HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).
 
 {\bf XO-2N/XO-2S:}
-A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
-each hosting planet(s):
+A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
+has received much attention due to possibly the most robust and significant
+difference between the component stars.
 XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
@@
 0.15$) orbits at $<0.5$~AU.
-The system has received much attention due to
-possibly the most robust and significant difference between the component stars
-among those so far studied.
 %TODO: check following with Biazzo+
@@
 to an even closer agreement.
-Given these limitations, the level of agreement for the refractory {\it and}
+Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
 \elem{Li} for \bizarreone\ is remarkable.

### 2017-06-13 paper/ms.tex
hogg todo and acks
Add Brewer ORCID
Edit title and abstract

@@
   Kronos \& Krios:
-  Evidence for accretion of a massive, rocky planetary system in a sun-like pair
+  Evidence for accretion of a massive, rocky planetary system
+  in a comoving pair of G dwarfs
 }
@@
 
-\author{John M. Brewer} % TODO: need ORCID
+\author[0000-0002-9873-1471]{John M. Brewer}
 \affil{Department of Astronomy, Yale University, 260 Whitney Ave,
@@
 \begin{abstract}
-  We report and discuss the discovery of a comoving pair of bright solar-type
+  We report and discuss the discovery of a comoving pair of bright G
   stars, HD~240430 and HD~240429, with a significant difference in their
@@
   indicate that both stars are $\sim 4$~Gyr old,
-  yet both stars show high surface \elem{Li} abundance for this age.
+  yet both stars show very high surface \elem{Li} abundance for this age.
   The more metal-rich of the two, HD~240430, shows an enhancement of refractory
   ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
-  enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
-  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}):
-  this is the largest and the most significant difference found in
-  wide binary pairs yet.
+  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
+  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
+  This is the largest and the most significant chemical difference found in
+  a wide binary pair yet.
   The proximity in phase-space and ages between the two stars suggests that
@@
   Follow-ups to study the existence and properties of the planetary systems
-  around these stars will help illuminate more on planet-star interactions.
+  around these stars will help illuminate planet-star interactions.
 \end{abstract}
@@
 
-% HOGG to provide some theoretical account adding to the above empirical evidence.
+\todo{HOGG: to provide some theoretical account adding to the above empirical evidence.}
 
@@
 
+We thank Nathan Leigh and Keith Hawkins for valuable discussions.
+
 % Gaia

### 2017-06-15 paper/ms.tex
Edit wording and fix small bugs

@@
 \newcommand{\kms}{\ensuremath{\rm km~s^{-1}}}
-\newcommand{\msun}{{\rm M}_\odot}
+\newcommand{\msun}{\ensuremath{{\mathrm M}_\odot}}
 \newcommand{\pc}{{\rm pc}}
@@
   ($\approx 4$~\mearth).
-  Follow-ups to study the existence and properties of the planetary systems
-  around these stars will help illuminate planet-star interactions.
+  %Follow-ups to study the existence and properties of the planetary systems
+  %around these stars will help illuminate planet-star interactions.
 \end{abstract}
@@
 
-Given their proximity in phase space, it is generally accepted to assume that
-the two stars were born together and, perhaps, are a bound wide binary system.
+For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
+1.2~pc (\citealt{jiangtremaine2010}).
+%TODO
+\bizarreone\ and \sunanalog\ are likely a bound system that formed coevally.
 Thus, we expect the two stars to have identical metallicities and abundance patterns.
-Surprisingly, one of the stars, \bizarreone\ is significantly more metal
+However, one of the stars, \bizarreone\ is significantly more metal
 rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
-Even more puzzling is that not all elements are equally enhanced:
+Moreover, not all elements are equally enhanced:
 the abundances of \bizarreone\ show selective depletion in
@@
 We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
-\lesssim 100$~K) wide binary pairs examined in \citealt{2016ApJS..225...32B}
+\lesssim 100$~K) wide binary pairs examined by \citealt{2016ApJS..225...32B}
 show discrepancies in abundances between the stars at this level.
@@
 \begin{eqnarray}
-  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
+  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
   \label{eq:crosssection}
 \end{eqnarray}
-where $v$ is the incoming velocity, $v_i$, in units of critical velocity,
-$v_c$, defined as
+where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
+defined as
 \begin{eqnarray}
@@
 
-In case we assume that the two stars were born together, one possibility to
+Assuming that the two stars were born together, one possibility to
 explain the chemical difference is that there was chemical inhomogeneity within
@@
 For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
-material results in $\Delta\elemH{Li} \approx 1.6$~dex (which
+material would result in $\Delta\elemH{Li} \approx 1.6$~dex (which
 is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
@@
 Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
-to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex
+to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
 enhancement in its \elem{Li}.
@@
 Furthermore, this implies that the accretion event should have happened very
-recently, or at least within the \elem{Li} depletion time.
+recently, or at least within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
 
@@
 elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
-as \elem{Fe} expected from accreting $4$~\mearth to the Sun is $\approx
+as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
 0.05$~dex.
@@
 Thus, we conclude that \sunanalog\ is also likely to have had a similar
-accretion event, but the amount of accretion was much smaller than \bizarreone.
+accretion event, but the amount of accretion was at least 5 time
+smaller than \bizarreone.
 
@@
 search for the existence and architectures of the planetary systems left
-behind, and whether they are very different between the two stars.
+behind.
 

### 2017-06-15 paper/ms.tex
Add acknowledgements

@@
 composition to \bizarreone\ can explain the enhancement in both refractory
-elements and the \elem{Li}.
+elements and lithium.
 For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
@@
 
-We thank Nathan Leigh and Keith Hawkins for valuable discussions.
+We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
+for valuable discussions and feedback.
+The Flatiron Institute is supported by the Simons Foundation.
 

### 2017-06-15 paper/ms.tex
Tweaks from Bedell's comments

@@
 
-Here, we report and discuss the discovery of a comoving pair of solar twin stars,
+Here, we report and discuss the discovery of a comoving pair of G stars,
 HD~240430 and HD~240429, with unusual chemical abundance differences
@@
 We carry out simple toy calculations of expected $\Delta\elemH{X}$
-in a Sun-like star's atmosphere by adding certian mass of bulk Earth composition
+in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
 under these simplifying assumptions:
@@
 (\citealt{mcdonough2001composition}).
+Similar calculations have been performed by \citet{Chambers:2010aa} and
+\citet{Mack:2014aa,Mack:2016aa}.
 

### 2017-06-15 paper/ms.tex
Many typos and dumb mistakes

@@
 We use the following convention for chemical abundances of stars: \elemH{X} is
-the ratio of number density of element \elem{X} to \elem{H} relative to the
+the log ratio of number density of element \elem{X} to \elem{H} relative to the
 solar value.
@@
     in \citealt{2016ApJS..225...32B} at two metallicity bins,
-    $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
+    $-0.025 < \feh < 0.025$ (160 stars) and $0.175 > \feh > 0.225$ (137 stars),
     similar to \bizarreone\ and \sunanalog.
@@
 using \tgas\ that the two stars belong to a larger group of young stars.
-Very young stars are often show signs of activity such as
+Very young stars often show signs of activity such as
 X-ray emission from magnetic activity, emission lines, or infrared excess due to
@@
 initial composition, we may see a difference in their surface abundances
-if the two stars then accreted different amounts of accretion
-of planetary material.
+if the two stars then accreted different amounts of planetary material.
 The resulting abundance difference may depend on the condensation
@@
 
-In Figure~\ref{fig:relabun_tcrank}, we show the abundace difference
+In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
 between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
@@
 provides an overall good match to the observed $\Delta\elemH{X}$,
-suggeting that the refractory-enhanced star, \bizarreone\,
+suggesting that the refractory-enhanced star, \bizarreone\,
 accreted $20~\mearth$ more of rocky planetary material than \sunanalog.
@@
 We stress that while the calculation carried out is useful in
-order-of-magnitude sense, further investigation of each of the simplifying
+an order-of-magnitude sense, further investigation of each of the simplifying
 assumptions made is warranted.

### 2017-06-17 paper/ms.tex
Trim text roughly

@@
 \usepackage{microtype}  % ALWAYS!
-\usepackage{amsmath,amssymb,natbib}
-\usepackage[flushleft]{threeparttable}
+\usepackage{amsmath,amssymb}
+\usepackage{natbib}
 \hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
 \graphicspath{{figures/}}
-\bibliographystyle{aasjournal}
 
@@
 \begin{abstract}
-  We report and discuss the discovery of a comoving pair of bright G
-  stars, HD~240430 and HD~240429, with a significant difference in their
-  chemical abundances.
-  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
-  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
-  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
-  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
-  high-resolution radial velocity measurements.
-  Stellar parameters determined from high-resolution Keck HIRES spectra
-  indicate that both stars are $\sim 4$~Gyr old,
-  yet both stars show very high surface \elem{Li} abundance for this age.
+
+  Stars that are born together are expected to have same space motion and chemical compositions initially.
+  Detailed chemical abundance studies of stars in wide binaries indeed reveal nearly identical
+  chemistry in most cases.
+  However, formation and evolution of different planetary systems around each star in a wide binary
+  may eventually lead to a difference in the compositions of the stars' radiative and convective layers.
+  A handful of wide binaries that show small differences in their surface chemical abundance have been reported so far.
+  However, no pair .
+  Here we report a comoving pair of bright G stars, HD~240430 and HD~240429,
+  with a significant difference ($\approx 0.2$~dex) in their chemical
+  abundances that strongly suggests accretion of rocky planetary system in one
+  of the stars within the last gigayear.
   The more metal-rich of the two, HD~240430, shows an enhancement of refractory
@@
   \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
-  This is the largest and the most significant chemical difference found in
-  a wide binary pair yet.
-  The proximity in phase-space and ages between the two stars suggests that
-  they formed together with the same composition, at odds with the observed
-  differences in metallicity and abundance patterns.
+  The two stars also show high Li abundance given their age of $\sim 4$ Gyr
+  inferred from their stellar parameters.
+  A prominent trend of element abundance enhancement with condensation temperature
+  indicates the accreted material is rocky.
   We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
@@
   ($\approx 4$~\mearth).
-  %Follow-ups to study the existence and properties of the planetary systems
-  %around these stars will help illuminate planet-star interactions.
+  This pair of stars provides evidence that dynamical accretion of rocky planets
+  happen during the lifetime of sun like stars.
+
 \end{abstract}
@@
 
-\section{Introduction} % (fold)
-\label{sec:introduction}
-
-Wide binary stars are valuable tools for studying star and planet formation as well
-as Galactic dynamics and chemical evolution.
-In the context of studying the evolution of the Milky Way, they are useful for
-two main reasons.
-First, because wide binaries are weakly bound systems that may be tidally
-disrupted by, e.g., field stars, molecular clouds, or the Galactic tidal field,
-their statistics can be informative of the Galactic mass distribution.
-For example, the separation distribution of halo binaries has been used to
-constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
-On the other hand, they are also prime targets to test the chemical tagging
-hypothesis that stars from the same birthplace may be traced back using detailed
-chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
-A multiple-star system of any size that we believe are born together can serve
-this purpose, with massive open clusters at one extreme.
-Wide binaries are at the other extreme in that we may be less confident of the
-coevality of individual systems but they are much more abundant than larger
-systems like open clusters, rendering their statistics a meaningful indication
-of whether the hypothesis works.
-
-Wide binaries with similar or very different planetary architectures around the
-component stars have been used to connect a host star's chemistry to its
-planetary system.
-A differential analysis may reveal chemical signatures related to planet
-formation or accretion without any regard to Galactic chemical evolution as
-long as the two stars are assumed to be born together with identical
-composition.
-For close-in giant planets, it has been established that the planet-metallicity
-relation is primordial, and that the enhanced metallicity in giant
-planet-hosting stars likely promotes the formation of giant planets by
-increasing the availability of small particle condensates that form
-planetesimals (\citealt{Fischer:2005aa}).
-On the other hand, if host stars are polluted after their birth by rocky
-planetary material with high refractory-to-volatile ratio, the convective
-envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
-compared to their initial state.
-Thus, differences in planet formation or accretion in two otherwise identical
-stars may imprint differences in chemical abundances that depend on the
-condensation temperature (\Tcondens).
-
-Several systems in which at least one star hosts at least one planet
-have been studied so far with high resolution spectroscopy in this context
-(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
-  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
-The results and interpretations of these studies are varied:
-while some systems appear to have undetectable differences
-(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
-studies have reported a \Tcondens-dependent difference in abundance
-with higher-\Tcondens\ elements showing larger differences.
-The increasing abundance difference with condensation temperature has been
-attributed both to more yet-undiscovered rocky planets around the relatively
-refractory-poor star and to late time accretion of refractory-rich planetary
-material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
-The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
-and often at $\approx 0.05$~dex level making them challenging to detect even
-with a careful analysis of high-resolution high signal-to-noise ratio spectra.
-% maybe want to point out the former interpretation roots back to melendez+09
-% and some doubt to that interpretation...
-
-So far the strongest evidence for accretion of planetary material by a host
-star comes from spectral analysis of polluted white dwarfs (WDs).
-Because the gravitational settling times of elements heavier than \elem{He} in
-atmosphere is much shorter than the WD cooling time, detection of metals likely
-indicates the presence of a reservoir of dusty material around the WD.
-Indeed, many of the polluted WDs host a dusty debris disk detected
-in the infrared.
-Some of the most dramatically polluted WDs show
-surface abundances closely matched by rocky planetary material
-with, e.g., bulk Earth composition, strongly arguing
-that the disk formed from tidally disrupted minor planets
-(\citealt{Zuckerman:2007aa,Klein:2010aa}).
-Recently, transit signals from small bodies orbiting around a polluted WD
-have been detected by \project{Kepler} adding further support to the picture
-(\citealt{2015Natur.526..546V}).
-
-Here, we report and discuss the discovery of a comoving pair of G stars,
-HD~240430 and HD~240429, with unusual chemical abundance differences
-that strongly suggest accretion of planetary material by the two stars.
-Throughout the \documentname, we nickname the two stars \bizarreone\
-(HD~240430) and \sunanalog\ (HD~240429).
-We use the following convention for chemical abundances of stars: \elemH{X} is
-the log ratio of number density of element \elem{X} to \elem{H} relative to the
-solar value.
-The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
-(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
-\elem{X}.
-In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
-about the two stars relevant to the present discussion.
-In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
-the abundance difference between the pair.
-We summarize our discussions in \sectionname~\ref{sec:summary}.
-
-\subsection{Review of Detailed Chemical Abundance Studies of Wide Binary Stars}
-\label{sub:review}
-
-Anticipating the forthcoming discussion, we review and summarize a handful of
-wide binary systems that have been studied in
-their detailed chemical abundances so far with high-resolution spectroscopy.
-These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
-WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
-We focus on key characteristics of stars and planets, and interpretations of
-any trend in $\Delta\elemH{X}$ with \Tcondens.
-(\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added})
-
-{\bf HD~20782/HD~20781:}
-Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
-$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
-host close-in giant planets.
-HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
-orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
-Neptune-mass planets within 0.3~AU with moderately high eccentricity
-($e\sim0.1-0.3$).\footnote{
-  The two stars were monitored by \project{HARPS} campaign, and it has recently
-  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
-  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
-  within $\approx 0.35$~AU.}
-The measured abundances of 15 elements in the two stars are consistent
-(\citealt{Mack:2014aa}).
-However, \citealt{Mack:2014aa} argued that there is a moderately significant
-($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
-increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
-Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
-the abundances of each star {\it individually}.
-They suggest that this slope is evidence that the stars accreted
-$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
-migration.
-
-{\bf HAT-P-1:}
-A pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
-different planetary systems:
-the secondary star is known to host one transiting giant planet
-while no planet has been discovered around the primary star.
-The two stars are identical
-in metallicities and abundances for 23 elements measured with
-the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
-Thus it seems that the presence of close-in giant planet does not necessarily
-lead to atmospheric pollution of its host star.
-
-{\bf HD~80606/HD~80607:}
-Similar to HAT-P-1, no significant chemical difference is found between two
-common proper motion G5 stars with super-solar metallicity ($\feh \approx
-0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
-HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).
-
-{\bf XO-2N/XO-2S:}
-A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
-has received much attention due to possibly the most robust and significant
-difference between the component stars.
-XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
-masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
-0.15$) orbits at $<0.5$~AU.
-%TODO: check following with Biazzo+
-All measured elements including \elem{Fe} are enhanced in XO-2N relative to
-XO-2S, and the difference shows a significant correlation with \Tcondens\
-(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
-\citealt{Teske:2013aa}).
-At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
-difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
-
-\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
-in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
-giant planets around XO-2S, following a similar interpretation of
-\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
-In this scenario, forming planets in the protoplanetary disk are supposed to
-``lock'' heavier elements to the core of gas giant planets as well as some
-volatile elements in their envelopes. Then, the host star will accrete {\it
-  gas} depleted in metals compared to their protostellar condition.
-By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
-of gas occurs in terms of how much mass is in the convective envelope of the
-host star, they can match the mass difference of gas giant planets around each
-star, which is at least $1~\mjupiter$.
-On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
-\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
-Earth and CM chondrite-like material can explain the trend either as refractory
-{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
-refractory enhancement in XO-2N by late time accretion in which case the
-opposite would be true.
-
-{\bf WASP-94A/WASP-94B:}
-Each star in a pair of F8 and F9 stars with super-solar metallicity
-($\feh\approx 0.3$) hosts a hot Jupiter.
-The planet around WASP-94A is transiting with a misaligned, probably retrograde
-circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
-massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
-WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
-elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
-elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
-uncertainty of $0.006$~dex among all elements
-resulting in a statistically significant non-zero slope between
-$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
-  %TODO: double check the following statement
-  Note that the condensation
-  temperature $\Tcondens$ used is for solar system composition
-  gas, which can differ from that of higher metallicity gas.}
-Multiple possibilities related to the formation and evolution
-of planetary systems around each star as well as causes unrelated to planets
-such as dust cleansing during the fully convective phase or different rotation
-and granulation between the stars were considered, but none was favored.
-
-\section{Data}
-\label{sec:data}
+\section{Main Text}
+\label{sec:main}
 
@@
 
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
-  \end{center}
-  \caption{%
-    Differences in posterior samples over Galactocentric phase-space coordinates
-    for the two stars \sunanalog\ and \bizarreone.
-    \label{fig:dxdv}}
-\end{figure}
+%Here, we report and discuss the discovery of a comoving pair of G stars,
+%HD~240430 and HD~240429, with unusual chemical abundance differences
+%that strongly suggest accretion of planetary material by the two stars.
+%Throughout the \documentname, we nickname the two stars \bizarreone\
+%(HD~240430) and \sunanalog\ (HD~240429).
+%We use the following convention for chemical abundances of stars: \elemH{X} is
+%the log ratio of number density of element \elem{X} to \elem{H} relative to the
+%solar value.
+%The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
+%(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
+%\elem{X}.
+%In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
+%about the two stars relevant to the present discussion.
+%In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
+%the abundance difference between the pair.
+%We summarize our discussions in \sectionname~\ref{sec:summary}.
 
@@
   \label{fig:abundances}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec1.pdf}
-  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
-    Alternating sets of two rows show
-    the continuum-normalized data and model in the upper panel,
-    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
-    in the lower panel.
-  }
-  \label{fig:spec1}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec2.pdf}
-  \caption{Same as \figname~\ref{fig:spec1}
-    but for smaller portions of spectra at longer wavelengths that are
-    not dominated by \elem{Fe}.
-    We mark elements that give rise to strong absorption lines.
-    The feature in the third column of the second row is a strong \elem{Li}
-    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
-    studied in a separate work (\citealt{jmlithium}).
-    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
-    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
-    show weaker residuals.
-  }
-  \label{fig:spec2}
 \end{figure}
@@
 (the astrometric measurements are listed in \tablename~\ref{tab:kk}).
-We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
-full explanation of the methodology behind this search and only briefly describe
-the method here.
-For a given pair, we compute a marginalized likelihood ratio between the
-hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
-(2) that they have independent 3D velocity vectors, both given only observations
-of two components of the velocities (parallaxes and proper motions).
-We then select a sample of high-confidence comoving star pairs by making a
-conservative cut on this likelihood ratio.
-In the resulting catalog of comoving pairs (\citealt{2017AJ....153..257O}),
-the pair presented in this paper was assigned a group id of 1199,
-and the marginalized likelihood ratio (Bayes factor)
-between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
-well above the adopted cut value of 6.
 The pair has also been previously recognized as a visual double star system
 in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
-We have checked that we do not find any possible additional comoving companions
-by lowering the likelihood ratio cut for the stars around this pair.
-
-In a separate effort to study detailed chemical abundances of potential
-planet-hosting stars, \citet{2016ApJS..225...32B} obtained and analyzed high resolution
-spectra of both stars using the HIRES spectrograph on the Keck~I telescope.
+High resolution spectra of both stars were obtained using the HIRES spectrograph
+on the Keck-I telescope in a separate effort to
+to study detailed chemical abundances of potential
+planet-hosting stars, \citet{2016ApJS..225...32B}
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is
@@
 A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
+
 The resulting measurements include elemental abundances for 15 chemical species
@@
 two stars.
-We start by generating posterior samples over the Heliocentric distance, $r$,
-tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
-given the observed parallax, $\hat\pi$, and proper motions,
-$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
-We assume the noise is Gaussian, and the radial velocity measurement is
-uncorrelated with the astrometric measurements.
-If we define
-\begin{eqnarray}
-  \vec{\hat y} &=&
-      \transp{\left(
-        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
-          \hat\pi &
-          \hat\mu_{\alpha^*} &
-          \hat\mu_\delta &
-          \hat v_r
-        \end{array}
-      \right)}\\
-  \vec{y} &=&
-      \transp{\left(
-        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
-          r^{-1} &
-          r^{-1}\,v_\alpha &
-          r^{-1}\,v_\delta &
-          v_r
-        \end{array}
-      \right)}
-\end{eqnarray}
-then the likelihood is
-\begin{equation}
-  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
-\end{equation} where $\mat{C}$ is the covariance matrix.
-We adopt a uniform space density prior for the distance and an isotropic
-Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
-\begin{eqnarray}
-p(r) &=&
-  \begin{cases}
-    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
-    0              & \text{otherwise}
-  \end{cases}\\
-p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
-  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
-\end{eqnarray}
-%
-For each of the two stars, we use \project{emcee}
-(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
-v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
-512 steps as the burn-in period.
-For each sample, we convert the heliocentric phase-space coordinates into
-Galactocentric coordinates assuming that the Sun's position and velocity are
-$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
-(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.
-
-\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
-Galactocentric phase-space coordinates for the two stars.
-The differences in positions and velocities are consistent with zero.
-\todo{should we instead show $|\Delta\boldsymbol{x}|$ and
-$|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
 
@@
 
-%TODO: plot styles...
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{orbits.pdf}
-  \end{center}
-  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
-    Sun (grey).
-    For \sunanalog, the initial conditions are set to the median of the
-    posterior samples over the phase-space coordinates.
-    The orbits are computed by integrating backwards from the present-day
-    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
-    integration scheme implemented in \project{Gala} (\citealt{gala}).
-    Right panel: distribution of maximum $z$-heights for orbits computed from
-    all posterior samples.
-  }
-  \label{fig:orbit}
-\end{figure}
+%\section{Discussion}
+%\label{sec:discussion}
 
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
-  \caption{Abundance differences of the \bizarreone-\sunanalog\ pair
-    ranked by the condensation temperature of elements for solar composition gas
-    from \citealt{2003ApJ...591.1220L}.
-    The condensation temperature may be read from the gray line and right y-axis.
-    We show three wide binary systems selected from the literature:
-    HD~20782/1 (\citealt{Mack:2014aa}, $\feh\approx0$),
-    XO-2N/S (\citealt{Biazzo:2015aa}, $\feh\approx0.35$),
-    and WASP-94AB (\citealt{Teske:2016aa}, $\feh\approx0.3$).
-    Locations of elements with at least one measurement from any study
-    are indicated by a vertical line and its symbol.
-    Note that often multiple values are reported for one element corresponding
-    to different ionization states in equivalent width analyses.
-    No other pair studied so far were shown to have such large difference
-    in metallicity or sharp contrast between (moderately) volatile and
-    refractory elements as \bizarreone-\sunanalog.
-  }
-  \label{fig:relabun_tcrank}
-\end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-
-We discuss the possible origins of the peculiar abundance differences of
-\bizarreone-\sunanalog.
-We first discuss the ages and coevality of the stars in this pair, and consider
-both possibilities in which the two stars are or are not coeval.
-Our favored scenario is discussed in the last subsection,
-\sectionname~\ref{sub:accretion}.
-
-% chance pair
-%Given that their metallicities and abundance patterns are significantly
-%different, one may simply conclude that the two stars are not related (coeval)
-%but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
-%by chance.
-%The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
-%at the stars' location, one may compute the probability that a star moving at
-%the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
-%...
-
-\subsection{Stellar Ages \& Coevality}
-\label{sub:ages}
+%\subsection{Stellar Ages \& Coevality}
+%\label{sub:ages}
 
@@
 requires an alternative explanation.
-
-\subsection{Exchange Scattering}
-\label{sub:exchange_scattering}
-
-Although the data described above strongly suggests that the two stars are
-coeval, we may still consider scenarios in which the two stars are not actually
-born together.
-Two stars unrelated at birth may end up in a binary system via a binary-single
-scattering event that results in an exchange of binary members.
-In order to estimate the rate at which any binary-single
-event will produce a wide binary system such as \sunanalog\ and \bizarreone,
-we may consider the rate at which this wide binary will scatter with a field star to
-result in an exchange reaction.
-The cross-section of exchange scattering for a binary with semi-major axis $a$ is
-\begin{eqnarray}
-  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
-  \label{eq:crosssection}
-\end{eqnarray}
-where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
-defined as
-\begin{eqnarray}
-  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
-\end{eqnarray}
-\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
-(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
-scattering with field (disk) stars.
-If we assume that field stars are made of solar mass stars with a constant
-number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
-$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
-any direction, the rate of exchange scattering is
-\begin{eqnarray}
-  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
-  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
-  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
-\end{eqnarray}
-which is low enough to be negligible.
-
-In fact, any exchange scattering scenario is unsatisfactory as typical
-field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
-unlikely to show the abundance difference pattern observed.
-In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
-\bizarreone-\sunanalog\ with the distribution of abundance differences,
-$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
-\feh\ as \bizarreone\ and \sunanalog.
-We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
-all other elements are typically enhanced at a similar level, with some variations.
-Specifically, for a typical star with $\feh \approx 0.2$~dex, we generally
-expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
-(\citealt{Battistini:2015aa,Bensby:2003aa}) making the low
-[\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
-unlikely to arise from variations in Galactic chemical evolution.
-
-\todo{HOGG: to provide some theoretical account adding to the above empirical evidence.}
 
@@
 
-\section{Summary}
-\label{sec:summary}
-
-We report the discovery of a comoving pair of bright
-solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
-metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
-(\Tcondens)-dependent abundance differences.
-The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
-all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
-enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
-\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
-The two stars also have anomalously high surface \elem{Li} abundance compared
-to their ages of $\sim 4$~Gyr.
-We consider that the comoving pair may have formed from two stars of different
-birth origins in a exchange scattering event, or that there may be chemical
-inhomogeneity in the birth cloud, and find both unlikely.
-
-In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
-abundance, we consider accretion of planetary material as the cause.
-We argue that a recent accretion of $20$~\mearth\ of bulk Earth
-composition to \bizarreone\ can explain the enhancement in both refractory
-elements and lithium.
-For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
-we put an upper limit of $\approx 4$~\mearth\ on the accreted mass
-based on the \elem{Li} concentration of carbonaceous chondrites and bulk Earth.
-While the case is not as clear as \bizarreone\ without a chemical reference star,
-the range of abundances from volatile to refractory elements is
-similar to that expected from $\approx 4$~\mearth\ accretion of bulk Earth.
-It is unclear what triggered the accretions to both stars.
-One possibility is that a fly-by field star may have
-perturbed the planetary systems of both stars.
-
+Given that the two stars must have engulfed planets,
+it is likely that they have not destroyed all of their planets.
+Any surviving planet around the stars must be giants.
+Fortunately, discovery of giant eccentric planets using astrometric jitter is in the sweet spot
+for Gaia.
 The two stars have not been included in any publicly released data from planet
@@
 
-%TODO: Implications
-%- chemical tagging, frequency is of concern
-%- exoplaneteers looking for accretion signature: look for the most odd ones in
-%the expected direction not just in binaries already known to host a planet.
-
 \acknowledgements
@@
 The Flatiron Institute is supported by the Simons Foundation.
-
 % Gaia

### 2017-06-17 paper/out.tex
Trim text roughly

\section{Introduction} % (fold)
\label{sec:introduction}

Wide binary stars are valuable tools for studying star and planet formation as well
as Galactic dynamics and chemical evolution.
In the context of studying the evolution of the Milky Way, they are useful for
two main reasons.
First, because wide binaries are weakly bound systems that may be tidally
disrupted by, e.g., field stars, molecular clouds, or the Galactic tidal field,
their statistics can be informative of the Galactic mass distribution.
For example, the separation distribution of halo binaries has been used to
constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
On the other hand, they are also prime targets to test the chemical tagging
hypothesis that stars from the same birthplace may be traced back using detailed
chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
A multiple-star system of any size that we believe are born together can serve
this purpose, with massive open clusters at one extreme.
Wide binaries are at the other extreme in that we may be less confident of the
coevality of individual systems but they are much more abundant than larger
systems like open clusters, rendering their statistics a meaningful indication
of whether the hypothesis works.

Wide binaries with similar or very different planetary architectures around the
component stars have been used to connect a host star's chemistry to its
planetary system.
A differential analysis may reveal chemical signatures related to planet
formation or accretion without any regard to Galactic chemical evolution as
long as the two stars are assumed to be born together with identical
composition.
For close-in giant planets, it has been established that the planet-metallicity
relation is primordial, and that the enhanced metallicity in giant
planet-hosting stars likely promotes the formation of giant planets by
increasing the availability of small particle condensates that form
planetesimals (\citealt{Fischer:2005aa}).
On the other hand, if host stars are polluted after their birth by rocky
planetary material with high refractory-to-volatile ratio, the convective
envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state.
Thus, differences in planet formation or accretion in two otherwise identical
stars may imprint differences in chemical abundances that depend on the
condensation temperature (\Tcondens).

Several systems in which at least one star hosts at least one planet
have been studied so far with high resolution spectroscopy in this context
(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
The results and interpretations of these studies are varied:
while some systems appear to have undetectable differences
(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies have reported a \Tcondens-dependent difference in abundance
with higher-\Tcondens\ elements showing larger differences.
The increasing abundance difference with condensation temperature has been
attributed both to more yet-undiscovered rocky planets around the relatively
refractory-poor star and to late time accretion of refractory-rich planetary
material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
and often at $\approx 0.05$~dex level making them challenging to detect even
with a careful analysis of high-resolution high signal-to-noise ratio spectra.
% maybe want to point out the former interpretation roots back to melendez+09
% and some doubt to that interpretation...

So far the strongest evidence for accretion of planetary material by a host
star comes from spectral analysis of polluted white dwarfs (WDs).
Because the gravitational settling times of elements heavier than \elem{He} in
atmosphere is much shorter than the WD cooling time, detection of metals likely
indicates the presence of a reservoir of dusty material around the WD.
Indeed, many of the polluted WDs host a dusty debris disk detected
in the infrared.
Some of the most dramatically polluted WDs show
surface abundances closely matched by rocky planetary material
with, e.g., bulk Earth composition, strongly arguing
that the disk formed from tidally disrupted minor planets
(\citealt{Zuckerman:2007aa,Klein:2010aa}).
Recently, transit signals from small bodies orbiting around a polluted WD
have been detected by \project{Kepler} adding further support to the picture
(\citealt{2015Natur.526..546V}).

\subsection{Review of Detailed Chemical Abundance Studies of Wide Binary Stars}
\label{sub:review}

Anticipating the forthcoming discussion, we review and summarize a handful of
wide binary systems that have been studied in
their detailed chemical abundances so far with high-resolution spectroscopy.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
We focus on key characteristics of stars and planets, and interpretations of
any trend in $\Delta\elemH{X}$ with \Tcondens.
(\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added})

{\bf HD~20782/HD~20781:}
Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$).\footnote{
  The two stars were monitored by \project{HARPS} campaign, and it has recently
  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
  within $\approx 0.35$~AU.}
The measured abundances of 15 elements in the two stars are consistent
(\citealt{Mack:2014aa}).
However, \citealt{Mack:2014aa} argued that there is a moderately significant
($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
the abundances of each star {\it individually}.
They suggest that this slope is evidence that the stars accreted
$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
migration.

{\bf HAT-P-1:}
A pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
different planetary systems:
the secondary star is known to host one transiting giant planet
while no planet has been discovered around the primary star.
The two stars are identical
in metallicities and abundances for 23 elements measured with
the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
Thus it seems that the presence of close-in giant planet does not necessarily
lead to atmospheric pollution of its host star.

{\bf HD~80606/HD~80607:}
Similar to HAT-P-1, no significant chemical difference is found between two
common proper motion G5 stars with super-solar metallicity ($\feh \approx
0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).

{\bf XO-2N/XO-2S:}
A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
has received much attention due to possibly the most robust and significant
difference between the component stars.
XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
0.15$) orbits at $<0.5$~AU.
%TODO: check following with Biazzo+
All measured elements including \elem{Fe} are enhanced in XO-2N relative to
XO-2S, and the difference shows a significant correlation with \Tcondens\
(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
\citealt{Teske:2013aa}).
At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
difference spans upto $0.1$~dex at $\Tcondens>1600$~K.

\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
giant planets around XO-2S, following a similar interpretation of
\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
In this scenario, forming planets in the protoplanetary disk are supposed to
``lock'' heavier elements to the core of gas giant planets as well as some
volatile elements in their envelopes. Then, the host star will accrete {\it
  gas} depleted in metals compared to their protostellar condition.
By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
of gas occurs in terms of how much mass is in the convective envelope of the
host star, they can match the mass difference of gas giant planets around each
star, which is at least $1~\mjupiter$.
On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
Earth and CM chondrite-like material can explain the trend either as refractory
{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
refractory enhancement in XO-2N by late time accretion in which case the
opposite would be true.

{\bf WASP-94A/WASP-94B:}
Each star in a pair of F8 and F9 stars with super-solar metallicity
($\feh\approx 0.3$) hosts a hot Jupiter.
The planet around WASP-94A is transiting with a misaligned, probably retrograde
circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
uncertainty of $0.006$~dex among all elements
resulting in a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
  %TODO: double check the following statement
  Note that the condensation
  temperature $\Tcondens$ used is for solar system composition
  gas, which can differ from that of higher metallicity gas.}
Multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars were considered, but none was favored.

% Section: Data

We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
full explanation of the methodology behind this search and only briefly describe
the method here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
(2) that they have independent 3D velocity vectors, both given only observations
of two components of the velocities (parallaxes and proper motions).
We then select a sample of high-confidence comoving star pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2017AJ....153..257O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.

We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix.
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}
(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.

\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
The differences in positions and velocities are consistent with zero.
\todo{should we instead show $|\Delta\boldsymbol{x}|$ and
$|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}

% Section discussion

We discuss the possible origins of the peculiar abundance differences of
\bizarreone-\sunanalog.
We first discuss the ages and coevality of the stars in this pair, and consider
both possibilities in which the two stars are or are not coeval.
Our favored scenario is discussed in the last subsection,
\sectionname~\ref{sub:accretion}.

% chance pair
%Given that their metallicities and abundance patterns are significantly
%different, one may simply conclude that the two stars are not related (coeval)
%but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
%by chance.
%The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
%at the stars' location, one may compute the probability that a star moving at
%the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
%...

\subsection{Exchange Scattering}
\label{sub:exchange_scattering}

Although the data described above strongly suggests that the two stars are
coeval, we may still consider scenarios in which the two stars are not actually
born together.
Two stars unrelated at birth may end up in a binary system via a binary-single
scattering event that results in an exchange of binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
which is low enough to be negligible.

In fact, any exchange scattering scenario is unsatisfactory as typical
field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
unlikely to show the abundance difference pattern observed.
In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
\bizarreone-\sunanalog\ with the distribution of abundance differences,
$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
\feh\ as \bizarreone\ and \sunanalog.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are typically enhanced at a similar level, with some variations.
Specifically, for a typical star with $\feh \approx 0.2$~dex, we generally
expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa}) making the low
[\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
unlikely to arise from variations in Galactic chemical evolution.

\todo{HOGG: to provide some theoretical account adding to the above empirical evidence.}

%TODO: Implications
%- chemical tagging, frequency is of concern
%- exoplaneteers looking for accretion signature: look for the most odd ones in
%the expected direction not just in binaries already known to host a planet.

\section{Summary}
\label{sec:summary}

We report the discovery of a comoving pair of bright
solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
(\Tcondens)-dependent abundance differences.
The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
The two stars also have anomalously high surface \elem{Li} abundance compared
to their ages of $\sim 4$~Gyr.
We consider that the comoving pair may have formed from two stars of different
birth origins in a exchange scattering event, or that there may be chemical
inhomogeneity in the birth cloud, and find both unlikely.

In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
abundance, we consider accretion of planetary material as the cause.
We argue that a recent accretion of $20$~\mearth\ of bulk Earth
composition to \bizarreone\ can explain the enhancement in both refractory
elements and lithium.
For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
we put an upper limit of $\approx 4$~\mearth\ on the accreted mass
based on the \elem{Li} concentration of carbonaceous chondrites and bulk Earth.
While the case is not as clear as \bizarreone\ without a chemical reference star,
the range of abundances from volatile to refractory elements is
similar to that expected from $\approx 4$~\mearth\ accretion of bulk Earth.
It is unclear what triggered the accretions to both stars.
One possibility is that a fly-by field star may have
perturbed the planetary systems of both stars.

### 2017-06-17 paper/supp.tex
Trim text roughly

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Abundance differences of the \bizarreone-\sunanalog\ pair
    ranked by the condensation temperature of elements for solar composition gas
    from \citealt{2003ApJ...591.1220L}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1 (\citealt{Mack:2014aa}, $\feh\approx0$),
    XO-2N/S (\citealt{Biazzo:2015aa}, $\feh\approx0.35$),
    and WASP-94AB (\citealt{Teske:2016aa}, $\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by a vertical line and its symbol.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately) volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars \sunanalog\ and \bizarreone.
    \label{fig:dxdv}}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec1.pdf}
  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
    Alternating sets of two rows show
    the continuum-normalized data and model in the upper panel,
    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
    in the lower panel.
  }
  \label{fig:spec1}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
    studied in a separate work (\citealt{jmlithium}).
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show weaker residuals.
  }
  \label{fig:spec2}
\end{figure}

%TODO: plot styles...
\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
    Sun (grey).
    For \sunanalog, the initial conditions are set to the median of the
    posterior samples over the phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
    integration scheme implemented in \project{Gala} (\citealt{gala}).
    Right panel: distribution of maximum $z$-heights for orbits computed from
    all posterior samples.
  }
  \label{fig:orbit}
\end{figure}

### 2017-06-18 paper/ms.tex
Trim more text to supplement

@@
 \graphicspath{{figures/}}
+
+\setcitestyle{square,numbers}
 
@@
 
-\input{kk.tex}
-
-%Here, we report and discuss the discovery of a comoving pair of G stars,
-%HD~240430 and HD~240429, with unusual chemical abundance differences
-%that strongly suggest accretion of planetary material by the two stars.
-%Throughout the \documentname, we nickname the two stars \bizarreone\
-%(HD~240430) and \sunanalog\ (HD~240429).
-%We use the following convention for chemical abundances of stars: \elemH{X} is
-%the log ratio of number density of element \elem{X} to \elem{H} relative to the
-%solar value.
-%The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
-%(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
-%\elem{X}.
 %In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
@@
 
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
-  \caption{Abundance difference in this pair and other twin-like
-    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
-    \citealt{2016ApJS..225...32B}.
-    The differences in other pairs are small ($<0.05$~dex)
-    for all elements except \elem{N} and \elem{O} which are the most
-    uncertain, making the difference of $\approx 0.2$~dex seen in
-    \bizarreone-\sunanalog\ rare.
-    Additionally, we show the distribution of abundance differences
-    between field stars with similar metallicity difference
-    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
-    as violins with medians indicated by black line segments.
-    These are random pairings of single stars in
-    in \citealt{2016ApJS..225...32B} at two metallicity bins,
-    $-0.025 < \feh < 0.025$ (160 stars) and $0.175 > \feh > 0.225$ (137 stars),
-    similar to \bizarreone\ and \sunanalog.
-    The difference is always taken to be
-    $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
-    Thus, the narrower range of in $\Delta\feh$ is by construction.
-    Random pairings of disk stars with similar $\Delta\feh$ usually show
-    similar enhancement in all other elements
-    unlike the pattern seen in \bizarreone-\sunanalog\ pair.
-  }
-  \label{fig:deltaXH}
-\end{figure}
-
 \sunanalog\ and \bizarreone\ were identified as a
@@
 in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
+The two stars have spectral types G0 and G2 like the Sun.
 High resolution spectra of both stars were obtained using the HIRES spectrograph
@@
 to study detailed chemical abundances of potential
-planet-hosting stars, \citet{2016ApJS..225...32B}
+planet-hosting stars (\citealt{2016ApJS..225...32B}).
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is
@@
 A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
-
 The resulting measurements include elemental abundances for 15 chemical species
@@
 and high precision radial velocities.
-For the details of the spectral analysis, we refer the readers to
-\citealt{2016ApJS..225...32B}.
-The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
-\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
-work (\citealt{jmlithium}).
-We list all spectroscopic measurements including
-the absolute abundance\footnote{
-  The absolute abundance of element \elem{X} is
-  $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
-  where $n_\elem{X}$ is the number density of element \elem{X}.
-}
-of \elem{Li} for the two stars in Table~\ref{tab:kk}.
 
@@
 two stars.
-
 For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
@@
 \bizarreone\ and \sunanalog\ are likely a bound system that formed coevally.
+
+%We use the following convention for chemical abundances of stars: \elemH{X} is
+%the log ratio of number density of element \elem{X} to \elem{H} relative to the
+%solar value.
+%The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
+%(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
+%\elem{X}.
+
 Thus, we expect the two stars to have identical metallicities and abundance patterns.
@@
 relative to \elem{Fe}.
-Both stars have high surface \elem{Li} abundances, and the difference in
-\elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
-measured.
 
@@
 
+Assuming that the two stars were born together, one possibility to
+explain the chemical difference is that there was chemical inhomogeneity within
+the birth cloud.
+However, there is already ample evidence against such a scenario.
+First, none of the other seven similar wide binaries examined in
+\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
+Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
+$\elem{O}$, and some pairs show a difference in particular elements as large as
+$\approx 0.15$~dex.
+The median and maximum \feh\ difference between component stars in the other
+seven pairs is $0.02$~dex and $0.09$~dex, respectively.
+The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
+compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
+(\figname~\ref{fig:deltaXH}).
+This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
+23 wide binaries of late F to K dwarfs, and found most pairs show a difference
+in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
+Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
+binaries have the same chemical composition with $\gtrsim 0.01$~dex
+uncertainties.
+Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
+not likely due to chemical inhomogeneity in the birth cloud.
+
 We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
@@
 
-%\section{Discussion}
-%\label{sec:discussion}
+The spectra of both stars 
+The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
+\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
+work (\citealt{jmlithium}).
+Both stars have high surface \elem{Li} abundances, and the difference in
+\elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
+measured.
 
@@
 
-\subsection{Chemical Inhomogeneity in Star Formation}
-\label{sub:chemical_inhomogeneity_in_star_formation}
-
-Assuming that the two stars were born together, one possibility to
-explain the chemical difference is that there was chemical inhomogeneity within
-the birth cloud.
-However, there is already ample evidence against such a scenario.
-First, none of the other seven similar wide binaries examined in
-\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
-Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
-$\elem{O}$, and some pairs show a difference in particular elements as large as
-$\approx 0.15$~dex.
-The median and maximum \feh\ difference between component stars in the other
-seven pairs is $0.02$~dex and $0.09$~dex, respectively.
-The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
-compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
-(\figname~\ref{fig:deltaXH}).
-This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
-23 wide binaries of late F to K dwarfs, and found most pairs show a difference
-in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
-Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
-binaries have the same chemical composition with $\gtrsim 0.01$~dex
-uncertainties.
-Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
-not likely due to chemical inhomogeneity in the birth cloud.
-
 \begin{figure}[htpb]
@@
 
-\subsection{Accretion of rocky planetary material}
-\label{sub:accretion}
-
-Another possibility that two coeval stars may end up with different surface
-abundances is accretion of planetary material after birth.
-Instabilities may develop in a multi-planet system due to its chaotic nature
-which may lead to planet engulfment or ejection by the host star
-(\todo{needs references}).
-%TODO: kozai?
-Indeed, it is an important goal of many exoplanet studies
-to detect chemical signatures of planet formation or accretion,
-distinguish them from Galactic chemical evolution, and
-connect them to theories of evolution of planetary systems.
-One approach that is free from confusion with Galactic chemical evolution
-is to compare two almost identical stars in a wide binary system.
-Assuming that the component stars were born together with identical
-initial composition, we may see a difference in their surface abundances
-if the two stars then accreted different amounts of planetary material.
-The resulting abundance difference may depend on the condensation
-temperatures of elements in the protoplanetary disks from which the accreted
-planets formed, as their compositions depend on the radial temperature gradient
-in the disk.
-%TODO: cautions on condensation temperature
-% 1. it is just a proxy
-% 2. it is **equlibrium** condensation temperature
-
 In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
@@
 
+We interpret the condensation temperature dependent
+difference of elemental abundance between the two stars
+as evidence for accretion of rocky planetary material in \bizarreone.
+Instabilities may develop in a multi-planet system due to its chaotic nature
+which may lead to planet engulfment or ejection by the host star
+(\todo{needs references}).
+%TODO: kozai?
+
+One approach that is free from confusion with Galactic chemical evolution
+is to compare two almost identical stars in a wide binary system.
+Assuming that the component stars were born together with identical
+initial composition, we may see a difference in their surface abundances
+if the two stars then accreted different amounts of planetary material.
+The resulting abundance difference may depend on the condensation
+temperatures of elements in the protoplanetary disks from which the accreted
+planets formed, as their compositions depend on the radial temperature gradient
+in the disk.
+%TODO: cautions on condensation temperature
+% 1. it is just a proxy
+% 2. it is **equlibrium** condensation temperature
+
 How much mass of rocky material is needed to explain an increment of
@@
 \end{itemize}
-
 We take the solar abundances, $\elemH{X}$, of element \elem{X}
@@
 
+\input{kk.tex}
+
 \end{document}

### 2017-06-18 paper/supp.tex
Trim more text to supplement

@@
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
+  \caption{Abundance difference in this pair and other twin-like
+    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
+    \citealt{2016ApJS..225...32B}.
+    The differences in other pairs are small ($<0.05$~dex)
+    for all elements except \elem{N} and \elem{O} which are the most
+    uncertain, making the difference of $\approx 0.2$~dex seen in
+    \bizarreone-\sunanalog\ rare.
+    Additionally, we show the distribution of abundance differences
+    between field stars with similar metallicity difference
+    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
+    as violins with medians indicated by black line segments.
+    These are random pairings of single stars in
+    in \citealt{2016ApJS..225...32B} at two metallicity bins,
+    $-0.025 < \feh < 0.025$ (160 stars) and $0.175 > \feh > 0.225$ (137 stars),
+    similar to \bizarreone\ and \sunanalog.
+    The difference is always taken to be
+    $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
+    Thus, the narrower range of in $\Delta\feh$ is by construction.
+    Random pairings of disk stars with similar $\Delta\feh$ usually show
+    similar enhancement in all other elements
+    unlike the pattern seen in \bizarreone-\sunanalog\ pair.
+  }
+  \label{fig:deltaXH}
+\end{figure}
+
 \begin{figure}[htpb]

### 2017-06-18 paper/ms.tex
Change document class

@@
-\documentclass[modern, letterpaper]{aastex61}
+\documentclass[12pt,letterpaper,margin=1in]{article}
 % \documentclass[twocolumn]{aastex61}
@@
 % packages
-\definecolor{cbblue}{HTML}{3182bd}
+\usepackage[letterpaper,margin=1in]{geometry}
+
+\usepackage{setspace}
+\onehalfspacing
 \usepackage{microtype}  % ALWAYS!
 \usepackage{amsmath,amssymb}
-\usepackage{natbib}
-\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
+\usepackage[sort&compress,super]{natbib}
+\usepackage{graphicx}
 \graphicspath{{figures/}}
+\usepackage{aas_macros}
+\usepackage{hyperref}
+\usepackage{mathptmx}
 
-\setcitestyle{square,numbers}
+%\setcitestyle{super}
+\bibliographystyle{unsrtnat}
 
@@
 
-\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
+\newcommand{\todo}[1]{{TODO: #1}}
 
@@
 }
+\maketitle
 
-\author[0000-0001-7790-5308]{Semyeong Oh}
-\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
-  Princeton, NJ 08544, USA}
-\affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}
+\author{
+  Semyeong Oh$^{1,*}$,\,
+  Adrian M. Price-Whelan$^{1}$,\,
+  John M. Brewer$^{2}$,\,
+  David W. Hogg$^{3,4,5,6}$,\,
+  David N. Spergel$^{1,3}$,\,
+  Justin Myles$^{2}$
+}
 
-\author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
-\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
-  Princeton, NJ 08544, USA}
+{\small\noindent
+  $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu} \\
+  $^1$Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA \\
+  $^2$Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA \\
+  $^3$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA \\
+  $^4$Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA \\
+  $^5$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA \\
+  $^6$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
+}
 
-\author[0000-0002-9873-1471]{John M. Brewer}
-\affil{Department of Astronomy, Yale University, 260 Whitney Ave,
-  New Haven, CT 06511, USA}
+%% \author{Keith A. Hawkins}
+%% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}
 
-\author[0000-0003-2866-9403]{David W. Hogg}
-\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
-  New York, NY 10010, USA}
-\affil{Center for Cosmology and Particle Physics,
-  Department of Physics, New York University, 726 Broadway,
-  New York, NY 10003, USA}
-\affil{Center for Data Science, New York University, 60 Fifth Ave,
-  New York, NY 10011, USA}
-\affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg}
+%% \author{Nathan W. C. Leigh}
+%% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
 
-\author{David N. Spergel} % TODO: need ORCID
-\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
-  Princeton, NJ 08544, USA}
-\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
-  New York, NY 10010, USA}
-
-% \author{Keith A. Hawkins}
-% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}
-
-% \author{Nathan W. C. Leigh}
-% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
-
-\author{Justin Myles} % TODO: need ORCID
-\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
-
-\begin{abstract}
-
+% ------------------------
+% nature summary paragraph
+% ------------------------
+{\bf \noindent
   Stars that are born together are expected to have same space motion and chemical compositions initially.
@@
   happen during the lifetime of sun like stars.
-
-\end{abstract}
-
-\keywords{
-  binaries: visual
-  ---
-  planet-star interactions
-  ---
-  stars: abundances
-  ---
-  stars: formation
-  ---
-  stars: individual (HD~240430, HD~240429)
-  ---
-  stars: solar-type
 }
-
-\section{Main Text}
-\label{sec:main}
-
-%In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
-%about the two stars relevant to the present discussion.
-%In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
-%the abundance difference between the pair.
-%We summarize our discussions in \sectionname~\ref{sec:summary}.
 
@@
     \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
+    \label{fig:abundances}
   }
-  \label{fig:abundances}
 \end{figure}
@@
 The pair has also been previously recognized as a visual double star system
-in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
+in Washington Double Star catalog \cite{2001AJ....122.3466M}.
 The two stars have spectral types G0 and G2 like the Sun.
@@
 to study detailed chemical abundances of potential
-planet-hosting stars (\citealt{2016ApJS..225...32B}).
+planet-hosting stars \cite{2016ApJS..225...32B}.
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is
@@
 
-The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
+The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
 and the 3D separation is $\approx 0.6$~pc.
@@
 For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
-1.2~pc (\citealt{jiangtremaine2010}).
+1.2~pc\cite{jiangtremaine2010}.
 %TODO
@@
 First, none of the other seven similar wide binaries examined in
-\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
+\cite{2016ApJS..225...32B} show the same level of differences in abundances.
 Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
@@
 (\figname~\ref{fig:deltaXH}).
-This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
+This is consistent with the findings of \cite{Desidera:2004aa}, who examined
 23 wide binaries of late F to K dwarfs, and found most pairs show a difference
 in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
-Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
+Similarly, \cite{Gratton:2001aa} found that four out of six equal mass
 binaries have the same chemical composition with $\gtrsim 0.01$~dex
@@
 We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
-\lesssim 100$~K) wide binary pairs examined by \citealt{2016ApJS..225...32B}
+\lesssim 100$~K) wide binary pairs examined by \cite{2016ApJS..225...32B}
 show discrepancies in abundances between the stars at this level.
@@
 \figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
-work (\citealt{jmlithium}).
+work (\cite{jmlithium}).
 Both stars have high surface \elem{Li} abundances, and the difference in
@@
 measured.
-
-%\subsection{Stellar Ages \& Coevality}
-%\label{sub:ages}
 
@@
 We perform isochrone fitting to these values using the Yale-Yonsei model
-isochrones (\citealt{2013ApJ...776...87S}).
+isochrones\cite{2013ApJ...776...87S}.
 The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
@@
 of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
-solar lithium abundance and rotational profile (\citealt{2005Sci...309.2189C}).
+solar lithium abundance and rotational profile (\cite{2005Sci...309.2189C}).
 The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
@@
 attributed to the engulfment of substellar companions such as gas giant planets
-or brown dwarfs which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
+or brown dwarfs which may replenish $\elem{Li}$ (\cite{Casey:2016aa}).
 
@@
 Way-like gravitational potential (similar to \texttt{MWPotential2014} from
-\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
+\cite{Bovy:2015}) using \project{Gala} (\cite{gala}).
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring
@@
     to the expected change in solar surface abundance after adding $20$~\mearth\ of
-    material with bulk Earth composition (\citealt{mcdonough2001composition}).
+    material with bulk Earth composition (\cite{mcdonough2001composition}).
     The assumed mass fraction in the convective zone is $0.03$.
@@
 The equilibrium condensation temperatures for the composition of solar system
-are taken from \citealt{2003ApJ...591.1220L} (Table~8).
+are taken from \cite{2003ApJ...591.1220L} (Table~8).
 The difference seen in \bizarreone-\sunanalog\ is
@@
 We take the solar abundances, $\elemH{X}$, of element \elem{X}
-(\citealt{Asplund:2009aa}) which can be converted to mass fraction as
+(\cite{Asplund:2009aa}) which can be converted to mass fraction as
 \begin{equation}
@@
 We take the composition of bulk Earth from a chondritic model of the Earth
-(\citealt{mcdonough2001composition}).
+(\cite{mcdonough2001composition}).
 Similar calculations have been performed by \citet{Chambers:2010aa} and
@@
 depleted in the Earth relative to CI or other carbonaceous chondrites
-has long been known (\citealt{mcdonough2001composition}).
+has long been known (\cite{mcdonough2001composition}).
 This trend is presumed to be closely related to the formation of terrestrial
@@
 Because Li is present in either carbonaceous chondrites or bulk Earth with
-a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition}),
+a concentration of $1-1.5$~ppm in mass (\cite{mcdonough2001composition}),
 but is depleted quickly within the first couple of Gyrs on the surface of a
@@
 This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
-$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \cite{jmlithium})
 approximately $1.65$~dex higher than the solar value of $1.1$~dex
@@
 $\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
-(\citealt{mcdonough2001composition}).
+(\cite{mcdonough2001composition}).
 Unlike \bizarreone, we cannot know the pre-accretion abundances of
@@
 For example, the reported bulk Earth concentration of the siderphile element
-\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
-While the latter value from \citealt{mcdonough2001composition} has been used in
+\elem{Mn}, varies from $800$ to $1700$~ppm (\cite{1998psc..book.....L}).
+While the latter value from \cite{mcdonough2001composition} has been used in
 our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
@@
 
-\acknowledgements
+%\software{
+%  %The data and code used in this project is available from
+%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
+%  %software license.
+%  This research utilized:
+%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
+%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
+%  \texttt{IPython} (\citealt{Perez:2007}),
+%  \texttt{matplotlib} (\citealt{Hunter:2007}),
+%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
+%  and \texttt{pandas} (\citealt{pandas}).}
 
+\bibliography{ref}
+
+\section*{Acknowledgements}
 We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
-for valuable discussions and feedback.
+for feedback.
 The Flatiron Institute is supported by the Simons Foundation.
@@
 
-\software{
-  %The data and code used in this project is available from
-  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
-  %software license.
-  This research utilized:
-  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
-  \texttt{emcee} (\citealt{2013PASP..125..306F}),
-  \texttt{IPython} (\citealt{Perez:2007}),
-  \texttt{matplotlib} (\citealt{Hunter:2007}),
-  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
-  and \texttt{pandas} (\citealt{pandas}).}
+\section*{Extended Data}
 
-\bibliography{ref}
+\section*{Supplementary Information}
 
-\input{kk.tex}
+%\input{kk.tex}
 

### 2017-06-18 paper/ms.tex
Put hypersetup back in
cite working

@@
 \usepackage{hyperref}
+\hypersetup{backref,breaklinks,colorlinks,citecolor=blue}
 \usepackage{mathptmx}
@@
 %\setcitestyle{super}
-\bibliographystyle{unsrtnat}
+\citestyle{nature}
+\bibliographystyle{naturemag}
 
@@
 
+% affiliations
 {\small\noindent
@@
   Detailed chemical abundance studies of stars in wide binaries indeed reveal nearly identical
-  chemistry in most cases.
+  chemistry in most cases\citep{Gratton:2001aa,Desidera:2004aa}.
   However, formation and evolution of different planetary systems around each star in a wide binary
-  may eventually lead to a difference in the compositions of the stars' radiative and convective layers.
-  A handful of wide binaries that show small differences in their surface chemical abundance have been reported so far.
+  may eventually lead to a difference in the compositions of the stars' radiative and
+  convective layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
+  A handful of wide binaries that show small differences in their surface
+  chemical abundance have been reported so far
+  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
   However, no pair .

### 2017-06-18 paper/ms.tex
Some edits and abridged table

@@
 {\bf \noindent
-  Stars that are born together are expected to have same space motion and chemical compositions initially.
+  Stars that are born together are expected to have same space motion and chemical composition initially.
   Detailed chemical abundance studies of stars in wide binaries indeed reveal nearly identical
@@
   However, formation and evolution of different planetary systems around each star in a wide binary
-  may eventually lead to a difference in the compositions of the stars' radiative and
+  may eventually lead to a difference in the compositions of the component stars' radiative and
   convective layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
   A handful of wide binaries that show small differences in their surface
-  chemical abundance have been reported so far
-  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
-  However, no pair .
-  Here we report a comoving pair of bright G stars, HD~240430 and HD~240429,
+  chemical abundances have been reported so far
+  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
+  However, a convincing example is yet to be found.
+  Here we report a comoving pair of bright sun-like stars, HD~240430 and HD~240429,
   with a significant difference ($\approx 0.2$~dex) in their chemical
   abundances that strongly suggests accretion of rocky planetary system in one
-  of the stars within the last gigayear.
+  of the stars within the last couple of billion years.
   The more metal-rich of the two, HD~240430, shows an enhancement of refractory
@@
 
+\begin{table*}[htpb]
+  \caption{Astrometric and spectroscopic measurements.}
+  \label{tab:t1}
+  \centering
+  \begin{tabular}{ccc}
+\hline\hline
+Name & HD 240429 & HD 240430 \\
+\hline
+Sp Type                                   & G2                & G0                \\
+$T_\mathrm{eff}$                          & 5878              & 5803              \\
+$\log{g}$                                 & 4.43              & 4.33              \\
+$v\sin{i}$                                & 1.1               & 2.5               \\
+$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
+$v_r$                                     & $-21.2$           & $-21.2$           \\
+$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
+$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
+$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
+\hline\hline 
+\end{tabular}
+\end{table*}
+
 \sunanalog\ and \bizarreone\ were identified as a
 candidate comoving star pair in our recent search for comoving stars using the
-proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr\
-(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
+proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas),
+a component of the astrometric space mission \gaia\ first data release
+(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
 The pair has also been previously recognized as a visual double star system
-in Washington Double Star catalog \cite{2001AJ....122.3466M}.
+in Washington Double Star catalog\cite{2001AJ....122.3466M}.
 The two stars have spectral types G0 and G2 like the Sun.
-High resolution spectra of both stars were obtained using the HIRES spectrograph
-on the Keck-I telescope in a separate effort to
-to study detailed chemical abundances of potential
-planet-hosting stars \cite{2016ApJS..225...32B}.
-The spectral resolution is $R\approx 70000$ and the wavelength coverage is
-$5164$--$7799$~\AA.
+In a separate effort to to study detailed chemical abundances of potential
+planet-hosting stars, high resolution, high
+signal-to-noise ratio spectra of both stars were obtained using the HIRES
+spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}. 
+The spectral resolution is $R=\lambda/\Delta\lambda\approx 70000$ and the
+wavelength coverage is $5164$--$7799$~\AA.
 A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
@@
 Although selected based only on their astrometry, the two stars
-have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
+have identical radial velocities within uncertainties (Table~\ref{tab:t1}),
 confirming that they are truly comoving.
-Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
+Combining these precise radial velocities with the \tgas\ astrometry, we
 can compare differences between the inferred 6D phase-space coordinates of the
@@
 For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
-1.2~pc\cite{jiangtremaine2010}.
+1.2~pc\cite{Jiang:2010aa}.
 %TODO
@@
 
+%% abundance notation 
 %We use the following convention for chemical abundances of stars: \elemH{X} is
@@
 
+\begin{table*}[htpb]
+  \caption{Astrometric and spectroscopic measurements.}
+  \label{tab:t2}
+  \centering
+  \begin{tabular}{ccc}
+\hline\hline
+Name & HD 240429 & HD 240430 \\
+\hline
+Sp Type                                   & G2                & G0                \\
+$T_\mathrm{eff}$                          & 5878              & 5803              \\
+$\log{g}$                                 & 4.43              & 4.33              \\
+$v\sin{i}$                                & 1.1               & 2.5               \\
+$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
+$v_r$                                     & $-21.2$           & $-21.2$           \\
+$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
+$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
+$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
+\hline
+\multicolumn{3}{c}{$T_c < 1200$~K} \\
+\hline
+$A(\elem{Li})$ \footnotemark[2]           & $2.25$            & $2.75$            \\
+$\elemH{C}$                               & $0.00$            & $0.09$            \\
+$\elemH{N}$                               & $-0.06$           & $-0.01$           \\
+$\elemH{O}$                               & $0.01$            & $0.09$            \\
+$\elemH{Na}$                              & $-0.06$           & $-0.04$           \\
+$\elemH{Mn}$                              & $-0.03$           & $0.00$            \\
+\hline
+\multicolumn{3}{c}{$T_c > 1200$~K} \\
+\hline
+$\elemH{Mg}$                              & $0.01$            & $0.19$            \\
+$\elemH{Al}$                              & $0.01$            & $0.21$            \\
+$\elemH{Si}$                              & $0.00$            & $0.16$            \\
+$\elemH{Ca}$                              & $0.02$            & $0.23$            \\
+$\elemH{Ti}$                              & $0.02$            & $0.20$            \\
+$\elemH{V}$                               & $0.02$            & $0.20$            \\
+$\elemH{Cr}$                              & $0.01$            & $0.17$            \\
+$\elemH{Fe}$                              & $0.01$            & $0.20$            \\
+$\elemH{Ni}$                              & $-0.01$           & $0.21$            \\
+$\elemH{Y}$                               & $0.04$            & $0.26$            \\
+\hline\hline
+\end{tabular}
+%
+%\begin{tablenotes}
+%  \item All spectroscopic measurements except $\elem{Li}$ are from \citealt{2016ApJS..225...32B}.
+%  \footnotetext[1]{From \tgas. }
+%  \footnotetext[2]{Absolute abundance from \todo{CITE}.}
+%\end{tablenotes}
+\end{table*}
+
+- all of table 1 here
+- FIG: posterior of dx dv
+- FIG: spectra + model
+- FIG: orbits
+- FIG: violin plot
+- FIG: comparison to other pairs
+
 \section*{Supplementary Information}

### 2017-06-18 paper/ms.tex
ref work

@@
 % ----------
-% - Add items here.
+% - cite gaia dr paper
 
@@
 of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
-solar lithium abundance and rotational profile (\cite{2005Sci...309.2189C}).
+solar lithium abundance and rotational profile\cite{2005Sci...309.2189C}.
 The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
@@
 attributed to the engulfment of substellar companions such as gas giant planets
-or brown dwarfs which may replenish $\elem{Li}$ (\cite{Casey:2016aa}).
+or brown dwarfs which may replenish $\elem{Li}$\cite{Casey:2016aa}.
 

### 2017-06-18 paper/ms.tex
more restructuring

@@
 \usepackage{mathptmx}
+
+% per section figure counting
+\usepackage{chngcntr}
+\counterwithin{figure}{section}
 
@@
 % ------------------------
+% - a fully referenced paragraph, ideally of about 200 words, but certainly no
+%   more than 300 words, aimed at readers in other disciplines.
+% - This paragraph starts with a 2-3 sentence basic introduction to the field;
+%   followed by a one-sentence statement of the main conclusions starting 'Here
+%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
+%   findings into general context so it is clear how the results described in
+%   the paper have moved the field forwards.
+% ------------------------
+\section{Summary}
 {\bf \noindent
-  Stars that are born together are expected to have same space motion and chemical composition initially.
+  Stars that are born together are expected to have same chemical compositions initially.
   Detailed chemical abundance studies of stars in wide binaries indeed reveal nearly identical
-  chemistry in most cases\citep{Gratton:2001aa,Desidera:2004aa}.
+  chemistry in most cases\citep{Gratton:2001aa,Desidera:2004aa} as well as stars in open clusters\cite{Bovy:2016aa}.
   However, formation and evolution of different planetary systems around each star in a wide binary
@@
   convective layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
+  Wide binary systems of two twin-like stars are particularly useful
+  as they are not subject to confusion with Galactic chemical evolution.
   A handful of wide binaries that show small differences in their surface
@@
 }
+
+\section{Main Text}
 
@@
 
-\sunanalog\ and \bizarreone\ were identified as a
-candidate comoving star pair in our recent search for comoving stars using the
-proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas),
-a component of the astrometric space mission \gaia\ first data release
+\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
+in our recent search for comoving stars using the proper motions and parallaxes
+from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
+component of the first data release of the astrometric space mission \gaia\
 (the astrometric measurements are listed in \tablename~\ref{tab:t1}).
@@
 in Washington Double Star catalog\cite{2001AJ....122.3466M}.
-The two stars have spectral types G0 and G2 like the Sun.
-In a separate effort to to study detailed chemical abundances of potential
-planet-hosting stars, high resolution, high
-signal-to-noise ratio spectra of both stars were obtained using the HIRES
-spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}. 
+The two stars have spectral types G0 and G2 both similar to the Sun (G2).
+In a separate effort to study detailed chemical abundances of potential
+planet-hosting stars, high resolution, high signal-to-noise ratio spectra of
+both stars were obtained using the HIRES spectrograph on the Keck-I
+telescope\cite{2016ApJS..225...32B}. 
 The spectral resolution is $R=\lambda/\Delta\lambda\approx 70000$ and the
@@
 The resulting measurements include elemental abundances for 15 chemical species
-(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
-and high precision radial velocities.
+(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
+parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities.
 
@@
 confirming that they are truly comoving.
-Combining these precise radial velocities with the \tgas\ astrometry, we
-can compare differences between the inferred 6D phase-space coordinates of the
-two stars.
-For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
-1.2~pc\cite{Jiang:2010aa}.
-%TODO
-\bizarreone\ and \sunanalog\ are likely a bound system that formed coevally.
+As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
+neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
+\sunanalog\ are likely a bound wide binary system that formed coevally.
 
-%% abundance notation 
-%We use the following convention for chemical abundances of stars: \elemH{X} is
-%the log ratio of number density of element \elem{X} to \elem{H} relative to the
-%solar value.
-%The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
-%(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
-%\elem{X}.
+Aside from the kinematics, their stellar parameters also indicates that they are coeval.
+We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
+and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
+We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, \elemH{Si}
+in order interpolate the mass, age, radius, and $\log(g)$ of each star
+in a grid of Yale-Yonsei model isochrones\cite{2013ApJ...776...87S}.
+The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
+$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
+consistent with them being coeval.
 
-Thus, we expect the two stars to have identical metallicities and abundance patterns.
 However, one of the stars, \bizarreone\ is significantly more metal
@@
 relative to \elem{Fe}.
-
+%
 The validity of the measured abundance differences is further demonstrated
@@
 the residuals are much smaller in amplitude.
-%Li?
 
-Assuming that the two stars were born together, one possibility to
-explain the chemical difference is that there was chemical inhomogeneity within
-the birth cloud.
-However, there is already ample evidence against such a scenario.
-First, none of the other seven similar wide binaries examined in
-\cite{2016ApJS..225...32B} show the same level of differences in abundances.
-Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
-$\elem{O}$, and some pairs show a difference in particular elements as large as
-$\approx 0.15$~dex.
-The median and maximum \feh\ difference between component stars in the other
-seven pairs is $0.02$~dex and $0.09$~dex, respectively.
-The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
-compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
-(\figname~\ref{fig:deltaXH}).
-This is consistent with the findings of \cite{Desidera:2004aa}, who examined
-23 wide binaries of late F to K dwarfs, and found most pairs show a difference
-in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
-Similarly, \cite{Gratton:2001aa} found that four out of six equal mass
-binaries have the same chemical composition with $\gtrsim 0.01$~dex
-uncertainties.
-Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
-not likely due to chemical inhomogeneity in the birth cloud.
+The observed difference in metallicity and abundances are genuinely rare and
+unexpected.
+None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) wide
+binary pairs examined using spectra of comparable quality and the same
+consistent measurement pipeline shows discrepancies in abundances between the
+stars at this level\cite{2016ApJS..225...32B} (see Figure~\ref{fig:deltaXH}).
+The maximum metallicity difference observed in the other pairs is $\Delta\feh = 0.03$~dex
+with $1-\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
+This is consistent with similar studies of metallicity and abundance differences
+in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
+The difference of $\approx 0.2$~dex is also the largest among a handful of
+wide binaries that do show metallicity and abundance differences with varying
+significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
+  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
+(see Figure~\ref{fig:relabun_tcrank}).
 
-We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
-\lesssim 100$~K) wide binary pairs examined by \cite{2016ApJS..225...32B}
-show discrepancies in abundances between the stars at this level.
-As shown in \figname~\ref{fig:deltaXH},
-the differences in other pairs for all elements except \elem{N} and \elem{O},
-which are also the most uncertain (\tablename~\ref{tab:kk}),
-are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
+%As shown in \figname~\ref{fig:deltaXH},
+%the differences in other pairs for all elements except \elem{N} and \elem{O},
+%which are also the most uncertain (\tablename~\ref{tab:kk}),
+%are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
 
-The spectra of both stars 
-The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
-\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
-work (\cite{jmlithium}).
-Both stars have high surface \elem{Li} abundances, and the difference in
-\elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
-measured.
-
-The fact that the two stars share nearly identical space motion
-at a separation of $< 1$~pc strongly supports that the pair is coeval.
-We therefore consider other age indicators apart from their phase-space
-coordinates to assess the ages and coevality of the two stars.
-First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
-we can constrain the ages of the two stars by
-comparing these values to theoretical isochrones.
-We perform isochrone fitting to these values using the Yale-Yonsei model
-isochrones\cite{2013ApJ...776...87S}.
-The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
-parallaxes, $B$-band magnitudes, and their errors.
-The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
-$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
-consistent with them being coeval.
-
+Both stars have high surface \elem{Li} abundances considering
+their ages of $\sim 4$~Gyr.
 The surface lithium abundance in a sun-like star decreases with its age due to
@@
 burning.
-Thus, surface lithium abundance is an indicator of stellar ages.
-The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
-of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
-solar lithium abundance and rotational profile\cite{2005Sci...309.2189C}.
-The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
+The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
+detectable at this age even for high signal-to-noise spectra, is clearly
+visible in the spectra of both stars (see \figname~\ref{fig:spec2}).
+The measured absolute abundances for \bizarreone\ and \sunanalog\ are
+$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep),
+resulting in the largest abundance difference ($\approx 0.5$~dex) seen
 among all measured elements.
-This translates to a $\sim 500$~Myr difference in age.
-Given the overall higher metal abundances and the peculiar abundance patterns
-in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
-abundance means a younger age or something else.
-For example, the presence of $\elem{Li}$-rich red giant stars has been
-attributed to the engulfment of substellar companions such as gas giant planets
-or brown dwarfs which may replenish $\elem{Li}$\cite{Casey:2016aa}.
-
-In fact, the surface lithium abundance is the only indication that points to
-younger ages.
-If the two stars are indeed only several hundred Myrs old at most,
-they are expected to be part of a larger comoving group of stars.
-However, as we mention above, there is no evidence in our search of comoving pairs
-using \tgas\ that the two stars belong to a larger group of young stars.
-Very young stars often show signs of activity such as
-X-ray emission from magnetic activity, emission lines, or infrared excess due to
-circumstellar disks (\todo{needs refernces}).
-We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
-and found no evidence for indications of activity in their spectral energy
-distributions.
-The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
-young ages that would be inferred from the surface lithium abundances.
-Finally, we computed the Galactic orbit of the pair using the median of the
-posterior sample over the phase space coordinates of \sunanalog, in a Milky
-Way-like gravitational potential (similar to \texttt{MWPotential2014} from
-\cite{Bovy:2015}) using \project{Gala} (\cite{gala}).
-The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age (\todo{needs references for vertical action as age indicator}).
-We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
-old main sequence stars, and that their unusually high \elem{Li} abundance
-requires an alternative explanation.
 
@@
 
-We interpret the condensation temperature dependent
-difference of elemental abundance between the two stars
-as evidence for accretion of rocky planetary material in \bizarreone.
+We interpret the \Tcondens-dependent difference of elemental abundance between
+the two stars as evidence for accretion of rocky planetary material in
+\bizarreone.
 Instabilities may develop in a multi-planet system due to its chaotic nature
@@
 
-One approach that is free from confusion with Galactic chemical evolution
-is to compare two almost identical stars in a wide binary system.
-Assuming that the component stars were born together with identical
-initial composition, we may see a difference in their surface abundances
-if the two stars then accreted different amounts of planetary material.
-The resulting abundance difference may depend on the condensation
-temperatures of elements in the protoplanetary disks from which the accreted
-planets formed, as their compositions depend on the radial temperature gradient
-in the disk.
-%TODO: cautions on condensation temperature
-% 1. it is just a proxy
-% 2. it is **equlibrium** condensation temperature
+%%TODO: cautions on condensation temperature
+%% 1. it is just a proxy
+%% 2. it is **equlibrium** condensation temperature
 
-How much mass of rocky material is needed to explain an increment of
-$\approx 0.2$~dex?
+We estimate how much mass of rocky material is needed to explain an increment of
+$\approx 0.2$~dex in refractory elements.
 We carry out simple toy calculations of expected $\Delta\elemH{X}$
@@
 
+\bibliography{ref}
+
+\section{Acknowledgements}
+We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
+for feedback.
+The Flatiron Institute is supported by the Simons Foundation.
+% Gaia
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement.
+% software
 %\software{
@@
 
-\bibliography{ref}
-
-\section*{Acknowledgements}
-We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
-for feedback.
-The Flatiron Institute is supported by the Simons Foundation.
-% Gaia
-This work has made use of data from the European Space Agency (ESA) mission
-{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
-Data Processing and Analysis Consortium (DPAC,
-\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
-has been provided by national institutions, in particular the institutions
-participating in the {\it Gaia} Multilateral Agreement.
-
-\section*{Extended Data}
+\section{Extended Data}
 
@@
 
-- all of table 1 here
-- FIG: posterior of dx dv
-- FIG: spectra + model
-- FIG: orbits
-- FIG: violin plot
-- FIG: comparison to other pairs
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
+  \caption{Abundance difference in this pair and other twin-like
+    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
+    \citealt{2016ApJS..225...32B}.
+    The differences in other pairs are small ($<0.05$~dex)
+    for all elements except \elem{N} and \elem{O} which are the most
+    uncertain, making the difference of $\approx 0.2$~dex seen in
+    \bizarreone-\sunanalog\ rare.
+    Additionally, we show the distribution of abundance differences
+    between field stars with similar metallicity difference
+    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
+    as violins with medians indicated by black line segments.
+    These are random pairings of single stars in
+    in \citealt{2016ApJS..225...32B} at two metallicity bins,
+    $-0.025 < \feh < 0.025$ (160 stars) and $0.175 > \feh > 0.225$ (137 stars),
+    similar to \bizarreone\ and \sunanalog.
+    The difference is always taken to be
+    $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
+    Thus, the narrower range of in $\Delta\feh$ is by construction.
+    Random pairings of disk stars with similar $\Delta\feh$ usually show
+    similar enhancement in all other elements
+    unlike the pattern seen in \bizarreone-\sunanalog\ pair.
+  }
+  \label{fig:deltaXH}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
+  \caption{Abundance differences of the \bizarreone-\sunanalog\ pair
+    ranked by the condensation temperature of elements for solar composition gas
+    from \citet{2003ApJ...591.1220L}.
+    The condensation temperature may be read from the gray line and right y-axis.
+    We show three wide binary systems selected from the literature:
+    HD~20782/1 (\citet{Mack:2014aa}, $\feh\approx0$),
+    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$)),
+    and WASP-94AB\cite{Teske:2016aa} ($\feh\approx0.3$).
+    Locations of elements with at least one measurement from any study
+    are indicated by a vertical line and its symbol.
+    Note that often multiple values are reported for one element corresponding
+    to different ionization states in equivalent width analyses.
+    No other pair studied so far were shown to have such large difference
+    in metallicity or sharp contrast between (moderately) volatile and
+    refractory elements as \bizarreone-\sunanalog.
+  }
+  \label{fig:relabun_tcrank}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec1.pdf}
+  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
+    Alternating sets of two rows show
+    the continuum-normalized data and model in the upper panel,
+    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
+    in the lower panel.
+  }
+  \label{fig:spec1}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec2.pdf}
+  \caption{Same as \figname~\ref{fig:spec1}
+    but for smaller portions of spectra at longer wavelengths that are
+    not dominated by \elem{Fe}.
+    We mark elements that give rise to strong absorption lines.
+    The feature in the third column of the second row is a strong \elem{Li}
+    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
+    studied in a separate work (\citealt{jmlithium}).
+    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
+    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
+    show weaker residuals.
+  }
+  \label{fig:spec2}
+\end{figure}
+
+%TODO: plot styles...
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{orbits.pdf}
+  \end{center}
+  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
+    Sun (grey).
+    For \sunanalog, the initial conditions are set to the median of the
+    posterior samples over the phase-space coordinates.
+    The orbits are computed by integrating backwards from the present-day
+    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
+    integration scheme implemented in \project{Gala} (\citealt{gala}).
+    Right panel: distribution of maximum $z$-heights for orbits computed from
+    all posterior samples.
+  }
+  \label{fig:orbit}
+\end{figure}
 
 \section*{Supplementary Information}
+
+\subsection*{Proximity in phase-space coordinates}
+
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
+  \end{center}
+  \caption{%
+    Differences in posterior samples over Galactocentric phase-space coordinates
+    for the two stars \sunanalog\ and \bizarreone.
+    \label{fig:dxdv}}
+\end{figure}
+
+Combining the precise radial velocities obtained from spectra with the \tgas\
+astrometry, we can compare differences between the inferred 6D phase-space
+coordinates of the two stars.
+We start by generating posterior samples over the Heliocentric distance, $r$,
+tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
+given the observed parallax, $\hat\pi$, and proper motions,
+$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
+We assume the noise is Gaussian, and the radial velocity measurement is
+uncorrelated with the astrometric measurements.
+If we define
+\begin{eqnarray}
+  \vec{\hat y} &=&
+      \transp{\left(
+        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
+          \hat\pi &
+          \hat\mu_{\alpha^*} &
+          \hat\mu_\delta &
+          \hat v_r
+        \end{array}
+      \right)}\\
+  \vec{y} &=&
+      \transp{\left(
+        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
+          r^{-1} &
+          r^{-1}\,v_\alpha &
+          r^{-1}\,v_\delta &
+          v_r
+        \end{array}
+      \right)}
+\end{eqnarray}
+then the likelihood is
+\begin{equation}
+  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
+\end{equation} where $\mat{C}$ is the covariance matrix.
+We adopt a uniform space density prior for the distance and an isotropic
+Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
+\begin{eqnarray}
+p(r) &=&
+  \begin{cases}
+    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
+    0              & \text{otherwise}
+  \end{cases}\\
+p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
+  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
+\end{eqnarray}
+%
+For each of the two stars, we use \project{emcee}
+(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
+v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
+512 steps as the burn-in period.
+For each sample, we convert the heliocentric phase-space coordinates into
+Galactocentric coordinates assuming that the Sun's position and velocity are
+$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
+(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.
+
+\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
+Galactocentric phase-space coordinates for the two stars.
+The differences in positions and velocities are consistent with zero.
+\todo{should we instead show $|\Delta\boldsymbol{x}|$ and
+$|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
+
+\subsection*{}
+
+The surface lithium abundance in a sun-like star decreases with its age due to
+mixing induced by convection or rotation, which brings the lithium into the
+interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
+burning.
+Thus, surface lithium abundance is an indicator of stellar ages.
+The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
+of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
+solar lithium abundance and rotational profile\cite{2005Sci...309.2189C}.
+The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
+among all measured elements.
+This translates to a $\sim 500$~Myr difference in age.
+Given the overall higher metal abundances and the peculiar abundance patterns
+in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
+abundance means a younger age or something else.
+For example, the presence of $\elem{Li}$-rich red giant stars has been
+attributed to the engulfment of substellar companions such as gas giant planets
+or brown dwarfs which may replenish $\elem{Li}$\cite{Casey:2016aa}.
+
+In fact, the surface lithium abundance is the only indication that points to
+younger ages.
+If the two stars are indeed only several hundred Myrs old at most,
+they are expected to be part of a larger comoving group of stars.
+However, as we mention above, there is no evidence in our search of comoving pairs
+using \tgas\ that the two stars belong to a larger group of young stars.
+Very young stars often show signs of activity such as
+X-ray emission from magnetic activity, emission lines, or infrared excess due to
+circumstellar disks (\todo{needs refernces}).
+We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
+and found no evidence for indications of activity in their spectral energy
+distributions.
+The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
+young ages that would be inferred from the surface lithium abundances.
+Finally, we computed the Galactic orbit of the pair using the median of the
+posterior sample over the phase space coordinates of \sunanalog, in a Milky
+Way-like gravitational potential (similar to \texttt{MWPotential2014} from
+\cite{Bovy:2015}) using \project{Gala} (\cite{gala}).
+The pair's fiducial orbit has a vertical action larger than the Sun, favoring
+an older age (\todo{needs references for vertical action as age indicator}).
+We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
+old main sequence stars, and that their unusually high \elem{Li} abundance
+requires an alternative explanation.
+
+\subsection{Chemical Inhomogeneity in Star Formation}
+\label{sub:chemical_inhomogeneity_in_star_formation}
+
+Assuming that the two stars were born together, one possibility to
+explain the chemical difference is that there was chemical inhomogeneity within
+the birth cloud.
+However, there is already ample evidence against such a scenario.
+First, none of the other seven similar wide binaries examined in
+\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
+Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
+$\elem{O}$, and some pairs show a difference in particular elements as large as
+$\approx 0.15$~dex.
+The median and maximum \feh\ difference between component stars in the other
+seven pairs is $0.02$~dex and $0.09$~dex, respectively.
+The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
+compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
+(\figname~\ref{fig:deltaXH}).
+This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
+23 wide binaries of late F to K dwarfs, and found most pairs show a difference
+in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
+Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
+binaries have the same chemical composition with $\gtrsim 0.01$~dex
+uncertainties.
+Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
+not likely due to chemical inhomogeneity in the birth cloud.
 

### 2017-06-19 paper/ms.tex
More trimming and references

@@
 
+% Titles:
+% - 90 characters (including spaces)
+% - do not normally include numbers, acronyms, abbreviations or punctuation
+% - They should include sufficient detail for indexing purposes but be general
+%   enough for readers outside the field to appreciate what the paper is about.
 \title{
-  Kronos \& Krios:
-  Evidence for accretion of a massive, rocky planetary system
-  in a comoving pair of G dwarfs
+  Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs
 }
@@
   However, formation and evolution of different planetary systems around each star in a wide binary
-  may eventually lead to a difference in the compositions of the component stars' radiative and
+  may eventually lead to a difference in compositions of the component stars' radiative and
   convective layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
@@
 
-Aside from the kinematics, their stellar parameters also indicates that they are coeval.
+Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
 We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
@@
 
-However, one of the stars, \bizarreone\ is significantly more metal
+However, one of the stars, \bizarreone\, is significantly more metal
 rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
 Moreover, not all elements are equally enhanced:
-the abundances of \bizarreone\ show selective depletion in
+the abundances of \bizarreone\ show selective under-enhancement in
 \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
-relative to \elem{Fe}.
+relative to \elem{Fe} and other refractory elements.
 %
@@
 The maximum metallicity difference observed in the other pairs is $\Delta\feh = 0.03$~dex
-with $1-\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
+with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
 This is consistent with similar studies of metallicity and abundance differences
@@
 
-In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
-between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
-of each element.
-The equilibrium condensation temperatures for the composition of solar system
-are taken from \cite{2003ApJ...591.1220L} (Table~8).
-The difference seen in \bizarreone-\sunanalog\ is
-compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
-The metallicity difference of $\approx 0.2$~dex observed in this pair
-is larger than the differences seen in any other pairs studied so far.
-Strikingly, the five under-enhanced elements in \bizarreone\
+We show the abundance difference between \bizarreone\ and \sunanalog\ ordered
+by each element's equilibrium \Tcondens\ in solar system composition
+gas\citet{2003ApJ...591.1220L} in Figure~\ref{fig:toycalc}.
+The five under-enhanced elements in \bizarreone\
 relative to \sunanalog\ are the five most volatile in all elements measured.
@@
 \elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
-This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
-combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
-strongly suggests that accretion of rocky material has occured in \bizarreone.
 
-We interpret the \Tcondens-dependent difference of elemental abundance between
-the two stars as evidence for accretion of rocky planetary material in
-\bizarreone.
-Instabilities may develop in a multi-planet system due to its chaotic nature
-which may lead to planet engulfment or ejection by the host star
-(\todo{needs references}).
-%TODO: kozai?
+We interpret the \Tcondens-dependent metal enhancement of \bizarreone\ relative
+to \sunanalog\ and the very high surface \elem{Li} abundance ($A(\elem{Li}) =
+2.75$) of \bizarreone\ as evidence for accretion of rocky (refractory-rich)
+planetary material in \bizarreone.
+In a multi-planet system, dynamical instabilities triggered by planet-planet
+scattering\cite{} or encounters\cite{Malmberg:2011aa} with a field star can
+lead some planets to be ejected or accreted onto its host star.
+If one of the two stars in a wide binary accreted refractory-rich (rocky) planets
+more than the other, the accretion may imprint a strong \Tcondens\-dependent
+abundance differences like those observed in \bizarreone-\sunanalog.
 
@@
 
-We estimate how much mass of rocky material is needed to explain an increment of
-$\approx 0.2$~dex in refractory elements.
-We carry out simple toy calculations of expected $\Delta\elemH{X}$
-in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
-under these simplifying assumptions:
-\begin{itemize}
-  \item The material added is instantly and completely mixed.
-  \item The atmospheric composition that we measure is identical throughout
-    the star's radiative and convective zone.
-  \item The surface abundance of the star has been altered only by the
-    accretion event(s).
-\end{itemize}
-We take the solar abundances, $\elemH{X}$, of element \elem{X}
-(\cite{Asplund:2009aa}) which can be converted to mass fraction as
-\begin{equation}
-  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
-\end{equation}
-where $m_X$ is the mass of each element in e.g., atomic mass unit.
-Assuming that the added material has a total mass $M_\mathrm{add}$, and the
-mass fraction in each element $f_{X,\mathrm{add}}$,
-the abundance difference is
-\begin{equation}
-  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
-    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
-    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
-\end{equation}
+We estimate that accretion of $\approx 20$~\mearth\ of rocky planets
+in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
+refractory elements as well as the surface Li abundance.
+
 where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
@@
 
-What about \elem{Li}?
 The element \elem{Li} is worth special attention in the context of the
@@
 
-\subsection*{}
+\subsection*{Stellar Ages and Coevality}
 
@@
 
-\subsection{Chemical Inhomogeneity in Star Formation}
+\subsection*{Chemical Inhomogeneity in Star Formation}
 \label{sub:chemical_inhomogeneity_in_star_formation}
@@
 
+\subsection*{Estimating the accreted masses}
+
+We estimate how much mass of rocky material is needed to explain an increment of
+$\approx 0.2$~dex in refractory elements.
+We carry out simple toy calculations of expected $\Delta\elemH{X}$
+in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
+under these simplifying assumptions:
+\begin{itemize}
+  \item The material added is instantly and completely mixed.
+  \item The atmospheric composition that we measure is identical throughout
+    the star's radiative and convective zone.
+  \item The surface abundance of the star has been altered only by the
+    accretion event(s).
+\end{itemize}
+We take the solar abundances, $\elemH{X}$, of element \elem{X}
+(\cite{Asplund:2009aa}) which can be converted to mass fraction as
+\begin{equation}
+  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
+\end{equation}
+where $m_X$ is the mass of each element in e.g., atomic mass unit.
+Assuming that the added material has a total mass $M_\mathrm{add}$, and the
+mass fraction in each element $f_{X,\mathrm{add}}$,
+the abundance difference is
+\begin{equation}
+  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
+    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
+    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
+\end{equation}
+where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
+We take the composition of bulk Earth from a chondritic model of the Earth
+(\cite{mcdonough2001composition}).
+Similar calculations have been performed by \citet{Chambers:2010aa} and
+\citet{Mack:2014aa,Mack:2016aa}.
+
 %\input{kk.tex}

### 2017-06-19 paper/ms.tex
Tweaks and todo

@@
 % ----------
-% - cite gaia dr paper
+% - Fit summary in the first page.
 
@@
 
-\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me
-
 % Titles:
@@
 \title{
+\vspace{-2cm}
   Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs
+  % \vspace{-1cm}
 }
-\maketitle
 
@@
   Adrian M. Price-Whelan$^{1}$,\,
-  John M. Brewer$^{2}$,\,
+  John M. Brewer$^{2}$,\,\\
   David W. Hogg$^{3,4,5,6}$,\,
@@
 }
+
+\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me
+\maketitle
 
@@
 %   the paper have moved the field forwards.
+% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
 % ------------------------
@@
 from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
-component of the first data release of the astrometric space mission \gaia\
+component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
 (the astrometric measurements are listed in \tablename~\ref{tab:t1}).

### 2017-06-21 paper/ms.tex
working

@@
 \usepackage{mathptmx}
+\usepackage{threeparttable}
 
@@
 {\bf \noindent
-  Stars that are born together are expected to have same chemical compositions initially.
-  Detailed chemical abundance studies of stars in wide binaries indeed reveal nearly identical
-  chemistry in most cases\citep{Gratton:2001aa,Desidera:2004aa} as well as stars in open clusters\cite{Bovy:2016aa}.
-  However, formation and evolution of different planetary systems around each star in a wide binary
-  may eventually lead to a difference in compositions of the component stars' radiative and
-  convective layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
+  Stars that are born together are expected to have same chemical compositions
+  initially.
+  Detailed chemical abundance studies of stars in wide binaries indeed reveal
+  nearly identical chemistry in most
+  cases\citep{Gratton:2001aa,Desidera:2004aa} as well as stars in open
+  clusters\cite{Bovy:2016aa}.
+  However, formation and evolution of different planetary systems around each
+  star in a wide binary may eventually lead to a difference in compositions of
+  the component stars' radiative and convective
+  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
   Wide binary systems of two twin-like stars are particularly useful
@@
   chemical abundances have been reported so far
-  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
+  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
+    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
   However, a convincing example is yet to be found.
@@
 \begin{table*}[htpb]
-  \caption{Astrometric and spectroscopic measurements.}
-  \label{tab:t1}
   \centering
-  \begin{tabular}{ccc}
+  \begin{threeparttable}
+  \caption{Astrometric and spectroscopic measurements of the pair\label{tab:t1}}
+\begin{tabular}{ccccc}
 \hline\hline
-Name & HD 240429 & HD 240430 \\
+                        &                & \sunanalog\            & \bizarreone\           &               \\
+Name                    & Units          & HD 240429              & HD 249439              & Uncertainties \\
 \hline
-Sp Type                                   & G2                & G0                \\
-$T_\mathrm{eff}$                          & 5878              & 5803              \\
-$\log{g}$                                 & 4.43              & 4.33              \\
-$v\sin{i}$                                & 1.1               & 2.5               \\
-$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
-$v_r$                                     & $-21.2$           & $-21.2$           \\
-$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
-$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
-$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
-\hline\hline 
+Sp Type                 &                & G2                     & G0                     &               \\
+R.A.\tnote{a}           & hh:mm:ss       & 23:51:55.21            & 23:52:09.42            &               \\
+Dec.\tnote{a}           & dd:mm:ss       & 59:42:48.16            & 59:42:26.08            &               \\
+2MASS $J$\tnote{a}      & mag            & $8.593 \pm 0.023$      & $8.415 \pm 0.026$      &               \\
+$T_\mathrm{eff}$        & K              & 5878                   & 5803                   & 25            \\
+$\log{g}$               &                & 4.43                   & 4.33                   & 0.028         \\
+$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    &               \\
+$[\elem{Fe}/\elem{H}]$  &                & 0.01                   & 0.20                   & 0.010         \\
+Age\tnote{b}            & Gyr            & $4.00_{-1.56}^{+1.51}$ & $4.28_{-1.03}^{+1.11}$ &               \\
+$v_r$                   & \kms\          & $-21.2$                & $-21.2$                & 0.2           \\
+$\varpi$\tnote{a}       & mas            & $9.35 \pm 0.24$        & $9.41 \pm 0.25$        &               \\
+$\mu_\alpha^*$\tnote{a} & mas\,yr$^{-1}$ & $89.25 \pm 0.66$       & $89.41 \pm 0.69$       &               \\
+$\mu_\delta$\tnote{a}   & mas\,yr$^{-1}$ & $-29.68 \pm 0.54$      & $-30.12 \pm 0.52$      &               \\
+\hline 
+\multicolumn{5}{c}{$T_c < 1200$~K} \\
+\hline 
+$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 &               \\
+$\elemH{C}$             &                & $0.00$                 & $0.09$                 & 0.026         \\
+$\elemH{N}$             &                & $-0.06$                & $-0.01$                & 0.042         \\
+$\elemH{O}$             &                & $0.01$                 & $0.09$                 & 0.036         \\
+$\elemH{Na}$            &                & $-0.06$                & $-0.04$                & 0.014         \\
+$\elemH{Mn}$            &                & $-0.03$                & $0.00$                 & 0.020         \\
+\hline 
+\multicolumn{5}{c}{$T_c > 1200$~K} \\
+\hline 
+$\elemH{Mg}$            &                & $0.01$                 & $0.19$                 & 0.012         \\
+$\elemH{Al}$            &                & $0.01$                 & $0.21$                 & 0.028         \\
+$\elemH{Si}$            &                & $0.00$                 & $0.16$                 & 0.008         \\
+$\elemH{Ca}$            &                & $0.02$                 & $0.23$                 & 0.014         \\
+$\elemH{Ti}$            &                & $0.02$                 & $0.20$                 & 0.012         \\
+$\elemH{V}$             &                & $0.02$                 & $0.20$                 & 0.034         \\
+$\elemH{Cr}$            &                & $0.01$                 & $0.17$                 & 0.014         \\
+$\elemH{Fe}$            &                & $0.01$                 & $0.20$                 & 0.010         \\
+$\elemH{Ni}$            &                & $-0.01$                & $0.21$                 & 0.014         \\
+$\elemH{Y}$             &                & $0.04$                 & $0.26$                 & 0.030         \\
+
 \end{tabular}
+\begin{tablenotes}
+\item [a] From \tgas.
+\item [b] Derived in this work by isochrone fitting using the Yale-Yonsei model
+  isochrones\cite{2013ApJ...776...87S}.
+\item [c] Absolute abundances from Myles \etal, in prep.
+\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
+\end{tablenotes}
+\end{threeparttable}
 \end{table*}
 
+% general description of the pair and measurements
 \sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
@@
 In a separate effort to study detailed chemical abundances of potential
-planet-hosting stars, high resolution, high signal-to-noise ratio spectra of
+planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
+high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
 both stars were obtained using the HIRES spectrograph on the Keck-I
 telescope\cite{2016ApJS..225...32B}. 
-The spectral resolution is $R=\lambda/\Delta\lambda\approx 70000$ and the
-wavelength coverage is $5164$--$7799$~\AA.
-A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
+The wavelength coverage is $5164$--$7799$~\AA.
 The resulting measurements include elemental abundances for 15 chemical species
@@
 
+% likely origin given its proximity in phase space
+% TODO reference dxdv figure here
 The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
@@
 
+% coevality based on stellar parameters
+% TODO reference supplement discussion on age here?
 Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
@@
 
-However, one of the stars, \bizarreone\, is significantly more metal
-rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
-Moreover, not all elements are equally enhanced:
-the abundances of \bizarreone\ show selective under-enhancement in
-\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
-relative to \elem{Fe} and other refractory elements.
-%
-The validity of the measured abundance differences is further demonstrated
-in \figname~\ref{fig:spec1} and \ref{fig:spec2} where we show
-segments of the spectra and models of the two stars
-used to measure their abundances.
-As expected from their reported metallicity difference ($\Delta\feh \approx 0.2$),
-the ratio of data and model between the two stars show significant
-residuals of almost all metal line features, largely dominated by \elem{Fe}.
-However, for lines of elements that are not as enhanced in \bizarreone\,
-the residuals are much smaller in amplitude.
+% metallicity and abundance difference
+However, one of the stars, \bizarreone\, is significantly more metal rich than
+the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
+Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
+show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
+and \elem{Mn} relative to \elem{Fe} and other refractory elements.
+As expected from their measured metallicity difference, the ratio of data and
+model between the two stars show significant residuals of almost all metal line
+features, largely dominated by \elem{Fe}.
+However, for lines of elements that are not as enhanced in \bizarreone\, the
+residuals are much smaller in amplitude demonstrating the validity of the
+measured abundance differences (see
+Figure~\ref{fig:spec1} and \ref{fig:spec2}).
 
+% novelty
 The observed difference in metallicity and abundances are genuinely rare and
@@
 None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) wide
-binary pairs examined using spectra of comparable quality and the same
+binary pairs examined using spectra of similar quality and the same
 consistent measurement pipeline shows discrepancies in abundances between the
 stars at this level\cite{2016ApJS..225...32B} (see Figure~\ref{fig:deltaXH}).
-The maximum metallicity difference observed in the other pairs is $\Delta\feh = 0.03$~dex
-with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
-This is consistent with similar studies of metallicity and abundance differences
-in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
-The difference of $\approx 0.2$~dex is also the largest among a handful of
-wide binaries that do show metallicity and abundance differences with varying
+The maximum metallicity difference observed in the other pairs is $\Delta\feh =
+0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
+This is consistent with similar studies of metallicity and abundance
+differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
+The difference of $\approx 0.2$~dex is also the largest among a handful of wide
+binaries that do show metallicity and abundance differences with varying
 significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
@@
 
-%As shown in \figname~\ref{fig:deltaXH},
-%the differences in other pairs for all elements except \elem{N} and \elem{O},
-%which are also the most uncertain (\tablename~\ref{tab:kk}),
-%are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
-
+% high Li
 Both stars have high surface \elem{Li} abundances considering
@@
 interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
-burning.
+burning. %TODO: REFERENCE
 The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
@@
 
-The element \elem{Li} is worth special attention in the context of the
-accretion scenario.
-Because Li is present in either carbonaceous chondrites or bulk Earth with
-a concentration of $1-1.5$~ppm in mass (\cite{mcdonough2001composition}),
-but is depleted quickly within the first couple of Gyrs on the surface of a
-Sun-like star, accretion of either material at later times will significantly
+The accretion scenario can naturally explain the anomalously high
+surface \elem{Li} abundance in \bizarreone.
+Because \elem{Li} is strongly depleted in old sun-like stars yet
+present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
+late-time accretion of rocky planetary material will significantly
 replenish the lithium on the star's surface.
@@
 
+%As shown in \figname~\ref{fig:deltaXH},
+%the differences in other pairs for all elements except \elem{N} and \elem{O},
+%which are also the most uncertain (\tablename~\ref{tab:kk}),
+%are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
+
 \begin{figure}[htpb]
@@
     The feature in the third column of the second row is a strong \elem{Li}
-    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
-    studied in a separate work (\citealt{jmlithium}).
+    line that was studied in Myles \etal, in prep.
     Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
     in \bizarreone\ relative to \elem{Fe} or other refractory elements,
-    show weaker residuals.
+    show noticeably weaker residuals compared to neighboring lines of
+    refractory elements.
   }
@@
   \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
-\end{equation} where $\mat{C}$ is the covariance matrix.
+\end{equation} where $\mat{C}$ is the covariance matrix, and $\mathcal{N}$ is
+normal (Gaussian) distribution.
 We adopt a uniform space density prior for the distance and an isotropic
@@
 %
-For each of the two stars, we use \project{emcee}
-(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
-v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
+For each of the two stars, we use \project{emcee}\cite{2013PASP..125..306F}
+to generate posterior samples in $(r, v_\alpha, v_\delta, v_r)$
+by running 64 walkers for 4608 steps and discarding the first
 512 steps as the burn-in period.
@@
 $\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
-(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.
+(-11.1,\,244,\,7.25)~\kms$\cite{Schonrich:2010, Schonrich:2012}.
 
@@
 We estimate how much mass of rocky material is needed to explain an increment of
-$\approx 0.2$~dex in refractory elements.
-We carry out simple toy calculations of expected $\Delta\elemH{X}$
+$\approx 0.2$~dex in refractory elements observed in \bizarreone\
+relative to \sunanalog.
+Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
+and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx XX$,
+$\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
+we may approximate the pre-accretion abundances of \bizarreone\ with the Sun.
+The expected $\Delta\elemH{X}$
 in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition

### 2017-06-22 paper/ms.tex
Move things around and add new figures

@@
   Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs
-  % \vspace{-1cm}
+  \vspace{-0.5cm}
 }
@@
 }
+\date{\small\today}
 
@@
 % affiliations
+\vspace{-1cm}
 {\small\noindent
-  $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu} \\
   $^1$Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA \\
@@
   $^6$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
+  $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}
 }
@@
 We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, \elemH{Si}
-in order interpolate the mass, age, radius, and $\log(g)$ of each star
+in order interpolate the age, mass, and radius of each star
 in a grid of Yale-Yonsei model isochrones\cite{2013ApJ...776...87S}.
@@
 $4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
-consistent with them being coeval.
+consistent with them being coeval (see Figure~\ref{fig:yyisofitting}).
 
@@
 interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
-burning. %TODO: REFERENCE
+burning. %TODO: REFERENCE?
 The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{toycalc.png}
+  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
   \caption{
@@
   }
-  \label{fig:toycalc}
+  \label{fig:deltaxh_tcrank}
 \end{figure}
 
-We show the abundance difference between \bizarreone\ and \sunanalog\ ordered
+The abundance differences show a strong increasing trend with condensation
+temperature of elements.
+In Figure~\ref{fig:deltaxh_tcrank},
+we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
 by each element's equilibrium \Tcondens\ in solar system composition
-gas\citet{2003ApJ...591.1220L} in Figure~\ref{fig:toycalc}.
+gas\citet{2003ApJ...591.1220L}.
 The five under-enhanced elements in \bizarreone\
@@
 In a multi-planet system, dynamical instabilities triggered by planet-planet
-scattering\cite{} or encounters\cite{Malmberg:2011aa} with a field star can
-lead some planets to be ejected or accreted onto its host star.
-If one of the two stars in a wide binary accreted refractory-rich (rocky) planets
-more than the other, the accretion may imprint a strong \Tcondens\-dependent
+scattering\cite{} or encounters with a field star\cite{Malmberg:2011aa} can
+lead to planet ejection or accretion.
+If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
+than the other, this may imprint a strong \Tcondens\-dependent
 abundance differences like those observed in \bizarreone-\sunanalog.
@@
 
-We estimate that accretion of $\approx 20$~\mearth\ of rocky planets
+We estimate that accretion of $\approx 15$~\mearth\ of rocky planets
 in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
 refractory elements as well as the surface Li abundance.
-
-where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
-We take the composition of bulk Earth from a chondritic model of the Earth
-(\cite{mcdonough2001composition}).
-Similar calculations have been performed by \citet{Chambers:2010aa} and
-\citet{Mack:2014aa,Mack:2016aa}.
-
-Figure~\ref{fig:toycalc} shows the expected change of surface abundances of
-metals in a Sun-like star after $20~\mearth$ of material with composition of
-bulk Earth is added.
+Because the anchor star, \sunanalog,
+is very close in its properties (\teff, \logg, \feh, age) to the Sun,
+we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
+pre-accretion state of \bizarreone.
+In Figure~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
+$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth
+composition\cite{2003TrGeo...2..547M}.
 A volatility trend that more volatile (low \Tcondens) elements are more
 depleted in the Earth relative to CI or other carbonaceous chondrites
-has long been known (\cite{mcdonough2001composition}).
+has long been known\cite{mcdonough2001composition}.
 This trend is presumed to be closely related to the formation of terrestrial
@@
 protoplanetary disk.
-The trend resulting from adding $20~\mearth$ of bulk Earth
+The trend resulting from adding $15$~\mearth\ of bulk Earth
 provides an overall good match to the observed $\Delta\elemH{X}$,
 suggesting that the refractory-enhanced star, \bizarreone\,
-accreted $20~\mearth$ more of rocky planetary material than \sunanalog.
+accreted $15$~\mearth more of rocky planetary material than \sunanalog.
 
@@
 % - more geochemical study references
-We stress that while the calculation carried out is useful in
-an order-of-magnitude sense, further investigation of each of the simplifying
-assumptions made is warranted.
-In addition, the composition of bulk Earth has some uncertainties.
-For example, the reported bulk Earth concentration of the siderphile element
-\elem{Mn}, varies from $800$ to $1700$~ppm (\cite{1998psc..book.....L}).
-While the latter value from \cite{mcdonough2001composition} has been used in
-our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
-to an even closer agreement.
-Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
-\elem{Li} for \bizarreone\ is remarkable.
+%We stress that while the calculation carried out is useful in
+%an order-of-magnitude sense, further investigation of each of the simplifying
+%assumptions made is warranted.
+%In addition, the composition of bulk Earth has some uncertainties.
+%For example, the reported bulk Earth concentration of the siderphile element
+%\elem{Mn}, varies from $800$ to $1700$~ppm (\cite{1998psc..book.....L}).
+%While the latter value from \cite{mcdonough2001composition} has been used in
+%our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
+%to an even closer agreement.
+%Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
+%\elem{Li} for \bizarreone\ is remarkable.
 
@@
 
-\begin{table*}[htpb]
-  \caption{Astrometric and spectroscopic measurements.}
-  \label{tab:t2}
+\begin{figure}[htpb]
   \centering
-  \begin{tabular}{ccc}
-\hline\hline
-Name & HD 240429 & HD 240430 \\
-\hline
-Sp Type                                   & G2                & G0                \\
-$T_\mathrm{eff}$                          & 5878              & 5803              \\
-$\log{g}$                                 & 4.43              & 4.33              \\
-$v\sin{i}$                                & 1.1               & 2.5               \\
-$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
-$v_r$                                     & $-21.2$           & $-21.2$           \\
-$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
-$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
-$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
-\hline
-\multicolumn{3}{c}{$T_c < 1200$~K} \\
-\hline
-$A(\elem{Li})$ \footnotemark[2]           & $2.25$            & $2.75$            \\
-$\elemH{C}$                               & $0.00$            & $0.09$            \\
-$\elemH{N}$                               & $-0.06$           & $-0.01$           \\
-$\elemH{O}$                               & $0.01$            & $0.09$            \\
-$\elemH{Na}$                              & $-0.06$           & $-0.04$           \\
-$\elemH{Mn}$                              & $-0.03$           & $0.00$            \\
-\hline
-\multicolumn{3}{c}{$T_c > 1200$~K} \\
-\hline
-$\elemH{Mg}$                              & $0.01$            & $0.19$            \\
-$\elemH{Al}$                              & $0.01$            & $0.21$            \\
-$\elemH{Si}$                              & $0.00$            & $0.16$            \\
-$\elemH{Ca}$                              & $0.02$            & $0.23$            \\
-$\elemH{Ti}$                              & $0.02$            & $0.20$            \\
-$\elemH{V}$                               & $0.02$            & $0.20$            \\
-$\elemH{Cr}$                              & $0.01$            & $0.17$            \\
-$\elemH{Fe}$                              & $0.01$            & $0.20$            \\
-$\elemH{Ni}$                              & $-0.01$           & $0.21$            \\
-$\elemH{Y}$                               & $0.04$            & $0.26$            \\
-\hline\hline
-\end{tabular}
-%
-%\begin{tablenotes}
-%  \item All spectroscopic measurements except $\elem{Li}$ are from \citealt{2016ApJS..225...32B}.
-%  \footnotetext[1]{From \tgas. }
-%  \footnotetext[2]{Absolute abundance from \todo{CITE}.}
-%\end{tablenotes}
-\end{table*}
+  \includegraphics[width=0.95\linewidth]{yyisofitting.pdf}
+  \caption{Probability density function of stellar age, mass, and radius
+    from isochrone fitting using Yonsei-Yale isochrones\cite{2013ApJ...776...87S}
+    and the star's luminosity, \teff, \feh, and \elemH{Si}.
+  }
+  \label{fig:yyisofitting}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec1.pdf}
+  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
+    Alternating sets of two rows show
+    the continuum-normalized data and model in the upper panel,
+    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
+    in the lower panel.
+  }
+  \label{fig:spec1}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{spec2.pdf}
+  \caption{Same as \figname~\ref{fig:spec1}
+    but for smaller portions of spectra at longer wavelengths that are
+    not dominated by \elem{Fe}.
+    We mark elements that give rise to strong absorption lines.
+    The feature in the third column of the second row is a strong \elem{Li}
+    line that was studied in Myles \etal, in prep.
+    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
+    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
+    show noticeably weaker residuals compared to neighboring lines of
+    refractory elements.
+  }
+  \label{fig:spec2}
+\end{figure}
+
+%TODO: plot styles...
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{orbits.pdf}
+  \end{center}
+  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
+    Sun (grey).
+    For \sunanalog, the initial conditions are set to the median of the
+    posterior samples over the phase-space coordinates.
+    The orbits are computed by integrating backwards from the present-day
+    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
+    integration scheme implemented in \project{Gala} (\citealt{gala}).
+    Right panel: distribution of maximum $z$-heights for orbits computed from
+    all posterior samples.
+  }
+  \label{fig:orbit}
+\end{figure}
 
@@
 
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec1.pdf}
-  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
-    Alternating sets of two rows show
-    the continuum-normalized data and model in the upper panel,
-    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
-    in the lower panel.
-  }
-  \label{fig:spec1}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{spec2.pdf}
-  \caption{Same as \figname~\ref{fig:spec1}
-    but for smaller portions of spectra at longer wavelengths that are
-    not dominated by \elem{Fe}.
-    We mark elements that give rise to strong absorption lines.
-    The feature in the third column of the second row is a strong \elem{Li}
-    line that was studied in Myles \etal, in prep.
-    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
-    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
-    show noticeably weaker residuals compared to neighboring lines of
-    refractory elements.
-  }
-  \label{fig:spec2}
-\end{figure}
-
-%TODO: plot styles...
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{orbits.pdf}
-  \end{center}
-  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
-    Sun (grey).
-    For \sunanalog, the initial conditions are set to the median of the
-    posterior samples over the phase-space coordinates.
-    The orbits are computed by integrating backwards from the present-day
-    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
-    integration scheme implemented in \project{Gala} (\citealt{gala}).
-    Right panel: distribution of maximum $z$-heights for orbits computed from
-    all posterior samples.
-  }
-  \label{fig:orbit}
-\end{figure}
-
 \section*{Supplementary Information}
@@
 We adopt a uniform space density prior for the distance and an isotropic
-Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
+Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$:
 \begin{eqnarray}

### 2017-06-22 paper/ms.tex
more edits

@@
   Detailed chemical abundance studies of stars in wide binaries indeed reveal
-  nearly identical chemistry in most
-  cases\citep{Gratton:2001aa,Desidera:2004aa} as well as stars in open
-  clusters\cite{Bovy:2016aa}.
+  little to no differences in most cases\citep{Gratton:2001aa,Desidera:2004aa}.
   However, formation and evolution of different planetary systems around each
-  star in a wide binary may eventually lead to a difference in compositions of
-  the component stars' radiative and convective
+  star in a wide binary may eventually lead to a difference in chemical
+  abundances of the component stars' radiative and convective
   layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
-  Wide binary systems of two twin-like stars are particularly useful
-  as they are not subject to confusion with Galactic chemical evolution.
-  A handful of wide binaries that show small differences in their surface
-  chemical abundances have been reported so far
+  Wide binary systems of two twin-like stars are particularly useful since such
+  chemical signature may be more easily detectable as abundance differences,
+  free from dependence on stellar parameters or confusion with Galactic chemical
+  evolution.
+  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
+  in their surface chemical abundances have been reported so far
   \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
@@
   However, a convincing example is yet to be found.
+  %
   Here we report a comoving pair of bright sun-like stars, HD~240430 and HD~240429,
+  hereafter ``\bizarreone'' and ``\sunanalog'',
   with a significant difference ($\approx 0.2$~dex) in their chemical
-  abundances that strongly suggests accretion of rocky planetary system in one
-  of the stars within the last couple of billion years.
-  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
-  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
-  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
-  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
-  The two stars also show high Li abundance given their age of $\sim 4$ Gyr
+  abundances that strongly suggests massive accretion of rocky planetary system in one
+  of the stars within the last billion years.
+  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
+  elements by $\approx 0.2$~dex but not as large
+  an enhancement of (moderately) volatile elements.
+  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr
   inferred from their stellar parameters.
-  A prominent trend of element abundance enhancement with condensation temperature
-  indicates the accreted material is rocky.
-  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
-  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
+  We suggest that the star \bizarreone, recently accreted
+  $\approx 15$~\mearth\ of rocky material selectively enhancing the
   refractory elements in its surface and convective envelope.
-  The other star HD~240429, ``Krios'', may also have had a similar accretion
+  The other star, \sunanalog, may also have had a similar accretion
   event given its high surface \elem{Li} abundance but of much smaller amount
@@
   \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
-    normalized to \elem{H} (top) and \elem{Fe} (bottom).
+  \caption{Abundances of the comoving pair, 
+    \bizarreone\ (red circles) and \sunanalog\ (blue squares).
     Lines are drawn for each star only to guide the eye.
@@
 $\elemH{Y}$             &                & $0.04$                 & $0.26$                 & 0.030         \\
-
+\hline
 \end{tabular}
@@
 \item [c] Absolute abundances from Myles \etal, in prep.
-\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
+%\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
 \end{tablenotes}
@@
   \caption{
-    Comparing the observed abundance difference vs. \Tcondens\ rank
-    to the expected change in solar surface abundance after adding $20$~\mearth\ of
-    material with bulk Earth composition (\cite{mcdonough2001composition}).
-    The assumed mass fraction in the convective zone is $0.03$.
-    All metals are ranked by their \Tcondens\ for solar composition gas,
-    and the condensation temperature may be read from the gray line and right y-axis,
-    same as in \figname~\ref{fig:relabun_tcrank}.
-    Locations of the elements measured for \bizarreone-\sunanalog\ pair are
-    indicated by a vertical line and its symbol.
+    Comparing the observed abundance difference (blue circles) to the expected
+    change in solar surface abundance after adding $15$~\mearth\ of material
+    with bulk Earth composition\cite{2003TrGeo...2..547M} (black open and
+    filled circles).
+    The assumed mass fraction in the convective zone is $0.02$.
+    All astronomical metals are ordered by their \Tcondens\ for solar
+    composition gas on the $x$-axis.
+    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
+    in filled circles, while those without a measurement are left open.
     The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
     suggests that the abundance difference may be due to accretion of
-    $20$~\mearth\ of rocky planetary material.
-    The element \elem{Li} is off the plot and indicated with a red arrow
-    (see text for details).
+    $15$~\mearth\ of rocky planetary material.
+    The element \elem{Li} is off the plot and indicated in the inset.
   }
@@
 The abundance differences show a strong increasing trend with condensation
-temperature of elements.
+temperature ($T_C$) of elements.
 In Figure~\ref{fig:deltaxh_tcrank},
@@
 by each element's equilibrium \Tcondens\ in solar system composition
-gas\citet{2003ApJ...591.1220L}.
+gas\cite{2003ApJ...591.1220L}.
 The five under-enhanced elements in \bizarreone\
@@
 $\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth
-composition\cite{2003TrGeo...2..547M}.
+composition\cite{2003TrGeo...2..547M} assuming that 2\% of the Sun's mass
+is in its convective zone\cite{Pinsonneault:2001aa}.
 A volatility trend that more volatile (low \Tcondens) elements are more
@@
 protoplanetary disk.
-The trend resulting from adding $15$~\mearth\ of bulk Earth
-provides an overall good match to the observed $\Delta\elemH{X}$,
-suggesting that the refractory-enhanced star, \bizarreone\,
-accreted $15$~\mearth more of rocky planetary material than \sunanalog.
+The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
+good match to the observed $\Delta\elemH{X}$, suggesting that the
+refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
+rocky planetary material than \sunanalog.
 
@@
 replenish the lithium on the star's surface.
-For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
-material would result in $\Delta\elemH{Li} \approx 1.6$~dex (which
-is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
-Incidentally, the star under examination, \bizarreone, has an age (informed by
-stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
+For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
+material would result in $\Delta\elemH{Li} \approx 1.6$~dex
+(see inset of Figure~\ref{fig:deltaxh_tcrank}).
+Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
+stellar parameters) very close to the Sun ($\sim 4$~Gyr).
 Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
@@
 This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
-$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \cite{jmlithium})
-approximately $1.65$~dex higher than the solar value of $1.1$~dex
-(\todo{needs reference}).
-Furthermore, this implies that the accretion event should have happened very
-recently, or at least within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep)
+approximately $1.65$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
+Furthermore, this implies that the accretion event should have happened
+recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
 
@@
 $\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
-(\cite{mcdonough2001composition}).
+\cite{mcdonough2001composition}.
 Unlike \bizarreone, we cannot know the pre-accretion abundances of
@@
 
-%TODO: augment this paragraph
-% - more geochemical study references
-%We stress that while the calculation carried out is useful in
-%an order-of-magnitude sense, further investigation of each of the simplifying
-%assumptions made is warranted.
-%In addition, the composition of bulk Earth has some uncertainties.
-%For example, the reported bulk Earth concentration of the siderphile element
-%\elem{Mn}, varies from $800$ to $1700$~ppm (\cite{1998psc..book.....L}).
-%While the latter value from \cite{mcdonough2001composition} has been used in
-%our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
-%to an even closer agreement.
-%Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
-%\elem{Li} for \bizarreone\ is remarkable.
-
-Given that the two stars must have engulfed planets,
-it is likely that they have not destroyed all of their planets.
-Any surviving planet around the stars must be giants.
-Fortunately, discovery of giant eccentric planets using astrometric jitter is in the sweet spot
-for Gaia.
+What triggered the planet engulfment in the two comoving stars
+within the last Gyr remains unclear.
+A possibility is that a fly-by interaction with a field star could have
+triggered eccentricity excitation of outer planets around each star, which may
+have propagated inward through planet-planet scattering, making inner rocky planets
+to be accreted\cite{Malmberg:2011aa}.
+If this is the case, there may be surviving highly eccentric giant planets that are
+potentially detectable with future data releases of \gaia.
 The two stars have not been included in any publicly released data from planet
@@
 
-\section*{Supplementary Information}
+\section{Supplementary Information}
 
-\subsection*{Proximity in phase-space coordinates}
+\subsection{Proximity in phase-space coordinates}
 
@@
     Differences in posterior samples over Galactocentric phase-space coordinates
-    for the two stars \sunanalog\ and \bizarreone.
+    for the two stars, \bizarreone\ and \sunanalog.
     \label{fig:dxdv}}
@@
 
-\subsection*{Stellar Ages and Coevality}
+\subsection{Stellar Ages and Coevality}
 
@@
 
-\subsection*{Chemical Inhomogeneity in Star Formation}
+\subsection{Alternative Scenarios}
+
+\subsubsection{Chemical Inhomogeneity in Star Formation}
 \label{sub:chemical_inhomogeneity_in_star_formation}
 
-Assuming that the two stars were born together, one possibility to
-explain the chemical difference is that there was chemical inhomogeneity within
-the birth cloud.
+Assuming that the two stars were born together, one alternative possibility to
+explain the chemical difference between the two stars is that there was
+chemical inhomogeneity within the birth cloud.
 However, there is already ample evidence against such a scenario.
-First, none of the other seven similar wide binaries examined in
-\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
+First, none of the other seven similar wide binaries examined
+with the same measurement pipeline\cite{2016ApJS..225...32B}
+show the same level of differences in abundances.
 Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
@@
 (\figname~\ref{fig:deltaXH}).
-This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
-23 wide binaries of late F to K dwarfs, and found most pairs show a difference
-in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
-Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
-binaries have the same chemical composition with $\gtrsim 0.01$~dex
-uncertainties.
+This is consistent with similar previous studies\cite{Gratton:2001aa,Desidera:2004aa}.
 Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
@@
 
-\subsection*{Estimating the accreted masses}
+\subsection{Estimating the accreted masses}
 
-We estimate how much mass of rocky material is needed to explain an increment of
-$\approx 0.2$~dex in refractory elements observed in \bizarreone\
-relative to \sunanalog.
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank_vari.pdf}
+  \caption{Expected differences in solar abundances after adding
+    varying mass of bulk Earth material.
+    Elements are ordered by their $T_C$ on $x$-axis, same as
+    Figure~\ref{fig:deltaxh_tcrank}.
+    The solid and dashed lines assume $f_\mathrm{CZ}=0.02$ and $f_\mathrm{CZ} =
+    0.03$ respectively.
+    For each $f_\mathrm{CZ}$, we show expected $\Delta\elemH{X}$
+    for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
+  }
+  \label{fig:vari}
+\end{figure}
+
+We estimate how much mass of rocky material is needed to explain an increment
+of $\approx 0.2$~dex in refractory elements observed in \bizarreone\ relative
+to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
 Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
@@
 we may approximate the pre-accretion abundances of \bizarreone\ with the Sun.
-The expected $\Delta\elemH{X}$
+We carry out simple toy calculations of expected $\Delta\elemH{X}$
 in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
@@
 \end{itemize}
-We take the solar abundances, $\elemH{X}$, of element \elem{X}
-(\cite{Asplund:2009aa}) which can be converted to mass fraction as
+We take the solar abundances\cite{Asplund:2009aa}, $\elemH{X}$, of element \elem{X}
+which can be converted to mass fraction as
 \begin{equation}
@@
 where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
-We take the composition of bulk Earth from a chondritic model of the Earth
-(\cite{mcdonough2001composition}).
-Similar calculations have been performed by \citet{Chambers:2010aa} and
-\citet{Mack:2014aa,Mack:2016aa}.
+We take the composition of bulk Earth\cite{mcdonough2001composition}
+as a proxy for rocky planet composition. We adopt $f_\mathrm{CZ} = 0.02$ for
+the fraction of mass in the convective zone\cite{Pinsonneault:2001aa}.
+
+The estimate of accreted mass depends sensitively on $f_\mathrm{CZ}$ and the
+mass of the star which are difficult quantities to constrain directly through
+data.
+While we adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, we show the
+expected changes in $\Delta\elemH{X}$ for $f_\mathrm{CZ}=0.03$ in
+Figure~\ref{fig:vari}.
+
+We stress that while the calculation carried out is useful in
+an order-of-magnitude sense, further investigation of each of the simplifying
+assumptions made is warranted.
+In addition, the composition of bulk Earth has some uncertainties.
+For example, the reported bulk Earth concentration of \elem{Mn}, varies from
+$800$ to $1700$~ppm\cite{1998psc..book.....L,mcdonough2001composition,2003TrGeo...2..547M}
+largely due to uncertainties in the composition of the Earth's core.
+Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
+\elem{Li} for \bizarreone\ is remarkable.
 

### 2017-06-23 paper/ms.tex
many tweaks; break page before supplement

@@
 (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
-parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities.
+parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
+(section~Table~\ref{tab:t1}).
 
 % likely origin given its proximity in phase space
-% TODO reference dxdv figure here
 The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
@@
 Although selected based only on their astrometry, the two stars
-have identical radial velocities within uncertainties (Table~\ref{tab:t1}),
-confirming that they are truly comoving.
+have identical radial velocities within uncertainties,
+confirming that they are truly comoving (\ref{supp:dxdv}).
 As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
@@
 in a grid of Yale-Yonsei model isochrones\cite{2013ApJ...776...87S}.
-The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
-$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
+The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
+$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
 consistent with them being coeval (see Figure~\ref{fig:yyisofitting}).
@@
 % metallicity and abundance difference
-However, one of the stars, \bizarreone\, is significantly more metal rich than
-the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
+However, one of the stars, \bizarreone, is significantly more metal rich than
+the other by 0.2~dex in \feh\ ($\approx 60\%$; \figname~\ref{fig:abundances}).
 Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
@@
 residuals are much smaller in amplitude demonstrating the validity of the
-measured abundance differences (see
-Figure~\ref{fig:spec1} and \ref{fig:spec2}).
+measured abundance differences (Figure~\ref{fig:spec1} and \ref{fig:spec2}).
 
@@
 consistent measurement pipeline shows discrepancies in abundances between the
-stars at this level\cite{2016ApJS..225...32B} (see Figure~\ref{fig:deltaXH}).
+stars at this level\cite{2016ApJS..225...32B} (Figure~\ref{fig:deltaXH}).
 The maximum metallicity difference observed in the other pairs is $\Delta\feh =
@@
 differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
+In fact, the abundance pattern of \bizarreone\ is a very unlikely one
+for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
+($\feh\approx 0$; \figname~\ref{fig:deltaXH}),
+implying that a scenario involving Galactic chemical evolution is not plausible
+even if we ignore a coeval star, \sunanalog, that we can compare with.
 The difference of $\approx 0.2$~dex is also the largest among a handful of wide
@@
   Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
-(see Figure~\ref{fig:relabun_tcrank}).
+(Figure~\ref{fig:relabun_tcrank}).
 
@@
 detectable at this age even for high signal-to-noise spectra, is clearly
-visible in the spectra of both stars (see \figname~\ref{fig:spec2}).
+visible in the spectra of both stars (\figname~\ref{fig:spec2}).
 The measured absolute abundances for \bizarreone\ and \sunanalog\ are
@@
 If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
-than the other, this may imprint a strong \Tcondens\-dependent
+than the other, this may imprint a strong \Tcondens-dependent
 abundance differences like those observed in \bizarreone-\sunanalog.
@@
 have propagated inward through planet-planet scattering, making inner rocky planets
-to be accreted\cite{Malmberg:2011aa}.
+to be accreted\cite{Zakamska:2004aa,Malmberg:2011aa}.
 If this is the case, there may be surviving highly eccentric giant planets that are
@@
 
-%TODO: plot styles...
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{orbits.pdf}
-  \end{center}
-  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
-    Sun (grey).
-    For \sunanalog, the initial conditions are set to the median of the
-    posterior samples over the phase-space coordinates.
-    The orbits are computed by integrating backwards from the present-day
-    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
-    integration scheme implemented in \project{Gala} (\citealt{gala}).
-    Right panel: distribution of maximum $z$-heights for orbits computed from
-    all posterior samples.
-  }
-  \label{fig:orbit}
-\end{figure}
-
 \begin{figure}[htpb]
@@
 
+\clearpage
+
 \section{Supplementary Information}
@@
 \subsection{Proximity in phase-space coordinates}
+\label{supp:dxdv}
 
@@
 \subsection{Stellar Ages and Coevality}
+
+%TODO: plot styles...
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{orbits.pdf}
+  \end{center}
+  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
+    Sun (grey).
+    For \sunanalog, the initial conditions are set to the median of the
+    posterior samples over the phase-space coordinates.
+    The orbits are computed by integrating backwards from the present-day
+    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
+    integration scheme implemented in \project{Gala} (\citealt{gala}).
+    Right panel: distribution of maximum $z$-heights for orbits computed from
+    all posterior samples.
+  }
+  \label{fig:orbit}
+\end{figure}
 

### 2017-06-23 paper/ms.tex
altering citations

@@
   \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
-  \caption{Abundance difference in this pair and other twin-like
-    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
-    \citealt{2016ApJS..225...32B}.
+  \caption{Abundance difference in this pair (blue circles) and other twin-like
+    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries\cite{2016ApJS..225...32B}
+    (black circles).
     The differences in other pairs are small ($<0.05$~dex)
@@
     Additionally, we show the distribution of abundance differences
-    between field stars with similar metallicity difference
+    between field stars in the same catalog\cite{2016ApJS..225...32B}
+    with similar metallicity difference
     ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
     as violins with medians indicated by black line segments.
-    These are random pairings of single stars in
-    in \citealt{2016ApJS..225...32B} at two metallicity bins,
+    These are random pairings of single stars in from two metallicity bins,
     $-0.025 < \feh < 0.025$ (160 stars) and $0.175 > \feh > 0.225$ (137 stars),
@@
   \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
-  \caption{Abundance differences of the \bizarreone-\sunanalog\ pair
+  \caption{Comparison to other pairs that show abundance differences.
+    %TODO
+    Abundance differences of the \bizarreone-\sunanalog\ pair
     ranked by the condensation temperature of elements for solar composition gas

### 2017-06-25 paper/ms.tex
whitespace edits by my editor - sorry
summary edits

@@
 {\bf \noindent
-  Stars that are born together are expected to have same chemical compositions
-  initially.
+  Stars that are born together are expected to have the same chemical
+  compositions initially.
   Detailed chemical abundance studies of stars in wide binaries indeed reveal
-  little to no differences in most cases\citep{Gratton:2001aa,Desidera:2004aa}.
-  However, formation and evolution of different planetary systems around each
-  star in a wide binary may eventually lead to a difference in chemical
+  little to no abundance differences in most
+  cases\citep{Gratton:2001aa,Desidera:2004aa}.
+  However, the formation and evolution of different planetary systems around
+  each star in a wide binary may eventually lead to differences in the chemical
   abundances of the component stars' radiative and convective
@@
   chemical signature may be more easily detectable as abundance differences,
-  free from dependence on stellar parameters or confusion with Galactic chemical
-  evolution.
+  free from dependences on stellar parameters or confusion with Galactic
+  chemical evolution.
   A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
@@
   \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
-    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
-  However, a convincing example is yet to be found.
+    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa},
+  however, a conclusive example of planetary accretion has not yet been found.
   %
-  Here we report a comoving pair of bright sun-like stars, HD~240430 and HD~240429,
-  hereafter ``\bizarreone'' and ``\sunanalog'',
-  with a significant difference ($\approx 0.2$~dex) in their chemical
-  abundances that strongly suggests massive accretion of rocky planetary system in one
-  of the stars within the last billion years.
+  Here we report the discovery of a comoving pair of bright, sun-like
+  stars---HD~240430 and HD~240429, hereafter ``\bizarreone'' and
+  ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
+  chemical abundances that strongly suggests accretion of a massive rocky
+  planetary system in one of the stars within the last billion years.
   The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
-  elements by $\approx 0.2$~dex but not as large
-  an enhancement of (moderately) volatile elements.
-  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr
-  inferred from their stellar parameters.
-  We suggest that the star \bizarreone, recently accreted
-  $\approx 15$~\mearth\ of rocky material selectively enhancing the
+  elements by $\approx 0.2$~dex and a small enhancement ($\lesssim 0.11$~dex) of
+  (moderately) volatile elements.
+  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr,
+  as inferred from their stellar parameters.
+  We suggest that the star \bizarreone recently accreted
+  $\approx 15$~\mearth\ of rocky material, selectively enhancing the
   refractory elements in its surface and convective envelope.
@@
   This pair of stars provides evidence that dynamical accretion of rocky planets
-  happen during the lifetime of sun like stars.
+  does happen during the lifetime of sun-like stars.
 }

### 2017-06-25 paper/ms.tex
main text

@@
     \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
-    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
-    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
+    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet much less in
+    \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
     \label{fig:abundances}
@@
   isochrones\cite{2013ApJ...776...87S}.
-\item [c] Absolute abundances from Myles \etal, in prep.
+\item [c] Absolute abundances from Myles \etal (in prep.).
 %\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
@@
 The pair has also been previously recognized as a visual double star system
-in Washington Double Star catalog\cite{2001AJ....122.3466M}.
-The two stars have spectral types G0 and G2 both similar to the Sun (G2).
-In a separate effort to study detailed chemical abundances of potential
+in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
+The two stars have spectral types G0 and G2, both similar to the Sun (G2).
+In a separate effort to study the detailed chemical abundances of potential
 planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
 high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
-both stars were obtained using the HIRES spectrograph on the Keck-I
-telescope\cite{2016ApJS..225...32B}.
-The wavelength coverage is $5164$--$7799$~\AA.
+both stars for the wavelength range $5164$--$7799$~\AA were obtained using the
+HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
 The resulting measurements include elemental abundances for 15 chemical species
@@
 The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
-and the 3D separation is $\approx 0.6$~pc.
+and the maximum-likelihood 3D separation is $\approx 0.6$~pc.
 Although selected based only on their astrometry, the two stars
@@
 neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
-\sunanalog\ are likely a bound wide binary system that formed coevally.
+\sunanalog\ are likely a coeval, bound wide-binary system.
 
@@
 and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
-We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, \elemH{Si}
-in order interpolate the age, mass, and radius of each star
-in a grid of Yale-Yonsei model isochrones\cite{2013ApJ...776...87S}.
+We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, and
+\elemH{Si} in order to interpolate the age, mass, and radius of each star
+using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
 The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
 $4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
-consistent with them being coeval (see Figure~\ref{fig:yyisofitting}).
+consistent with them being coeval (see \figname~\ref{fig:yyisofitting}).
 
@@
 and \elem{Mn} relative to \elem{Fe} and other refractory elements.
-As expected from their measured metallicity difference, the ratio of data and
-model between the two stars show significant residuals of almost all metal line
-features, largely dominated by \elem{Fe}.
-However, for lines of elements that are not as enhanced in \bizarreone\, the
-residuals are much smaller in amplitude demonstrating the validity of the
-measured abundance differences (Figure~\ref{fig:spec1} and \ref{fig:spec2}).
+As expected from their measured metallicity difference, the ratio of spectral
+data and model between the two stars show significant residuals of almost all
+metal line features, largely dominated by \elem{Fe}.
+However, for absorption lines of elements that are not as enhanced in
+\bizarreone\, the residuals are much smaller in amplitude demonstrating the
+validity of the measured abundance differences (\figname~\ref{fig:spec1} and
+\ref{fig:spec2}).
 
@@
 unexpected.
-None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) wide
-binary pairs examined using spectra of similar quality and the same
+None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K), wide-binary pairs examined using spectra of similar quality and the same
 consistent measurement pipeline shows discrepancies in abundances between the
-stars at this level\cite{2016ApJS..225...32B} (Figure~\ref{fig:deltaXH}).
+stars at this level\cite{2016ApJS..225...32B} (\figname~\ref{fig:deltaXH}).
 The maximum metallicity difference observed in the other pairs is $\Delta\feh =
@@
 differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
-In fact, the abundance pattern of \bizarreone\ is a very unlikely one
+In fact, the abundance pattern of \bizarreone\ is very unusual
 for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
@@
 implying that a scenario involving Galactic chemical evolution is not plausible
-even if we ignore a coeval star, \sunanalog, that we can compare with.
+even if we ignore the coeval comparison star, \sunanalog.
 The difference of $\approx 0.2$~dex is also the largest among a handful of wide
@@
   Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
-(Figure~\ref{fig:relabun_tcrank}).
+(\figname~\ref{fig:relabun_tcrank}).
 
@@
 mixing induced by convection or rotation, which brings the lithium into the
-interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
+interior ($T>2.5 \times 10^{6}$~K) where it is destroyed by proton capture
 burning. %TODO: REFERENCE?
@@
 The measured absolute abundances for \bizarreone\ and \sunanalog\ are
-$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep),
+$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep.),
 resulting in the largest abundance difference ($\approx 0.5$~dex) seen
@@
 
-The abundance differences show a strong increasing trend with condensation
-temperature ($T_C$) of elements.
-In Figure~\ref{fig:deltaxh_tcrank},
+Sorting the abundance differences by condensation temperature ($T_C$) of the
+elements shows a clear increasing trend.
+In \figname~\ref{fig:deltaxh_tcrank},
 we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
@@
 The five under-enhanced elements in \bizarreone\
-relative to \sunanalog\ are the five most volatile in all elements measured.
-The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
-\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
+relative to \sunanalog\ are the five most volatile of all elements measured.
+The differences in \elem{Mn} ($\Tcondens = 1158$~K) and
+\elem{Cr} ($\Tcondens = 1296$~K) suggest a break in $\Tcondens \approx 1200$~K.
 
@@
 In a multi-planet system, dynamical instabilities triggered by planet-planet
-scattering\cite{} or encounters with a field star\cite{Malmberg:2011aa} can
+scattering\cite{TODO} or encounters with a field star\cite{Malmberg:2011aa} can
 lead to planet ejection or accretion.
@@
 
-We estimate that accretion of $\approx 15$~\mearth\ of rocky planets
+We estimate that the accretion of $\approx 15$~\mearth\ of rocky planets
 in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
@@
 Because the anchor star, \sunanalog,
-is very close in its properties (\teff, \logg, \feh, age) to the Sun,
+is very similar to the Sun in its stellar properties (\teff, \logg, \feh, age),
 we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
 pre-accretion state of \bizarreone.
-In Figure~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
-$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth
-composition\cite{2003TrGeo...2..547M} assuming that 2\% of the Sun's mass
-is in its convective zone\cite{Pinsonneault:2001aa}.
-A volatility trend that more volatile (low \Tcondens) elements are more
-depleted in the Earth relative to CI or other carbonaceous chondrites
-has long been known\cite{mcdonough2001composition}.
+In \figname~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
+$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth composition
+material\cite{2003TrGeo...2..547M} assuming that 2\% of the star's mass is in
+its convective zone\cite{Pinsonneault:2001aa}.
+It has long been known that more volatile (low \Tcondens) elements are more
+depleted in the Earth relative to CI or other carbonaceous
+chondrites\cite{mcdonough2001composition} that are thought to reflect the
+elemental composition of the pre-solar nebula. \todo{Check end of last sentence}
 This trend is presumed to be closely related to the formation of terrestrial
@@
 surface \elem{Li} abundance in \bizarreone.
-Because \elem{Li} is strongly depleted in old sun-like stars yet
+Because \elem{Li} is strongly depleted in old sun-like stars, yet
 present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
 late-time accretion of rocky planetary material will significantly
-replenish the lithium on the star's surface.
+replenish the lithium in the star's surface.
 For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
 material would result in $\Delta\elemH{Li} \approx 1.6$~dex
-(see inset of Figure~\ref{fig:deltaxh_tcrank}).
+(see inset of \figname~\ref{fig:deltaxh_tcrank}).
 Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
@@
 Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
-to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
-enhancement in its \elem{Li}.
+to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with a $1.6$~dex
+enhancement in \elem{Li} abundance.
 This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
-$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep)
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
 approximately $1.65$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
@@
 
-What about \sunanalog?
-Considering its age of $4.00_{-1.56}^{+1.51}$~Gyr, \sunanalog\ is also enhanced
-in \elem{Li} compared to other stars of similar ages by $\approx 1$~dex.
+\sunanalog\ is also enhanced in \elem{Li} compared to other stars of similar
+ages by $\approx 1$~dex, considering its age of $4.00_{-1.56}^{+1.51}$~Gyr.
 This enhancement puts an upper limit on the accreted mass to be
-$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
-\cite{mcdonough2001composition}.
+$\approx 4$~\mearth\ assuming a \elem{Li} concentration of $1.1$~ppm
+\cite{mcdonough2001composition}, as above.
 Unlike \bizarreone, we cannot know the pre-accretion abundances of
@@
   large, it is reasonable to consider accretion by the Sun.
-  In reality, \sunanalog\ may as well have had its own accretion history,
+  In reality, \sunanalog\ may also have had its own accretion history,
   which indeed seems to be the case according to its \elem{Li} abundance.
@@
 0.05$~dex.
-This is comparable to the abundance difference between N, Na and Fe in
+This is comparable to the abundance difference between N, Na, and Fe in
 \sunanalog.
@@
 Thus, we conclude that \sunanalog\ is also likely to have had a similar
-accretion event, but the amount of accretion was at least 5 time
+accretion event, but the amount of accretion was at least 5 times
 smaller than \bizarreone.
@@
 What triggered the planet engulfment in the two comoving stars
-within the last Gyr remains unclear.
-A possibility is that a fly-by interaction with a field star could have
+within the last $\sim 1$~Gyr remains unclear.
+One possibility is that a fly-by interaction with a field star could have
 triggered eccentricity excitation of outer planets around each star, which may
-have propagated inward through planet-planet scattering, making inner rocky planets
-to be accreted\cite{Zakamska:2004aa,Malmberg:2011aa}.
-If this is the case, there may be surviving highly eccentric giant planets that are
-potentially detectable with future data releases of \gaia.
+have propagated inward through planet-planet scattering, leading to the accretion of inner rocky planets\cite{Zakamska:2004aa,Malmberg:2011aa}.
+If this is the case, there may be surviving, highly-eccentric giant planets.
 The two stars have not been included in any publicly released data from planet
-search programs.
+search programs, however, outer eccentric planets are potentially detectable with future data releases of the \gaia\ mission.
 If both stars have accreted planetary material, it would be very interesting to
@@
     Elements are ordered by their $T_C$ on $x$-axis, same as
-    Figure~\ref{fig:deltaxh_tcrank}.
+    \figname~\ref{fig:deltaxh_tcrank}.
     The solid and dashed lines assume $f_\mathrm{CZ}=0.02$ and $f_\mathrm{CZ} =
@@
 expected changes in $\Delta\elemH{X}$ for $f_\mathrm{CZ}=0.03$ in
-Figure~\ref{fig:vari}.
+\figname~\ref{fig:vari}.
 

### 2017-06-25 paper/ms.tex
supplement

@@
     The feature in the third column of the second row is a strong \elem{Li}
-    line that was studied in Myles \etal, in prep.
+    line that was studied separately in Myles \etal (in prep.).
     Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
@@
     ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
-    as violins with medians indicated by black line segments.
-    These are random pairings of single stars in from two metallicity bins,
+    as violins (shaded regions) with medians indicated by black line segments.
+    These are random pairings of single stars from two metallicity bins,
     $-0.025 < \feh < 0.025$ (160 stars) and $0.175 > \feh > 0.225$ (137 stars),
@@
 \end{equation} where $\mat{C}$ is the covariance matrix, and $\mathcal{N}$ is
-normal (Gaussian) distribution.
-We adopt a uniform space density prior for the distance and an isotropic
+normal (Gaussian) distribution (see also appendices of
+\citealt{2017AJ....153..257O}).
+We adopt a uniform space-density prior for the distance and an isotropic
 Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$:
@@
 512 steps as the burn-in period.
-For each sample, we convert the heliocentric phase-space coordinates into
+For each sample, we convert the Heliocentric phase-space coordinates into
 Galactocentric coordinates assuming that the Sun's position and velocity are
@@
 The differences in positions and velocities are consistent with zero.
-\todo{should we instead show $|\Delta\boldsymbol{x}|$ and
-$|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
+% \todo{should we instead show $|\Delta\boldsymbol{x}|$ and
+% $|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
 
@@
 circumstellar disks (\todo{needs refernces}).
-We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
-and found no evidence for indications of activity in their spectral energy
-distributions.
+We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
+found no evidence for indications of activity or infrared excess in their
+spectral energy distributions.
 The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
@@
 old main sequence stars, and that their unusually high \elem{Li} abundance
-requires an alternative explanation.
+requires an alternative explanation; our favored explanation being the accretion
+of rocky, Lithium-rich material.
 
@@
 Assuming that the two stars were born together, one alternative possibility to
-explain the chemical difference between the two stars is that there was
+explain the chemical differences between the two stars is that there was
 chemical inhomogeneity within the birth cloud.
@@
 
-We estimate how much mass of rocky material is needed to explain an increment
-of $\approx 0.2$~dex in refractory elements observed in \bizarreone\ relative
-to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
+Here we estimate how much added rocky material is needed to explain an
+increment of $\approx 0.2$~dex in refractory elements observed in \bizarreone\
+relative to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
 Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
@@
 $\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
-we may approximate the pre-accretion abundances of \bizarreone\ with the Sun.
+we may approximate the pre-accretion abundances of \bizarreone\ as being
+equivalent to the sun.
 We carry out simple toy calculations of expected $\Delta\elemH{X}$
-in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
-under these simplifying assumptions:
+in a Sun-like star's atmosphere by adding a certain mass of bulk Earth
+composition under these simplifying assumptions:
 \begin{itemize}
@@
 \end{equation}
-where $m_X$ is the mass of each element in e.g., atomic mass unit.
+where $m_X$ is the mass of each element in, e.g., atomic mass unit.
 Assuming that the added material has a total mass $M_\mathrm{add}$, and the
-mass fraction in each element $f_{X,\mathrm{add}}$,
+mass fraction in each element is $f_{X,\mathrm{add}}$,
 the abundance difference is

### 2017-06-26 paper/ms.tex
minor tweaks (mostly latex quirks)

@@
   ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
-  chemical abundances that strongly suggests accretion of a massive rocky
+  chemical abundances that strongly suggest accretion of a massive rocky
   planetary system in one of the stars within the last billion years.
@@
   as inferred from their stellar parameters.
-  We suggest that the star \bizarreone recently accreted
+  We suggest that the star \bizarreone\ recently accreted
   $\approx 15$~\mearth\ of rocky material, selectively enhancing the
@@
   isochrones\cite{2013ApJ...776...87S}.
-\item [c] Absolute abundances from Myles \etal (in prep.).
+\item [c] Absolute abundances from Myles \etal\ (in prep.).
 %\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
@@
 high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
-both stars for the wavelength range $5164$--$7799$~\AA were obtained using the
+both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
 HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
@@
 unexpected.
-None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K), wide-binary pairs examined using spectra of similar quality and the same
+None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K)
+wide-binary pairs examined using spectra of similar quality and the same
 consistent measurement pipeline shows discrepancies in abundances between the
@@
 chondrites\cite{mcdonough2001composition} that are thought to reflect the
-elemental composition of the pre-solar nebula. \todo{Check end of last sentence}
+elemental composition of the proto-solar nebula. \todo{Check end of last sentence}
 This trend is presumed to be closely related to the formation of terrestrial
@@
 triggered eccentricity excitation of outer planets around each star, which may
-have propagated inward through planet-planet scattering, leading to the accretion of inner rocky planets\cite{Zakamska:2004aa,Malmberg:2011aa}.
+have propagated inward through planet-planet scattering,
+leading to the accretion of inner rocky planets\cite{Zakamska:2004aa,Malmberg:2011aa}.
 If this is the case, there may be surviving, highly-eccentric giant planets.
 The two stars have not been included in any publicly released data from planet
-search programs, however, outer eccentric planets are potentially detectable with future data releases of the \gaia\ mission.
+search programs, however, outer eccentric planets are potentially detectable
+with future data releases of the \gaia\ mission.
 If both stars have accreted planetary material, it would be very interesting to
@@
     The feature in the third column of the second row is a strong \elem{Li}
-    line that was studied separately in Myles \etal (in prep.).
+    line that was studied separately in Myles \etal\ (in prep.).
     Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced

### 2017-06-26 paper/ms.tex
some tweaks including title

@@
 \vspace{-2cm}
-  Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs
+  Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars
   \vspace{-0.5cm}
@@
 parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
-(section~Table~\ref{tab:t1}).
+(Table~\ref{tab:t1}).
 
@@
 However, one of the stars, \bizarreone, is significantly more metal rich than
-the other by 0.2~dex in \feh\ ($\approx 60\%$; \figname~\ref{fig:abundances}).
+the other by 0.2~dex in \feh\ ($\approx 60\%$ in number density;
+\figname~\ref{fig:abundances}).
 Moreover, not all elements are equally enhanced: the abundances of \bizarreone\

### 2017-06-26 paper/ms.tex
show only one f_CZ

@@
     \figname~\ref{fig:deltaxh_tcrank}.
-    The solid and dashed lines assume $f_\mathrm{CZ}=0.02$ and $f_\mathrm{CZ} =
-    0.03$ respectively.
-    For each $f_\mathrm{CZ}$, we show expected $\Delta\elemH{X}$
+    We assume $f_\mathrm{CZ} = 0.02$ and show expected $\Delta\elemH{X}$
     for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
@@
 data.
-While we adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, we show the
-expected changes in $\Delta\elemH{X}$ for $f_\mathrm{CZ}=0.03$ in
-\figname~\ref{fig:vari}.
+We adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, and show
+expected changes for the accretion of $5-25$~\mearth\ of bulk Earth material
+in \figname~\ref{fig:vari}.
+However, we note that if $f_\mathrm{CZ}$ is $0.03$, the estimate for the accreted
+mass would be $\approx 20$~\mearth.
 

### 2017-06-26 notebooks/specplot.py
Revise spectra plots
- Make y tick at 1 visible in ratio plots.
- Separate lithium line.
- Make wavelength ranges compatible in all subpanels.

@@ -27,17 +27,17 @@ import re
 # Speed of light for calculating offsets in wavelengths due to RV shifts
 cLight = 299792.458 # km/s
 
-# These are the "Tableau 20" colors as RGB.  
-tableau20 = [(31, 119, 180), (174, 199, 232), (255, 127, 14), (255, 187, 120),  
-             (44, 160, 44), (152, 223, 138), (214, 39, 40), (255, 152, 150),  
-             (148, 103, 189), (197, 176, 213), (140, 86, 75), (196, 156, 148),  
-             (227, 119, 194), (247, 182, 210), (127, 127, 127), (199, 199, 199),  
-             (188, 189, 34), (219, 219, 141), (23, 190, 207), (158, 218, 229)]  
-  
-# Scale the RGB values to the [0, 1] range, which is the format matplotlib accepts.  
-for i in range(len(tableau20)):  
-    r, g, b = tableau20[i]  
-    tableau20[i] = (r / 255., g / 255., b / 255.)  
+# These are the "Tableau 20" colors as RGB.
+tableau20 = [(31, 119, 180), (174, 199, 232), (255, 127, 14), (255, 187, 120),
+             (44, 160, 44), (152, 223, 138), (214, 39, 40), (255, 152, 150),
+             (148, 103, 189), (197, 176, 213), (140, 86, 75), (196, 156, 148),
+             (227, 119, 194), (247, 182, 210), (127, 127, 127), (199, 199, 199),
+             (188, 189, 34), (219, 219, 141), (23, 190, 207), (158, 218, 229)]
+
+# Scale the RGB values to the [0, 1] range, which is the format matplotlib accepts.
+for i in range(len(tableau20)):
+    r, g, b = tableau20[i]
+    tableau20[i] = (r / 255., g / 255., b / 255.)
 
 def getColor(i):
     return tableau20[i % len(tableau20)]
@@ -56,7 +56,7 @@ def lineColor(elem):
         cIdx = coloredElems.index(elem)
     else:
         return getColor(14) # dark grey
-        
+
     lineColors = [
         {'elem': 'Mg', 'color': getColor(0)}, # dark blue
         {'elem': 'Fe', 'color': getColor(6)}, # dark red
@@ -83,22 +83,22 @@ class SpecPlot(object):
     def getGoodSegs(self, elem ):
         # return counts of # lines of elem in each segment
         spec = self.spec
-        
+
         # Grab the line information
         lines = spec.atomic[0]
         lineWaves = lines[:,2]
[…]

### 2017-06-26 paper/ms.tex
Add separated lithium line figure

@@
 \bizarreone\, the residuals are much smaller in amplitude demonstrating the
-validity of the measured abundance differences (\figname~\ref{fig:spec1} and
-\ref{fig:spec2}).
+validity of the measured abundance differences (\figname~\ref{fig:spec1},
+\ref{fig:spec2} and \ref{fig:spec_lithium}).
 
@@
 detectable at this age even for high signal-to-noise spectra, is clearly
-visible in the spectra of both stars (\figname~\ref{fig:spec2}).
+visible in the spectra of both stars (\figname~\ref{fig:spec_lithium}).
 The measured absolute abundances for \bizarreone\ and \sunanalog\ are
@@
     We mark elements that give rise to strong absorption lines.
-    The feature in the third column of the second row is a strong \elem{Li}
-    line that was studied separately in Myles \etal\ (in prep.).
     Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
@@
   \label{fig:spec2}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.6\linewidth]{spec_lithium.pdf}
+  \caption{Lithium lines in the spectra of \bizarreone\ and \sunanalog.
+    This line is studied in Myles \etal\ (in prep.).
+    Line legends are the same as in \figname~\ref{fig:spec1}.
+  }
+  \label{fig:spec_lithium}
 \end{figure}

### 2017-06-26 paper/ms.tex
all numbers to be consistent with f_CZ=0.02

@@
 Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
-to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with a $1.6$~dex
+to be ordinary, the accretion of $15$~\mearth\ by \bizarreone\ is consistent with a $1.65$~dex
 enhancement in \elem{Li} abundance.
@@
 $A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
-approximately $1.65$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
+approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
 Furthermore, this implies that the accretion event should have happened

### 2017-06-27 paper/ms.tex
Add lithium remark and refs

@@
 % coevality based on stellar parameters
-% TODO reference supplement discussion on age here?
 Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
@@
 In a multi-planet system, dynamical instabilities triggered by planet-planet
-scattering\cite{TODO} or encounters with a field star\cite{Malmberg:2011aa} can
-lead to planet ejection or accretion.
+scattering\cite{1996Sci...274..954R,1996Natur.384..619W} or encounters with a
+field star\cite{Malmberg:2011aa} can lead to planet ejection or accretion.
 If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
@@
 recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
+Finally, while the current analysis of \elem{Li} line assumed a solar ratio of
+$^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that higher resolution
+spectrum of the star will reveal a significant $^{6}\elem{Li}$ which are
+normally destroyed early in solar-type stars, but present in rocky
+planets\cite{Israelian:2001}.
 
@@
 \section{Acknowledgements}
+We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
 We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
-for feedback.
+for their valuable feedback.
 The Flatiron Institute is supported by the Simons Foundation.

### 2017-06-27 paper/ms.tex
Add sed figure and other tweaks

@@
 
-\newcommand{\todo}[1]{{TODO: #1}}
+\newcommand{\todo}[1]{{\color{red}TODO: #1}}
 
@@
 \sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
-in our recent search for comoving stars using the proper motions and parallaxes
-from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
-component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
-(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
+in our recent search\cite{2017AJ....153..257O} for comoving stars using the
+proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
+catalog (hereafter \tgas), a component of the first data release of the
+astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
+measurements are listed in \tablename~\ref{tab:t1}).
 The pair has also been previously recognized as a visual double star system
@@
 chondrites\cite{mcdonough2001composition} that are thought to reflect the
-elemental composition of the proto-solar nebula. \todo{Check end of last sentence}
+elemental composition of the proto-solar nebula.
 This trend is presumed to be closely related to the formation of terrestrial
@@
 participating in the {\it Gaia} Multilateral Agreement.
+% 2MASS
+This publication makes use of data products from the Two Micron All Sky Survey,
+which is a joint project of the University of Massachusetts and the Infrared
+Processing and Analysis Center/California Institute of Technology, funded by
+the National Aeronautics and Space Administration and the National Science
+Foundation.
+% all-WISE
+This publication makes use of data products from the Wide-field Infrared Survey
+Explorer, which is a joint project of the University of California, Los
+Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
+funded by the National Aeronautics and Space Administration.
 % software
@@
     %TODO
-    Abundance differences of the \bizarreone-\sunanalog\ pair
-    ranked by the condensation temperature of elements for solar composition gas
-    from \citet{2003ApJ...591.1220L}.
+    Abundance differences of the \bizarreone-\sunanalog\ pair ranked by the
+    condensation temperature of elements for solar composition
+    gas\cite{2003ApJ...591.1220L}.
     The condensation temperature may be read from the gray line and right y-axis.
     We show three wide binary systems selected from the literature:
-    HD~20782/1 (\citet{Mack:2014aa}, $\feh\approx0$),
-    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$)),
+    HD~20782/1\cite{Mack:2014aa} ($\feh\approx0$),
+    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$),
     and WASP-94AB\cite{Teske:2016aa} ($\feh\approx0.3$).
@@
 \end{equation} where $\mat{C}$ is the covariance matrix, and $\mathcal{N}$ is
-normal (Gaussian) distribution (see also appendices of
-\citealt{2017AJ....153..257O}).
+normal (Gaussian) distribution\cite{2017AJ....153..257O}.
 We adopt a uniform space-density prior for the distance and an isotropic
@@
 
-%TODO: plot styles...
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=0.65\linewidth]{sed.pdf}
+  \end{center}
+  \caption{Spectral energy distributions of \bizarreone\ and \sunanalog.
+    We compiled the photometric measurements from
+    \project{Tycho-2}\cite{2000A&A...355L..27H},
+    \project{2MASS}\cite{2006AJ....131.1163S}, and
+    \project{WISE}\cite{2010AJ....140.1868W}.
+  }
+  \label{fig:sed}
+\end{figure}
+
 \begin{figure}[htbp]
@@
   \end{center}
-  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
+  \caption{Left panel: Galactic orbits computed for \sunanalog\ (blue) and the
     Sun (grey).
-    For \sunanalog, the initial conditions are set to the median of the
+    For \sunanalog, the initial condition is set to the median of the
     posterior samples over the phase-space coordinates.
@@
     positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
-    integration scheme implemented in \project{Gala} (\citealt{gala}).
-    Right panel: distribution of maximum $z$-heights for orbits computed from
-    all posterior samples.
+    integration scheme implemented in \project{Gala}\cite{gala}.
+    Right panel: Distribution of maximum $z$-heights for orbits computed from
+    all posterior samples for \sunanalog.
   }
@@
 
+We provide a more detailed discussion of stellar ages and coevality of
+\bizarreone-\sunanalog\ pair, especially on whether the stars may be
+very young ($\lesssim 1$~Gyr).
 The surface lithium abundance in a sun-like star decreases with its age due to
@@
 burning.
-Thus, surface lithium abundance is an indicator of stellar ages.
+Thus, surface lithium abundance can be an indicator of stellar ages.
 The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
@@
 they are expected to be part of a larger comoving group of stars.
-However, as we mention above, there is no evidence in our search of comoving pairs
-using \tgas\ that the two stars belong to a larger group of young stars.
+However, there is no evidence in our search\cite{2017AJ....153..257O} of
+comoving pairs using \tgas\ that the two stars belong to a larger group of
+young stars.
 Very young stars often show signs of activity such as
@@
 found no evidence for indications of activity or infrared excess in their
-spectral energy distributions.
+spectral energy distributions (\figname~\ref{fig:sed}).
 The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
@@
 posterior sample over the phase space coordinates of \sunanalog, in a Milky
-Way-like gravitational potential (similar to \texttt{MWPotential2014} from
-\cite{Bovy:2015}) using \project{Gala} (\cite{gala}).
+Way-like gravitational potential\cite{Bovy:2015} using \project{Gala}\cite{gala}.
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age (\todo{needs references for vertical action as age indicator}).
+an older age (\figname~\ref{fig:orbit}).
+%TODO:APW needs references for vertical action as age indicator
 We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
@@
 requires an alternative explanation; our favored explanation being the accretion
-of rocky, Lithium-rich material.
+of rocky material that has locked lithium.
 
 \subsection{Alternative Scenarios}
+
+\subsubsection{Exchange Scattering}
+\label{sub:exchange_scattering}
+
+Although the data described above strongly suggests that the two stars are
+coeval, we may still consider scenarios in which the two stars are not actually
+born together.
+Two stars unrelated at birth may end up in a binary system via a binary-single
+scattering event that results in an exchange of binary members.
+In order to estimate the rate at which any binary-single
+event will produce a wide binary system such as \sunanalog\ and \bizarreone,
+we may consider the rate at which this wide binary will scatter with a field star to
+result in an exchange reaction.
+The cross-section of exchange scattering for a binary with semi-major axis $a$ is
+\cite{Hut:1983ab,Hut:1983aa}
+\begin{eqnarray}
+  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
+  \label{eq:crosssection}
+\end{eqnarray}
+where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
+defined as
+\begin{eqnarray}
+  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
+\end{eqnarray}
+\eqname~\ref{eq:crosssection} is appropriate when $v_i/v_c \gg 1$,
+which is the case for wide binaries
+scattering with field (disk) stars.
+If we assume that field stars are made of solar mass stars with a constant
+number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
+$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
+any direction, the rate of exchange scattering is
+\begin{eqnarray}
+  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
+  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
+  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
+\end{eqnarray}
+which is low enough to be negligible.
+
+In fact, any exchange scattering scenario is unsatisfactory as typical
+field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
+unlikely to show the abundance difference pattern observed.
+In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
+\bizarreone-\sunanalog\ with the distribution of abundance differences,
+$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
+\feh\ as \bizarreone\ and \sunanalog.
+We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
+all other elements are typically enhanced at a similar level, with some variations.
+Specifically, for a typical star with $\feh \approx 0.2$~dex, we generally
+expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
+\cite{Battistini:2015aa,Bensby:2003aa}, making the low
+[\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
+unlikely to arise from variations in Galactic chemical evolution.
 
@@
 
-Here we estimate how much added rocky material is needed to explain an
+We estimate how much added rocky material is needed to explain an
 increment of $\approx 0.2$~dex in refractory elements observed in \bizarreone\

### 2017-06-27 paper/ms.tex
minor tweaks

@@
   This pair of stars provides evidence that dynamical accretion of rocky planets
-  does happen during the lifetime of sun-like stars.
+  does happen during the main-sequence lifetime of sun-like stars.
 }
@@
 have identical radial velocities within uncertainties,
-confirming that they are truly comoving (\ref{supp:dxdv}).
+confirming that they are truly comoving (\sectionname~\ref{supp:dxdv}).
 As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
@@
 $4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
-consistent with them being coeval (see \figname~\ref{fig:yyisofitting}).
+consistent with them being coeval (\figname~\ref{fig:yyisofitting}).
 
@@
 % novelty
-The observed difference in metallicity and abundances are genuinely rare and
+The observed difference in metallicity and abundances is genuinely rare and
 unexpected.
@@
 wide-binary pairs examined using spectra of similar quality and the same
-consistent measurement pipeline shows discrepancies in abundances between the
+consistent measurement procedure shows discrepancies in abundances between the
 stars at this level\cite{2016ApJS..225...32B} (\figname~\ref{fig:deltaXH}).
@@
 
-Sorting the abundance differences by condensation temperature ($T_C$) of the
+Sorting the abundance differences by $50$\% condensation temperature ($T_C$) of the
 elements shows a clear increasing trend.
@@
 Finally, while the current analysis of \elem{Li} line assumed a solar ratio of
-$^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that higher resolution
+$^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that a higher resolution
 spectrum of the star will reveal a significant $^{6}\elem{Li}$ which are

### 2017-06-27 paper/coverletter.tex
Add coverletter

%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
%Version for spanish users, by dgarhdez

\documentclass[12pt,letter,roman]{moderncv}

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{green}
% to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}
% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Semyeong}{Oh}
\title{Resumé title}
\address{4 Ivy Ln}{Princeton, NJ 08540}{United States}
\email{semyeong@astro.princeton.edu}

\begin{document}

% recipient data
\recipient{Dr. Leslie Sage}{968 National Press Building\\529 14th Street NW\\Washington DC 20045-1938\\United States}
\date{\today}
\opening{Dear Dr. Sage,}
\closing{Best regards,}
\makelettertitle

We submit the enclosed document for consideration for a Nature Letter.
The paper lays out a simple and clear account for evidences in stellar
chemical abundances that massive rocky accretion happened in one of the two
stars that are comoving in space, and possibly also in the other one albeit in
smaller amount.
We think the result is one of the most convincing examples that shows a
catastrophic ending possible to planets around sun-like stars, and thus will be
interesting to scientists in other disciplines as well as those in astronomy or
exoplanet field.

The document has been formatted with \LaTeX\ article class.
The summary is 286 words long, and the main text has $\approx 1424$ words,
29 references,
and two single-panel figures and one table, which should fit the page limit
of a Nature Letter.
We also include six extended data figure that will help the interested readers
get the full context, as well as supplementary material discussing several
aspects of the main text.

\vspace{0.5cm}

\makeletterclosing

\end{document}

### 2017-06-27 paper/ms.tex
Fix wrong label reference
Edits to supplement (DNS)

@@
 \subsection{Stellar Ages and Coevality}
+\label{sub:age_coevality}
 
@@
     all posterior samples for \sunanalog.
+    The large $z$-height is consistent with an old ($\sim 4$~Gyr) age
+    (\sectionname~\ref{sub:age_coevality}).
   }
@@
 We provide a more detailed discussion of stellar ages and coevality of
-\bizarreone-\sunanalog\ pair, especially on whether the stars may be
-very young ($\lesssim 1$~Gyr).
+\bizarreone-\sunanalog\ pair, aside from the isochrone fitting,
+especially on whether the stars may be very young ($\lesssim 1$~Gyr).
 The surface lithium abundance in a sun-like star decreases with its age due to
@@
 abundance means a younger age or something else.
-For example, the presence of $\elem{Li}$-rich red giant stars has been
+For example, the presence of $\elem{Li}$-rich red giant stars was
 attributed to the engulfment of substellar companions such as gas giant planets
@@
 
-In fact, the surface lithium abundance is the only indication that points to
-younger ages.
-If the two stars are indeed only several hundred Myrs old at most,
-they are expected to be part of a larger comoving group of stars.
+The surface lithium abundance is the only indicator of a
+younger age.
+If the two stars were only several hundred Myrs old, then they would likely
+have been part of a larger comoving group of stars.
 However, there is no evidence in our search\cite{2017AJ....153..257O} of
-comoving pairs using \tgas\ that the two stars belong to a larger group of
+comoving pairs using \tgas\ that these stars belong to a larger group of
 young stars.
@@
 spectral energy distributions (\figname~\ref{fig:sed}).
-The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
+The low $v\sin(i)$ values (\tablename~\ref{tab:t1}) also argue against very
 young ages that would be inferred from the surface lithium abundances.
@@
 
-Although the data described above strongly suggests that the two stars are
-coeval, we may still consider scenarios in which the two stars are not actually
-born together.
+While the data described above strongly suggests that the two stars are
+coeval, this subsection explores the possibility that this is not a primordial
+binary.
 Two stars unrelated at birth may end up in a binary system via a binary-single
@@
 number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
-$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
-any direction, the rate of exchange scattering is
+$10$~\kms, the rate of exchange scattering is
 \begin{eqnarray}
@@
 which is low enough to be negligible.
+This is a conservative estimate as the relative velocity of
+disk stars exceeds $10$~\kms.
 
-In fact, any exchange scattering scenario is unsatisfactory as typical
-field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
-unlikely to show the abundance difference pattern observed.
-In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
+An exchange scattering scenario is unlikely to be able to explain the observed
+abundance difference pattern.
+We test this by comparing the observed abundance difference of
 \bizarreone-\sunanalog\ with the distribution of abundance differences,
-$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
-\feh\ as \bizarreone\ and \sunanalog.
+$\Delta[\elem{X}/\elem{H}]$, between pairs of two stars randomly drawn
+from two metallicity (\feh) bins similar to \bizarreone\ and \sunanalog\
+(\figname~\ref{fig:deltaXH}).
 We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
@@
 
-Assuming that the two stars were born together, one alternative possibility to
-explain the chemical differences between the two stars is that there was
-chemical inhomogeneity within the birth cloud.
-However, there is already ample evidence against such a scenario.
-First, none of the other seven similar wide binaries examined
+In this subsection, we explore the hypothesis that the chemical inhomogeneity
+within the birth cloud is the source of the \bizarreone-\sunanalog\ abundance
+anomalies.
+There is ample evidence against this scenario.
+None of the other seven similar wide binaries examined
 with the same measurement pipeline\cite{2016ApJS..225...32B}

### 2017-06-27 paper/coverletter.tex
no the?

@@
 of a Nature Letter.
-We also include six extended data figure that will help the interested readers
+We also include six extended data figure that will help interested readers
 get the full context, as well as supplementary material discussing several
-aspects of the main text.
+aspects of the main text in more detail.
 

### 2017-06-28 paper/ms.tex
ack
vertical action refs. fixes #10

@@
 We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
-We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
-for their valuable feedback.
+We thank Megan Bedell and Andy Casey for valuable discussions,
+and Keith Hawkins, Nathan Leigh, and Josh Winn for comments
+on early version of the draft.
 The Flatiron Institute is supported by the Simons Foundation.
@@
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age (\figname~\ref{fig:orbit}).
-%TODO:APW needs references for vertical action as age indicator
+an older age (\citealt{Wielen:1977,Aumer:2016}); see \figname~\ref{fig:orbit}.
 We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr

### 2017-06-29 paper/ms.tex
The accretion need not be recent (JMB)

@@
   as inferred from their stellar parameters.
-  We suggest that the star \bizarreone\ recently accreted
+  We suggest that the star \bizarreone\ accreted
   $\approx 15$~\mearth\ of rocky material, selectively enhancing the
@@
 approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
-Furthermore, this implies that the accretion event should have happened
-recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
-Finally, while the current analysis of \elem{Li} line assumed a solar ratio of
+While the current analysis of \elem{Li} line assumed a solar ratio of
 $^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that a higher resolution

### 2017-06-29 paper/coverletter.tex
Point to figure

@@
 \moderncvcolor{green}
-% to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
-%\renewcommand{\familydefault}{\sfdefault}
-% uncomment to suppress automatic page numbering for CVs longer than one page
-%\nopagenumbers{}
 
@@
 \name{Semyeong}{Oh}
-\title{Resumé title}
 \address{4 Ivy Ln}{Princeton, NJ 08540}{United States}
@@
 % recipient data
-\recipient{Dr. Leslie Sage}{968 National Press Building\\529 14th Street NW\\Washington DC 20045-1938\\United States}
+\recipient{Dr. Leslie Sage}{
+  968 National Press Building\\
+  529 14th Street NW\\
+  Washington DC 20045-1938\\
+  United States}
 \date{\today}
@@
 
-We submit the enclosed document for consideration for a Nature Letter.
+We submit the enclosed paper for consideration for a Nature Letter.
 The paper lays out a simple and clear account for evidences in stellar
@@
 stars that are comoving in space, and possibly also in the other one albeit in
-smaller amount.
+smaller amount. Figure~2 demonstrates this key result where we compare
+the abundance difference between the two stars with the change
+expected from accretion of bulk Earth by a sun-like star.
 We think the result is one of the most convincing examples that shows a

### 2017-06-29 paper/ms.tex
Remove leftover recent accretion statement
Add uncertainties and definitions

@@
 \usepackage{setspace}
-\onehalfspacing
+\doublespacing
+\usepackage{lineno}
+\linenumbers
 \usepackage{microtype}  % ALWAYS!
@@
 $\log{g}$               &                & 4.43                   & 4.33                   & 0.028         \\
-$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    &               \\
+$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    & 0.5           \\
 $[\elem{Fe}/\elem{H}]$  &                & 0.01                   & 0.20                   & 0.010         \\
@@
 \hline
-$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 &               \\
+$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 & 0.05          \\
 $\elemH{C}$             &                & $0.00$                 & $0.09$                 & 0.026         \\
@@
 (Table~\ref{tab:t1}).
+The abundances are noted as \elemH{X}, defined as the log ratio of number
+density of element \elem{X} to \elem{H} relative to the solar value
+($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
+Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
+For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
+\log_{10} (n_\elem{Li}/n_\elem{H})$.
 
@@
 and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
-We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, and
+We then combine the luminosities with effective temperature, \elemH{Fe}, and
 \elemH{Si} in order to interpolate the age, mass, and radius of each star
@@
 
-What triggered the planet engulfment in the two comoving stars
-within the last $\sim 1$~Gyr remains unclear.
+What triggered the planet engulfment in the two comoving stars remains unclear.
 One possibility is that a fly-by interaction with a field star could have

### 2017-06-29 paper/coverletter.tex
APW edit

@@
 
-We submit the enclosed paper for consideration for a Nature Letter.
-The paper lays out a simple and clear account for evidences in stellar
-chemical abundances that massive rocky accretion happened in one of the two
-stars that are comoving in space, and possibly also in the other one albeit in
-smaller amount. Figure~2 demonstrates this key result where we compare
-the abundance difference between the two stars with the change
-expected from accretion of bulk Earth by a sun-like star.
-We think the result is one of the most convincing examples that shows a
-catastrophic ending possible to planets around sun-like stars, and thus will be
+The enclosed paper presents clear evidence of massive accretion of rocky,
+planetary material in the differential stellar chemical abundances of one star
+in a comoving pair of sun-like stars. The other star in the pair also appears
+to have accreted rocky material albeit in smaller amount. Figure~2 demonstrates
+this key result: we show the abundance differences between the two stars
+along with the change expected from accretion of bulk Earth material by a
+sun-like star. We think that this result is the most convincing example of a
+catastrophic end to planetary systems around sun-like stars, and thus will be
 interesting to scientists in other disciplines as well as those in astronomy or
-exoplanet field.
+the exoplanets sub-field. We therefore submit the enclosed paper for
+consideration for a Nature Letter.
 
-The document has been formatted with \LaTeX\ article class.
+The document has been formatted with the \LaTeX\ article class.
 The summary is 286 words long, and the main text has $\approx 1424$ words,
@@
 of a Nature Letter.
-We also include six extended data figure that will help interested readers
+We also include six extended data figures that will help interested readers
 get the full context, as well as supplementary material discussing several

### 2017-06-29 paper/ms.tex
Fix cite; minor tweaks

@@
 % ----------
-% - Fit summary in the first page.
+% - Add items here.
 
@@
 X-ray emission from magnetic activity, emission lines, or infrared excess due to
-circumstellar disks (\todo{needs refernces}).
+circumstellar disks.
 We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
@@
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age (\citealt{Wielen:1977,Aumer:2016}); see \figname~\ref{fig:orbit}.
+an older age\cite{Wielen:1977,Aumer:2016} (\figname~\ref{fig:orbit}).
 We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
@@
 $800$ to $1700$~ppm\cite{1998psc..book.....L,mcdonough2001composition,2003TrGeo...2..547M}
-largely due to uncertainties in the composition of the Earth's core.
+largely due to uncertainties in how much \elem{Mn} is in the Earth's core.
 Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}

### 2017-06-29 paper/ms.tex
Use right values for figures and text

@@
 $\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
-(-11.1,\,244,\,7.25)~\kms$\cite{Schonrich:2010, Schonrich:2012}.
+(11.1,\,244,\,7.25)~\kms$\cite{Schonrich:2010, Schonrich:2012}.
 

### 2017-06-29 paper/ms.tex
Put in numbers

@@
 Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
-and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx XX$,
-$\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
+and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx 100$~K,
+$\Delta\logg \approx 0$, and $\Delta\feh \approx 0$),
 we may approximate the pre-accretion abundances of \bizarreone\ as being

### 2017-06-29 paper/ms.tex
Tweak figure and caption

@@
   \caption{Comparison to other pairs that show abundance differences.
-    %TODO
-    Abundance differences of the \bizarreone-\sunanalog\ pair ranked by the
-    condensation temperature of elements for solar composition
-    gas\cite{2003ApJ...591.1220L}.
+    All astronomical metals are ordered by their \Tcondens\ for solar
+    composition gas\cite{2003ApJ...591.1220L} on the $x$-axis, same as \figname~\ref{fig:deltaxh_tcrank}.
     The condensation temperature may be read from the gray line and right y-axis.
@@
     Locations of elements with at least one measurement from any study
-    are indicated by a vertical line and its symbol.
+    are indicated by vertical lines and their symbols.
     Note that often multiple values are reported for one element corresponding

### 2017-06-29 paper/ms.tex
Add JMB affiliation

@@
   Adrian M. Price-Whelan$^{1}$,\,
-  John M. Brewer$^{2}$,\,\\
-  David W. Hogg$^{3,4,5,6}$,\,
-  David N. Spergel$^{1,3}$,\,
+  John M. Brewer$^{2,3}$,\,\\
+  David W. Hogg$^{4,5,6,7}$,\,
+  David N. Spergel$^{1,4}$,\,
   Justin Myles$^{2}$
@@
   $^2$Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA \\
-  $^3$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA \\
-  $^4$Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA \\
-  $^5$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA \\
-  $^6$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
+  $^3$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA \\
+  $^4$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA \\
+  $^5$Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA \\
+  $^6$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA \\
+  $^7$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
   $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}

### 2017-06-29 paper/ms.tex
Move table in order to respect reference order
Reformat end notes

@@
 
+% general description of the pair and measurements
+\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
+in our recent search\cite{2017AJ....153..257O} for comoving stars using the
+proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
+catalog (hereafter \tgas), a component of the first data release of the
+astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
+measurements are listed in \tablename~\ref{tab:t1}).
+The pair has also been previously recognized as a visual double star system
+in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
+The two stars have spectral types G0 and G2, both similar to the Sun (G2).
+In a separate effort to study the detailed chemical abundances of potential
+planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
+high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
+both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
+HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
+The resulting measurements include elemental abundances for 15 chemical species
+(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
+parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
+(Table~\ref{tab:t1}).
+The abundances are noted as \elemH{X}, defined as the log ratio of number
+density of element \elem{X} to \elem{H} relative to the solar value
+($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
+Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
+For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
+\log_{10} (n_\elem{Li}/n_\elem{H})$.
+
 \begin{table*}[htpb]
@@
 \end{table*}
-
-% general description of the pair and measurements
-\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
-in our recent search\cite{2017AJ....153..257O} for comoving stars using the
-proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
-catalog (hereafter \tgas), a component of the first data release of the
-astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
-measurements are listed in \tablename~\ref{tab:t1}).
-The pair has also been previously recognized as a visual double star system
-in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
-The two stars have spectral types G0 and G2, both similar to the Sun (G2).
-In a separate effort to study the detailed chemical abundances of potential
-planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
-high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
-both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
-HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
-The resulting measurements include elemental abundances for 15 chemical species
-(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
-parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
-(Table~\ref{tab:t1}).
-The abundances are noted as \elemH{X}, defined as the log ratio of number
-density of element \elem{X} to \elem{H} relative to the solar value
-($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
-Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
-For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
-\log_{10} (n_\elem{Li}/n_\elem{H})$.
 
@@
 
-\section{Acknowledgements}
+\section{End notes}
+
+\begin{itemize}
+  \item {\bf Acknowledgements}
     We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
@@
     funded by the National Aeronautics and Space Administration.
-% software
-%\software{
-%  %The data and code used in this project is available from
-%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
-%  %software license.
-%  This research utilized:
-%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
-%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
-%  \texttt{IPython} (\citealt{Perez:2007}),
-%  \texttt{matplotlib} (\citealt{Hunter:2007}),
-%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
-%  and \texttt{pandas} (\citealt{pandas}).}
+    % Software
+    This research utilized:
+    \texttt{Astropy}\cite{Astropy-Collaboration:2013},
+    \texttt{emcee}\cite{2013PASP..125..306F},
+    \texttt{IPython}\cite{Perez:2007},
+    \texttt{matplotlib}\cite{Hunter:2007},
+    \texttt{numpy}\cite{Van-der-Walt:2011},
+    and \texttt{pandas}\cite{pandas}.
+
+  \item {\bf Author Contributions} All authors contributed to the work presented in this paper.
+
+  \item {\bf Author Information}
+    Reprints and permissions information is available at \url{www.nature.com/reprints}.
+    The authors declare no competing financial interests.
+    Correspondence and requests for materials should be addressed to
+    \texttt{semyeong@astro.princeton.edu}.
+\end{itemize}
 

### 2017-06-29 paper/ms.tex
Add verbose Tc definition

@@
 Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
-For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
+For lithium, we also use the absolute abundance defined as $A(\elem{Li}) = 12 +
 \log_{10} (n_\elem{Li}/n_\elem{H})$.
@@
 Sorting the abundance differences by $50$\% condensation temperature ($T_C$) of the
-elements shows a clear increasing trend.
+elements, defined as the temperature at which $50$\% of the element in mass
+is condensed into solid forms, shows a clear increasing trend.
 In \figname~\ref{fig:deltaxh_tcrank},

### 2017-06-29 paper/coverletter.tex
Tweak counts

@@
 The document has been formatted with the \LaTeX\ article class.
-The summary is 286 words long, and the main text has $\approx 1424$ words,
-29 references,
-and two single-panel figures and one table, which should fit the page limit
-of a Nature Letter.
+The summary is 286 words long, and the main text has $\approx 1467$ words, 29
+references, two single-panel figures and one table, which should fit the page
+limit of a Nature Letter.
 We also include six extended data figures that will help interested readers

### 2017-08-03 paper/ms.tex
Fix spectral types
back

--- 2017-06-29 paper/ms.tex
@@
-\documentclass[12pt,letterpaper,margin=1in]{article}
+\documentclass[modern, letterpaper]{aastex61}
 % \documentclass[twocolumn]{aastex61}
@@
 % packages
-\usepackage[letterpaper,margin=1in]{geometry}
-
-\usepackage{setspace}
-\doublespacing
-\usepackage{lineno}
-\linenumbers
+\definecolor{cbblue}{HTML}{3182bd}
 \usepackage{microtype}  % ALWAYS!
-\usepackage{amsmath,amssymb}
-\usepackage[sort&compress,super]{natbib}
-\usepackage{graphicx}
+\usepackage{amsmath,amssymb,natbib}
+\usepackage[flushleft]{threeparttable}
+\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
 \graphicspath{{figures/}}
-\usepackage{aas_macros}
-\usepackage{hyperref}
-\hypersetup{backref,breaklinks,colorlinks,citecolor=blue}
-\usepackage{mathptmx}
-\usepackage{threeparttable}
-
-% per section figure counting
-\usepackage{chngcntr}
-\counterwithin{figure}{section}
-
-%\setcitestyle{super}
-\citestyle{nature}
-\bibliographystyle{naturemag}
+\bibliographystyle{aasjournal}
 
@@
 
-\newcommand{\todo}[1]{{\color{red}TODO: #1}}
+\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
 
@@
 
-% Titles:
-% - 90 characters (including spaces)
-% - do not normally include numbers, acronyms, abbreviations or punctuation
-% - They should include sufficient detail for indexing purposes but be general
-%   enough for readers outside the field to appreciate what the paper is about.
+\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me
+
 \title{
-\vspace{-2cm}
-  Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars
-  \vspace{-0.5cm}
+  Kronos \& Krios:
+  Evidence for accretion of a massive, rocky planetary system
+  in a comoving pair of G dwarfs
 }
 
-\author{
-  Semyeong Oh$^{1,*}$,\,
-  Adrian M. Price-Whelan$^{1}$,\,
-  John M. Brewer$^{2,3}$,\,\\
-  David W. Hogg$^{4,5,6,7}$,\,
-  David N. Spergel$^{1,4}$,\,
-  Justin Myles$^{2}$
-}
-\date{\small\today}
-
-\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me
-\maketitle
-
-% affiliations
-\vspace{-1cm}
-{\small\noindent
-  $^1$Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA \\
-  $^2$Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA \\
-  $^3$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA \\
-  $^4$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA \\
-  $^5$Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA \\
-  $^6$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA \\
-  $^7$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
-  $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}
-}
-
-%% \author{Keith A. Hawkins}
-%% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}
-
-%% \author{Nathan W. C. Leigh}
-%% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
-
-% ------------------------
-% nature summary paragraph
-% ------------------------
-% - a fully referenced paragraph, ideally of about 200 words, but certainly no
-%   more than 300 words, aimed at readers in other disciplines.
-% - This paragraph starts with a 2-3 sentence basic introduction to the field;
-%   followed by a one-sentence statement of the main conclusions starting 'Here
-%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
-%   findings into general context so it is clear how the results described in
-%   the paper have moved the field forwards.
-% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
-% ------------------------
-\section{Summary}
-{\bf \noindent
-  Stars that are born together are expected to have the same chemical
-  compositions initially.
-  Detailed chemical abundance studies of stars in wide binaries indeed reveal
-  little to no abundance differences in most
-  cases\citep{Gratton:2001aa,Desidera:2004aa}.
-  However, the formation and evolution of different planetary systems around
-  each star in a wide binary may eventually lead to differences in the chemical
-  abundances of the component stars' radiative and convective
-  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
-  Wide binary systems of two twin-like stars are particularly useful since such
-  chemical signature may be more easily detectable as abundance differences,
-  free from dependences on stellar parameters or confusion with Galactic
-  chemical evolution.
-  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
-  in their surface chemical abundances have been reported so far
-  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
-    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa},
-  however, a conclusive example of planetary accretion has not yet been found.
-  %
-  Here we report the discovery of a comoving pair of bright, sun-like
-  stars---HD~240430 and HD~240429, hereafter ``\bizarreone'' and
-  ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
-  chemical abundances that strongly suggest accretion of a massive rocky
-  planetary system in one of the stars within the last billion years.
-  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
-  elements by $\approx 0.2$~dex and a small enhancement ($\lesssim 0.11$~dex) of
-  (moderately) volatile elements.
-  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr,
-  as inferred from their stellar parameters.
-  We suggest that the star \bizarreone\ accreted
-  $\approx 15$~\mearth\ of rocky material, selectively enhancing the
+\author[0000-0001-7790-5308]{Semyeong Oh}
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
+  Princeton, NJ 08544, USA}
+\affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}
+
+\author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
+  Princeton, NJ 08544, USA}
+
+\author[0000-0002-9873-1471]{John M. Brewer}
+\affil{Department of Astronomy, Yale University, 260 Whitney Ave,
+  New Haven, CT 06511, USA}
+
+\author[0000-0003-2866-9403]{David W. Hogg}
+\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
+  New York, NY 10010, USA}
+\affil{Center for Cosmology and Particle Physics,
+  Department of Physics, New York University, 726 Broadway,
+  New York, NY 10003, USA}
+\affil{Center for Data Science, New York University, 60 Fifth Ave,
+  New York, NY 10011, USA}
+\affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg}
+
+\author{David N. Spergel} % TODO: need ORCID
+\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
+  Princeton, NJ 08544, USA}
+\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
+  New York, NY 10010, USA}
+
+% \author{Keith A. Hawkins}
+% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}
+
+% \author{Nathan W. C. Leigh}
+% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
+
+\author{Justin Myles} % TODO: need ORCID
+\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
+
+\begin{abstract}
+  We report and discuss the discovery of a comoving pair of bright G
+  stars, HD~240430 and HD~240429, with a significant difference in their
+  chemical abundances.
+  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
+  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
+  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
+  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
+  high-resolution radial velocity measurements.
+  Stellar parameters determined from high-resolution Keck HIRES spectra
+  indicate that both stars are $\sim 4$~Gyr old,
+  yet both stars show very high surface \elem{Li} abundance for this age.
+  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
+  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
+  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
+  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
+  This is the largest and the most significant chemical difference found in
+  a wide binary pair yet.
+  The proximity in phase-space and ages between the two stars suggests that
+  they formed together with the same composition, at odds with the observed
+  differences in metallicity and abundance patterns.
+  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
+  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
   refractory elements in its surface and convective envelope.
-  The other star, \sunanalog, may also have had a similar accretion
+  The other star HD~240429, ``Krios'', may also have had a similar accretion
   event given its high surface \elem{Li} abundance but of much smaller amount
   ($\approx 4$~\mearth).
-  This pair of stars provides evidence that dynamical accretion of rocky planets
-  does happen during the main-sequence lifetime of sun-like stars.
+  %Follow-ups to study the existence and properties of the planetary systems
+  %around these stars will help illuminate planet-star interactions.
+\end{abstract}
+
+\keywords{
+  binaries: visual
+  ---
+  planet-star interactions
+  ---
+  stars: abundances
+  ---
+  stars: formation
+  ---
+  stars: individual (HD~240430, HD~240429)
+  ---
+  stars: solar-type
 }
 
-\section{Main Text}
+\section{Introduction} % (fold)
+\label{sec:introduction}
+
+Wide binary stars are valuable tools for studying star and planet formation as well
+as Galactic dynamics and chemical evolution.
+In the context of studying the evolution of the Milky Way, they are useful for
+two main reasons.
+First, because wide binaries are weakly bound systems that may be tidally
+disrupted by, e.g., field stars, molecular clouds, or the Galactic tidal field,
+their statistics can be informative of the Galactic mass distribution.
+For example, the separation distribution of halo binaries has been used to
+constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
+On the other hand, they are also prime targets to test the chemical tagging
+hypothesis that stars from the same birthplace may be traced back using detailed
+chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
+A multiple-star system of any size that we believe are born together can serve
+this purpose, with massive open clusters at one extreme.
+Wide binaries are at the other extreme in that we may be less confident of the
+coevality of individual systems but they are much more abundant than larger
+systems like open clusters, rendering their statistics a meaningful indication
+of whether the hypothesis works.
+
+Wide binaries with similar or very different planetary architectures around the
+component stars have been used to connect a host star's chemistry to its
+planetary system.
+A differential analysis may reveal chemical signatures related to planet
+formation or accretion without any regard to Galactic chemical evolution as
+long as the two stars are assumed to be born together with identical
+composition.
+For close-in giant planets, it has been established that the planet-metallicity
+relation is primordial, and that the enhanced metallicity in giant
+planet-hosting stars likely promotes the formation of giant planets by
+increasing the availability of small particle condensates that form
+planetesimals (\citealt{Fischer:2005aa}).
+On the other hand, if host stars are polluted after their birth by rocky
+planetary material with high refractory-to-volatile ratio, the convective
+envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
+compared to their initial state.
+Thus, differences in planet formation or accretion in two otherwise identical
+stars may imprint differences in chemical abundances that depend on the
+condensation temperature (\Tcondens).
+
+Several systems in which at least one star hosts at least one planet
+have been studied so far with high resolution spectroscopy in this context
+(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
+  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
+The results and interpretations of these studies are varied:
+while some systems appear to have undetectable differences
+(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
+studies have reported a \Tcondens-dependent difference in abundance
+with higher-\Tcondens\ elements showing larger differences.
+The increasing abundance difference with condensation temperature has been
+attributed both to more yet-undiscovered rocky planets around the relatively
+refractory-poor star and to late time accretion of refractory-rich planetary
+material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
+The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
+and often at $\approx 0.05$~dex level making them challenging to detect even
+with a careful analysis of high-resolution high signal-to-noise ratio spectra.
+% maybe want to point out the former interpretation roots back to melendez+09
+% and some doubt to that interpretation...
+
+So far the strongest evidence for accretion of planetary material by a host
+star comes from spectral analysis of polluted white dwarfs (WDs).
+Because the gravitational settling times of elements heavier than \elem{He} in
+atmosphere is much shorter than the WD cooling time, detection of metals likely
+indicates the presence of a reservoir of dusty material around the WD.
+Indeed, many of the polluted WDs host a dusty debris disk detected
+in the infrared.
+Some of the most dramatically polluted WDs show
+surface abundances closely matched by rocky planetary material
+with, e.g., bulk Earth composition, strongly arguing
+that the disk formed from tidally disrupted minor planets
+(\citealt{Zuckerman:2007aa,Klein:2010aa}).
+Recently, transit signals from small bodies orbiting around a polluted WD
+have been detected by \project{Kepler} adding further support to the picture
+(\citealt{2015Natur.526..546V}).
+
+Here, we report and discuss the discovery of a comoving pair of G stars,
+HD~240430 and HD~240429, with unusual chemical abundance differences
+that strongly suggest accretion of planetary material by the two stars.
+Throughout the \documentname, we nickname the two stars \bizarreone\
+(HD~240430) and \sunanalog\ (HD~240429).
+We use the following convention for chemical abundances of stars: \elemH{X} is
+the log ratio of number density of element \elem{X} to \elem{H} relative to the
+solar value.
+The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
+(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
+\elem{X}.
+In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
+about the two stars relevant to the present discussion.
+In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
+the abundance difference between the pair.
+We summarize our discussions in \sectionname~\ref{sec:summary}.
+
+\subsection{Review of Detailed Chemical Abundance Studies of Wide Binary Stars}
+\label{sub:review}
+
+Anticipating the forthcoming discussion, we review and summarize a handful of
+wide binary systems that have been studied in
+their detailed chemical abundances so far with high-resolution spectroscopy.
+These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
+WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
+We focus on key characteristics of stars and planets, and interpretations of
+any trend in $\Delta\elemH{X}$ with \Tcondens.
+(\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added})
+
+{\bf HD~20782/HD~20781:}
+Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
+$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
+host close-in giant planets.
+HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
+orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
+Neptune-mass planets within 0.3~AU with moderately high eccentricity
+($e\sim0.1-0.3$).\footnote{
+  The two stars were monitored by \project{HARPS} campaign, and it has recently
+  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
+  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
+  within $\approx 0.35$~AU.}
+The measured abundances of 15 elements in the two stars are consistent
+(\citealt{Mack:2014aa}).
+However, \citealt{Mack:2014aa} argued that there is a moderately significant
+($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
+increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
+Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
+the abundances of each star {\it individually}.
+They suggest that this slope is evidence that the stars accreted
+$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
+migration.
+
+{\bf HAT-P-1:}
+A pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
+different planetary systems:
+the secondary star is known to host one transiting giant planet
+while no planet has been discovered around the primary star.
+The two stars are identical
+in metallicities and abundances for 23 elements measured with
+the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
+Thus it seems that the presence of close-in giant planet does not necessarily
+lead to atmospheric pollution of its host star.
+
+{\bf HD~80606/HD~80607:}
+Similar to HAT-P-1, no significant chemical difference is found between two
+common proper motion G5 stars with super-solar metallicity ($\feh \approx
+0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
+HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).
+
+{\bf XO-2N/XO-2S:}
+A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
+has received much attention due to possibly the most robust and significant
+difference between the component stars.
+XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
+masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
+0.15$) orbits at $<0.5$~AU.
+%TODO: check following with Biazzo+
+All measured elements including \elem{Fe} are enhanced in XO-2N relative to
+XO-2S, and the difference shows a significant correlation with \Tcondens\
+(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
+\citealt{Teske:2013aa}).
+At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
+difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
+
+\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
+in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
+giant planets around XO-2S, following a similar interpretation of
+\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
+In this scenario, forming planets in the protoplanetary disk are supposed to
+``lock'' heavier elements to the core of gas giant planets as well as some
+volatile elements in their envelopes. Then, the host star will accrete {\it
+  gas} depleted in metals compared to their protostellar condition.
+By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
+of gas occurs in terms of how much mass is in the convective envelope of the
+host star, they can match the mass difference of gas giant planets around each
+star, which is at least $1~\mjupiter$.
+On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
+\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
+Earth and CM chondrite-like material can explain the trend either as refractory
+{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
+refractory enhancement in XO-2N by late time accretion in which case the
+opposite would be true.
+
+{\bf WASP-94A/WASP-94B:}
+Each star in a pair of F8 and F9 stars with super-solar metallicity
+($\feh\approx 0.3$) hosts a hot Jupiter.
+The planet around WASP-94A is transiting with a misaligned, probably retrograde
+circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
+massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
+WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
+elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
+elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
+uncertainty of $0.006$~dex among all elements
+resulting in a statistically significant non-zero slope between
+$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
+  %TODO: double check the following statement
+  Note that the condensation
+  temperature $\Tcondens$ used is for solar system composition
+  gas, which can differ from that of higher metallicity gas.}
+Multiple possibilities related to the formation and evolution
+of planetary systems around each star as well as causes unrelated to planets
+such as dust cleansing during the fully convective phase or different rotation
+and granulation between the stars were considered, but none was favored.
+
+\section{Data}
+\label{sec:data}
+
+\input{kk.tex}
+
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
+  \end{center}
+  \caption{%
+    Differences in posterior samples over Galactocentric phase-space coordinates
+    for the two stars \sunanalog\ and \bizarreone.
+    \label{fig:dxdv}}
+\end{figure}
 
@@
   \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the comoving pair,
-    \bizarreone\ (red circles) and \sunanalog\ (blue squares).
+  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
+    normalized to \elem{H} (top) and \elem{Fe} (bottom).
     Lines are drawn for each star only to guide the eye.
@@
     \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
-    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet much less in
-    \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
+    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
+    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
+  }
   \label{fig:abundances}
-  }
-\end{figure}
-
-\begin{table*}[htpb]
-  \centering
-  \begin{threeparttable}
-  \caption{Astrometric and spectroscopic measurements of the pair\label{tab:t1}}
-\begin{tabular}{ccccc}
-\hline\hline
-                        &                & \sunanalog\            & \bizarreone\           &               \\
-Name                    & Units          & HD 240429              & HD 249439              & Uncertainties \\
-\hline
-Sp Type                 &                & G2                     & G0                     &               \\
-R.A.\tnote{a}           & hh:mm:ss       & 23:51:55.21            & 23:52:09.42            &               \\
-Dec.\tnote{a}           & dd:mm:ss       & 59:42:48.16            & 59:42:26.08            &               \\
-2MASS $J$\tnote{a}      & mag            & $8.593 \pm 0.023$      & $8.415 \pm 0.026$      &               \\
-$T_\mathrm{eff}$        & K              & 5878                   & 5803                   & 25            \\
-$\log{g}$               &                & 4.43                   & 4.33                   & 0.028         \\
-$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    & 0.5           \\
-$[\elem{Fe}/\elem{H}]$  &                & 0.01                   & 0.20                   & 0.010         \\
-Age\tnote{b}            & Gyr            & $4.00_{-1.56}^{+1.51}$ & $4.28_{-1.03}^{+1.11}$ &               \\
-$v_r$                   & \kms\          & $-21.2$                & $-21.2$                & 0.2           \\
-$\varpi$\tnote{a}       & mas            & $9.35 \pm 0.24$        & $9.41 \pm 0.25$        &               \\
-$\mu_\alpha^*$\tnote{a} & mas\,yr$^{-1}$ & $89.25 \pm 0.66$       & $89.41 \pm 0.69$       &               \\
-$\mu_\delta$\tnote{a}   & mas\,yr$^{-1}$ & $-29.68 \pm 0.54$      & $-30.12 \pm 0.52$      &               \\
-\hline
-\multicolumn{5}{c}{$T_c < 1200$~K} \\
-\hline
-$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 & 0.05          \\
-$\elemH{C}$             &                & $0.00$                 & $0.09$                 & 0.026         \\
-$\elemH{N}$             &                & $-0.06$                & $-0.01$                & 0.042         \\
-$\elemH{O}$             &                & $0.01$                 & $0.09$                 & 0.036         \\
-$\elemH{Na}$            &                & $-0.06$                & $-0.04$                & 0.014         \\
-$\elemH{Mn}$            &                & $-0.03$                & $0.00$                 & 0.020         \\
-\hline
-\multicolumn{5}{c}{$T_c > 1200$~K} \\
-\hline
-$\elemH{Mg}$            &                & $0.01$                 & $0.19$                 & 0.012         \\
-$\elemH{Al}$            &                & $0.01$                 & $0.21$                 & 0.028         \\
-$\elemH{Si}$            &                & $0.00$                 & $0.16$                 & 0.008         \\
-$\elemH{Ca}$            &                & $0.02$                 & $0.23$                 & 0.014         \\
-$\elemH{Ti}$            &                & $0.02$                 & $0.20$                 & 0.012         \\
-$\elemH{V}$             &                & $0.02$                 & $0.20$                 & 0.034         \\
-$\elemH{Cr}$            &                & $0.01$                 & $0.17$                 & 0.014         \\
-$\elemH{Fe}$            &                & $0.01$                 & $0.20$                 & 0.010         \\
-$\elemH{Ni}$            &                & $-0.01$                & $0.21$                 & 0.014         \\
-$\elemH{Y}$             &                & $0.04$                 & $0.26$                 & 0.030         \\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item [a] From \tgas.
-\item [b] Derived in this work by isochrone fitting using the Yale-Yonsei model
-  isochrones\cite{2013ApJ...776...87S}.
-\item [c] Absolute abundances from Myles \etal\ (in prep.).
-%\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
-\end{tablenotes}
-\end{threeparttable}
-\end{table*}
-
-% general description of the pair and measurements
-\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
-in our recent search\cite{2017AJ....153..257O} for comoving stars using the
-proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
-catalog (hereafter \tgas), a component of the first data release of the
-astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
-measurements are listed in \tablename~\ref{tab:t1}).
-The pair has also been previously recognized as a visual double star system
-in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
-The two stars have spectral types G0 and G2, both similar to the Sun (G2).
-In a separate effort to study the detailed chemical abundances of potential
-planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
-high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
-both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
-HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
-The resulting measurements include elemental abundances for 15 chemical species
-(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
-parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
-(Table~\ref{tab:t1}).
-The abundances are noted as \elemH{X}, defined as the log ratio of number
-density of element \elem{X} to \elem{H} relative to the solar value
-($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
-Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
-For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
-\log_{10} (n_\elem{Li}/n_\elem{H})$.
-
-% likely origin given its proximity in phase space
-The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
-and the maximum-likelihood 3D separation is $\approx 0.6$~pc.
-Although selected based only on their astrometry, the two stars
-have identical radial velocities within uncertainties,
-confirming that they are truly comoving (\sectionname~\ref{supp:dxdv}).
-As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
-neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
-\sunanalog\ are likely a coeval, bound wide-binary system.
-
-% coevality based on stellar parameters
-Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
-We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
-and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
-We then combine the luminosities with effective temperature, \elemH{Fe}, and
-\elemH{Si} in order to interpolate the age, mass, and radius of each star
-using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
-The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
-$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
-consistent with them being coeval (\figname~\ref{fig:yyisofitting}).
-
-% metallicity and abundance difference
-However, one of the stars, \bizarreone, is significantly more metal rich than
-the other by 0.2~dex in \feh\ ($\approx 60\%$ in number density;
-\figname~\ref{fig:abundances}).
-Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
-show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
-and \elem{Mn} relative to \elem{Fe} and other refractory elements.
-As expected from their measured metallicity difference, the ratio of spectral
-data and model between the two stars show significant residuals of almost all
-metal line features, largely dominated by \elem{Fe}.
-However, for absorption lines of elements that are not as enhanced in
-\bizarreone\, the residuals are much smaller in amplitude demonstrating the
-validity of the measured abundance differences (\figname~\ref{fig:spec1},
-\ref{fig:spec2} and \ref{fig:spec_lithium}).
-
-% novelty
-The observed difference in metallicity and abundances is genuinely rare and
-unexpected.
-None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K)
-wide-binary pairs examined using spectra of similar quality and the same
-consistent measurement procedure shows discrepancies in abundances between the
-stars at this level\cite{2016ApJS..225...32B} (\figname~\ref{fig:deltaXH}).
-The maximum metallicity difference observed in the other pairs is $\Delta\feh =
-0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
-This is consistent with similar studies of metallicity and abundance
-differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
-In fact, the abundance pattern of \bizarreone\ is very unusual
-for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
-($\feh\approx 0$; \figname~\ref{fig:deltaXH}),
-implying that a scenario involving Galactic chemical evolution is not plausible
-even if we ignore the coeval comparison star, \sunanalog.
-The difference of $\approx 0.2$~dex is also the largest among a handful of wide
-binaries that do show metallicity and abundance differences with varying
-significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
-  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
-(\figname~\ref{fig:relabun_tcrank}).
-
-% high Li
-Both stars have high surface \elem{Li} abundances considering
-their ages of $\sim 4$~Gyr.
-The surface lithium abundance in a sun-like star decreases with its age due to
-mixing induced by convection or rotation, which brings the lithium into the
-interior ($T>2.5 \times 10^{6}$~K) where it is destroyed by proton capture
-burning. %TODO: REFERENCE?
-The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
-detectable at this age even for high signal-to-noise spectra, is clearly
-visible in the spectra of both stars (\figname~\ref{fig:spec_lithium}).
-The measured absolute abundances for \bizarreone\ and \sunanalog\ are
-$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep.),
-resulting in the largest abundance difference ($\approx 0.5$~dex) seen
-among all measured elements.
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
-  \caption{
-    Comparing the observed abundance difference (blue circles) to the expected
-    change in solar surface abundance after adding $15$~\mearth\ of material
-    with bulk Earth composition\cite{2003TrGeo...2..547M} (black open and
-    filled circles).
-    The assumed mass fraction in the convective zone is $0.02$.
-    All astronomical metals are ordered by their \Tcondens\ for solar
-    composition gas on the $x$-axis.
-    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
-    in filled circles, while those without a measurement are left open.
-    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
-    suggests that the abundance difference may be due to accretion of
-    $15$~\mearth\ of rocky planetary material.
-    The element \elem{Li} is off the plot and indicated in the inset.
-  }
-  \label{fig:deltaxh_tcrank}
-\end{figure}
-
-Sorting the abundance differences by $50$\% condensation temperature ($T_C$) of the
-elements shows a clear increasing trend.
-In \figname~\ref{fig:deltaxh_tcrank},
-we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
-by each element's equilibrium \Tcondens\ in solar system composition
-gas\cite{2003ApJ...591.1220L}.
-The five under-enhanced elements in \bizarreone\
-relative to \sunanalog\ are the five most volatile of all elements measured.
-The differences in \elem{Mn} ($\Tcondens = 1158$~K) and
-\elem{Cr} ($\Tcondens = 1296$~K) suggest a break in $\Tcondens \approx 1200$~K.
-
-We interpret the \Tcondens-dependent metal enhancement of \bizarreone\ relative
-to \sunanalog\ and the very high surface \elem{Li} abundance ($A(\elem{Li}) =
-2.75$) of \bizarreone\ as evidence for accretion of rocky (refractory-rich)
-planetary material in \bizarreone.
-In a multi-planet system, dynamical instabilities triggered by planet-planet
-scattering\cite{1996Sci...274..954R,1996Natur.384..619W} or encounters with a
-field star\cite{Malmberg:2011aa} can lead to planet ejection or accretion.
-If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
-than the other, this may imprint a strong \Tcondens-dependent
-abundance differences like those observed in \bizarreone-\sunanalog.
-
-%%TODO: cautions on condensation temperature
-%% 1. it is just a proxy
-%% 2. it is **equlibrium** condensation temperature
-
-We estimate that the accretion of $\approx 15$~\mearth\ of rocky planets
-in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
-refractory elements as well as the surface Li abundance.
-Because the anchor star, \sunanalog,
-is very similar to the Sun in its stellar properties (\teff, \logg, \feh, age),
-we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
-pre-accretion state of \bizarreone.
-In \figname~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
-$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth composition
-material\cite{2003TrGeo...2..547M} assuming that 2\% of the star's mass is in
-its convective zone\cite{Pinsonneault:2001aa}.
-It has long been known that more volatile (low \Tcondens) elements are more
-depleted in the Earth relative to CI or other carbonaceous
-chondrites\cite{mcdonough2001composition} that are thought to reflect the
-elemental composition of the proto-solar nebula.
-This trend is presumed to be closely related to the formation of terrestrial
-planets and, in particular to the radial temperature gradient in a
-protoplanetary disk.
-The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
-good match to the observed $\Delta\elemH{X}$, suggesting that the
-refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
-rocky planetary material than \sunanalog.
-
-The accretion scenario can naturally explain the anomalously high
-surface \elem{Li} abundance in \bizarreone.
-Because \elem{Li} is strongly depleted in old sun-like stars, yet
-present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
-late-time accretion of rocky planetary material will significantly
-replenish the lithium in the star's surface.
-For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
-material would result in $\Delta\elemH{Li} \approx 1.6$~dex
-(see inset of \figname~\ref{fig:deltaxh_tcrank}).
-Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
-stellar parameters) very close to the Sun ($\sim 4$~Gyr).
-Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
-to be ordinary, the accretion of $15$~\mearth\ by \bizarreone\ is consistent with a $1.65$~dex
-enhancement in \elem{Li} abundance.
-This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
-$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
-approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
-While the current analysis of \elem{Li} line assumed a solar ratio of
-$^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that a higher resolution
-spectrum of the star will reveal a significant $^{6}\elem{Li}$ which are
-normally destroyed early in solar-type stars, but present in rocky
-planets\cite{Israelian:2001}.
-
-\sunanalog\ is also enhanced in \elem{Li} compared to other stars of similar
-ages by $\approx 1$~dex, considering its age of $4.00_{-1.56}^{+1.51}$~Gyr.
-This enhancement puts an upper limit on the accreted mass to be
-$\approx 4$~\mearth\ assuming a \elem{Li} concentration of $1.1$~ppm
-\cite{mcdonough2001composition}, as above.
-Unlike \bizarreone, we cannot know the pre-accretion abundances of
-\sunanalog.\footnote{
-  Strictly speaking, we can never know the pre-accretion abundances
-  for \bizarreone\ either.
-  We only have an {\it approximate} idea that this is not far from a solar-twin
-  star \sunanalog, and because the deviation from this ``anchor'' star is
-  large, it is reasonable to consider accretion by the Sun.
-  In reality, \sunanalog\ may also have had its own accretion history,
-  which indeed seems to be the case according to its \elem{Li} abundance.
-}
-However, we note that the span of abundance difference between highly volatile
-elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
-as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
-0.05$~dex.
-This is comparable to the abundance difference between N, Na, and Fe in
-\sunanalog.
-It is also interesting that \sunanalog\ shows a deficit in the same volatile
-and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
-\elem{Mn}) relative to Fe as in \bizarreone.
-Thus, we conclude that \sunanalog\ is also likely to have had a similar
-accretion event, but the amount of accretion was at least 5 times
-smaller than \bizarreone.
-
-What triggered the planet engulfment in the two comoving stars remains unclear.
-One possibility is that a fly-by interaction with a field star could have
-triggered eccentricity excitation of outer planets around each star, which may
-have propagated inward through planet-planet scattering,
-leading to the accretion of inner rocky planets\cite{Zakamska:2004aa,Malmberg:2011aa}.
-If this is the case, there may be surviving, highly-eccentric giant planets.
-The two stars have not been included in any publicly released data from planet
-search programs, however, outer eccentric planets are potentially detectable
-with future data releases of the \gaia\ mission.
-If both stars have accreted planetary material, it would be very interesting to
-search for the existence and architectures of the planetary systems left
-behind.
-
-\bibliography{ref}
-
-\section{Acknowledgements}
-We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
-We thank Megan Bedell and Andy Casey for valuable discussions,
-and Keith Hawkins, Nathan Leigh, and Josh Winn for comments
-on early version of the draft.
-The Flatiron Institute is supported by the Simons Foundation.
-% Gaia
-This work has made use of data from the European Space Agency (ESA) mission
-{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
-Data Processing and Analysis Consortium (DPAC,
-\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
-has been provided by national institutions, in particular the institutions
-participating in the {\it Gaia} Multilateral Agreement.
-% 2MASS
-This publication makes use of data products from the Two Micron All Sky Survey,
-which is a joint project of the University of Massachusetts and the Infrared
-Processing and Analysis Center/California Institute of Technology, funded by
-the National Aeronautics and Space Administration and the National Science
-Foundation.
-% all-WISE
-This publication makes use of data products from the Wide-field Infrared Survey
-Explorer, which is a joint project of the University of California, Los
-Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
-funded by the National Aeronautics and Space Administration.
-% software
-%\software{
-%  %The data and code used in this project is available from
-%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
-%  %software license.
-%  This research utilized:
-%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
-%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
-%  \texttt{IPython} (\citealt{Perez:2007}),
-%  \texttt{matplotlib} (\citealt{Hunter:2007}),
-%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
-%  and \texttt{pandas} (\citealt{pandas}).}
-
-\section{Extended Data}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{yyisofitting.pdf}
-  \caption{Probability density function of stellar age, mass, and radius
-    from isochrone fitting using Yonsei-Yale isochrones\cite{2013ApJ...776...87S}
-    and the star's luminosity, \teff, \feh, and \elemH{Si}.
-  }
-  \label{fig:yyisofitting}
 \end{figure}
@@
     We mark elements that give rise to strong absorption lines.
+    The feature in the third column of the second row is a strong \elem{Li}
+    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
+    studied in a separate work (\citealt{jmlithium}).
     Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
     in \bizarreone\ relative to \elem{Fe} or other refractory elements,
-    show noticeably weaker residuals compared to neighboring lines of
-    refractory elements.
+    show weaker residuals.
   }
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{spec_lithium.pdf}
-  \caption{Lithium lines in the spectra of \bizarreone\ and \sunanalog.
-    This line is studied in Myles \etal\ (in prep.).
-    Line legends are the same as in \figname~\ref{fig:spec1}.
-  }
-  \label{fig:spec_lithium}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
   \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
-  \caption{Abundance difference in this pair (blue circles) and other twin-like
-    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries\cite{2016ApJS..225...32B}
-    (black circles).
+  \caption{Abundance difference in this pair and other twin-like
+    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
+    \citealt{2016ApJS..225...32B}.
     The differences in other pairs are small ($<0.05$~dex)
@@
     Additionally, we show the distribution of abundance differences
-    between field stars in the same catalog\cite{2016ApJS..225...32B}
-    with similar metallicity difference
+    between field stars with similar metallicity difference
     ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
-    as violins (shaded regions) with medians indicated by black line segments.
-    These are random pairings of single stars from two metallicity bins,
+    as violins with medians indicated by black line segments.
+    These are random pairings of single stars in
+    in \citealt{2016ApJS..225...32B} at two metallicity bins,
     $-0.025 < \feh < 0.025$ (160 stars) and $0.175 > \feh > 0.225$ (137 stars),
@@
 
-%As shown in \figname~\ref{fig:deltaXH},
-%the differences in other pairs for all elements except \elem{N} and \elem{O},
-%which are also the most uncertain (\tablename~\ref{tab:kk}),
-%are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
-  \caption{Comparison to other pairs that show abundance differences.
-    All astronomical metals are ordered by their \Tcondens\ for solar
-    composition gas\cite{2003ApJ...591.1220L} on the $x$-axis, same as \figname~\ref{fig:deltaxh_tcrank}.
-    The condensation temperature may be read from the gray line and right y-axis.
-    We show three wide binary systems selected from the literature:
-    HD~20782/1\cite{Mack:2014aa} ($\feh\approx0$),
-    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$),
-    and WASP-94AB\cite{Teske:2016aa} ($\feh\approx0.3$).
-    Locations of elements with at least one measurement from any study
-    are indicated by vertical lines and their symbols.
-    Note that often multiple values are reported for one element corresponding
-    to different ionization states in equivalent width analyses.
-    No other pair studied so far were shown to have such large difference
-    in metallicity or sharp contrast between (moderately) volatile and
-    refractory elements as \bizarreone-\sunanalog.
+\sunanalog\ and \bizarreone\ were identified as a
+candidate comoving star pair in our recent search for comoving stars using the
+proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr\
+(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
+We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
+full explanation of the methodology behind this search and only briefly describe
+the method here.
+For a given pair, we compute a marginalized likelihood ratio between the
+hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
+(2) that they have independent 3D velocity vectors, both given only observations
+of two components of the velocities (parallaxes and proper motions).
+We then select a sample of high-confidence comoving star pairs by making a
+conservative cut on this likelihood ratio.
+In the resulting catalog of comoving pairs (\citealt{2017AJ....153..257O}),
+the pair presented in this paper was assigned a group id of 1199,
+and the marginalized likelihood ratio (Bayes factor)
+between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
+well above the adopted cut value of 6.
+The pair has also been previously recognized as a visual double star system
+in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
+We have checked that we do not find any possible additional comoving companions
+by lowering the likelihood ratio cut for the stars around this pair.
+
+In a separate effort to study detailed chemical abundances of potential
+planet-hosting stars, \citet{2016ApJS..225...32B} obtained and analyzed high resolution
+spectra of both stars using the HIRES spectrograph on the Keck~I telescope.
+The spectral resolution is $R\approx 70000$ and the wavelength coverage is
+$5164$--$7799$~\AA.
+A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
+The resulting measurements include elemental abundances for 15 chemical species
+(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
+and high precision radial velocities.
+For the details of the spectral analysis, we refer the readers to
+\citealt{2016ApJS..225...32B}.
+The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
+\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
+work (\citealt{jmlithium}).
+We list all spectroscopic measurements including
+the absolute abundance\footnote{
+  The absolute abundance of element \elem{X} is
+  $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
+  where $n_\elem{X}$ is the number density of element \elem{X}.
 }
-  \label{fig:relabun_tcrank}
-\end{figure}
-
-\clearpage
-
-\section{Supplementary Information}
-
-\subsection{Proximity in phase-space coordinates}
-\label{supp:dxdv}
-
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
-  \end{center}
-  \caption{%
-    Differences in posterior samples over Galactocentric phase-space coordinates
-    for the two stars, \bizarreone\ and \sunanalog.
-    \label{fig:dxdv}}
-\end{figure}
-
-Combining the precise radial velocities obtained from spectra with the \tgas\
-astrometry, we can compare differences between the inferred 6D phase-space
-coordinates of the two stars.
+of \elem{Li} for the two stars in Table~\ref{tab:kk}.
+
+The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
+and the 3D separation is $\approx 0.6$~pc.
+Although selected based only on their astrometry, the two stars
+have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
+confirming that they are truly comoving.
+Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
+can compare differences between the inferred 6D phase-space coordinates of the
+two stars.
 We start by generating posterior samples over the Heliocentric distance, $r$,
@@
   \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
-\end{equation} where $\mat{C}$ is the covariance matrix, and $\mathcal{N}$ is
-normal (Gaussian) distribution\cite{2017AJ....153..257O}.
-We adopt a uniform space-density prior for the distance and an isotropic
-Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$:
+\end{equation} where $\mat{C}$ is the covariance matrix.
+We adopt a uniform space density prior for the distance and an isotropic
+Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
 \begin{eqnarray}
@@
 %
-For each of the two stars, we use \project{emcee}\cite{2013PASP..125..306F}
-to generate posterior samples in $(r, v_\alpha, v_\delta, v_r)$
-by running 64 walkers for 4608 steps and discarding the first
+For each of the two stars, we use \project{emcee}
+(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
+v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
 512 steps as the burn-in period.
-For each sample, we convert the Heliocentric phase-space coordinates into
+For each sample, we convert the heliocentric phase-space coordinates into
 Galactocentric coordinates assuming that the Sun's position and velocity are
 $\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
-(11.1,\,244,\,7.25)~\kms$\cite{Schonrich:2010, Schonrich:2012}.
+(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.
 
@@
 The differences in positions and velocities are consistent with zero.
-% \todo{should we instead show $|\Delta\boldsymbol{x}|$ and
-% $|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
-
-\subsection{Stellar Ages and Coevality}
-\label{sub:age_coevality}
-
-\begin{figure}[htbp]
-  \begin{center}
-    \includegraphics[width=0.65\linewidth]{sed.pdf}
-  \end{center}
-  \caption{Spectral energy distributions of \bizarreone\ and \sunanalog.
-    We compiled the photometric measurements from
-    \project{Tycho-2}\cite{2000A&A...355L..27H},
-    \project{2MASS}\cite{2006AJ....131.1163S}, and
-    \project{WISE}\cite{2010AJ....140.1868W}.
-  }
-  \label{fig:sed}
-\end{figure}
-
+\todo{should we instead show $|\Delta\boldsymbol{x}|$ and
+$|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
+
+For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
+1.2~pc (\citealt{jiangtremaine2010}).
+%TODO
+\bizarreone\ and \sunanalog\ are likely a bound system that formed coevally.
+Thus, we expect the two stars to have identical metallicities and abundance patterns.
+However, one of the stars, \bizarreone\ is significantly more metal
+rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
+Moreover, not all elements are equally enhanced:
+the abundances of \bizarreone\ show selective depletion in
+\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
+relative to \elem{Fe}.
+Both stars have high surface \elem{Li} abundances, and the difference in
+\elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
+measured.
+
+The validity of the measured abundance differences is further demonstrated
+in \figname~\ref{fig:spec1} and \ref{fig:spec2} where we show
+segments of the spectra and models of the two stars
+used to measure their abundances.
+As expected from their reported metallicity difference ($\Delta\feh \approx 0.2$),
+the ratio of data and model between the two stars show significant
+residuals of almost all metal line features, largely dominated by \elem{Fe}.
+However, for lines of elements that are not as enhanced in \bizarreone\,
+the residuals are much smaller in amplitude.
+%Li?
+
+We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
+\lesssim 100$~K) wide binary pairs examined by \citealt{2016ApJS..225...32B}
+show discrepancies in abundances between the stars at this level.
+As shown in \figname~\ref{fig:deltaXH},
+the differences in other pairs for all elements except \elem{N} and \elem{O},
+which are also the most uncertain (\tablename~\ref{tab:kk}),
+are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
+
+%TODO: plot styles...
 \begin{figure}[htbp]
@@
   \end{center}
-  \caption{Left panel: Galactic orbits computed for \sunanalog\ (blue) and the
+  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
     Sun (grey).
-    For \sunanalog, the initial condition is set to the median of the
+    For \sunanalog, the initial conditions are set to the median of the
     posterior samples over the phase-space coordinates.
@@
     positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
-    integration scheme implemented in \project{Gala}\cite{gala}.
-    Right panel: Distribution of maximum $z$-heights for orbits computed from
-    all posterior samples for \sunanalog.
-    The large $z$-height is consistent with an old ($\sim 4$~Gyr) age
-    (\sectionname~\ref{sub:age_coevality}).
+    integration scheme implemented in \project{Gala} (\citealt{gala}).
+    Right panel: distribution of maximum $z$-heights for orbits computed from
+    all posterior samples.
   }
@@
 
-We provide a more detailed discussion of stellar ages and coevality of
-\bizarreone-\sunanalog\ pair, aside from the isochrone fitting,
-especially on whether the stars may be very young ($\lesssim 1$~Gyr).
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
+  \caption{Abundance differences of the \bizarreone-\sunanalog\ pair
+    ranked by the condensation temperature of elements for solar composition gas
+    from \citealt{2003ApJ...591.1220L}.
+    The condensation temperature may be read from the gray line and right y-axis.
+    We show three wide binary systems selected from the literature:
+    HD~20782/1 (\citealt{Mack:2014aa}, $\feh\approx0$),
+    XO-2N/S (\citealt{Biazzo:2015aa}, $\feh\approx0.35$),
+    and WASP-94AB (\citealt{Teske:2016aa}, $\feh\approx0.3$).
+    Locations of elements with at least one measurement from any study
+    are indicated by a vertical line and its symbol.
+    Note that often multiple values are reported for one element corresponding
+    to different ionization states in equivalent width analyses.
+    No other pair studied so far were shown to have such large difference
+    in metallicity or sharp contrast between (moderately) volatile and
+    refractory elements as \bizarreone-\sunanalog.
+  }
+  \label{fig:relabun_tcrank}
+\end{figure}
+
+\section{Discussion}
+\label{sec:discussion}
+
+We discuss the possible origins of the peculiar abundance differences of
+\bizarreone-\sunanalog.
+We first discuss the ages and coevality of the stars in this pair, and consider
+both possibilities in which the two stars are or are not coeval.
+Our favored scenario is discussed in the last subsection,
+\sectionname~\ref{sub:accretion}.
+
+% chance pair
+%Given that their metallicities and abundance patterns are significantly
+%different, one may simply conclude that the two stars are not related (coeval)
+%but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
+%by chance.
+%The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
+%at the stars' location, one may compute the probability that a star moving at
+%the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
+%...
+
+\subsection{Stellar Ages \& Coevality}
+\label{sub:ages}
+
+The fact that the two stars share nearly identical space motion
+at a separation of $< 1$~pc strongly supports that the pair is coeval.
+We therefore consider other age indicators apart from their phase-space
+coordinates to assess the ages and coevality of the two stars.
+First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
+we can constrain the ages of the two stars by
+comparing these values to theoretical isochrones.
+We perform isochrone fitting to these values using the Yale-Yonsei model
+isochrones (\citealt{2013ApJ...776...87S}).
+The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
+parallaxes, $B$-band magnitudes, and their errors.
+The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
+$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
+consistent with them being coeval.
+
 The surface lithium abundance in a sun-like star decreases with its age due to
@@
 burning.
-Thus, surface lithium abundance can be an indicator of stellar ages.
+Thus, surface lithium abundance is an indicator of stellar ages.
 The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
 of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
-solar lithium abundance and rotational profile\cite{2005Sci...309.2189C}.
+solar lithium abundance and rotational profile (\citealt{2005Sci...309.2189C}).
 The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
@@
 abundance means a younger age or something else.
-For example, the presence of $\elem{Li}$-rich red giant stars was
+For example, the presence of $\elem{Li}$-rich red giant stars has been
 attributed to the engulfment of substellar companions such as gas giant planets
-or brown dwarfs which may replenish $\elem{Li}$\cite{Casey:2016aa}.
-
-The surface lithium abundance is the only indicator of a
-younger age.
-If the two stars were only several hundred Myrs old, then they would likely
-have been part of a larger comoving group of stars.
-However, there is no evidence in our search\cite{2017AJ....153..257O} of
-comoving pairs using \tgas\ that these stars belong to a larger group of
-young stars.
+or brown dwarfs which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
+
+In fact, the surface lithium abundance is the only indication that points to
+younger ages.
+If the two stars are indeed only several hundred Myrs old at most,
+they are expected to be part of a larger comoving group of stars.
+However, as we mention above, there is no evidence in our search of comoving pairs
+using \tgas\ that the two stars belong to a larger group of young stars.
 Very young stars often show signs of activity such as
 X-ray emission from magnetic activity, emission lines, or infrared excess due to
-circumstellar disks.
-We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
-found no evidence for indications of activity or infrared excess in their
-spectral energy distributions (\figname~\ref{fig:sed}).
-The low $v\sin(i)$ values (\tablename~\ref{tab:t1}) also argue against very
+circumstellar disks (\todo{needs refernces}).
+We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
+and found no evidence for indications of activity in their spectral energy
+distributions.
+The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
 young ages that would be inferred from the surface lithium abundances.
@@
 posterior sample over the phase space coordinates of \sunanalog, in a Milky
-Way-like gravitational potential\cite{Bovy:2015} using \project{Gala}\cite{gala}.
+Way-like gravitational potential (similar to \texttt{MWPotential2014} from
+\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age\cite{Wielen:1977,Aumer:2016} (\figname~\ref{fig:orbit}).
+an older age (\todo{needs references for vertical action as age indicator}).
 We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
 old main sequence stars, and that their unusually high \elem{Li} abundance
-requires an alternative explanation; our favored explanation being the accretion
-of rocky material that has locked lithium.
-
-\subsection{Alternative Scenarios}
-
-\subsubsection{Exchange Scattering}
+requires an alternative explanation.
+
+\subsection{Exchange Scattering}
 \label{sub:exchange_scattering}
 
-While the data described above strongly suggests that the two stars are
-coeval, this subsection explores the possibility that this is not a primordial
-binary.
+Although the data described above strongly suggests that the two stars are
+coeval, we may still consider scenarios in which the two stars are not actually
+born together.
 Two stars unrelated at birth may end up in a binary system via a binary-single
@@
 The cross-section of exchange scattering for a binary with semi-major axis $a$ is
-\cite{Hut:1983ab,Hut:1983aa}
 \begin{eqnarray}
@@
 \end{eqnarray}
-\eqname~\ref{eq:crosssection} is appropriate when $v_i/v_c \gg 1$,
-which is the case for wide binaries
+\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
+(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
 scattering with field (disk) stars.
@@
 number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
-$10$~\kms, the rate of exchange scattering is
+$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
+any direction, the rate of exchange scattering is
 \begin{eqnarray}
@@
 which is low enough to be negligible.
-This is a conservative estimate as the relative velocity of
-disk stars exceeds $10$~\kms.
-
-An exchange scattering scenario is unlikely to be able to explain the observed
-abundance difference pattern.
-We test this by comparing the observed abundance difference of
+
+In fact, any exchange scattering scenario is unsatisfactory as typical
+field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
+unlikely to show the abundance difference pattern observed.
+In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
 \bizarreone-\sunanalog\ with the distribution of abundance differences,
-$\Delta[\elem{X}/\elem{H}]$, between pairs of two stars randomly drawn
-from two metallicity (\feh) bins similar to \bizarreone\ and \sunanalog\
-(\figname~\ref{fig:deltaXH}).
+$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
+\feh\ as \bizarreone\ and \sunanalog.
 We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
@@
 expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
-\cite{Battistini:2015aa,Bensby:2003aa}, making the low
+(\citealt{Battistini:2015aa,Bensby:2003aa}) making the low
 [\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
@@
 
-\subsubsection{Chemical Inhomogeneity in Star Formation}
+\todo{HOGG: to provide some theoretical account adding to the above empirical evidence.}
+
+\subsection{Chemical Inhomogeneity in Star Formation}
 \label{sub:chemical_inhomogeneity_in_star_formation}
 
-In this subsection, we explore the hypothesis that the chemical inhomogeneity
-within the birth cloud is the source of the \bizarreone-\sunanalog\ abundance
-anomalies.
-There is ample evidence against this scenario.
-None of the other seven similar wide binaries examined
-with the same measurement pipeline\cite{2016ApJS..225...32B}
-show the same level of differences in abundances.
+Assuming that the two stars were born together, one possibility to
+explain the chemical difference is that there was chemical inhomogeneity within
+the birth cloud.
+However, there is already ample evidence against such a scenario.
+First, none of the other seven similar wide binaries examined in
+\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
 Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
@@
 (\figname~\ref{fig:deltaXH}).
-This is consistent with similar previous studies\cite{Gratton:2001aa,Desidera:2004aa}.
+This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
+23 wide binaries of late F to K dwarfs, and found most pairs show a difference
+in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
+Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
+binaries have the same chemical composition with $\gtrsim 0.01$~dex
+uncertainties.
 Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
@@
 
-\subsection{Estimating the accreted masses}
-
 \begin{figure}[htpb]
   \centering
-  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank_vari.pdf}
-  \caption{Expected differences in solar abundances after adding
-    varying mass of bulk Earth material.
-    Elements are ordered by their $T_C$ on $x$-axis, same as
-    \figname~\ref{fig:deltaxh_tcrank}.
-    We assume $f_\mathrm{CZ} = 0.02$ and show expected $\Delta\elemH{X}$
-    for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
+  \includegraphics[width=0.95\linewidth]{toycalc.png}
+  \caption{
+    Comparing the observed abundance difference vs. \Tcondens\ rank
+    to the expected change in solar surface abundance after adding $20$~\mearth\ of
+    material with bulk Earth composition (\citealt{mcdonough2001composition}).
+    The assumed mass fraction in the convective zone is $0.03$.
+    All metals are ranked by their \Tcondens\ for solar composition gas,
+    and the condensation temperature may be read from the gray line and right y-axis,
+    same as in \figname~\ref{fig:relabun_tcrank}.
+    Locations of the elements measured for \bizarreone-\sunanalog\ pair are
+    indicated by a vertical line and its symbol.
+    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
+    suggests that the abundance difference may be due to accretion of
+    $20$~\mearth\ of rocky planetary material.
+    The element \elem{Li} is off the plot and indicated with a red arrow
+    (see text for details).
   }
-  \label{fig:vari}
+  \label{fig:toycalc}
 \end{figure}
 
-We estimate how much added rocky material is needed to explain an
-increment of $\approx 0.2$~dex in refractory elements observed in \bizarreone\
-relative to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
-Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
-and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx 100$~K,
-$\Delta\logg \approx 0$, and $\Delta\feh \approx 0$),
-we may approximate the pre-accretion abundances of \bizarreone\ as being
-equivalent to the sun.
+\subsection{Accretion of rocky planetary material}
+\label{sub:accretion}
+
+Another possibility that two coeval stars may end up with different surface
+abundances is accretion of planetary material after birth.
+Instabilities may develop in a multi-planet system due to its chaotic nature
+which may lead to planet engulfment or ejection by the host star
+(\todo{needs references}).
+%TODO: kozai?
+Indeed, it is an important goal of many exoplanet studies
+to detect chemical signatures of planet formation or accretion,
+distinguish them from Galactic chemical evolution, and
+connect them to theories of evolution of planetary systems.
+One approach that is free from confusion with Galactic chemical evolution
+is to compare two almost identical stars in a wide binary system.
+Assuming that the component stars were born together with identical
+initial composition, we may see a difference in their surface abundances
+if the two stars then accreted different amounts of planetary material.
+The resulting abundance difference may depend on the condensation
+temperatures of elements in the protoplanetary disks from which the accreted
+planets formed, as their compositions depend on the radial temperature gradient
+in the disk.
+%TODO: cautions on condensation temperature
+% 1. it is just a proxy
+% 2. it is **equlibrium** condensation temperature
+
+In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
+between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
+of each element.
+The equilibrium condensation temperatures for the composition of solar system
+are taken from \citealt{2003ApJ...591.1220L} (Table~8).
+The difference seen in \bizarreone-\sunanalog\ is
+compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
+The metallicity difference of $\approx 0.2$~dex observed in this pair
+is larger than the differences seen in any other pairs studied so far.
+Strikingly, the five under-enhanced elements in \bizarreone\
+relative to \sunanalog\ are the five most volatile in all elements measured.
+The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
+\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
+This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
+combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
+strongly suggests that accretion of rocky material has occured in \bizarreone.
+
+How much mass of rocky material is needed to explain an increment of
+$\approx 0.2$~dex?
 We carry out simple toy calculations of expected $\Delta\elemH{X}$
-in a Sun-like star's atmosphere by adding a certain mass of bulk Earth
-composition under these simplifying assumptions:
+in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
+under these simplifying assumptions:
 \begin{itemize}
@@
 \end{itemize}
-We take the solar abundances\cite{Asplund:2009aa}, $\elemH{X}$, of element \elem{X}
-which can be converted to mass fraction as
+
+We take the solar abundances, $\elemH{X}$, of element \elem{X}
+(\citealt{Asplund:2009aa}) which can be converted to mass fraction as
 \begin{equation}
@@
 \end{equation}
-where $m_X$ is the mass of each element in, e.g., atomic mass unit.
+where $m_X$ is the mass of each element in e.g., atomic mass unit.
 Assuming that the added material has a total mass $M_\mathrm{add}$, and the
-mass fraction in each element is $f_{X,\mathrm{add}}$,
+mass fraction in each element $f_{X,\mathrm{add}}$,
 the abundance difference is
@@
 where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
-We take the composition of bulk Earth\cite{mcdonough2001composition}
-as a proxy for rocky planet composition. We adopt $f_\mathrm{CZ} = 0.02$ for
-the fraction of mass in the convective zone\cite{Pinsonneault:2001aa}.
-
-The estimate of accreted mass depends sensitively on $f_\mathrm{CZ}$ and the
-mass of the star which are difficult quantities to constrain directly through
-data.
-We adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, and show
-expected changes for the accretion of $5-25$~\mearth\ of bulk Earth material
-in \figname~\ref{fig:vari}.
-However, we note that if $f_\mathrm{CZ}$ is $0.03$, the estimate for the accreted
-mass would be $\approx 20$~\mearth.
-
+We take the composition of bulk Earth from a chondritic model of the Earth
+(\citealt{mcdonough2001composition}).
+Similar calculations have been performed by \citet{Chambers:2010aa} and
+\citet{Mack:2014aa,Mack:2016aa}.
+
+Figure~\ref{fig:toycalc} shows the expected change of surface abundances of
+metals in a Sun-like star after $20~\mearth$ of material with composition of
+bulk Earth is added.
+A volatility trend that more volatile (low \Tcondens) elements are more
+depleted in the Earth relative to CI or other carbonaceous chondrites
+has long been known (\citealt{mcdonough2001composition}).
+This trend is presumed to be closely related to the formation of terrestrial
+planets and, in particular to the radial temperature gradient in a
+protoplanetary disk.
+The trend resulting from adding $20~\mearth$ of bulk Earth
+provides an overall good match to the observed $\Delta\elemH{X}$,
+suggesting that the refractory-enhanced star, \bizarreone\,
+accreted $20~\mearth$ more of rocky planetary material than \sunanalog.
+
+What about \elem{Li}?
+The element \elem{Li} is worth special attention in the context of the
+accretion scenario.
+Because Li is present in either carbonaceous chondrites or bulk Earth with
+a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition}),
+but is depleted quickly within the first couple of Gyrs on the surface of a
+Sun-like star, accretion of either material at later times will significantly
+replenish the lithium on the star's surface.
+For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
+material would result in $\Delta\elemH{Li} \approx 1.6$~dex (which
+is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
+Incidentally, the star under examination, \bizarreone, has an age (informed by
+stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
+Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
+to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
+enhancement in its \elem{Li}.
+This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
+$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
+approximately $1.65$~dex higher than the solar value of $1.1$~dex
+(\todo{needs reference}).
+Furthermore, this implies that the accretion event should have happened very
+recently, or at least within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
+
+What about \sunanalog?
+Considering its age of $4.00_{-1.56}^{+1.51}$~Gyr, \sunanalog\ is also enhanced
+in \elem{Li} compared to other stars of similar ages by $\approx 1$~dex.
+This enhancement puts an upper limit on the accreted mass to be
+$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
+(\citealt{mcdonough2001composition}).
+Unlike \bizarreone, we cannot know the pre-accretion abundances of
+\sunanalog.\footnote{
+  Strictly speaking, we can never know the pre-accretion abundances
+  for \bizarreone\ either.
+  We only have an {\it approximate} idea that this is not far from a solar-twin
+  star \sunanalog, and because the deviation from this ``anchor'' star is
+  large, it is reasonable to consider accretion by the Sun.
+  In reality, \sunanalog\ may as well have had its own accretion history,
+  which indeed seems to be the case according to its \elem{Li} abundance.
+}
+However, we note that the span of abundance difference between highly volatile
+elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
+as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
+0.05$~dex.
+This is comparable to the abundance difference between N, Na and Fe in
+\sunanalog.
+It is also interesting that \sunanalog\ shows a deficit in the same volatile
+and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
+\elem{Mn}) relative to Fe as in \bizarreone.
+Thus, we conclude that \sunanalog\ is also likely to have had a similar
+accretion event, but the amount of accretion was at least 5 time
+smaller than \bizarreone.
+
+%TODO: augment this paragraph
+% - more geochemical study references
 We stress that while the calculation carried out is useful in
@@
 In addition, the composition of bulk Earth has some uncertainties.
-For example, the reported bulk Earth concentration of \elem{Mn}, varies from
-$800$ to $1700$~ppm\cite{1998psc..book.....L,mcdonough2001composition,2003TrGeo...2..547M}
-largely due to uncertainties in how much \elem{Mn} is in the Earth's core.
+For example, the reported bulk Earth concentration of the siderphile element
+\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
+While the latter value from \citealt{mcdonough2001composition} has been used in
+our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
+to an even closer agreement.
 Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
@@
 
-%\input{kk.tex}
+\section{Summary}
+\label{sec:summary}
+
+We report the discovery of a comoving pair of bright
+solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
+metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
+(\Tcondens)-dependent abundance differences.
+The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
+all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
+enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
+\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
+The two stars also have anomalously high surface \elem{Li} abundance compared
+to their ages of $\sim 4$~Gyr.
+We consider that the comoving pair may have formed from two stars of different
+birth origins in a exchange scattering event, or that there may be chemical
+inhomogeneity in the birth cloud, and find both unlikely.
+
+In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
+abundance, we consider accretion of planetary material as the cause.
+We argue that a recent accretion of $20$~\mearth\ of bulk Earth
+composition to \bizarreone\ can explain the enhancement in both refractory
+elements and lithium.
+For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
+we put an upper limit of $\approx 4$~\mearth\ on the accreted mass
+based on the \elem{Li} concentration of carbonaceous chondrites and bulk Earth.
+While the case is not as clear as \bizarreone\ without a chemical reference star,
+the range of abundances from volatile to refractory elements is
+similar to that expected from $\approx 4$~\mearth\ accretion of bulk Earth.
+It is unclear what triggered the accretions to both stars.
+One possibility is that a fly-by field star may have
+perturbed the planetary systems of both stars.
+
+The two stars have not been included in any publicly released data from planet
+search programs.
+If both stars have accreted planetary material, it would be very interesting to
+search for the existence and architectures of the planetary systems left
+behind.
+
+%TODO: Implications
+%- chemical tagging, frequency is of concern
+%- exoplaneteers looking for accretion signature: look for the most odd ones in
+%the expected direction not just in binaries already known to host a planet.
+
+\acknowledgements
+
+We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
+We thank Megan Bedell and Andy Casey for valuable discussions,
+and Keith Hawkins, Nathan Leigh, and Josh Winn for comments
+on the early version of the draft.
+The Flatiron Institute is supported by the Simons Foundation.
+
+% Gaia
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement.
+% 2MASS
+This publication makes use of data products from the Two Micron All Sky Survey,
+which is a joint project of the University of Massachusetts and the Infrared
+Processing and Analysis Center/California Institute of Technology, funded by
+the National Aeronautics and Space Administration and the National Science
+Foundation.
+% all-WISE
+This publication makes use of data products from the Wide-field Infrared Survey
+Explorer, which is a joint project of the University of California, Los
+Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
+funded by the National Aeronautics and Space Administration.
+
+%TODO: corner.py
+%TODO: data/code available
+\software{
+  %The data and code used in this project is available from
+  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
+  %software license.
+  This research utilized:
+  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
+  \texttt{emcee} (\citealt{2013PASP..125..306F}),
+  \texttt{IPython} (\citealt{Perez:2007}),
+  \texttt{matplotlib} (\citealt{Hunter:2007}),
+  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
+  and \texttt{pandas} (\citealt{pandas}).}
+
+\bibliography{ref}
 

### 2017-08-09 paper/ms.tex
Review the review section

@@
 
-\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
+\newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
 
@@
   Evidence for accretion of a massive, rocky planetary system
-  in a comoving pair of G dwarfs
+  in a comoving pair of solar-type stars
 }
@@
   New York, NY 10010, USA}
-
-% \author{Keith A. Hawkins}
-% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}
-
-% \author{Nathan W. C. Leigh}
-% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
-
 \author{Justin Myles} % TODO: need ORCID
@@
 \begin{abstract}
-  We report and discuss the discovery of a comoving pair of bright G
+  We report and discuss the discovery of a comoving pair of bright solar-type
   stars, HD~240430 and HD~240429, with a significant difference in their
@@
   as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
-  high-resolution radial velocity measurements.
+  high-precision radial velocity measurements.
   Stellar parameters determined from high-resolution Keck HIRES spectra
@@
 
-\subsection{Review of Detailed Chemical Abundance Studies of Wide Binary Stars}
+\subsection{
+  Review of Detailed Chemical Abundance Studies of Stars in Comoving Pairs}
 \label{sub:review}
@@
 Anticipating the forthcoming discussion, we review and summarize a handful of
-wide binary systems that have been studied in
-their detailed chemical abundances so far with high-resolution spectroscopy.
+wide binary systems that have been studied in their detailed chemical
+abundances so far with high-resolution spectroscopy.
 These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
@@
 any trend in $\Delta\elemH{X}$ with \Tcondens.
-(\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added})
+
+\todo{might as well note no orbits ever established at these separations}
+\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added}
 
@@
   within $\approx 0.35$~AU.}
-The measured abundances of 15 elements in the two stars are consistent
-(\citealt{Mack:2014aa}).
+The measured abundances of 15 elements between the two stars are consistent
+with each other (\citealt{Mack:2014aa}).
 However, \citealt{Mack:2014aa} argued that there is a moderately significant
@@
 {\bf HAT-P-1:}
-A pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
+This pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
 different planetary systems:
@@
 the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
-Thus it seems that the presence of close-in giant planet does not necessarily
+Thus, it seems that the presence of close-in giant planet does not necessarily
 lead to atmospheric pollution of its host star.
@@
 {\bf XO-2N/XO-2S:}
-A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
+This pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
 has received much attention due to possibly the most robust and significant

### 2017-08-09 paper/ms.tex
Correct caption

@@
   \includegraphics[width=0.9\linewidth]{abundances.pdf}
-  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
-    normalized to \elem{H} (top) and \elem{Fe} (bottom).
-    Lines are drawn for each star only to guide the eye.
-    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
-    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
-    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
-    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
+  \caption{Abundances of the comoving pair, \sunanalog\ (blue) and \bizarreone\
+    (red). Lines are drawn for each star only to guide the eye. \bizarreone\ is
+    enhanced in \elem{Fe} by $\approx 0.2$~dex relative to \sunanalog\ along
+    with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca}, \elem{Ti}, \elem{V},
+    \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C}, \elem{N}, \elem{O},
+    \elem{Na}, and \elem{Mn}.
   }

### 2017-08-09 paper/ms.tex
Add separate lithium figure

@@
     We mark elements that give rise to strong absorption lines.
-    The feature in the third column of the second row is a strong \elem{Li}
-    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
-    studied in a separate work (\citealt{jmlithium}).
     Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced

### 2017-08-14 paper/ms.tex
tweaks and todos

@@
 \usepackage[flushleft]{threeparttable}
-\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
+\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=gray}
 \graphicspath{{figures/}}
@@
 
+\todo{add microturb vel to tab 1}
+
 \sunanalog\ and \bizarreone\ were identified as a
@@
 We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
-full explanation of the methodology behind this search and only briefly describe
-the method here.
+full explanation of the methodology behind this search and only include
+a brief description here.
 For a given pair, we compute a marginalized likelihood ratio between the
-hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
-(2) that they have independent 3D velocity vectors, both given only observations
-of two components of the velocities (parallaxes and proper motions).
-We then select a sample of high-confidence comoving star pairs by making a
+hypotheses (1) that a given pair of stars share the same 3D velocity vector,
+and (2) that they have independent 3D velocity vectors, using only the
+astrometric measurements from \tgas\ (parallaxes and proper motions).
+We then select a sample of high-confidence comoving pairs by making a
 conservative cut on this likelihood ratio.
@@
 In a separate effort to study detailed chemical abundances of potential
-planet-hosting stars, \citet{2016ApJS..225...32B} obtained and analyzed high resolution
-spectra of both stars using the HIRES spectrograph on the Keck~I telescope.
+planet-hosting stars, high-resolution spectra of both stars were obtained using
+the HIRES spectrograph on the Keck~I telescope, and analyzed
+\citep{2016ApJS..225...32B}.
 The spectral resolution is $R\approx 70000$ and the wavelength coverage is

### 2017-08-14 paper/ms.tex
am i even getting somewhere

@@
 candidate comoving star pair in our recent search for comoving stars using the
-proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr\
-(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
+proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr.
 We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
@@
 \citealt{2016ApJS..225...32B}.
-The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
-\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
-work (\citealt{jmlithium}).
-We list all spectroscopic measurements including
-the absolute abundance\footnote{
+Additionally, the \elem{Li} doublet at $6707.6$~\AA\
+%--- clearly visible in both spectra (see \figname~\ref{fig:spec2}) ---
+for this sample was investigated in a separate work (\citealt{jmlithium}).
+We list all relevant astrometric and spectroscopic measurements
+including the absolute abundance\footnote{
   The absolute abundance of element \elem{X} is
@@
 Galactocentric phase-space coordinates for the two stars.
-The differences in positions and velocities are consistent with zero.
-\todo{should we instead show $|\Delta\boldsymbol{x}|$ and
-$|\Delta\boldsymbol{v}|$ computed from the 6D posterior samples?}
-
+The differences in velocities are consistent with zero.
 For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
-1.2~pc (\citealt{jiangtremaine2010}).
-%TODO
-\bizarreone\ and \sunanalog\ are likely a bound system that formed coevally.
-Thus, we expect the two stars to have identical metallicities and abundance patterns.
+1.2~pc (\citealt{Jiang:2010aa}).
+Thus, \bizarreone\ and \sunanalog\ are likely a bound system that formed coevally,
+and we expect the two stars to have identical metallicities and abundance patterns.
 However, one of the stars, \bizarreone\ is significantly more metal
@@
 relative to \elem{Fe}.
-Both stars have high surface \elem{Li} abundances, and the difference in
+\bizarreone\ also has a high surface \elem{Li} abundances, and the difference in
 \elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
@@
 
-The validity of the measured abundance differences is further demonstrated
-in \figname~\ref{fig:spec1} and \ref{fig:spec2} where we show
-segments of the spectra and models of the two stars
-used to measure their abundances.
+The validity of the measured abundance differences is further demonstrated in
+\figname~\ref{fig:spec1}, \ref{fig:spec2}, and \ref{fig:spec_lithium}, where we
+show segments of the spectra and models of the two stars used to measure their
+abundances (\citealt{2016ApJS..225...32B}).
 As expected from their reported metallicity difference ($\Delta\feh \approx 0.2$),
@@
 However, for lines of elements that are not as enhanced in \bizarreone\,
-the residuals are much smaller in amplitude.
-%Li?
+the residuals are much smaller in amplitude (\figname~\ref{fig:spec2}).
+The \elem{Li} doublet, analyzed in a separate work (Myles \etal\ in prep.),
+is clearly visible in the spectra of both stars, and is stronger in \bizarreone\
+(\figname~\ref{fig:spec_lithium}).
 
@@
 are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
+The statistical uncertainties for each parameter
+presented in \tablename~\ref{tab:kk} from \citealt{2016ApJS..225...32B}
+are estimated from repeated measurements of multiple spectra of the same stars.
+We note that while there may be systematic uncertainties (bias) in the elemental
+abundances of these two stars unconstrained by this procedure,
+the systematic uncertainties for these two solar-type ``twin-like'' stars in
+terms of $T_\mathrm{eff}$ and $\log{g}$, if any, are unlikely to wash out
+the observed abundance differences.
 

### 2017-08-15 paper/ms.tex
word treak and add JMB affil

@@
   New Haven, CT 06511, USA}
+\affil{Department of Astronomy, Columbia University, 550 West 120th Street,
+  New York, NY 10027, USA}
 
@@
 abundances of these two stars unconstrained by this procedure,
-the systematic uncertainties for these two solar-type ``twin-like'' stars in
-terms of $T_\mathrm{eff}$ and $\log{g}$, if any, are unlikely to wash out
-the observed abundance differences.
-
-%TODO: plot styles...
+the systematic uncertainties for these two solar-type ``twin-like'' stars
+with small differences in $T_\mathrm{eff}$ and $\log{g}$, if any, are unlikely to wash out
+the observed abundance differences of $\approx 0.2$~dex.
+
 \begin{figure}[htbp]

### 2017-08-21 paper/ms.tex
improve intro via DNS comments

@@
 \newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
+\newcommand*{\askjmb}[1]{{\bf #1}}
 
@@
 
-\author{David N. Spergel} % TODO: need ORCID
+\author{David N. Spergel}
 \affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
@@
   New York, NY 10010, USA}
-\author{Justin Myles} % TODO: need ORCID
+\author{Justin Myles}
 \affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
@@
 
-Wide binary stars are valuable tools for studying star and planet formation as well
-as Galactic dynamics and chemical evolution.
+Wide binary stars are valuable tools for studying star and planet formation as
+well as Galactic dynamics and chemical evolution.
 In the context of studying the evolution of the Milky Way, they are useful for
@@
 For example, the separation distribution of halo binaries has been used to
-constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
-On the other hand, they are also prime targets to test the chemical tagging
-hypothesis that stars from the same birthplace may be traced back using detailed
-chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
-A multiple-star system of any size that we believe are born together can serve
-this purpose, with massive open clusters at one extreme.
-Wide binaries are at the other extreme in that we may be less confident of the
-coevality of individual systems but they are much more abundant than larger
-systems like open clusters, rendering their statistics a meaningful indication
-of whether the hypothesis works.
-
-Wide binaries with similar or very different planetary architectures around the
-component stars have been used to connect a host star's chemistry to its
-planetary system.
-A differential analysis may reveal chemical signatures related to planet
-formation or accretion without any regard to Galactic chemical evolution as
-long as the two stars are assumed to be born together with identical
+constrain the mass of massive compact halo objects
+(\citealt{Yoo:2004aa,Quinn:2009,Allen:2014}).
+They can also be used to test the ``chemical tagging'' hypothesis that stars
+from the same birthplace may be traced back using detailed chemical abundance
+patterns as birth tags (\citealt{2002ARA&A..40..487F}).
+While any multiple-star system including massive open clusters can be used to
+test the hypothesis, wide binaries have the advantage of being extremely
+abundant, rendering their statistics a meaningful indication of whether the
+hypothesis works.
+
+Binary stars that form from the same birth cloud start with nearly identical
 composition.
-For close-in giant planets, it has been established that the planet-metallicity
-relation is primordial, and that the enhanced metallicity in giant
-planet-hosting stars likely promotes the formation of giant planets by
-increasing the availability of small particle condensates that form
-planetesimals (\citealt{Fischer:2005aa}).
+A differential analaysis of the chemical composition of binary stars can reveal
+their history through the chemical signatures related to planet formation or
+accretion regardless of the Galactic chemical evolution.
+\askjmb{
+For example, \citealt{Fischer:2005aa} showed that the higher metallicity in
+stars hosting close-in giant planets compared to those without likely promotes
+the formation of giant planets by increasing the availability of small particle
+condensates that form planetesimals.
+}
 On the other hand, if host stars are polluted after their birth by rocky
@@
 envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
-compared to their initial state.
+compared to their initial state (e.g., \citealt{Pinsonneault:2001aa}).
 Thus, differences in planet formation or accretion in two otherwise identical
@@
 
-Several systems in which at least one star hosts at least one planet
-have been studied so far with high resolution spectroscopy in this context
+High resolution spectroscopic studies of binary star systems hosting at least
+one planet
 (\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
-  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
-The results and interpretations of these studies are varied:
+  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab})
+have yielded varied results:
 while some systems appear to have undetectable differences
@@
 with higher-\Tcondens\ elements showing larger differences.
-The increasing abundance difference with condensation temperature has been
-attributed both to more yet-undiscovered rocky planets around the relatively
-refractory-poor star and to late time accretion of refractory-rich planetary
-material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
+A possible explanation for the increasing abundance difference with
+condensation temperature is that more yet-undiscovered rocky planets formed
+around the relatively refractory-poor star
+(\citealt{Ramirez:2015aa,Biazzo:2015aa}).
+Alternatively, late time accretion of refractory-rich planetary material to the
+relatively refractory-rich star can also produce the trend.
 The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
 and often at $\approx 0.05$~dex level making them challenging to detect even
-with a careful analysis of high-resolution high signal-to-noise ratio spectra.
-% maybe want to point out the former interpretation roots back to melendez+09
-% and some doubt to that interpretation...
-
-So far the strongest evidence for accretion of planetary material by a host
-star comes from spectral analysis of polluted white dwarfs (WDs).
+with a careful analysis of high-resolution, high signal-to-noise ratio spectra,
+and differential analyses of two stars that are very similar in their
+stellar parameters.
+
+Spectral analysis of polluted white dwarfs (WDs) currently provides the
+strongest evidence for accretion of planetary material by a host star
+(\citealt{2003ApJ...596..477Z,2010ApJ...722..725Z,2014A&A...566A..34K};
+see \citealt{2016NewAR..71....9F} for review).
 Because the gravitational settling times of elements heavier than \elem{He} in
-atmosphere is much shorter than the WD cooling time, detection of metals likely
-indicates the presence of a reservoir of dusty material around the WD.
-Indeed, many of the polluted WDs host a dusty debris disk detected
-in the infrared.
+atmosphere is much shorter than the WD cooling time
+(\citealt{1986ApJS...61..197P}), detection of metals likely indicates the
+presence of a reservoir of dusty material around the WD.
+Indeed, many of the polluted WDs host a dusty debris disk detected in the
+infrared (\citealt{1987Natur.330..138Z,1990ApJ...357..216G,2005ApJ...635L.161R,
+  2009ApJ...694..805F,2006ApJ...646..474K}).
 Some of the most dramatically polluted WDs show
@@
 Here, we report and discuss the discovery of a comoving pair of G stars,
-HD~240430 and HD~240429, with unusual chemical abundance differences
-that strongly suggest accretion of planetary material by the two stars.
+HD~240430 and HD~240429, with unusual chemical abundance differences that
+strongly suggest accretion of rocky planetary material by one of the two stars,
+HD~240430.
 Throughout the \documentname, we nickname the two stars \bizarreone\
 (HD~240430) and \sunanalog\ (HD~240429).
+In Greek mythology, Kronos and Krios were sons of Uranos and Gaia.
+Kronos notoriously devoured all of his children (except Zeus)
+to prevent the prophecy that one day he will be overthrown by them.
 We use the following convention for chemical abundances of stars: \elemH{X} is
@@
 \end{figure}
-
-\todo{add microturb vel to tab 1}
 

### 2017-08-28 paper/ms.tex
more lit summary and abstract edit

@@
   Stellar parameters determined from high-resolution Keck HIRES spectra
-  indicate that both stars are $\sim 4$~Gyr old,
-  yet both stars show very high surface \elem{Li} abundance for this age.
+  indicate that both stars are $\sim 4$~Gyr old.
   The more metal-rich of the two, HD~240430, shows an enhancement of refractory
@@
   a wide binary pair yet.
+  Additionally, it shows anomalously high surface lithium abundance
+  ($A(\elem{Li}=2.75$), higher by $0.5$~dex than its companion.
   The proximity in phase-space and ages between the two stars suggests that
@@
   refractory elements in its surface and convective envelope.
-  The other star HD~240429, ``Krios'', may also have had a similar accretion
-  event given its high surface \elem{Li} abundance but of much smaller amount
-  ($\approx 4$~\mearth).
-  %Follow-ups to study the existence and properties of the planetary systems
-  %around these stars will help illuminate planet-star interactions.
 \end{abstract}
@@
 
-\todo{might as well note no orbits ever established at these separations}
 \todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added}
+
+{\bf 16 Cygni A/B:}
+The chemical composition of this well know pair of solar-type stars (G1.5/G3)
+has been studied many times.
+The hotter star 16 Cyg A has no detected planets, but a M dwarf companion $\sim
+70$~AU away in projected separation which is probably physically associated
+(\citealt{2002ApJ...581..654P}), and may have affected planet formation process
+around the star (\citealt{1996ApJ...458..312J,2005MNRAS.363..641M}).
+The other star, 16 Cyg B, hosts a giant planet on an eccentric orbit ($e=0.63$,
+\citealt{1997ApJ...483..457C}).
+While past measurements of metallicity and abundance difference between the two stars
+claimed conflicting results (\citealt{2001ApJ...553..405L,2011ApJ...737L..32S}),
+recent studies using high quality spectra consistently reported that
+A is more metal rich than B by $\approx 0.04 \pm 0.005$~dex.
+However, there is still a disagreement between studies on
+whether abundance differences shows a correlation with $\Tcondens$ as well as
+its interpretation.
 
@@
 
-{\bf WASP-94A/WASP-94B:}
+{\bf WASP-94A/B:}
 Each star in a pair of F8 and F9 stars with super-solar metallicity
@@
 and granulation between the stars were considered, but none was favored.
+
+{\bf $\zeta^1/\zeta^2$ Reticuli (HD 20807/HD 20766):}
+With a projected separation of $\approx 3700$~AU, both solar-type stars in this pair have
+no detected planets.
+However, $\zeta^2$ hosts a debris disk detected via infrared excess
+(\citealt{2008ApJ...674.1086T}) as well as direct imaging
+(\citealt{2010A&A...518L.131E}).
+Both stars have super-solar metallicity of $\approx 0.2$~dex.
+A differential abundance analysis using high-resolution spectra
+shows that $\zeta^1$ is more metal rich than $\zeta^2$ by $\sim 0.02 \pm 0.003$~dex,
+and that there is a positive slope between the abundance differences of 24 species
+and $\Tcondens$.
+A possible explanation proposed is that the relative lack of refractory elements
+in $\zeta^2$ is because they are locked up in rocky bodies
+that make up its debris disk (\citealt{2016A&A...588A..81S}).
+
+{\bf HD~133131A/B:}
 

### 2017-09-08 paper/ms.tex
many changes
- move review to appendix
- many new refs
- 6Li
- remove krios accretion hypothesis

@@
 \newcommand{\estimates}{\ensuremath{\{\hat{\varpi_i},\hat{\mu_{\alpha,i}},\hat{\mu_{\delta,i}},\hat{v_{r,i}}\}}}
+\newcommand{\maccreted}{\ensuremath{15~\mearth}}
 
@@
   \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
+  % TODO: Hmmm...
   This is the largest and the most significant chemical difference found in
   a wide binary pair yet.
-  Additionally, it shows anomalously high surface lithium abundance
-  ($A(\elem{Li}=2.75$), higher by $0.5$~dex than its companion.
+  Additionally, it shows an anomalously high surface lithium abundance
+  ($A(\elem{Li})=2.75$), higher by $0.5$~dex than its companion.
   The proximity in phase-space and ages between the two stars suggests that
@@
   differences in metallicity and abundance patterns.
-  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
-  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
-  refractory elements in its surface and convective envelope.
+  We therefore suggest that the star HD~240430, ``Kronos'', accreted
+  \maccreted\ of rocky material after birth selectively enhancing the
+  refractory elements as well as lihtium in its surface and convective
+  envelope.
 \end{abstract}
@@
 composition.
-A differential analaysis of the chemical composition of binary stars can reveal
+A differential analysis of the chemical composition of binary stars can reveal
 their history through the chemical signatures related to planet formation or
@@
 High resolution spectroscopic studies of binary star systems hosting at least
-one planet
-(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
+one planet (\citealt{2011ApJ...740...76R,2014ApJ...790L..25T,Teske:2013aa,
+  Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
   Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab})
@@
 with higher-\Tcondens\ elements showing larger differences.
-A possible explanation for the increasing abundance difference with
-condensation temperature is that more yet-undiscovered rocky planets formed
-around the relatively refractory-poor star
+A possible explanation for the difference is that
+forming more gas giants or rocky planets leads to
+an overall or \Tcondens-dependent depletion
 (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
@@
 stellar parameters.
+We refer the readers to Appendix~\ref{app:review} for a review of
+a handful of individual pairs studied in their detailed chemical abundances
+(see also \citealt{2016arXiv161104064M}).
 
@@
 about the two stars relevant to the present discussion.
-In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
-the abundance difference between the pair.
+In \sectionname~\ref{sec:discussion} we discuss possible interpretations of the
+abundance difference between the pair.
 We summarize our discussions in \sectionname~\ref{sec:summary}.
-
-\subsection{
-  Review of Detailed Chemical Abundance Studies of Stars in Comoving Pairs}
-\label{sub:review}
-
-Anticipating the forthcoming discussion, we review and summarize a handful of
-wide binary systems that have been studied in their detailed chemical
-abundances so far with high-resolution spectroscopy.
-These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
-WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
-We focus on key characteristics of stars and planets, and interpretations of
-any trend in $\Delta\elemH{X}$ with \Tcondens.
-
-\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added}
-
-{\bf 16 Cygni A/B:}
-The chemical composition of this well know pair of solar-type stars (G1.5/G3)
-has been studied many times.
-The hotter star 16 Cyg A has no detected planets, but a M dwarf companion $\sim
-70$~AU away in projected separation which is probably physically associated
-(\citealt{2002ApJ...581..654P}), and may have affected planet formation process
-around the star (\citealt{1996ApJ...458..312J,2005MNRAS.363..641M}).
-The other star, 16 Cyg B, hosts a giant planet on an eccentric orbit ($e=0.63$,
-\citealt{1997ApJ...483..457C}).
-While past measurements of metallicity and abundance difference between the two stars
-claimed conflicting results (\citealt{2001ApJ...553..405L,2011ApJ...737L..32S}),
-recent studies using high quality spectra consistently reported that
-A is more metal rich than B by $\approx 0.04 \pm 0.005$~dex.
-However, there is still a disagreement between studies on
-whether abundance differences shows a correlation with $\Tcondens$ as well as
-its interpretation.
-
-{\bf HD~20782/HD~20781:}
-Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
-$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
-host close-in giant planets.
-HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
-orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
-Neptune-mass planets within 0.3~AU with moderately high eccentricity
-($e\sim0.1-0.3$).\footnote{
-  The two stars were monitored by \project{HARPS} campaign, and it has recently
-  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
-  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
-  within $\approx 0.35$~AU.}
-The measured abundances of 15 elements between the two stars are consistent
-with each other (\citealt{Mack:2014aa}).
-However, \citealt{Mack:2014aa} argued that there is a moderately significant
-($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
-increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
-Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
-the abundances of each star {\it individually}.
-They suggest that this slope is evidence that the stars accreted
-$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
-migration.
-
-{\bf HAT-P-1:}
-This pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
-different planetary systems:
-the secondary star is known to host one transiting giant planet
-while no planet has been discovered around the primary star.
-The two stars are identical
-in metallicities and abundances for 23 elements measured with
-the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
-Thus, it seems that the presence of close-in giant planet does not necessarily
-lead to atmospheric pollution of its host star.
-
-{\bf HD~80606/HD~80607:}
-Similar to HAT-P-1, no significant chemical difference is found between two
-common proper motion G5 stars with super-solar metallicity ($\feh \approx
-0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
-HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).
-
-{\bf XO-2N/XO-2S:}
-This pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
-has received much attention due to possibly the most robust and significant
-difference between the component stars.
-XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
-masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
-0.15$) orbits at $<0.5$~AU.
-%TODO: check following with Biazzo+
-All measured elements including \elem{Fe} are enhanced in XO-2N relative to
-XO-2S, and the difference shows a significant correlation with \Tcondens\
-(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
-\citealt{Teske:2013aa}).
-At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
-difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
-
-\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
-in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
-giant planets around XO-2S, following a similar interpretation of
-\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
-In this scenario, forming planets in the protoplanetary disk are supposed to
-``lock'' heavier elements to the core of gas giant planets as well as some
-volatile elements in their envelopes. Then, the host star will accrete {\it
-  gas} depleted in metals compared to their protostellar condition.
-By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
-of gas occurs in terms of how much mass is in the convective envelope of the
-host star, they can match the mass difference of gas giant planets around each
-star, which is at least $1~\mjupiter$.
-On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
-\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
-Earth and CM chondrite-like material can explain the trend either as refractory
-{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
-refractory enhancement in XO-2N by late time accretion in which case the
-opposite would be true.
-
-{\bf WASP-94A/B:}
-Each star in a pair of F8 and F9 stars with super-solar metallicity
-($\feh\approx 0.3$) hosts a hot Jupiter.
-The planet around WASP-94A is transiting with a misaligned, probably retrograde
-circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
-massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
-WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
-elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
-elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
-uncertainty of $0.006$~dex among all elements
-resulting in a statistically significant non-zero slope between
-$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
-  %TODO: double check the following statement
-  Note that the condensation
-  temperature $\Tcondens$ used is for solar system composition
-  gas, which can differ from that of higher metallicity gas.}
-Multiple possibilities related to the formation and evolution
-of planetary systems around each star as well as causes unrelated to planets
-such as dust cleansing during the fully convective phase or different rotation
-and granulation between the stars were considered, but none was favored.
-
-{\bf $\zeta^1/\zeta^2$ Reticuli (HD 20807/HD 20766):}
-With a projected separation of $\approx 3700$~AU, both solar-type stars in this pair have
-no detected planets.
-However, $\zeta^2$ hosts a debris disk detected via infrared excess
-(\citealt{2008ApJ...674.1086T}) as well as direct imaging
-(\citealt{2010A&A...518L.131E}).
-Both stars have super-solar metallicity of $\approx 0.2$~dex.
-A differential abundance analysis using high-resolution spectra
-shows that $\zeta^1$ is more metal rich than $\zeta^2$ by $\sim 0.02 \pm 0.003$~dex,
-and that there is a positive slope between the abundance differences of 24 species
-and $\Tcondens$.
-A possible explanation proposed is that the relative lack of refractory elements
-in $\zeta^2$ is because they are locked up in rocky bodies
-that make up its debris disk (\citealt{2016A&A...588A..81S}).
-
-{\bf HD~133131A/B:}
 
@@
 
-The fact that the two stars share nearly identical space motion
-at a separation of $< 1$~pc strongly supports that the pair is coeval.
-We therefore consider other age indicators apart from their phase-space
-coordinates to assess the ages and coevality of the two stars.
-First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
-we can constrain the ages of the two stars by
-comparing these values to theoretical isochrones.
-We perform isochrone fitting to these values using the Yale-Yonsei model
-isochrones (\citealt{2013ApJ...776...87S}).
-The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
-parallaxes, $B$-band magnitudes, and their errors.
-The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
-$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
+Apart from their closeness in phase-space coordinates,
+we can constrain the ages of the two stars
+given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$
+by comparing these values to theoretical isochrones.
+We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
+and $B-V$ colors to obtain bolometric luminosities of the two stars
+(\citealt{2003AJ....126..778V}).
+We then combine the luminosities with effective temperature, \elemH{Fe}, and
+\elemH{Si} in order to interpolate the age, mass, and radius of each star using
+a grid of Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
+The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
+$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
 consistent with them being coeval.
 
-The surface lithium abundance in a sun-like star decreases with its age due to
+{\bf
+The surface lithium abundance in a Sun-like star decreases with its age due to
 mixing induced by convection or rotation, which brings the lithium into the
@@
 burning.
-Thus, surface lithium abundance is an indicator of stellar ages.
-The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
-of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
-solar lithium abundance and rotational profile (\citealt{2005Sci...309.2189C}).
-The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
-among all measured elements.
-This translates to a $\sim 500$~Myr difference in age.
+Thus, surface lithium abundance can be an indicator of stellar ages,
+especially whether the star is very young ($\lesssim 1$~Gyr).
+The absolute $\elem{Li}$ abundance of solar-type stars also correlates steeply
+with the effective temperature (e.g., \citealt{Chen2001,2012ApJ...756...46R}).
+Generally, cooler stars with larger convective envelope have lower \elem{Li}
+abundance.
+The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\
+is typical for its \teff.
+On the other hand, the lithium abundance ($A(\elem{Li}) = 2.75$) of \bizarreone,
+which has lower \teff\ than \sunanalog, is not only higher than that of
+\sunanalog\ but also much higher compared to other field stars of similar \teff.
 Given the overall higher metal abundances and the peculiar abundance patterns
@@
 abundance means a younger age or something else.
-For example, the presence of $\elem{Li}$-rich red giant stars has been
-attributed to the engulfment of substellar companions such as gas giant planets
-or brown dwarfs which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
-
-In fact, the surface lithium abundance is the only indication that points to
-younger ages.
-If the two stars are indeed only several hundred Myrs old at most,
-they are expected to be part of a larger comoving group of stars.
-However, as we mention above, there is no evidence in our search of comoving pairs
-using \tgas\ that the two stars belong to a larger group of young stars.
+For example, \citealt{Casey:2016aa} attributes the presence of $\elem{Li}$-rich
+red giant stars to the engulfment of substellar companions such as gas giant
+planets or brown dwarfs which may replenish $\elem{Li}$.
+}
+
+The surface lithium abundance of \bizarreone\ is the only indicator of a
+younger age.
+If the two stars were only several hundred Myrs old, then
+they may have been part of a larger comoving group of stars.
+However, as we mention above, there is no evidence in our search of comoving
+pairs using \tgas\ that the two stars belong to a larger group of young stars.
 Very young stars often show signs of activity such as
 X-ray emission from magnetic activity, emission lines, or infrared excess due to
-circumstellar disks (\todo{needs refernces}).
+circumstellar disks (\citealt{1999ARA&A..37..363F,1987ApJ...312..788A}).
 We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
@@
 distributions.
+%
 The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
@@
 The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age (\todo{needs references for vertical action as age indicator}).
+an older age (\citealt{Wielen:1977,Aumer:2016}).
 We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
-old main sequence stars, and that their unusually high \elem{Li} abundance
-requires an alternative explanation.
+old main sequence stars, and that the unusually high \elem{Li} abundance of
+\bizarreone\ requires an alternative explanation.
 
@@
 
-Although the data described above strongly suggests that the two stars are
-coeval, we may still consider scenarios in which the two stars are not actually
-born together.
+While the data described above strongly suggests that the two stars are coeval,
+this subsection explores the possibility that this pair is not a primordial
+binary.
 Two stars unrelated at birth may end up in a binary system via a binary-single
@@
 number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
-$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
-any direction, the rate of exchange scattering is
+$10$~km\,s$^{-1}$, the rate of exchange scattering is
 \begin{eqnarray}
@@
 \end{eqnarray}
-which is low enough to be negligible.
-
-In fact, any exchange scattering scenario is unsatisfactory as typical
-field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
-unlikely to show the abundance difference pattern observed.
-In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
-\bizarreone-\sunanalog\ with the distribution of abundance differences,
-$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
-\feh\ as \bizarreone\ and \sunanalog.
+low enough to be negligible.
+
+An exchange scattering scenario is unlikely to be able to explain
+the observed abundance difference pattern of \bizarreone\ and \sunanalog.
+We test this by randomly drawing pairs of stars in the sample of
+\citealt{2016ApJS..225...32B} from two \feh\ bins at $\feh = 0 \pm 0.025$
+and $\feh = 0.2 \pm 0.025$, each similar to \sunanalog\ and \bizarreone.
+In \figname~\ref{fig:deltaXH}, we compare the observed abundance difference of
+\bizarreone-\sunanalog\ with the distribution of abundance differences
+from 300 random pairs.
 We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
@@
 
-\todo{HOGG: to provide some theoretical account adding to the above empirical evidence.}
-
 \subsection{Chemical Inhomogeneity in Star Formation}
@@
 
-Assuming that the two stars were born together, one possibility to
-explain the chemical difference is that there was chemical inhomogeneity within
-the birth cloud.
-However, there is already ample evidence against such a scenario.
-First, none of the other seven similar wide binaries examined in
+In this subsection, we explore the hypothesis that chemical inhomogeneity
+within the birth cloud is the source of the observed abundance difference.
+There is ample evidence against this scenario as most wide binaries show in
+\feh\ less than $0.02$~dex (\citealt{Desidera:2004aa,Gratton:2001aa}.
+In the cases in which a significant difference is detected
+with high-precision abundance measurements (see \sectionname~\ref{app:review}),
+the difference is typically $\sim 0.05$~dex.
+Consistent with these results,
+none of the other seven similar wide binaries examined in
 \citealt{2016ApJS..225...32B} show the same level of differences in abundances.
@@
 compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
-(\figname~\ref{fig:deltaXH}).
-This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
-23 wide binaries of late F to K dwarfs, and found most pairs show a difference
-in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
-Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
-binaries have the same chemical composition with $\gtrsim 0.01$~dex
-uncertainties.
+(\figname~\ref{fig:deltaXH}, black lines).
 Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
-not likely due to chemical inhomogeneity in the birth cloud.
+unlikely to be due to chemical inhomogeneity in the birth cloud.
 
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{toycalc.png}
+  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
   \caption{
-    Comparing the observed abundance difference vs. \Tcondens\ rank
-    to the expected change in solar surface abundance after adding $20$~\mearth\ of
-    material with bulk Earth composition (\citealt{mcdonough2001composition}).
-    The assumed mass fraction in the convective zone is $0.03$.
-    All metals are ranked by their \Tcondens\ for solar composition gas,
-    and the condensation temperature may be read from the gray line and right y-axis,
-    same as in \figname~\ref{fig:relabun_tcrank}.
-    Locations of the elements measured for \bizarreone-\sunanalog\ pair are
-    indicated by a vertical line and its symbol.
+    Comparing the observed abundance difference (blue circles) to the expected
+    change in solar surface abundance after adding \maccreted\ of material
+    with bulk Earth composition (\citealt{2003TrGeo...2..547M}; black open and
+    filled circles).
+    The assumed mass fraction in the convective zone is $0.02$.
+    All astronomical metals are ordered by their \Tcondens\ for solar
+    composition gas on the $x$-axis.
+    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
+    in filled circles, while those without a measurement are left open.
     The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
     suggests that the abundance difference may be due to accretion of
-    $20$~\mearth\ of rocky planetary material.
-    The element \elem{Li} is off the plot and indicated with a red arrow
-    (see text for details).
+    $15$~\mearth\ of rocky planetary material.
+    The element \elem{Li} is off the plot and indicated in the inset.
   }
@@
 abundances is accretion of planetary material after birth.
-Instabilities may develop in a multi-planet system due to its chaotic nature
-which may lead to planet engulfment or ejection by the host star
-(\todo{needs references}).
-%TODO: kozai?
+In a multi-planet system, dynamical instabilities triggered by planet-planet
+scattering\cite{1996Sci...274..954R,1996Natur.384..619W} or encounters with a
+field star\cite{Malmberg:2011aa} can lead to planet ejection or accretion.
 Indeed, it is an important goal of many exoplanet studies
@@
 is larger than the differences seen in any other pairs studied so far.
-Strikingly, the five under-enhanced elements in \bizarreone\
+The five under-enhanced elements in \bizarreone\
 relative to \sunanalog\ are the five most volatile in all elements measured.
@@
 combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
-strongly suggests that accretion of rocky material has occured in \bizarreone.
+strongly suggests that accretion of rocky material has occurred in \bizarreone.
 
@@
   \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
-    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
+    + f_{X,\mathrm{acc}}\,M_\mathrm{acc}}
     {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
@@
 where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
-We take the composition of bulk Earth from a chondritic model of the Earth
-(\citealt{mcdonough2001composition}).
-Similar calculations have been performed by \citet{Chambers:2010aa} and
+We assume $f_\mathrm{CZ} = 0.02$ (\citealt{2013ApJ...776...87S}),
+and take the composition of bulk Earth from a chondritic model of the Earth
+(\citealt{2003TrGeo...2..547M}).
+Similar calculations have been performed by e.g., \citet{Chambers:2010aa},
 \citet{Mack:2014aa,Mack:2016aa}.
@@
 Figure~\ref{fig:toycalc} shows the expected change of surface abundances of
-metals in a Sun-like star after $20~\mearth$ of material with composition of
+metals in a Sun-like star after \maccreted\ of material with composition of
 bulk Earth is added.
@@
 protoplanetary disk.
-The trend resulting from adding $20~\mearth$ of bulk Earth
+The trend resulting from adding \maccreted\ of bulk Earth
 provides an overall good match to the observed $\Delta\elemH{X}$,
 suggesting that the refractory-enhanced star, \bizarreone\,
-accreted $20~\mearth$ more of rocky planetary material than \sunanalog.
+accreted \maccreted\ more of rocky planetary material than \sunanalog.
 
@@
 accretion scenario.
-Because Li is present in either carbonaceous chondrites or bulk Earth with
-a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition}),
-but is depleted quickly within the first couple of Gyrs on the surface of a
-Sun-like star, accretion of either material at later times will significantly
-replenish the lithium on the star's surface.
-For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
-material would result in $\Delta\elemH{Li} \approx 1.6$~dex (which
-is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
-Incidentally, the star under examination, \bizarreone, has an age (informed by
-stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
-Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
-to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
-enhancement in its \elem{Li}.
-This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
+Because Li is present in either carbonaceous chondrites or bulk Earth with a
+concentration of $1-1.5$~ppm in mass (\citealt{2003TrGeo...2..547M}), but
+is depleted quickly within the first couple of Gyrs on the surface of a
+Sun-like star (\askjmb{CITE?}), accretion of either material at later times
+will significantly replenish the lithium on the star's surface.
+For the present-day Sun ($A(\elem{Li}) = 1.05$), the accretion of \maccreted\ of
+bulk Earth-like material would result in $\Delta\elemH{Li} \approx 1.65$~dex
+(see the inset of \figname~\ref{fig:toycalc}).
+This closely matches what we find: the \elem{Li} abundance of \bizarreone\ is
 $A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
-approximately $1.65$~dex higher than the solar value of $1.1$~dex
-(\todo{needs reference}).
-Furthermore, this implies that the accretion event should have happened very
-recently, or at least within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
-
-What about \sunanalog?
-Considering its age of $4.00_{-1.56}^{+1.51}$~Gyr, \sunanalog\ is also enhanced
-in \elem{Li} compared to other stars of similar ages by $\approx 1$~dex.
-This enhancement puts an upper limit on the accreted mass to be
-$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
-(\citealt{mcdonough2001composition}).
-Unlike \bizarreone, we cannot know the pre-accretion abundances of
-\sunanalog.\footnote{
-  Strictly speaking, we can never know the pre-accretion abundances
-  for \bizarreone\ either.
-  We only have an {\it approximate} idea that this is not far from a solar-twin
-  star \sunanalog, and because the deviation from this ``anchor'' star is
-  large, it is reasonable to consider accretion by the Sun.
-  In reality, \sunanalog\ may as well have had its own accretion history,
-  which indeed seems to be the case according to its \elem{Li} abundance.
-}
-However, we note that the span of abundance difference between highly volatile
-elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
-as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
-0.05$~dex.
-This is comparable to the abundance difference between N, Na and Fe in
-\sunanalog.
-It is also interesting that \sunanalog\ shows a deficit in the same volatile
-and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
-\elem{Mn}) relative to Fe as in \bizarreone.
-Thus, we conclude that \sunanalog\ is also likely to have had a similar
-accretion event, but the amount of accretion was at least 5 time
-smaller than \bizarreone.
-
-%TODO: augment this paragraph
-% - more geochemical study references
+approximately $1.7$~dex higher than the solar value.
+
 We stress that while the calculation carried out is useful in
@@
 In addition, the composition of bulk Earth has some uncertainties.
-For example, the reported bulk Earth concentration of the siderphile element
-\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
-While the latter value from \citealt{mcdonough2001composition} has been used in
-our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
-to an even closer agreement.
+For example, the reported bulk Earth concentration of the siderophile element
+\elem{Mn}, varies from $800$ to $\approx 2000$~ppm
+(\citealt{1998psc..book.....L,mcdonough2001composition,2003TrGeo...2..547M})
+mainly due to the uncertainty of the Earth's core composition.
 Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
@@
 
+The fractional mass in the convective zone of solar-type stars
+decrease dramatically in the first Gyr,
+and then stays nearly constant at $\approx 2$~\% (\citealt{2013ApJ...776...87S}).
+Because the accreted mass $M_\mathrm{acc}$ is proportional to $f_\mathrm{CZ}$,
+given the large metallicity enhancement ($\approx 0.2$~dex),
+the accretion must have happened after a thin convective envelop is established.
+Otherwise, the accreted mass would be unreasonably high.
+Thus, it is plausible that a dynamical process after the planet formation ended
+is responsible for pushing rocky planets in.
+
+{\bf
+Finally, we mention that if the hypothesized accretion is
+\askjmb{recent (HOW RECENT?)},
+detection of $^6 \elem{Li}$ provides a strong test for this
+scenario.
+This isotope of \elem{Li} is destroyed at even lower temperatures than
+$^7\elem{Li}$, and theoretically expected to be absent
+(\citealt{1997ARA&A..35..557P}).
+However, an accretion of rocky material could have replenished $^6 \elem{Li}$.
+Because $^6\elem{Li}$ lines are slightly longer in wavelengths,
+presence of $^6\elem{Li}$ increases the asymmetry of \elem{Li} $6707.6$ feature.
+This is a very subtle effect that requires a careful modelling effort
+and a higher signal-to-noise, higher resolution spectra
+(see e.g., \citealt{Israelian:2001,2002MNRAS.335.1005R}).
+Such investigation was not warranted by the current data (\citealt{jmlithium}).
+}
+
 \section{Summary}
@@
 
-We report the discovery of a comoving pair of bright
+We report and discuss the discovery of a comoving pair of bright
 solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
@@
 \elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
-The two stars also have anomalously high surface \elem{Li} abundance compared
-to their ages of $\sim 4$~Gyr.
+It also has an anomalously high surface \elem{Li} abundance for its age of
+$\sim 4$~Gyr, and its effective temperature very close to that of the Sun.
 We consider that the comoving pair may have formed from two stars of different
-birth origins in a exchange scattering event, or that there may be chemical
-inhomogeneity in the birth cloud, and find both unlikely.
+birth origins in a exchange scattering event
+(\sectionname~\ref{sub:exchange_scattering}), or that there may be chemical
+inhomogeneity in the birth cloud
+(\sectionname~\ref{sub:chemical_inhomogeneity_in_star_formation}) to find
+both unlikely.
 
 In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
-abundance, we consider accretion of planetary material as the cause.
-We argue that a recent accretion of $20$~\mearth\ of bulk Earth
-composition to \bizarreone\ can explain the enhancement in both refractory
-elements and lithium.
-For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
-we put an upper limit of $\approx 4$~\mearth\ on the accreted mass
-based on the \elem{Li} concentration of carbonaceous chondrites and bulk Earth.
-While the case is not as clear as \bizarreone\ without a chemical reference star,
-the range of abundances from volatile to refractory elements is
-similar to that expected from $\approx 4$~\mearth\ accretion of bulk Earth.
-It is unclear what triggered the accretions to both stars.
-One possibility is that a fly-by field star may have
-perturbed the planetary systems of both stars.
+abundance of \bizarreone, we consider accretion of planetary material as the
+cause (\sectionname~\ref{sub:accretion}).
+We argue that an accretion of \maccreted\ of bulk Earth composition to
+\bizarreone\ after its thin convective zone is in place can explain the
+enhancement in both refractory elements and lithium.
+What triggered the planet engulfment in the two comoving stars remains unclear.
+One possibility is that a fly-by interaction with a field star could have
+triggered eccentricity excitation of outer planets around each star, which may
+have propagated inward through planet-planet scattering, leading to the
+accretion of inner rocky planets (\citealt{Zakamska:2004aa,Malmberg:2011aa}).
+If this is the case, there may be surviving, highly-eccentric giant planets.
+The two stars have not been included in any publicly released data from planet
+search programs, however, outer eccentric planets are potentially detectable
+with future data releases of the \gaia\ mission.
 
@@
 
+\appendix
+\section{
+  Review of Detailed Chemical Abundance Studies of Stars in Comoving Pairs}
+\label{app:review}
+
+We review and summarize a handful of
+wide binary systems that have been studied in their detailed chemical
+abundances so far with high-resolution spectroscopy.
+These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
+WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
+We focus on key characteristics of stars and planets, and interpretations of
+any trend in $\Delta\elemH{X}$ with \Tcondens.
+
+{\bf 16 Cygni A/B:}
+The chemical composition of this well know pair of solar-type stars (G1.5/G3)
+has been studied many times.
+The hotter star 16 Cyg A has no detected planets, but a M dwarf companion $\sim
+70$~AU away in projected separation which is probably physically associated
+(\citealt{2002ApJ...581..654P}), and may have affected planet formation process
+around the star (\citealt{1996ApJ...458..312J,2005MNRAS.363..641M}).
+The other star, 16 Cyg B, hosts a giant planet on an eccentric orbit ($e=0.63$,
+\citealt{1997ApJ...483..457C}).
+While past measurements of metallicity and abundance difference between the two
+stars claimed conflicting results
+(\citealt{2001ApJ...553..405L,2011ApJ...737L..32S}), recent studies using high
+quality spectra (\citealt{2011ApJ...740...76R,2014ApJ...790L..25T})
+consistently reported that A is more metal rich than B by $\approx 0.04 \pm
+0.005$~dex.
+However, there is still a disagreement between studies on
+whether abundance differences shows a correlation with $\Tcondens$ as well as
+its interpretation.
+
+{\bf HD~20782/HD~20781:}
+Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
+$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
+host close-in giant planets.
+HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
+orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
+Neptune-mass planets within 0.3~AU with moderately high eccentricity
+($e\sim0.1-0.3$).\footnote{
+  The two stars were monitored by \project{HARPS} campaign, and it has recently
+  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
+  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
+  within $\approx 0.35$~AU.}
+The measured abundances of 15 elements between the two stars are consistent
+with each other (\citealt{Mack:2014aa}).
+However, \citealt{Mack:2014aa} argued that there is a moderately significant
+($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
+increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
+Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
+the abundances of each star {\it individually}.
+They suggest that this slope is evidence that the stars accreted
+$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
+migration.
+
+{\bf HAT-P-1:}
+This pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
+different planetary systems:
+the secondary star is known to host one transiting giant planet
+while no planet has been discovered around the primary star.
+The two stars are identical
+in metallicities and abundances for 23 elements measured with
+the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
+Thus, it seems that the presence of close-in giant planet does not necessarily
+lead to atmospheric pollution of its host star.
+
+{\bf HD~80606/HD~80607:}
+Similar to HAT-P-1, no significant chemical difference is found between two
+common proper motion G5 stars with super-solar metallicity ($\feh \approx
+0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
+HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).
+
+{\bf XO-2N/XO-2S:}
+This pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
+has received much attention due to possibly the most robust and significant
+difference between the component stars.
+XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
+masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
+0.15$) orbits at $<0.5$~AU.
+%TODO: check following with Biazzo+
+All measured elements including \elem{Fe} are enhanced in XO-2N relative to
+XO-2S, and the difference shows a significant correlation with \Tcondens\
+(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
+\citealt{Teske:2013aa}).
+At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
+difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
+
+\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
+in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
+giant planets around XO-2S, following a similar interpretation of
+\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
+In this scenario, forming planets in the protoplanetary disk are supposed to
+``lock'' heavier elements to the core of gas giant planets as well as some
+volatile elements in their envelthe metal content ($Z/X$) of gas giant planets and when the accretion
+of gas occurs in terms of how much mass is in the convective envelope of the
+host star, they can match the mass difference of gas giant planets around each
+star, which is at least $1~\mjupiter$.
+On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
+\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
+Earth and CM chondrite-like material can explain the trend either as refractory
+{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
+refractory enhancement in XO-2N by late time accretion in which case the
+opposite would be true.
+
+{\bf WASP-94A/B:}
+Each star in a pair of F8 and F9 stars with super-solar metallicity
+($\feh\approx 0.3$) hosts a hot Jupiter.
+The planet around WASP-94A is transiting with a misaligned, probably retrograde
+circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
+massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
+WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
+elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
+elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
+uncertainty of $0.006$~dex among all elements
+resulting in a statistically significant non-zero slope between
+$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
+  %TODO: double check the following statement
+  Note that the condensation
+  temperature $\Tcondens$ used is for solar system composition
+  gas, which can differ from that of higher metallicity gas.}
+Multiple possibilities related to the formation and evolution
+of planetary systems around each star as well as causes unrelated to planets
+such as dust cleansing during the fully convective phase or different rotation
+and granulation between the stars were considered, but none was favored.
+
+{\bf $\zeta^1/\zeta^2$ Reticuli (HD 20807/HD 20766):}
+With a projected separation of $\approx 3700$~AU, both solar-type stars in this pair have
+no detected planets.
+However, $\zeta^2$ hosts a debris disk detected via infrared excess
+(\citealt{2008ApJ...674.1086T}) as well as direct imaging
+(\citealt{2010A&A...518L.131E}).
+Both stars have super-solar metallicity of $\approx 0.2$~dex.
+A differential abundance analysis using high-resolution spectra
+shows that $\zeta^1$ is more metal rich than $\zeta^2$ by $\sim 0.02 \pm 0.003$~dex,
+and that there is a positive slope between the abundance differences of 24 species
+and $\Tcondens$.
+A possible explanation proposed is that the relative lack of refractory elements
+in $\zeta^2$ is because they are locked up in rocky bodies
+that make up its debris disk (\citealt{2016A&A...588A..81S}).
+
+{\bf HD~133131A/B:}
+For this metal-poor ($\feh\approx -0.3$), old ($\sim 9.5$~Gyr) pair of
+solar-type stars, high-precision radial velocity monitoring recently revealed
+several planets (\citealt{Teske:2016ab}): star A hosts two eccentric giant
+planets at $\approx 1.4$ and $\approx 5$~AU while star star B hosts a longer
+period giant planet at $\approx 6.5$~AU.
+\citealt{Teske:2016ab} measured a deficit of $0.03 \pm 0.017$~dex in
+refractory elements in A relative two B without any conclusive interpretation.
+
 \end{document}

### 2017-09-08 paper/ms.tex
missed notation change

@@
 where $m_X$ is the mass of each element in e.g., atomic mass unit.
-Assuming that the added material has a total mass $M_\mathrm{add}$, and the
-mass fraction in each element $f_{X,\mathrm{add}}$,
+Assuming that the accreted material has a total mass $M_\mathrm{acc}$, and the
+mass fraction in each element $f_{X,\mathrm{acc}}$,
 the abundance difference is

### 2017-09-10 paper/ms.tex
spergels orcid
abstract edits

@@
 
-\author{David N. Spergel}
+\author[0000-0002-5151-0006]{David N. Spergel}
 \affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
@@
   chemical abundances.
-  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
+  The two stars have an estimated 3D separation of $\approx 0.6$~pc ($\approx 0.01$~pc tangentially) at a distance of
   $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
@@
   The more metal-rich of the two, HD~240430, shows an enhancement of refractory
-  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
-  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
+  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex and a marginal
+  enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
   \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
@@
   a wide binary pair yet.
-  Additionally, it shows an anomalously high surface lithium abundance
+  Additionally, HD~240430 shows an anomalously high surface lithium abundance
   ($A(\elem{Li})=2.75$), higher by $0.5$~dex than its companion.
@@
   We therefore suggest that the star HD~240430, ``Kronos'', accreted
-  \maccreted\ of rocky material after birth selectively enhancing the
-  refractory elements as well as lihtium in its surface and convective
+  \maccreted\ of rocky material after birth, selectively enhancing the
+  refractory elements as well as lithium in its surface and convective
   envelope.

### 2017-09-10 paper/ms.tex
intro

@@
 \newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
+\newcommand{\apw}[1]{{\color{purple}APW asks: #1}}
 \newcommand*{\askjmb}[1]{{\bf #1}}
@@
 patterns as birth tags (\citealt{2002ARA&A..40..487F}).
-While any multiple-star system including massive open clusters can be used to
+While any multiple-star system, including massive open clusters, can be used to
 test the hypothesis, wide binaries have the advantage of being extremely
@@
 their history through the chemical signatures related to planet formation or
-accretion regardless of the Galactic chemical evolution.
+accretion regardless of Galactic chemical evolution.
 \askjmb{
-For example, \citealt{Fischer:2005aa} showed that the higher metallicity in
-stars hosting close-in giant planets compared to those without likely promotes
+For example, \citealt{Fischer:2005aa} showed that higher metallicity
+stars more likely host close-in giant planets, which likely promotes
 the formation of giant planets by increasing the availability of small particle
@@
 forming more gas giants or rocky planets leads to
-an overall or \Tcondens-dependent depletion
+an overall or \Tcondens-dependent depletion of higher-\Tcondens\ elements that
+eventually accrete onto the host star
 (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
 Alternatively, late time accretion of refractory-rich planetary material to the
-relatively refractory-rich star can also produce the trend.
+relatively refractory-rich star can also produce the trend \apw{do you mean "relatively refractory-poor star" instead?}.
 The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
-and often at $\approx 0.05$~dex level making them challenging to detect even
+and often closer to $\approx 0.05$~dex, making them challenging to detect even
 with a careful analysis of high-resolution, high signal-to-noise ratio spectra,

### 2017-09-10 paper/ms.tex
discussion and summary

@@
 We discuss the possible origins of the peculiar abundance differences of
-\bizarreone-\sunanalog.
+\bizarreone\ \& \sunanalog.
 We first discuss the ages and coevality of the stars in this pair, and consider
@@
 Generally, cooler stars with larger convective envelope have lower \elem{Li}
-abundance.
+abundances.
 The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\
@@
 In a multi-planet system, dynamical instabilities triggered by planet-planet
-scattering\cite{1996Sci...274..954R,1996Natur.384..619W} or encounters with a
-field star\cite{Malmberg:2011aa} can lead to planet ejection or accretion.
+scattering (\citealt{1996Sci...274..954R,1996Natur.384..619W}) or encounters with a
+field star (\citealt{Malmberg:2011aa}) can lead to planet ejection or accretion.
 Indeed, it is an important goal of many exoplanet studies
@@
 $\approx 0.2$~dex?
-We carry out simple toy calculations of expected $\Delta\elemH{X}$
-in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
+We carry out simple toy calculations of the expected $\Delta\elemH{X}$
+in a Sun-like star's atmosphere by adding a certain mass of bulk Earth composition
 under these simplifying assumptions:
 \begin{itemize}
-  \item The material added is instantly and completely mixed.
+  \item The material added is instantly and completely mixed through the star's convective zone.
   \item The atmospheric composition that we measure is identical throughout
@@
 \begin{equation}
-  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
+  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} \, m_X}{\Sigma_X 10^{\elemH{X}} \, m_X}
 \end{equation}
-where $m_X$ is the mass of each element in e.g., atomic mass unit.
+where $m_X$ is the mass of each element in, e.g., atomic mass unit.
 Assuming that the accreted material has a total mass $M_\mathrm{acc}$, and the
@@
 (\citealt{2003TrGeo...2..547M}).
-Similar calculations have been performed by e.g., \citet{Chambers:2010aa},
+Similar calculations have been performed by, e.g., \citet{Chambers:2010aa},
 \citet{Mack:2014aa,Mack:2016aa}.
@@
 bulk Earth is added.
-A volatility trend that more volatile (low \Tcondens) elements are more
+A volatility trend such that more volatile (low \Tcondens) elements are more
 depleted in the Earth relative to CI or other carbonaceous chondrites
@@
 This trend is presumed to be closely related to the formation of terrestrial
-planets and, in particular to the radial temperature gradient in a
+planets and, in particular, to the radial temperature gradient in a
 protoplanetary disk.
@@
 concentration of $1-1.5$~ppm in mass (\citealt{2003TrGeo...2..547M}), but
-is depleted quickly within the first couple of Gyrs on the surface of a
+is depleted quickly within a few gigayears on the surface of a
 Sun-like star (\askjmb{CITE?}), accretion of either material at later times
@@
 The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
-all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
-enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
+all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while
+under-enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
 \elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
@@
 In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
-abundance of \bizarreone, we consider accretion of planetary material as the
-cause (\sectionname~\ref{sub:accretion}).
+abundance of \bizarreone, we consider the accretion of planetary material as the
+most plausible cause (\sectionname~\ref{sub:accretion}).
 We argue that an accretion of \maccreted\ of bulk Earth composition to

### 2017-09-11 paper/ms.tex
Minor edits to clarify; corner attribution

@@
 \newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
-\newcommand{\apw}[1]{{\color{purple}APW asks: #1}}
 \newcommand*{\askjmb}[1]{{\bf #1}}
@@
   chemical abundances.
-  The two stars have an estimated 3D separation of $\approx 0.6$~pc ($\approx 0.01$~pc tangentially) at a distance of
+  The two stars have an estimated 3D separation of $\approx 0.6$~pc
+  ($\approx 0.01$~pc projected) at a distance of
   $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
@@
 forming more gas giants or rocky planets leads to
-an overall or \Tcondens-dependent depletion of higher-\Tcondens\ elements that
-eventually accrete onto the host star
+an overall or \Tcondens-dependent depletion of high-\Tcondens\ elements in
+gas that eventually accretes onto the host star
 (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
-Alternatively, late time accretion of refractory-rich planetary material to the
-relatively refractory-rich star can also produce the trend \apw{do you mean "relatively refractory-poor star" instead?}.
+Alternatively, late time accretion of refractory-rich planetary material can
+also produce the trend by enhancing the abundance of high-\Tcondens\ elements
+in one of the two stars instead.
 The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
@@
 
-%TODO: corner.py
 %TODO: data/code available
@@
   \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
+  \texttt{corner.py} (\citealt{corner}),
   \texttt{emcee} (\citealt{2013PASP..125..306F}),

### 2017-09-12 paper/ms.tex
minor edits per JMB comments

@@
 accretion regardless of Galactic chemical evolution.
-\askjmb{
-For example, \citealt{Fischer:2005aa} showed that higher metallicity
-stars more likely host close-in giant planets, which likely promotes
-the formation of giant planets by increasing the availability of small particle
-condensates that form planetesimals.
-}
-On the other hand, if host stars are polluted after their birth by rocky
-planetary material with high refractory-to-volatile ratio, the convective
-envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
-compared to their initial state (e.g., \citealt{Pinsonneault:2001aa}).
+Stars hosting giant planets on short period orbits have been shown, via
+population studies, to form more readily around inherently metal rich stars
+(\citealt{Fischer:2005aa,Santos2004}).
+However, the post-formation accretion of rocky planets can still alter the
+photospheric abundances.
+If host stars are polluted after their birth by rocky planetary material with a
+high refractory-to-volatile ratio, the convective envelope of the stars may be
+enhanced in refractory elements (e.g., \elem{Fe}) compared to their initial
+state (e.g., \citealt{Pinsonneault:2001aa}).
 Thus, differences in planet formation or accretion in two otherwise identical
@@
     $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
-    Thus, the narrower range of in $\Delta\feh$ is by construction.
+    Thus, the narrower range of $\Delta\feh$ is by construction.
     Random pairings of disk stars with similar $\Delta\feh$ usually show
@@
 
-{\bf
 The surface lithium abundance in a Sun-like star decreases with its age due to
@@
 burning.
+In hotter stars with thin convective zones on the main sequence, most of this
+mixing occurs in the pre-main sequence phase when the star is fully convective.
+% TODO: REF?
 Thus, surface lithium abundance can be an indicator of stellar ages,
@@
 planets or brown dwarfs which may replenish $\elem{Li}$.
-}
 
@@
 within the birth cloud is the source of the observed abundance difference.
-There is ample evidence against this scenario as most wide binaries show in
-\feh\ less than $0.02$~dex (\citealt{Desidera:2004aa,Gratton:2001aa}.
+There is ample evidence against this scenario as most wide binaries show a
+difference in \feh\ less than $0.02$~dex
+(\citealt{Desidera:2004aa,Gratton:2001aa}.
 In the cases in which a significant difference is detected
@@
 Because Li is present in either carbonaceous chondrites or bulk Earth with a
-concentration of $1-1.5$~ppm in mass (\citealt{2003TrGeo...2..547M}), but
-is depleted quickly within a few gigayears on the surface of a
-Sun-like star (\askjmb{CITE?}), accretion of either material at later times
-will significantly replenish the lithium on the star's surface.
+concentration of $1-1.5$~ppm in mass (\citealt{2003TrGeo...2..547M}), but is
+depleted quickly within the first Gyr on the surface of a Sun-like star
+(\citealt{Thevenin2017,Baraffe2017}), accretion of either material at later
+times will significantly replenish the lithium on the star's surface.
 For the present-day Sun ($A(\elem{Li}) = 1.05$), the accretion of \maccreted\ of
@@
 
-{\bf
-Finally, we mention that if the hypothesized accretion is
-\askjmb{recent (HOW RECENT?)},
-detection of $^6 \elem{Li}$ provides a strong test for this
-scenario.
+Finally, we mention that detection of $^6 \elem{Li}$ provides a strong test for
+this scenario.
 This isotope of \elem{Li} is destroyed at even lower temperatures than
@@
 presence of $^6\elem{Li}$ increases the asymmetry of \elem{Li} $6707.6$ feature.
-This is a very subtle effect that requires a careful modelling effort
-and a higher signal-to-noise, higher resolution spectra
+Depending on how recent the accretion was and how fast $^6 \elem{Li}$ is
+depleted on the main sequence, this feature may be detectable.
+This is a very subtle effect that requires a higher signal-to-noise, higher
+resolution spectra and careful modelling effort
 (see e.g., \citealt{Israelian:2001,2002MNRAS.335.1005R}).
 Such investigation was not warranted by the current data (\citealt{jmlithium}).
-}
 
@@
 search programs.
+We have begun a precision radial velocity campaign for the two stars and early
+indications are that there are no close in giant planets.
 If both stars have accreted planetary material, it would be very interesting to

### 2017-09-12 paper/ms.tex
final minor edits to abstract and intro

@@
   % TODO: Hmmm...
-  This is the largest and the most significant chemical difference found in
-  a wide binary pair yet.
+  This is the largest metallicity difference found in a wide binary pair yet.
   Additionally, HD~240430 shows an anomalously high surface lithium abundance
-  ($A(\elem{Li})=2.75$), higher by $0.5$~dex than its companion.
+  ($A(\elem{Li})=2.75$), higher than its companion by $0.5$~dex.
   The proximity in phase-space and ages between the two stars suggests that
@@
 accretion regardless of Galactic chemical evolution.
-Stars hosting giant planets on short period orbits have been shown, via
+Giant planets on short period orbits have been shown, via
 population studies, to form more readily around inherently metal rich stars
-(\citealt{Fischer:2005aa,Santos2004}).
+(e.g., \citealt{Fischer:2005aa,Santos2004}).
 However, the post-formation accretion of rocky planets can still alter the
@@
 with higher-\Tcondens\ elements showing larger differences.
-A possible explanation for the difference is that
-forming more gas giants or rocky planets leads to
-an overall or \Tcondens-dependent depletion of high-\Tcondens\ elements in
+A possible explanation for the difference is that forming more gas giants or
+rocky planets leads to an overall or \Tcondens-dependent depletion of metals in
 gas that eventually accretes onto the host star
@@
 also produce the trend by enhancing the abundance of high-\Tcondens\ elements
-in one of the two stars instead.
+in one of the two stars.
 The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
-and often closer to $\approx 0.05$~dex, making them challenging to detect even
+and often at a level of $\approx 0.05$~dex, making them challenging to detect even
 with a careful analysis of high-resolution, high signal-to-noise ratio spectra,
@@
 Because the gravitational settling times of elements heavier than \elem{He} in
-atmosphere is much shorter than the WD cooling time
+the WD atmosphere is much shorter than the WD cooling time
 (\citealt{1986ApJS...61..197P}), detection of metals likely indicates the
@@
 to prevent the prophecy that one day he will be overthrown by them.
-We use the following convention for chemical abundances of stars: \elemH{X} is
-the log ratio of number density of element \elem{X} to \elem{H} relative to the
-solar value.
-The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
-(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
-\elem{X}.
+We use the following convention for chemical abundances of stars:
+\elemH{X} is the log ratio of the number density of an element \elem{X} to \elem{H}
+relative to the solar value,
+$\elemH{X} = \log_{10} ((n_\elem{X}/n_\elem{H})/(n_{\elem{X},~\odot}/n_{\elem{H},~\odot}))$.
+The absolute abundance of an element \elem{X} is $A(\elem{X}) = 12 + \log_{10}
+(n_\elem{X}/n_\elem{H})$.
 In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data

### 2017-09-14 paper/ms.tex
final edits
- mostly grammar, minor wordings
- appendix finalized

@@
 \newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
-\newcommand*{\askjmb}[1]{{\bf #1}}
 
@@
   \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
-  % TODO: Hmmm...
   This is the largest metallicity difference found in a wide binary pair yet.
@@
 
-\sunanalog\ and \bizarreone\ were identified as a
-candidate comoving star pair in our recent search for comoving stars using the
-proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr.
+\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
+in our recent search for comoving stars using the proper motions and parallaxes
+from the Tycho-Gaia Astrometric Solution catalog (\tgas), a component of \gaia\
+\dr.
 We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
@@
 a brief description here.
-For a given pair, we compute a marginalized likelihood ratio between the
+For a given pair, we compute the marginalized likelihood ratio between the
 hypotheses (1) that a given pair of stars share the same 3D velocity vector,
@@
 for this sample was investigated in a separate work (\citealt{jmlithium}).
-We list all relevant astrometric and spectroscopic measurements
-including the absolute abundance\footnote{
-  The absolute abundance of element \elem{X} is
-  $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
-  where $n_\elem{X}$ is the number density of element \elem{X}.
-}
-of \elem{Li} for the two stars in Table~\ref{tab:kk}.
+We list all relevant astrometric and spectroscopic measurements including the
+absolute abundances of \elem{Li} for the two stars in Table~\ref{tab:kk}.
 
@@
 Although selected based only on their astrometry, the two stars
-have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
+have identical radial velocities within their uncertainties (Table~\ref{tab:kk}),
 confirming that they are truly comoving.
@@
 We start by generating posterior samples over the Heliocentric distance, $r$,
-tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
-given the observed parallax, $\hat\pi$, and proper motions,
-$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
-We assume the noise is Gaussian, and the radial velocity measurement is
+tangential velocities, $(v_{\alpha^*}, v_\delta)$, and radial velocity, $v_r$,
+given the observed parallax, $\hat\pi$, proper motions,
+$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$
+\footnote{$\alpha^*$ denotes the projection in right ascension direction,
+  i.e., $\mu_{\alpha^*} = \dot\alpha \cos\delta$.
+}.
+We assume the noise is Gaussian, and the radial velocity measurements are
 uncorrelated with the astrometric measurements.
@@
 The differences in velocities are consistent with zero.
-For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
+For a 2~\msun\ binary system, the Jacobi radius in the Solar neighborhood is
 1.2~pc (\citealt{Jiang:2010aa}).
@@
 However, one of the stars, \bizarreone\ is significantly more metal
-rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
+rich than the other by 0.2~dex ($\approx 60\%$; \figname~\ref{fig:abundances}).
 Moreover, not all elements are equally enhanced:
@@
 the ratio of data and model between the two stars show significant
-residuals of almost all metal line features, largely dominated by \elem{Fe}.
+residuals for almost all metal line features, largely dominated by \elem{Fe}.
 However, for lines of elements that are not as enhanced in \bizarreone\,
@@
 abundances of these two stars unconstrained by this procedure,
-the systematic uncertainties for these two solar-type ``twin-like'' stars
-with small differences in $T_\mathrm{eff}$ and $\log{g}$, if any, are unlikely to wash out
+the systematic uncertainties, if any, for these two solar-type ``twin-like'' stars
+with small differences in $T_\mathrm{eff}$ and $\log{g}$ are unlikely to wash out
 the observed abundance differences of $\approx 0.2$~dex.
@@
 mixing occurs in the pre-main sequence phase when the star is fully convective.
-% TODO: REF?
 Thus, surface lithium abundance can be an indicator of stellar ages,
@@
 they may have been part of a larger comoving group of stars.
-However, as we mention above, there is no evidence in our search of comoving
-pairs using \tgas\ that the two stars belong to a larger group of young stars.
+However, as we mention above (\sectionname~\ref{sec:data}), there is no
+evidence in our search of comoving pairs using \tgas\ that the two stars belong
+to a larger group of young stars.
 Very young stars often show signs of activity such as
@@
 The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
-young ages that would be inferred from the surface lithium abundances.
+young ages that would be inferred from the surface lithium abundance.
 Finally, we computed the Galactic orbit of the pair using the median of the
-posterior sample over the phase space coordinates of \sunanalog, in a Milky
+posterior sample over the phase-space coordinates of \sunanalog, in a Milky
 Way-like gravitational potential (similar to \texttt{MWPotential2014} from
@@
 While the data described above strongly suggests that the two stars are coeval,
-this subsection explores the possibility that this pair is not a primordial
-binary.
+this subsection explores the possibility that this pair is still not a
+primordial binary.
 Two stars unrelated at birth may end up in a binary system via a binary-single
@@
 \end{eqnarray}
-\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
+\eqname~\ref{eq:crosssection} is appropriate when $v_i/v_c \gg 1$
 (\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
 scattering with field (disk) stars.
-If we assume that field stars are made of solar mass stars with a constant
+If we assume that field stars are made of solar-mass stars with a constant
 number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
@@
 difference in \feh\ less than $0.02$~dex
-(\citealt{Desidera:2004aa,Gratton:2001aa}.
-In the cases in which a significant difference is detected
-with high-precision abundance measurements (see \sectionname~\ref{app:review}),
-the difference is typically $\sim 0.05$~dex.
-Consistent with these results,
-none of the other seven similar wide binaries examined in
-\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
-Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
-$\elem{O}$, and some pairs show a difference in particular elements as large as
-$\approx 0.15$~dex.
+(\citealt{Desidera:2004aa,Gratton:2001aa}).
+Even when a significant difference is detected with high-precision abundance
+measurements, the difference is typically $\sim 0.05$~dex (see
+\figname~\ref{fig:relabun_tcrank} and \sectionname~\ref{app:review}).
+Consistent with these results, none of the other seven similar wide binaries
+examined in \citealt{2016ApJS..225...32B} show such large differences in
+abundances though there is generally a larger spread in $\elem{C}$, $\elem{N}$
+and $\elem{O}$, and some pairs show a difference in particular elements as
+large as $\approx 0.15$~dex.
 The median and maximum \feh\ difference between component stars in the other
@@
 in the disk.
-%TODO: cautions on condensation temperature
-% 1. it is just a proxy
-% 2. it is **equlibrium** condensation temperature
 
@@
 The metallicity difference of $\approx 0.2$~dex observed in this pair
-is larger than the differences seen in any other pairs studied so far.
+is larger than the differences seen in any other pairs studied so far
+(see also Appendix~\ref{app:review}).
 The five under-enhanced elements in \bizarreone\
@@
 We consider that the comoving pair may have formed from two stars of different
-birth origins in a exchange scattering event
+birth origins in an exchange scattering event
 (\sectionname~\ref{sub:exchange_scattering}), or that there may be chemical
@@
 One possibility is that a fly-by interaction with a field star could have
-triggered eccentricity excitation of outer planets around each star, which may
+triggered eccentricity excitation of outer planets, which may
 have propagated inward through planet-planet scattering, leading to the
 accretion of inner rocky planets (\citealt{Zakamska:2004aa,Malmberg:2011aa}).
-If this is the case, there may be surviving, highly-eccentric giant planets.
-The two stars have not been included in any publicly released data from planet
-search programs, however, outer eccentric planets are potentially detectable
-with future data releases of the \gaia\ mission.
+If this is the case, there may be surviving, highly-eccentric giant planets
+potentially detectable with future data releases of the \gaia\ mission.
 
@@
 
-%TODO: Implications
-%- chemical tagging, frequency is of concern
-%- exoplaneteers looking for accretion signature: look for the most odd ones in
-%the expected direction not just in binaries already known to host a planet.
-
 \acknowledgements
-
 We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
@@
 \software{
+  %TODO: clean up by report
   %The data and code used in this project is available from
@@
   \texttt{numpy} (\citealt{Van-der-Walt:2011}),
-  and \texttt{pandas} (\citealt{pandas}).}
+  and \texttt{pandas} (\citealt{pandas}).
+}
 
@@
 abundances so far with high-resolution spectroscopy.
-These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
-WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
+These systems are
+  16 Cygni A/B,
+  HD~20782/HD~20781,
+  HD~80606/HD~80607,
+  XO-2N/XO-2S,
+  HAT-P-1,
+  WASP-94A/WASP94-B, and
+  HD~133131A/HD~133131B.
 We focus on key characteristics of stars and planets, and interpretations of
 any trend in $\Delta\elemH{X}$ with \Tcondens.
+Interested readers may also consult \citealt{2016arXiv161104064M}.
 
@@
 has been studied many times.
-The hotter star 16 Cyg A has no detected planets, but a M dwarf companion $\sim
-70$~AU away in projected separation which is probably physically associated
-(\citealt{2002ApJ...581..654P}), and may have affected planet formation process
-around the star (\citealt{1996ApJ...458..312J,2005MNRAS.363..641M}).
+The hotter star 16 Cyg A has no detected planets, but has an M dwarf companion
+$\sim 70$~AU away in projected separation which is probably physically
+associated (\citealt{2002ApJ...581..654P}), and may have affected planet
+formation process around the star
+(\citealt{1996ApJ...458..312J,2005MNRAS.363..641M}).
 The other star, 16 Cyg B, hosts a giant planet on an eccentric orbit ($e=0.63$,
@@
 While past measurements of metallicity and abundance difference between the two
-stars claimed conflicting results
+stars reported conflicting results
 (\citealt{2001ApJ...553..405L,2011ApJ...737L..32S}), recent studies using high
@@
 its interpretation.
+\citealt{2014ApJ...790L..25T} suggested that formation of $1.5-6$~\mearth\
+rocky core for the giant planet around 16 Cyg B can explain the offset and the
+positive correlation between $\Delta\elemH{X} (\mathrm{A}-\mathrm{B})$
+and \Tcondens. On the other hand, \citealt{2011ApJ...740...76R},
+who found no correlation, argued that forming giant planets
+results in an overall shift in all elements.
 
@@
 They suggest that this slope is evidence that the stars accreted
-$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
+$10-20$~\mearth\ of \elem{H}-depleted rocky material during giant planet
 migration.
@@
 common proper motion G5 stars with super-solar metallicity ($\feh \approx
-0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
+0.35$). HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
 HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).
@@
 {\bf XO-2N/XO-2S:}
-This pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
-has received much attention due to possibly the most robust and significant
-difference between the component stars.
+A few independent studies have investigated this pair of G9 stars with
+super-solar metallicity ($\feh \gtrsim 0.35$).
 XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
@@
 0.15$) orbits at $<0.5$~AU.
-%TODO: check following with Biazzo+
-All measured elements including \elem{Fe} are enhanced in XO-2N relative to
-XO-2S, and the difference shows a significant correlation with \Tcondens\
-(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
-\citealt{Teske:2013aa}).
-At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
-difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
-
-\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
-in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
+A significant difference of metallicity ($\gtrsim0.05$~dex) is detected between
+the two stars with a possible correlation with \Tcondens\
+(\citealt{Ramirez:2015aa,Biazzo:2015aa} although see also
+\citealt{Teske:2015aa,Teske:2013aa}).
+At low \Tcondens, the difference $(\mathrm{N}-\mathrm{S})$ in volatile elements
+differ by $\sim 0.01$~dex while the range of difference spans upto $0.1$~dex at
+$\Tcondens>1600$~K.
+
+\citealt{Ramirez:2015aa} suggested that the small overall depletion
+($\approx 0.015$~dex) of metals in
+XO-2S compared to XO-2N is plausibly due to the presence of more gas
 giant planets around XO-2S, following a similar interpretation of
 \citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
-In this scenario, forming planets in the protoplanetary disk are supposed to
-``lock'' heavier elements to the core of gas giant planets as well as some
-volatile elements in their envelthe metal content ($Z/X$) of gas giant planets and when the accretion
-of gas occurs in terms of how much mass is in the convective envelope of the
-host star, they can match the mass difference of gas giant planets around each
-star, which is at least $1~\mjupiter$.
-On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
-\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
-Earth and CM chondrite-like material can explain the trend either as refractory
-{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
-refractory enhancement in XO-2N by late time accretion in which case the
-opposite would be true.
+In this scenario, forming planets in the protoplanetary disk
+locks heavier elements to the core of gas giant planets.
+The positive correlation of $\Delta\elemH{X} (\mathrm{N}-\mathrm{S})$
+with \Tcondens\ requires a scenario involving rocky planets.
+Both forming more rocky planets in XO-2S and accreting more rocky planets to
+XO-2N at later stage were discussed (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
+The estimated mass of rocky material required to explain the observed trend
+is a few tens of $\mearth$.
 
 {\bf WASP-94A/B:}
-Each star in a pair of F8 and F9 stars with super-solar metallicity
+Each star in this pair of F8 and F9 stars with super-solar metallicity
 ($\feh\approx 0.3$) hosts a hot Jupiter.
@@
 elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
-elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
+elements ($\Tcondens>1200$~K) relative to WASP-94B, with a median
 uncertainty of $0.006$~dex among all elements
@@
 $\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
-  %TODO: double check the following statement
   Note that the condensation

### 2017-09-14 paper/submit.sh
add submit script

@@ -1,0 +1,30 @@
+#!/bin/bash
+set -e
+
+target_dir="submission"
+if [ -d "$target_dir" ]; then
+  echo "${target_dir} exists; do nothing"
+  exit 1;
+fi
+mkdir $target_dir
+
+list_of_figures=$(grep includegraphics ms.tex | sed 's/.*{\(.*\)}/figures\/\1/')
+echo "grabbing following figures\n";
+echo $list_of_figures;
+for figfile in $list_of_figures; do
+  cp $figfile $target_dir;
+done
+
+paperfiles=$(git ls-tree --name-only HEAD | grep -v ".gitignore\|Makefile\|figures|*.sh")
+for f in $paperfiles; do
+  echo "copying $f to $target_dir";
+  cp $f $target_dir;
+done
+
+echo "compress all files in $submission to $submission.tar.gz? [yn]"
+select yn in "y" "n"; do
+  case $yn in
+      Yes ) tar -czvf "$target_dir.tar.gz" $target_dir/*; break;;
+      No ) exit;;
+  esac
+done

### 2017-09-14 paper/submit.sh
cannot get prompting to work; remove

@@ -15,16 +15,11 @@ for figfile in $list_of_figures; do
   cp $figfile $target_dir;
 done
 
-paperfiles=$(git ls-tree --name-only HEAD | grep -v ".gitignore\|Makefile\|figures|*.sh")
+paperfiles=$(git ls-tree --name-only HEAD | grep -v ".gitignore\|Makefile\|figures\|*.sh")
 for f in $paperfiles; do
   echo "copying $f to $target_dir";
   cp $f $target_dir;
 done
 
-echo "compress all files in $submission to $submission.tar.gz? [yn]"
-select yn in "y" "n"; do
-  case $yn in
-      Yes ) tar -czvf "$target_dir.tar.gz" $target_dir/*; break;;
-      No ) exit;;
-  esac
-done
+echo "compress all files in $submission to $submission.tar.gz"
+tar -czvf "$target_dir.tar.gz" $target_dir/*;

### 2017-09-14 paper/submit.sh
bug

@@ -15,7 +15,7 @@ for figfile in $list_of_figures; do
   cp $figfile $target_dir;
 done
 
-paperfiles=$(git ls-tree --name-only HEAD | grep -v ".gitignore\|Makefile\|figures\|*.sh")
+paperfiles=$(git ls-tree --name-only HEAD | grep -v ".gitignore\|Makefile\|figures\|.*.sh")
 for f in $paperfiles; do
   echo "copying $f to $target_dir";
   cp $f $target_dir;

### 2017-09-14 paper/ms.tex
remove comment line

@@
 % packages
-\definecolor{cbblue}{HTML}{3182bd}
+\definecolor{cbblue}{HTML}{0D47A1}
 \usepackage{microtype}  % ALWAYS!
@@
   $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
-  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
   as inferred from \gaia\ \tgas\ parallaxes and proper motions, and

### 2017-09-15 paper/ms.tex
tweak caption

@@
   \caption{
-    Comparing the observed abundance difference (blue circles) to the expected
-    change in solar surface abundance after adding \maccreted\ of material
-    with bulk Earth composition (\citealt{2003TrGeo...2..547M}; black open and
-    filled circles).
+    Comparing the observed abundance difference ($\bizarreone-\sunanalog$; blue
+    circles) to the expected change in solar surface abundance after adding
+    \maccreted\ of material with bulk Earth composition
+    (\citealt{2003TrGeo...2..547M}; black open and filled circles).
     The assumed mass fraction in the convective zone is $0.02$.

### 2017-11-19 paper/report.tex
Add response stuff

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage[margin=1in]{geometry}

\usepackage{quoting}

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
  citecolor=blue,%
  filecolor=blue,%
  linkcolor=blue,%
  urlcolor=blue}

% Set font of quotation to something different.
\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\sf}

\usepackage{natbib}
\usepackage{aas_macros}
\bibliographystyle{aasjournal}

% \usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\setlength{\parskip}{0.5em}

\begin{document}

\section*{Response to the referee's report}
\label{response-to-the-referees-report}

We thank the referee for his/her report and suggestions. The referee's
concerns and suggestions are largely based on Andrews et al. 2017, which
we do not agree with in many aspects. We have fully addressed the
referee's concerns and discussed aspects of this work that are directly
relevant when necessary.

We think the referee may be confusing three different levels of concerns
and is lumping them together as ``random alignments''. These are that
this pair may not physically associated

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  because it may be an optical pair, two stars that only happen to be
  close on sky
\item
  because the two stars may be only moving in the same direction on sky
\item
  because the two stars with such proximity in full 6D phase-space
  coordinates are still possible from a chance pair of unassociated
  field single stars.
\end{enumerate}

The first two concerns are already answered in the paper:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  is addressed by that the two stars have nearly identical parallaxes
  meaning the two stars are physically close in position not just on
  sky.
\item
  is addressed by that the two stars have nearly identical radial
  velocities with 0.2 km/s precision meaning that the two stars have
  very similar 3D velocity vector not just proper motion.
\end{enumerate}

The last concern is not the ``random alignments'' that Andrews et al.
2017 sample suffers from at projected separation above 0.1 pc nor
something addressed in that work.

Nonetheless the last concern is valid, and we have addressed this using the Gaia
Universe Mock Simulation, a mock end-of-mission Gaia catalog with realistic a
Milky Way model \citep{gums}, and still find this unlikely. We have added a new
section in Discussion, and acknowledged that such skepticism may still exist in
Summary.

We answer each of {\sf the referee's comments} in detail below.

\begin{quote}
Oh et al. calculate the likelihoods both that a pair is an associated
binary, and that it is a random alignment (an optical pair). They use a
model for the stellar components of the galaxy, which necessarily
involves assumptions. Thus, their list of binaries likely contains a
good number of false pairs, especially among those of projected
separations larger than about 10,000 AU (Andrews et al. 2017).
\end{quote}

While this is not a point of main discussion here, we note that this
summary of our work that the referee cites from Andrews et al. 2017 is
incorrect. We consciously did not overextend to say that we calculate
the likelihood that a pair is ``an associated binary'', and referred to
the candidates we found as candidate comoving pairs throughout the paper.
Nor do we calculate the likelihood that it is a `random alignment'.

\begin{quote}
My major concern is that the authors fail to make a convincing case for
both stars of the studied pair being physically associated. In fact, the
different chemical compositions can be viewed as a strong argument
against their physical association. Both stars do have nearly identical
proper motions and radial velocities, as well as similar parallaxes.
However, the statistical argument presented for their physical
association is not convincing for this particular pair.
\end{quote}

We would like to point out again that the two stars have \emph{maximum a
posteriori} separation of 0.6 pc and \emph{3D} velocity difference
consistent with zero. If the referee is concerned that the two stars
merely happen to lie closely on sky (`optical pair'), this is already
answered by the observation that the parallaxes of the two stars are
nearly identical. If the referee is concerned that the two stars only
happened to have nearly identical proper motions but not actually same
velocities, this concern is already answered by the observation that
their radial velocities measured to 0.2 km/s precision are also
identical.

\begin{quote}
The authors state that the velocity differences are consistent with
zero, but never mention the position differences.
\end{quote}

We point out that both the 3D and projected separation are explicitly
mentioned in the abstract and in the beginning of paragraph 3 in the
Data section where we discuss the similarity in their velocities.

\begin{quote}
The graph they show has a very poor spatial resolution, and cannot be
used to establish physical nearness.
\end{quote}

We think that in fact the contrary is true: the graph shows in all 6
dimensions how uncertain the differences in positions and velocities
are, and how the uncertainties are correlated. The graph reflects to the
fullest the uncertainties in parallaxes and proper motions as well as
their covariances.

\begin{quote}
In fact, the observed parallax difference alone implies a separation (in
the line of sight direction) of 140,275 AU, more than an order of
magnitude larger than the projected separation of the pair (12,198 AU).
Taking into account the parallax errors would allow even larger
line-of-sight separations. So, a random alignment cannot be excluded.
\end{quote}

The pair indeed has a larger radial separation than the projected
separation given current data, but we are not sure why that should
raise the suspicion of ``random alignments'' given that the 3D
velocities of the stars are very similar. We note that a) the 0.6 pc
separation we mention throughout the paper is the maximum a posteriori
estimation of separation, which corresponds to the peak of the
maginalized $p(\Delta x)$, $p(\Delta y)$, $p(\Delta z)$, and b) the
parallax uncertainties are not biases that goes in one direction to
increase the separation but may also go in the other direction to
decrease it although we do not think that our results are not contingent
on this.
What is presented is the best astrometric data available yet, and the span of
this uncertainty is fully displayed in Figure 1.

\begin{quote}
As shown by Andrews et al. (2017), equal radial velocities are a
necessary but not sufficient condition for true binarity.
\end{quote}

Here, the referee's concern is shifting from that the pair might be an
optical pair or that only their proper motions are consistent to that it
is still insufficient that the two stars are close in 3D separation and
3D velocity.

We do not agree that Andrews et al. showed equal radial velocities are a
necessary but not sufficient condition of true binarity (or more
appropriately, physical association). The basis of their claim, or what
might have convinced the referee of this statement in their work is
two-fold.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The ``random pairs'' that they select by calculating \emph{the
  probability of being a true binary} from the TGAS matched with the
  catalog shifted by certain amount in declination and both components
  of proper motions sometimes do have identical velocities although they
  ought to be all ``random alignments'' (Figure 9.)
\item
  The contamination rate that they estimate by matching RVs is higher
  than that by these ``random pairs'': ``Secondly, a consistent RV does
  not guarantee binarity; even systems with RVs consistent at the
  $3\sigma$ level may, in fact, be random alignments with similar, but
  slightly different RVs'' (par 5 Sec 5.2 in Andrews et al. 2017)"
\end{enumerate}

We do not find any of the two a convincing argument for the statement
as it may as well be a sign that there are shortcomings in
either their calculation of probability that a given pair forms a `true
binary'/`random alignment' or in the way they estimate the contamination
rates.

Because we cannot resolve the Keplerian orbits of such wide-separation comoving
pairs (as we argue below), if the alternative explanation to the physical
association of the two stars is that two random single stars could have ended up
in such configuration, this {\it requires} an assumption about the structure of
single-star-only Milky Way. This is not addressed in Andrews et al. 2017.

\begin{quote}
The authors need to provide an estimate of the contamination fraction
allowed by the parallax and radial velocity differences. It would be
illustrative to estimate the contribution of orbital motion (Gaia is
sensitive enough) and projection effects (the declination is
sufficiently large) to the observed differences, and to take these into
account in estimating the probability of the two stars being an optical
pair.
\end{quote}

A ``detection'' of orbital motion with a single-epoch astrometry of two
stars is ill-defined to begin with.

The magnitude of (3D) orbital velocity of a equal-mass binary of solar-mass
stars for binary semi-major axis of 0.01 pc (projected separation of this pair)
is 0.93 km/s,
which is an upper limit to the actual magnitude as the data
indicates that the 3D separation is likely larger as have been pointed
out by the referee as well.
Even if the proper motion difference is entirely from the orbital motion, some
(unknown) inclination of the orbital plane with respect to the line-of-sight
will only decrease the observable orbital velocity on sky.
Figure 1 is exactly what should urge the referee to re-think the claim of
Andrews et al. 2017 that the orbital motion can be detected for binaries with
orbital period as large as 10\^{}6 yrs (a=).
We note that the astrometric data in the two studies is identical.

Still we have considered the referee's concern that two unassociated
single field stars may have ended up in this close configuration in
phase-space coordinates. Because the orbital motion of such
wide-separation comoving pairs are not detectable, whether this
proximity in 6D phase-space coordinates, which is a naturally expected
outcome of coeval group of stars like wide binaries, is a very rare
configuration to be found among unassociated field stars or not
\emph{inevitably requires} an assumption about the Galactic distribution
function of single stars.

We used the Gaia Universe Mock Simulation (GUMS) -- a mock
end-of-mission Gaia catalog with realistic Milky Way model \citep{gums}.

\begin{itemize}
\item Among 67795 primary stars with roughly solar-mass and solar-age ($0.9~M_\odot< M <
  1.1~M_\odot$, $3~\mathrm{Gyr}<\mathrm{Age} < 5~\mathrm{Gyr}$) within $r<300$~pc, we find 0
  pairings that results in $\Delta \mu_\alpha^* < 2$~mas/yr, $\Delta
  \mu_\delta<2$~mas/yar and $\Delta v_r < 1$~km/s.
\item TODO
\item TODO
\end{itemize}

%TODO We further emphasize that this is ...

Finally, we note that the projection effects are not soley dependent on the
declination as the referee (and Andrews et al.) seem to imply.
% detail maybe..

\begin{quote}
Without a convincing argument for both stars being physically associated
the discussion about chemical abundance differences becomes largely
irrelevant.
\end{quote}

Hopefully, we have addressed all three levels of the referee's concern.

%TODO: quote section verbatim

\begin{quote}
The (evolutionary) ages of both stars are also similar, but have a large
uncertainty. Their similarity is not a convincing argument for true
binarity.
In fact, the rotational velocities of both stars are very different,
which would argue for Kronos being younger than Krios. Although Li
abundances are a complicated matter, the surface Li abundance also
points to a younger age for Kronos. In summary, I cannot recommend
publication of the paper in its present form. I remain unconvinced about
the physical association of these stars. Perhaps the authors could
provide further arguments in favor of their true binarity (see eg.
Halbwachs 1986, Poveda et al. 2009), and thus make relevant the
interesting discussion about the abundance differences.
\end{quote}

%TODO

\section*{Minor concerns}\label{minor-concerns}

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The authors should be reminded that the IAU is the agency responsible
  for nomenclature of astronomical objects. They do refer to Kronos and
  Krios as ``nicknames'', but actually use them as names throughout the
  paper, as well as in the title. Using HD 240430/29 in the title makes
  the stars readily accessible in the astronomical databases, not so
  Kronos and Krios.
\end{enumerate}
\end{quote}

Thanks for reminding us but we will leave them as are. It is not our intention
to enforce the names in any way outside this publication. We refer to them as HD
identifiers in the abstract, introduction and summary as well as in keywords,
and we do no think the searchability of this work suffers.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Please define the entries in Table 1. Lower-case pi is often used for
  the radial galactocentric coordinate. Please include the separation
  (in arcsec) and the position angle.
\end{enumerate}
\end{quote}

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The pair is also listed in Halbwachs (1986)
\end{enumerate}
\end{quote}

We explicitly mention that despite the proximity 6D phase-space
coordinates, very similar spectral types and similar ages which are
extremely rare to arise by chance from two unassociated field stars (see
section X), the metallicity difference of 0.2 dex may seem uncomfortably
large to treat the two stars as coeval although an interesting,
plausible physical explanation of planet engulfment exists. However, we
think that what may seem as a rather exotic scenario at first is
actually the more simple and natural explanation than resorting to that
there happens to be two solar-type stars with such proximity in
phase-space coordinates, and one of them happens to display a unique
abundance pattern distinct from what is generally expected as well as
high Lithium for its age.

%
\bibliography{ref}

\end{document}

### 2017-11-20 paper/ms.tex
Modify according to comments

@@
 \begin{abstract}
-  We report and discuss the discovery of a comoving pair of bright solar-type
-  stars, HD~240430 and HD~240429, with a significant difference in their
-  chemical abundances.
+  We report and discuss the discovery of a significant difference in chemical
+  abundances of a comoving pair of bright solar-type
+  stars, HD~240430 and HD~240429.
   The two stars have an estimated 3D separation of $\approx 0.6$~pc
@@
   Additionally, HD~240430 shows an anomalously high surface lithium abundance
-  ($A(\elem{Li})=2.75$), higher than its companion by $0.5$~dex.
+  ($A(\elem{Li})=2.75$), higher than its cooler companion by $0.5$~dex.
   The proximity in phase-space and ages between the two stars suggests that
@@
 well above the adopted cut value of 6.
-The pair has also been previously recognized as a visual double star system
-in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
+While we independently identified this pair as described above,
+the pair has also been previously recognized as a common proper motion pair
+by \citealt{1986A&AS...66..131H} and listed as 
+a visual double star system
+in the Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
 We have checked that we do not find any possible additional comoving companions
@@
 
-% chance pair
-%Given that their metallicities and abundance patterns are significantly
-%different, one may simply conclude that the two stars are not related (coeval)
-%but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
-%by chance.
-%The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
-%at the stars' location, one may compute the probability that a star moving at
-%the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
-%...
+\subsection{Chance pair of unassociated single field stars?}
+\label{sub:chance_pair}
+
+Given that their metallicities and abundance patterns are significantly
+different, one may simply conclude that the two stars are not physically
+associated but they merely happen to be comoving at such a small separation
+($\approx 0.6$~pc) by chance.
+An estimate of this probability requires an assumption about the distribution
+function of single stars in the Milky Way.
+We used the Gaia Universe Mock Simulation (GUMS; \citealt{gums}), a mock
+\emph{end-of-mission} Gaia catalog with TODO model, and 
+looked for a chance pair of solar-mass ($0.9~M_\odot< M < 1.1~M_\odot$) primary
+stars ignoring any companions to the primary.
+Within 200~pc from the Sun, there are 7061 pairs
+with separation less than 2~pc among 119259 solar-mass primary stars.
+Of these pairs, we find zero with small enough differences in observed
+quantities such that
+$\Delta \mu_\alpha^* < 2$~mas\,yr$^{-1}$,
+$\Delta \mu_\delta<2$~mas\,yr$^{-1}$ and $\Delta v_r < 2$~km\,s$^{-1}$.
+These are still with generous difference budgets in both positions and
+velocities, and the actual observed differences are smaller
+(\tablename~\ref{tab:kk}).
+We find a single pair with velocity difference less than 2~km\,s$^{-1}$.
+Thus, while we cannot prove the binarity this pair by resolving its orbit,
+it seems more natural to assume that they are physically associated rather than
+a chance pair of unrelated single stars.
+This does not take into account the fact that one of the stars,
+\bizarreone, shows an unusual abundance difference pattern
+(\figname~\ref{fig:deltaXH}) and an unusually high \elem{Li} abundance,
+which would make the chance pair scenario even more unlikely.
 
@@
 We consider that the comoving pair may have formed from two stars of different
-birth origins in an exchange scattering event
+birth origins by chance (\sectionname~\ref{sub:chance_pair}) or in an exchange scattering event
 (\sectionname~\ref{sub:exchange_scattering}), or that there may be chemical
@@
 (\sectionname~\ref{sub:chemical_inhomogeneity_in_star_formation}) to find
-both unlikely.
+all unlikely.
 
@@
 potentially detectable with future data releases of the \gaia\ mission.
+
+% We explicitly mention that despite the proximity 6D phase-space
+% coordinates, very similar spectral types and similar ages which are
+% extremely rare to arise by chance from two unassociated field stars (see
+% section X), the metallicity difference of 0.2 dex may seem uncomfortably
+% large to treat the two stars as coeval although an interesting,
+% plausible physical explanation of planet engulfment exists. However, we
+% think that what may seem as a rather exotic scenario at first is
+% actually the more simple and natural explanation than resorting to that
+% there happens to be two solar-type stars with such proximity in
+% phase-space coordinates, and one of them happens to display a unique
+% abundance pattern distinct from what is generally expected as well as
+% high Lithium for its age.
 

### 2017-11-20 paper/report.tex
Add a remark
Modify according to comments

@@
   meaning the two stars are physically close in position not just on
-  sky.
+  sky. (e.g., section 3 in Poveda et al. 2009)
 \item
@@
 Andrews et al. 2017 that the orbital motion can be detected for binaries with
-orbital period as large as 10\^{}6 yrs (a=).
+orbital period as large as $10^6$ yrs (a=).
 We note that the astrometric data in the two studies is identical.
@@
 
-We used the Gaia Universe Mock Simulation (GUMS) -- a mock
+We used the Gaia Universe Mock Simulation (GUMS), a mock
 end-of-mission Gaia catalog with realistic Milky Way model \citep{gums}.
-
-\begin{itemize}
-\item Among 67795 primary stars with roughly solar-mass and solar-age ($0.9~M_\odot< M <
-  1.1~M_\odot$, $3~\mathrm{Gyr}<\mathrm{Age} < 5~\mathrm{Gyr}$) within $r<300$~pc, we find 0
-  pairings that results in $\Delta \mu_\alpha^* < 2$~mas/yr, $\Delta
-  \mu_\delta<2$~mas/yar and $\Delta v_r < 1$~km/s.
-\item TODO
-\item TODO
-\end{itemize}
-
-%TODO We further emphasize that this is ...
+Among 119259 solar-mass ($0.9~M_\odot< M < 1.1~M_\odot$) primary stars excluding
+any companions to the primary, we find zero with differences in observed
+quantities as small as this pair
+(separation $<2$~pc,
+$\Delta \mu_\alpha^* < 2$~mas\,yr$^{-1}$,
+$\Delta \mu_\delta<2$~mas\,yr$^{-1}$ and
+$\Delta v_r < 2$~km\,s$^{-1}$) still
+allowing a larger difference than actually observed.
+We find a single pair with velocity difference less than 2 km/s.
+We conclude that this is an unlikely possibility, and 
+have added a new section in Discussion (section 3.1).
 
@@
 
-Hopefully, we have addressed all three levels of the referee's concern.
+We hope to have addressed all three levels of the referee's concern.
 
-%TODO: quote section verbatim
+We note that this particular pair is listed in the catalog of Andrews et al.
+with ``true binary probability'' of 1.
 
@@
 The (evolutionary) ages of both stars are also similar, but have a large
-uncertainty. Their similarity is not a convincing argument for true
-binarity.
+uncertainty. Their similarity is not a convincing argument for true binarity.
 In fact, the rotational velocities of both stars are very different,
@@
 abundances are a complicated matter, the surface Li abundance also
-points to a younger age for Kronos. In summary, I cannot recommend
-publication of the paper in its present form. I remain unconvinced about
-the physical association of these stars. Perhaps the authors could
-provide further arguments in favor of their true binarity (see eg.
-Halbwachs 1986, Poveda et al. 2009), and thus make relevant the
-interesting discussion about the abundance differences.
+points to a younger age for Kronos. 
 \end{quote}
-
-%TODO
 
@@
 \end{quote}
-
 Thanks for reminding us but we will leave them as are. It is not our intention
@@
 identifiers in the abstract, introduction and summary as well as in keywords,
-and we do no think the searchability of this work suffers.
+and we do not think the searchability of this work suffers.
 
@@
 \end{quote}
+We have defined all quantities besides the abundances in the caption of Table 1.
 
@@
 \end{quote}
-
-We explicitly mention that despite the proximity 6D phase-space
-coordinates, very similar spectral types and similar ages which are
-extremely rare to arise by chance from two unassociated field stars (see
-section X), the metallicity difference of 0.2 dex may seem uncomfortably
-large to treat the two stars as coeval although an interesting,
-plausible physical explanation of planet engulfment exists. However, we
-think that what may seem as a rather exotic scenario at first is
-actually the more simple and natural explanation than resorting to that
-there happens to be two solar-type stars with such proximity in
-phase-space coordinates, and one of them happens to display a unique
-abundance pattern distinct from what is generally expected as well as
-high Lithium for its age.
+Noted in sec 2 par 1.
 

### 2017-11-21 paper/ms.tex
Tidy up for circulation

@@
 
+\subsection{Stellar Ages \& Coevality}
+\label{sub:ages}
+
+Apart from their closeness in phase-space coordinates,
+we can constrain the ages of the two stars
+given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$
+by comparing these values to theoretical isochrones.
+We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
+and $B-V$ colors to obtain bolometric luminosities of the two stars
+(\citealt{2003AJ....126..778V}).
+We then combine the luminosities with effective temperature, \elemH{Fe}, and
+\elemH{Si} in order to interpolate the age, mass, and radius of each star using
+a grid of Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
+The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
+$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
+consistent with them being coeval.
+
+The surface lithium abundance in a Sun-like star decreases with its age due to
+mixing induced by convection or rotation, which brings the lithium into the
+interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
+burning.
+In hotter stars with thin convective zones on the main sequence, most of this
+mixing occurs in the pre-main sequence phase when the star is fully convective.
+Thus, surface lithium abundance can be an indicator of stellar ages,
+especially whether the star is very young ($\lesssim 1$~Gyr).
+The absolute $\elem{Li}$ abundance of solar-type stars also correlates steeply
+with the effective temperature (e.g., \citealt{Chen2001,2012ApJ...756...46R}).
+Generally, cooler stars with larger convective envelope have lower \elem{Li}
+abundances.
+The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\
+is typical for its \teff.
+On the other hand, the lithium abundance ($A(\elem{Li}) = 2.75$) of \bizarreone,
+which has lower \teff\ than \sunanalog, is not only higher than that of
+\sunanalog\ but also much higher compared to other field stars of similar \teff.
+Given the overall higher metal abundances and the peculiar abundance patterns
+in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
+abundance means a younger age or something else.
+For example, \citealt{Casey:2016aa} attributes the presence of $\elem{Li}$-rich
+red giant stars to the engulfment of substellar companions such as gas giant
+planets or brown dwarfs which may replenish $\elem{Li}$.
+
+The surface lithium abundance of \bizarreone\ is the only indicator of a
+younger age.
+If the two stars were only several hundred Myrs old, then
+they may have been part of a larger comoving group of stars.
+However, as we mention above (\sectionname~\ref{sec:data}), there is no
+evidence in our search of comoving pairs using \tgas\ that the two stars belong
+to a larger group of young stars.
+Very young stars often show signs of activity such as
+X-ray emission from magnetic activity, emission lines, or infrared excess due to
+circumstellar disks (\citealt{1999ARA&A..37..363F,1987ApJ...312..788A}).
+We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
+and found no evidence for indications of activity in their spectral energy
+distributions.
+%
+The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
+young ages that would be inferred from the surface lithium abundance.
+Finally, we computed the Galactic orbit of the pair using the median of the
+posterior sample over the phase-space coordinates of \sunanalog, in a Milky
+Way-like gravitational potential (similar to \texttt{MWPotential2014} from
+\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
+The pair's fiducial orbit has a vertical action larger than the Sun, favoring
+an older age (\citealt{Wielen:1977,Aumer:2016}).
+We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
+old main sequence stars, and that the unusually high \elem{Li} abundance of
+\bizarreone\ requires an alternative explanation.
+
 \subsection{Chance pair of unassociated single field stars?}
@@
 
-\subsection{Stellar Ages \& Coevality}
-\label{sub:ages}
-
-Apart from their closeness in phase-space coordinates,
-we can constrain the ages of the two stars
-given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$
-by comparing these values to theoretical isochrones.
-We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
-and $B-V$ colors to obtain bolometric luminosities of the two stars
-(\citealt{2003AJ....126..778V}).
-We then combine the luminosities with effective temperature, \elemH{Fe}, and
-\elemH{Si} in order to interpolate the age, mass, and radius of each star using
-a grid of Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
-The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
-$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
-consistent with them being coeval.
-
-The surface lithium abundance in a Sun-like star decreases with its age due to
-mixing induced by convection or rotation, which brings the lithium into the
-interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
-burning.
-In hotter stars with thin convective zones on the main sequence, most of this
-mixing occurs in the pre-main sequence phase when the star is fully convective.
-Thus, surface lithium abundance can be an indicator of stellar ages,
-especially whether the star is very young ($\lesssim 1$~Gyr).
-The absolute $\elem{Li}$ abundance of solar-type stars also correlates steeply
-with the effective temperature (e.g., \citealt{Chen2001,2012ApJ...756...46R}).
-Generally, cooler stars with larger convective envelope have lower \elem{Li}
-abundances.
-The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\
-is typical for its \teff.
-On the other hand, the lithium abundance ($A(\elem{Li}) = 2.75$) of \bizarreone,
-which has lower \teff\ than \sunanalog, is not only higher than that of
-\sunanalog\ but also much higher compared to other field stars of similar \teff.
-Given the overall higher metal abundances and the peculiar abundance patterns
-in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
-abundance means a younger age or something else.
-For example, \citealt{Casey:2016aa} attributes the presence of $\elem{Li}$-rich
-red giant stars to the engulfment of substellar companions such as gas giant
-planets or brown dwarfs which may replenish $\elem{Li}$.
-
-The surface lithium abundance of \bizarreone\ is the only indicator of a
-younger age.
-If the two stars were only several hundred Myrs old, then
-they may have been part of a larger comoving group of stars.
-However, as we mention above (\sectionname~\ref{sec:data}), there is no
-evidence in our search of comoving pairs using \tgas\ that the two stars belong
-to a larger group of young stars.
-Very young stars often show signs of activity such as
-X-ray emission from magnetic activity, emission lines, or infrared excess due to
-circumstellar disks (\citealt{1999ARA&A..37..363F,1987ApJ...312..788A}).
-We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
-and found no evidence for indications of activity in their spectral energy
-distributions.
-%
-The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
-young ages that would be inferred from the surface lithium abundance.
-Finally, we computed the Galactic orbit of the pair using the median of the
-posterior sample over the phase-space coordinates of \sunanalog, in a Milky
-Way-like gravitational potential (similar to \texttt{MWPotential2014} from
-\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
-The pair's fiducial orbit has a vertical action larger than the Sun, favoring
-an older age (\citealt{Wielen:1977,Aumer:2016}).
-We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
-old main sequence stars, and that the unusually high \elem{Li} abundance of
-\bizarreone\ requires an alternative explanation.
-
 \subsection{Exchange Scattering}
@@
 
-While the data described above strongly suggests that the two stars are coeval,
-this subsection explores the possibility that this pair is still not a
-primordial binary.
-Two stars unrelated at birth may end up in a binary system via a binary-single
-scattering event that results in an exchange of binary members.
+Another possibility that two stars unrelated at birth may end up in a binary
+system is via a binary-single scattering event that results in an exchange of
+binary members.
 In order to estimate the rate at which any binary-single

### 2017-11-21 paper/response.tex
Rename from report.tex to response.tex

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage[margin=1in]{geometry}

\usepackage{quoting}

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
  citecolor=blue,%
  filecolor=blue,%
  linkcolor=blue,%
  urlcolor=blue}

% Set font of quotation to something different.
\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\sf}

\usepackage{natbib}
\usepackage{aas_macros}
\bibliographystyle{aasjournal}

% \usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\setlength{\parskip}{0.5em}

\begin{document}

\section*{Response to the referee's report}
\label{response-to-the-referees-report}

We thank the referee for his/her report and suggestions. The referee's
concerns and suggestions are largely based on Andrews et al. 2017, which
we do not agree with in many aspects. We have fully addressed the
referee's concerns and discussed aspects of this work that are directly
relevant when necessary.

We think the referee may be confusing three different levels of concerns
and is lumping them together as ``random alignments''. These are that
this pair may not physically associated

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  because it may be an optical pair, two stars that only happen to be
  close on sky
\item
  because the two stars may be only moving in the same direction on sky
\item
  because the two stars with such proximity in full 6D phase-space
  coordinates are still possible from a chance pair of unassociated
  field single stars.
\end{enumerate}

The first two concerns are already answered in the paper:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  is addressed by that the two stars have nearly identical parallaxes
  meaning the two stars are physically close in position not just on
  sky. (e.g., section 3 in Poveda et al. 2009)
\item
  is addressed by that the two stars have nearly identical radial
  velocities with 0.2 km/s precision meaning that the two stars have
  very similar 3D velocity vector not just proper motion.
\end{enumerate}

The last concern is not the ``random alignments'' that Andrews et al.
2017 sample suffers from at projected separation above 0.1 pc nor
something addressed in that work.

Nonetheless the last concern is valid, and we have addressed this using the Gaia
Universe Mock Simulation, a mock end-of-mission Gaia catalog with realistic a
Milky Way model \citep{gums}, and still find this unlikely. We have added a new
section in Discussion, and acknowledged that such skepticism may still exist in
Summary.

We answer each of {\sf the referee's comments} in detail below.

\begin{quote}
Oh et al. calculate the likelihoods both that a pair is an associated
binary, and that it is a random alignment (an optical pair). They use a
model for the stellar components of the galaxy, which necessarily
involves assumptions. Thus, their list of binaries likely contains a
good number of false pairs, especially among those of projected
separations larger than about 10,000 AU (Andrews et al. 2017).
\end{quote}

While this is not a point of main discussion here, we note that this
summary of our work that the referee cites from Andrews et al. 2017 is
incorrect. We consciously did not overextend to say that we calculate
the likelihood that a pair is ``an associated binary'', and referred to
the candidates we found as candidate comoving pairs throughout the paper.
Nor do we calculate the likelihood that it is a `random alignment'.

\begin{quote}
My major concern is that the authors fail to make a convincing case for
both stars of the studied pair being physically associated. In fact, the
different chemical compositions can be viewed as a strong argument
against their physical association. Both stars do have nearly identical
proper motions and radial velocities, as well as similar parallaxes.
However, the statistical argument presented for their physical
association is not convincing for this particular pair.
\end{quote}

We would like to point out again that the two stars have \emph{maximum a
posteriori} separation of 0.6 pc and \emph{3D} velocity difference
consistent with zero. If the referee is concerned that the two stars
merely happen to lie closely on sky (`optical pair'), this is already
answered by the observation that the parallaxes of the two stars are
nearly identical. If the referee is concerned that the two stars only
happened to have nearly identical proper motions but not actually same
velocities, this concern is already answered by the observation that
their radial velocities measured to 0.2 km/s precision are also
identical.

\begin{quote}
The authors state that the velocity differences are consistent with
zero, but never mention the position differences.
\end{quote}

We point out that both the 3D and projected separation are explicitly
mentioned in the abstract and in the beginning of paragraph 3 in the
Data section where we discuss the similarity in their velocities.

\begin{quote}
The graph they show has a very poor spatial resolution, and cannot be
used to establish physical nearness.
\end{quote}

We think that in fact the contrary is true: the graph shows in all 6
dimensions how uncertain the differences in positions and velocities
are, and how the uncertainties are correlated. The graph reflects to the
fullest the uncertainties in parallaxes and proper motions as well as
their covariances.

\begin{quote}
In fact, the observed parallax difference alone implies a separation (in
the line of sight direction) of 140,275 AU, more than an order of
magnitude larger than the projected separation of the pair (12,198 AU).
Taking into account the parallax errors would allow even larger
line-of-sight separations. So, a random alignment cannot be excluded.
\end{quote}

The pair indeed has a larger radial separation than the projected
separation given current data, but we are not sure why that should
raise the suspicion of ``random alignments'' given that the 3D
velocities of the stars are very similar. We note that a) the 0.6 pc
separation we mention throughout the paper is the maximum a posteriori
estimation of separation, which corresponds to the peak of the
maginalized $p(\Delta x)$, $p(\Delta y)$, $p(\Delta z)$, and b) the
parallax uncertainties are not biases that goes in one direction to
increase the separation but may also go in the other direction to
decrease it although we do not think that our results are not contingent
on this.
What is presented is the best astrometric data available yet, and the span of
this uncertainty is fully displayed in Figure 1.

\begin{quote}
As shown by Andrews et al. (2017), equal radial velocities are a
necessary but not sufficient condition for true binarity.
\end{quote}

Here, the referee's concern is shifting from that the pair might be an
optical pair or that only their proper motions are consistent to that it
is still insufficient that the two stars are close in 3D separation and
3D velocity.

We do not agree that Andrews et al. showed equal radial velocities are a
necessary but not sufficient condition of true binarity (or more
appropriately, physical association). The basis of their claim, or what
might have convinced the referee of this statement in their work is
two-fold.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The ``random pairs'' that they select by calculating \emph{the
  probability of being a true binary} from the TGAS matched with the
  catalog shifted by certain amount in declination and both components
  of proper motions sometimes do have identical velocities although they
  ought to be all ``random alignments'' (Figure 9.)
\item
  The contamination rate that they estimate by matching RVs is higher
  than that by these ``random pairs'': ``Secondly, a consistent RV does
  not guarantee binarity; even systems with RVs consistent at the
  $3\sigma$ level may, in fact, be random alignments with similar, but
  slightly different RVs'' (par 5 Sec 5.2 in Andrews et al. 2017)"
\end{enumerate}

We do not find any of the two a convincing argument for the statement
as it may as well be a sign that there are shortcomings in
either their calculation of probability that a given pair forms a `true
binary'/`random alignment' or in the way they estimate the contamination
rates.

Because we cannot resolve the Keplerian orbits of such wide-separation comoving
pairs (as we argue below), if the alternative explanation to the physical
association of the two stars is that two random single stars could have ended up
in such configuration, this {\it requires} an assumption about the structure of
single-star-only Milky Way. This is not addressed in Andrews et al. 2017.

\begin{quote}
The authors need to provide an estimate of the contamination fraction
allowed by the parallax and radial velocity differences. It would be
illustrative to estimate the contribution of orbital motion (Gaia is
sensitive enough) and projection effects (the declination is
sufficiently large) to the observed differences, and to take these into
account in estimating the probability of the two stars being an optical
pair.
\end{quote}

A ``detection'' of orbital motion with a single-epoch astrometry of two
stars is ill-defined to begin with.
The magnitude of (3D) orbital velocity of a equal-mass binary of solar-mass
stars for binary semi-major axis of 0.01 pc (projected separation of this pair)
is 0.93 km/s,
which is an upper limit to the actual magnitude as the data
indicates that the 3D separation is likely larger as have been pointed
out by the referee as well.
Even if the proper motion difference is entirely from the orbital motion, some
(unknown) inclination of the orbital plane with respect to the line-of-sight
will only decrease the observable orbital velocity on sky.
Figure 1 is exactly what should urge the referee to re-think the claim of
Andrews et al. 2017 that the orbital motion can be detected for binaries with
orbital period as large as $10^6$ yrs (a=).
We note that the astrometric data in the two studies is identical.

Still we have considered the referee's concern that two unassociated
single field stars may have ended up in this close configuration in
phase-space coordinates. Because the orbital motion of such
wide-separation comoving pairs are not detectable, whether this
proximity in 6D phase-space coordinates, which is a naturally expected
outcome of coeval group of stars like wide binaries, is a very rare
configuration to be found among unassociated field stars or not
\emph{inevitably requires} an assumption about the Galactic distribution
function of single stars.

We used the Gaia Universe Mock Simulation (GUMS), a mock
end-of-mission Gaia catalog with realistic Milky Way model \citep{gums}.
Among 119259 solar-mass ($0.9~M_\odot< M < 1.1~M_\odot$) primary stars excluding
any companions to the primary, we find zero with differences in observed
quantities as small as this pair
(separation $<2$~pc,
$\Delta \mu_\alpha^* < 2$~mas\,yr$^{-1}$,
$\Delta \mu_\delta<2$~mas\,yr$^{-1}$ and
$\Delta v_r < 2$~km\,s$^{-1}$) still
allowing a larger difference than actually observed.
We find a single pair with velocity difference less than 2 km/s.
We conclude that this is an unlikely possibility, and 
have added a new section in Discussion (section 3.2).

\begin{quote}
Without a convincing argument for both stars being physically associated
the discussion about chemical abundance differences becomes largely
irrelevant.
The (evolutionary) ages of both stars are also similar, but have a large
uncertainty. Their similarity is not a convincing argument for true binarity.
In fact, the rotational velocities of both stars are very different,
which would argue for Kronos being younger than Krios. Although Li
abundances are a complicated matter, the surface Li abundance also
points to a younger age for Kronos. 
In summary, I cannot recommend
publication of the paper in its present form. I remain unconvinced about
the physical association of these stars. Perhaps the authors could
provide further arguments in favor of their true binarity (see eg.
Halbwachs 1986, Poveda et al. 2009), and thus make relevant the
interesting discussion about the abundance differences.
\end{quote}

We hope to have addressed all three levels of the referee's concern that the two
stars are unrelated.
We would also like to note that while having a comoving companion to anchor the
abundance differences to makes this pair even more interesting, the abundance
pattern of Kronos is quite unusual for the median expectation of differences
from unrelated single stars as we discuss in the last paragraph of section 2,
section 3.3 and Figure 6.

We discuss the possibility that Kronos is a very young star from many
perspectives in the last paragraph of section 3.1 and why we think this is not
the case.
The difference in $v\sin(i)$ could be due to a difference in inclinations or 
in initial angular momentum at formation. Or Kronos, which has a higher value,
could have spun up because of the angular momentum of the engulfed material.

Finally, we note that this particular pair is listed in the catalog of Andrews et al.
with ``true binary probability'' of 1.

% ask jmb: I think he said that he difference in values themselves are not
% significant aside from sin(i) factor.
% Also could have spun up.

\section*{Minor concerns}\label{minor-concerns}

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The authors should be reminded that the IAU is the agency responsible
  for nomenclature of astronomical objects. They do refer to Kronos and
  Krios as ``nicknames'', but actually use them as names throughout the
  paper, as well as in the title. Using HD 240430/29 in the title makes
  the stars readily accessible in the astronomical databases, not so
  Kronos and Krios.
\end{enumerate}
\end{quote}
Thanks for reminding us but we will leave them as are. It is not our intention
to enforce the names in any way outside this publication. We refer to them as HD
identifiers in the abstract, introduction and summary as well as in keywords,
and we do not think the searchability of this work suffers.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Please define the entries in Table 1. Lower-case pi is often used for
  the radial galactocentric coordinate. Please include the separation
  (in arcsec) and the position angle.
\end{enumerate}
\end{quote}
We have defined all quantities besides the abundances in the caption of Table 1.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The pair is also listed in Halbwachs (1986)
\end{enumerate}
\end{quote}
Noted in sec 2 par 1.

\section*{Other changes}
\label{sec:other}

\begin{itemize}
\item Minor wording changes in the abstract.
\end{itemize}

%
\bibliography{ref}

\end{document}

### 2017-11-21 paper/ms.tex
Add reference for besancon model

@@
 \definecolor{cbblue}{HTML}{0D47A1}
+\usepackage[utf8]{inputenc}
 \usepackage{microtype}  % ALWAYS!
@@
 We used the Gaia Universe Mock Simulation (GUMS; \citealt{gums}), a mock
-\emph{end-of-mission} Gaia catalog with TODO model, and 
-looked for a chance pair of solar-mass ($0.9~M_\odot< M < 1.1~M_\odot$) primary
-stars ignoring any companions to the primary.
+\emph{end-of-mission} Gaia catalog with the Besançon Galaxy model
+(\citealt{besancon}), and looked for a chance pair of solar-mass
+($0.9~M_\odot< M < 1.1~M_\odot$) primary stars ignoring any companions to the primary.
 Within 200~pc from the Sun, there are 7061 pairs

### 2017-11-21 paper/response.tex
Tweak to focus on this paper only

@@
 will only decrease the observable orbital velocity on sky.
-Figure 1 is exactly what should urge the referee to re-think the claim of
-Andrews et al. 2017 that the orbital motion can be detected for binaries with
-orbital period as large as $10^6$ yrs (a=).
-We note that the astrometric data in the two studies is identical.
+Given the current data and its uncertainties, we do not find it meaningful to
+attribute a fraction of the differences in velocity to orbital motion.
 

### 2017-12-07 paper/response.tex
update

@@
 
-We thank the referee for his/her report and suggestions. The referee's
-concerns and suggestions are largely based on Andrews et al. 2017, which
-we do not agree with in many aspects. We have fully addressed the
-referee's concerns and discussed aspects of this work that are directly
-relevant when necessary.
+We thank the referee for his/her report and suggestions. 
+We have tried to address all of the referee's concerns.
 
-We think the referee may be confusing three different levels of concerns
-and is lumping them together as ``random alignments''. These are that
-this pair may not physically associated
+We think that there are three different levels of concerns
+in what the referee is referring to as ``random alignments''.
+These are that this pair may not physically associated
 
@@
   is addressed by that the two stars have nearly identical parallaxes
-  meaning the two stars are physically close in position not just on
+  meaning the two stars are physically close in position not just on the
   sky. (e.g., section 3 in Poveda et al. 2009)
@@
   velocities with 0.2 km/s precision meaning that the two stars have
-  very similar 3D velocity vector not just proper motion.
+  very similar 3D velocity vectors not just proper motion.
 \end{enumerate}
 
-The last concern is not the ``random alignments'' that Andrews et al.
-2017 sample suffers from at projected separation above 0.1 pc nor
-something addressed in that work.
-
-Nonetheless the last concern is valid, and we have addressed this using the Gaia
-Universe Mock Simulation, a mock end-of-mission Gaia catalog with realistic a
+We have addressed the third concern using the Gaia
+Universe Mock Simulation, a mock end-of-mission Gaia catalog with a realistic
 Milky Way model \citep{gums}, and still find this unlikely. We have added a new
 section in Discussion, and acknowledged that such skepticism may still exist in
-Summary.
+the Summary.
+
+We do not think the third concern above is ``random alignments'' that the
+Andrews et al. 2017 sample suffers from at projected separations above 0.1 pc
+nor something addressed in that work.
 
@@
 summary of our work that the referee cites from Andrews et al. 2017 is
-incorrect. We consciously did not overextend to say that we calculate
-the likelihood that a pair is ``an associated binary'', and referred to
-the candidates we found as candidate comoving pairs throughout the paper.
-Nor do we calculate the likelihood that it is a `random alignment'.
+incorrect. We do not have a model for an associated binary, and
+consciously referred to the candidates we found as candidate comoving pairs
+throughout the paper.
+Nor do we calculate the likelihood that a given pair is a random alignment.
 
@@
 
-We would like to point out again that the two stars have \emph{maximum a
-posteriori} separation of 0.6 pc and \emph{3D} velocity difference
+We would like to point out again that the two stars have maximum a
+posteriori separation of 0.6 pc and \emph{3D} velocity difference
 consistent with zero. If the referee is concerned that the two stars
@@
 
-We point out that both the 3D and projected separation are explicitly
-mentioned in the abstract and in the beginning of paragraph 3 in the
-Data section where we discuss the similarity in their velocities.
+The 3D and projected separation are explicitly mentioned in the abstract and in
+the beginning of paragraph 3 in the Data section where we discuss the similarity
+in their velocities.
 
@@
 The pair indeed has a larger radial separation than the projected
-separation given current data, but we are not sure why that should
-raise the suspicion of ``random alignments'' given that the 3D
+separation given the current data, but we are not sure why that should
+raise the suspicion of random alignments given that the 3D
 velocities of the stars are very similar. We note that a) the 0.6 pc
 separation we mention throughout the paper is the maximum a posteriori
-estimation of separation, which corresponds to the peak of the
+estimate of separation, which corresponds to the peak of the
 maginalized $p(\Delta x)$, $p(\Delta y)$, $p(\Delta z)$, and b) the
@@
 increase the separation but may also go in the other direction to
-decrease it although we do not think that our results are not contingent
+decrease it. We do not think that our results are not contingent
 on this.
@@
 necessary but not sufficient condition of true binarity (or more
-appropriately, physical association). The basis of their claim, or what
-might have convinced the referee of this statement in their work is
-two-fold.
+appropriately, physical association). The basis of their claim, as we
+understand, is two-fold.
 
@@
 \item
-  The ``random pairs'' that they select by calculating \emph{the
-  probability of being a true binary} from the TGAS matched with the
+  The ``random pairs'' that they select by calculating the
+  probability of being a true binary from the TGAS matched with the
   catalog shifted by certain amount in declination and both components
@@
 as it may as well be a sign that there are shortcomings in
-either their calculation of probability that a given pair forms a `true
-binary'/`random alignment' or in the way they estimate the contamination
+either their calculation of probability that a given pair forms a true
+binary/random alignment or in the way they estimate the contamination
 rates.
@@
 Because we cannot resolve the Keplerian orbits of such wide-separation comoving
-pairs (as we argue below), if the alternative explanation to the physical
-association of the two stars is that two random single stars could have ended up
-in such configuration, this {\it requires} an assumption about the structure of
-single-star-only Milky Way. This is not addressed in Andrews et al. 2017.
+pairs even if they are bound (as we argue below), if the alternative explanation
+to the physical association of the two stars is that two random single stars
+could have ended up in such configuration, we think that this \emph{requires} an
+assumption about the structure of single-star-only Milky Way. This is not
+addressed in Andrews et al. 2017.
 
@@
 
-A ``detection'' of orbital motion with a single-epoch astrometry of two
+We have considered the referee's concern that two unassociated
+single field stars may have ended up in this close configuration in
+phase-space coordinates. Because the orbital motion of such
+wide-separation comoving pairs are not detectable, whether this
+proximity in 6D phase-space coordinates, which is a naturally expected
+outcome of coeval group of stars like wide binaries, is a very rare
+configuration to be found among unassociated field stars or not
+requires an assumption about the Galactic distribution
+function of single stars.
+
+We used the Gaia Universe Mock Simulation (GUMS), a mock
+end-of-mission Gaia catalog with a realistic Milky Way model \citep{gums}.
+Among 119259 solar-mass ($0.9~M_\odot< M < 1.1~M_\odot$) primary stars excluding
+any companions to the primary, we find zero with differences in observed
+quantities as small as this pair
+(separation $<2$~pc,
+$\Delta \mu_\alpha^* < 2$~mas\,yr$^{-1}$,
+$\Delta \mu_\delta<2$~mas\,yr$^{-1}$ and
+$\Delta v_r < 2$~km\,s$^{-1}$) still
+allowing a larger difference than actually observed.
+We find a single pair with velocity difference less than 2 km/s.
+We conclude that this is unlikely, and 
+have added a new section in Discussion (section 3.2).
+
+A detection of orbital motion with a single-epoch astrometry of two
 stars is ill-defined to begin with.
@@
 attribute a fraction of the differences in velocity to orbital motion.
-
-Still we have considered the referee's concern that two unassociated
-single field stars may have ended up in this close configuration in
-phase-space coordinates. Because the orbital motion of such
-wide-separation comoving pairs are not detectable, whether this
-proximity in 6D phase-space coordinates, which is a naturally expected
-outcome of coeval group of stars like wide binaries, is a very rare
-configuration to be found among unassociated field stars or not
-\emph{inevitably requires} an assumption about the Galactic distribution
-function of single stars.
-
-We used the Gaia Universe Mock Simulation (GUMS), a mock
-end-of-mission Gaia catalog with realistic Milky Way model \citep{gums}.
-Among 119259 solar-mass ($0.9~M_\odot< M < 1.1~M_\odot$) primary stars excluding
-any companions to the primary, we find zero with differences in observed
-quantities as small as this pair
-(separation $<2$~pc,
-$\Delta \mu_\alpha^* < 2$~mas\,yr$^{-1}$,
-$\Delta \mu_\delta<2$~mas\,yr$^{-1}$ and
-$\Delta v_r < 2$~km\,s$^{-1}$) still
-allowing a larger difference than actually observed.
-We find a single pair with velocity difference less than 2 km/s.
-We conclude that this is an unlikely possibility, and 
-have added a new section in Discussion (section 3.2).
 
@@
 from unrelated single stars as we discuss in the last paragraph of section 2,
-section 3.3 and Figure 6.
+section 3.3 and Figure 6. Even in the case that the two unassociated stars
+happen to be very close in phase-space coordiantes (which we argued above is
+already unlikely), it seems even more unlikely that one of them will be
+this atypical and atypical in the direction expected from rocky planet accretion.
 
@@
 Finally, we note that this particular pair is listed in the catalog of Andrews et al.
-with ``true binary probability'' of 1.
-
-% ask jmb: I think he said that he difference in values themselves are not
-% significant aside from sin(i) factor.
-% Also could have spun up.
+with true binary probability of 1.
 
@@
 \end{quote}
-Noted in sec 2 par 1.
+A citation is added in sec 2 par 1.
 
@@
 \item Minor wording changes in the abstract.
+\item Updated Figure 5 with model fits from Myles et al. (in prep) including the
+  Lithium feature.
 \end{itemize}

### 2017-12-07 paper/ms.tex
update

@@
 
-We report and discuss the discovery of a comoving pair of bright
-solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
-metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
-(\Tcondens)-dependent abundance differences.
+We report and discuss very different metallicities ($\Delta\feh \approx
+0.2$~dex), and condensation temperature(\Tcondens)-dependent abundance
+differences in a comoving pair of bright 
+solar-type stars HD~240430 and HD~240429 (G0 and G2).
 The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
@@
 
-% We explicitly mention that despite the proximity 6D phase-space
-% coordinates, very similar spectral types and similar ages which are
-% extremely rare to arise by chance from two unassociated field stars (see
-% section X), the metallicity difference of 0.2 dex may seem uncomfortably
-% large to treat the two stars as coeval although an interesting,
-% plausible physical explanation of planet engulfment exists. However, we
-% think that what may seem as a rather exotic scenario at first is
-% actually the more simple and natural explanation than resorting to that
-% there happens to be two solar-type stars with such proximity in
-% phase-space coordinates, and one of them happens to display a unique
-% abundance pattern distinct from what is generally expected as well as
-% high Lithium for its age.
+Despite the arguments presented above for the two star's physical association
+based on phase-space coordinates and a physically interesting explanation for
+their metallicity and abundance differences, we can never completely rule out
+a very rare possibility that the two stars, in which one has
+an uncommon abundance pattern including high \elem{Li} abundance, are not coeval
+but happen to be so close in phase-space coordinates.
+Indeed, we do not resolve the orbital motions of the system, and cannot know
+whether they are gravitationally bound or, possibly, they have recently been
+disrupted.
+Such skepticism may be based on or amplified the large metalicity
+differences.
+Yet, another recent study has reported a comoving pair of solar-type stars
+in which one shows similarly disparate metallicity ($\Delta\feh
+\approx 0.1$~dex) and \Tcondens-dependent abundance patterns as well as higher
+\elem{Li}, leading to a similar conclusion (\citealt{2017A&A...604L...4S}).
+From the possibilities that we have considered, we think that, in fact, the
+seemingly exotic explanation of rocky planet engulfment is the simpler and more
+natural scenario for all of the observed properties of the two stars.
 

### 2017-12-07 paper/response.tex
Remove par break
Fix grammar

@@
 We have tried to address all of the referee's concerns.
-
 We think that there are three different levels of concerns
@@
   because it may be an optical pair, two stars that only happen to be
-  close on sky
+  close on the sky
 \item
@@
   is addressed by that the two stars have nearly identical parallaxes
-  meaning the two stars are physically close in position not just on the
+  meaning the two stars are physically close in positions not just on the
   sky. (e.g., section 3 in Poveda et al. 2009)
@@
   velocities with 0.2 km/s precision meaning that the two stars have
-  very similar 3D velocity vectors not just proper motion.
+  very similar 3D velocity vectors, not just proper motion.
 \end{enumerate}
@@
 Milky Way model \citep{gums}, and still find this unlikely. We have added a new
-section in Discussion, and acknowledged that such skepticism may still exist in
+section in Discussion and acknowledged that such skepticism may still exist in
 the Summary.
@@
 
-While this is not a point of main discussion here, we note that this
+While this is not a point of the main discussion here, we note that this
 summary of our work that the referee cites from Andrews et al. 2017 is
-incorrect. We do not have a model for an associated binary, and
+incorrect. We do not have a model for an associated binary and
 consciously referred to the candidates we found as candidate comoving pairs
@@
 consistent with zero. If the referee is concerned that the two stars
-merely happen to lie closely on sky (`optical pair'), this is already
+merely happen to lie closely on the sky (`optical pair'), this is already
 answered by the observation that the parallaxes of the two stars are
@@
 
-We think that in fact the contrary is true: the graph shows in all 6
+We think that in fact, the contrary is true: the graph shows in all 6
 dimensions how uncertain the differences in positions and velocities
@@
 estimate of separation, which corresponds to the peak of the
-maginalized $p(\Delta x)$, $p(\Delta y)$, $p(\Delta z)$, and b) the
-parallax uncertainties are not biases that goes in one direction to
+marginalized $p(\Delta x)$, $p(\Delta y)$, $p(\Delta z)$, and b) the
+parallax uncertainties are not biases that go in one direction to
 increase the separation but may also go in the other direction to
@@
   probability of being a true binary from the TGAS matched with the
-  catalog shifted by certain amount in declination and both components
+  catalog shifted by a certain amount in declination and both components
   of proper motions sometimes do have identical velocities although they
@@
 as it may as well be a sign that there are shortcomings in
-either their calculation of probability that a given pair forms a true
+either their calculation of the probability that a given pair forms a true
 binary/random alignment or in the way they estimate the contamination
@@
 Because we cannot resolve the Keplerian orbits of such wide-separation comoving
-pairs even if they are bound (as we argue below), if the alternative explanation
+pairs even if they are bound (as we argue below) if the alternative explanation
 to the physical association of the two stars is that two random single stars
@@
 We have considered the referee's concern that two unassociated
-single field stars may have ended up in this close configuration in
+single field stars may have ended up in this configuration in
 phase-space coordinates. Because the orbital motion of such
@@
 proximity in 6D phase-space coordinates, which is a naturally expected
-outcome of coeval group of stars like wide binaries, is a very rare
+outcome of a coeval group of stars like wide binaries, is a very rare
 configuration to be found among unassociated field stars or not
@@
 stars is ill-defined to begin with.
-The magnitude of (3D) orbital velocity of a equal-mass binary of solar-mass
+The magnitude of (3D) orbital velocity of an equal-mass binary of solar-mass
 stars for binary semi-major axis of 0.01 pc (projected separation of this pair)
@@
 section 3.3 and Figure 6. Even in the case that the two unassociated stars
-happen to be very close in phase-space coordiantes (which we argued above is
+happen to be very close in phase-space coordinates (which we argued above is
 already unlikely), it seems even more unlikely that one of them will be
@@
 Finally, we note that this particular pair is listed in the catalog of Andrews et al.
-with true binary probability of 1.
+with the true binary probability of 1.
 

### 2017-12-11 paper/response.tex
Clean up stuff

@@
 
+In order to explicitly acknowledge the skepticism,
+we added the following paragraph in the Summary:
+
+``Despite the arguments presented above for the two star's physical association
+based on phase-space coordinates and a physically interesting explanation for
+their metallicity and abundance differences, we can never completely rule out
+a very rare possibility that the two stars, in which one has
+an uncommon abundance pattern including high Li abundance, are not coeval
+but happen to be so close in phase-space coordinates.
+Indeed, we do not resolve the orbital motions of the system, and cannot know
+whether they are gravitationally bound or, possibly, they have recently been
+disrupted.
+Such skepticism may be based on or amplified the large metalicity
+differences.
+Yet, another recent study has reported a comoving pair of solar-type stars
+in which one shows similarly disparate metallicity ($\Delta[\mathrm{Fe}/\mathrm{H}]
+\approx 0.1$~dex) and $T_C$-dependent abundance patterns as well as higher
+Li, leading to a similar conclusion \citep{2017A&A...604L...4S}.
+From the possibilities that we have considered, we think that, in fact, the
+seemingly exotic explanation of rocky planet engulfment is the simpler and more
+natural scenario for all of the observed properties of the two stars.''
+
 Finally, we note that this particular pair is listed in the catalog of Andrews et al.
-with the true binary probability of 1.
+with the \emph{true binary probability} of 1.
 

### 2017-12-11 paper/ms.tex
Update caption
Clean up stuff

@@
 \usepackage[flushleft]{threeparttable}
-\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=gray}
+\hypersetup{
+  backref,
+  breaklinks,
+  colorlinks,
+  urlcolor=cbblue,
+  linkcolor=cbblue,
+  citecolor=black}
 \graphicspath{{figures/}}
@@
   \caption{Lithium lines in the spectra of \bizarreone\ and \sunanalog.
-    This line is studied in Myles \etal\ (in prep.).
+    This line is studied in Myles \etal\ (in prep.), and the fitting shown here
+    is from that work.
     Line legends are the same as in \figname~\ref{fig:spec1}.
@@
 
-%TODO: data/code available
 \software{
-  %TODO: clean up by report
-  %The data and code used in this project is available from
-  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
-  %software license.
   This research utilized:
